### 2021-08-20 appendix/appendix.Rmd
structure

---
title: |
       | Supplementary Materials for "Legislature Size and Welfare: Evidence from Brazil"
author:
  - Gabriel Cepaluni[^gabriel]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.

[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.

\appendix
\addtocounter{section}{2}

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r, include=FALSE}
## Starting
#XXXX

# Required packages
#XXXX

# Load datasets
#XXXX
```

\newpage

## A Model of Legislature Size and Service Provision

### Primitives of the Model

Consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors, indexed in $i \in \{1, 2, \cdots, N \}$. The mayor is the head of the local executive branch, and has the prerogative of proposing a vector of policies, that is voted by the city councilors. Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors \textbf{x}.

The city council votes the mayor's proposal and if they accept it, it is implemented. Otherwise, a reversal policy takes place. Reversal policy in this context means that the mayor's proposal failed to secure majority of council votes. The decision process leaves the mayor's office, and either immediately stops or it is transferred to the council. The types of reversal policies are crucial for our argument, as it changes the relative strength of the council in their bargaining with the mayor. We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan affiliation; a \textit{partisan} reversal mechanism, where the council is divided in supporters and non-supporters of the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan with non-partisan features. In the main paper, we focus on the hybrid model, as it is the more realistic scenario. Despite that, comparing the partisan and non-partisan reversal mechanisms illustrate clearly our argument that the partisan a mechanism is what drives our results.

To govern, the mayor has to convince at least half of the city councilors to support her policy proposals. Similar to \citet{buenodemesquita2005logic}, we assume that the selectorate, i.e. the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors. The winning coalition, which is the minimum number of members that have to be convinced to implement the policy, is equal to half of the selectorate $N/2$. City councilors are moved by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}. We leave the definition of these transfers open, as this facilitates the relation with several instruments that mayors can use to pressure city councilors. To illustrate, examples of transfers are granting electoral favors, spending in areas that the councilor has political or personal interests, granting portfolio and public jobs within the municipal bureaucracy, or even campaign contributions and bribes. The use of transfers to affect the councilors' choices and generate a governing cost of $C_G$. The governing costs vary with the reversal mechanism and the legislature size.

Finally, after paying the costs of govern, the mayor proposes a level of public goods provision ($g$) and rents ($r$). Public goods provision help the mayor to get reelected. Rents are for direct mayor's consumption, and does not contribute to the mayor's electoral success. This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection. Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.\footnote{In technical terms, $u'>0$ and $\pi'>0$; and $u''<0$ and $\pi''<0$.} The probability of reelection is multiplied by the benefit from holding office $B_M > 0$. This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office. We assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to say that mayors have a strong preference to be reelected. If the mayor's policy proposal is approved, then the expected utility for the mayor is:

\[
\mathbb{E}U(r, g) \ = \ u(r) + B_M\pi(g)
\]

The policy choices of the mayor are subject to the municipal budget constraint. The municipality has $R > 0$ resources, and cannot run debts, meaning that the budget has to be balanced. We also assume that there are enough resources for the mayor to govern.

Let $C_G$ be the costs of govern. The budget balance constraint requires the offers that the mayor makes to the city councilors satisfy the following inequality:

\[
r + g + C_G \ \leq \ R
\]

The expected utility for the city councilors depend on the reversal policy. As discussed, we explore three different mechanisms. First, in \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminish by a factor of $\delta \in (0,1)$ and the selection of one councilor randomly. The randomly selected councilor becomes the new proposer. If her proposal is accepted, it is implemented. If it is rejected, the budget shrinks again by a factor $\delta$, and another city councilor is recognized to make the proposal. The process repeats, until one proposal is finally accepted.

In the second reversal mode, the \textit{partisan} reversal mechanism, we assume that each councilor has a party affiliation. Party affiliations are mutually exclusive (a councilor cannot belong to two parties at once). If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$. Otherwise, the city councilor belongs to the opposition $O  = \{1, 2, \cdots, N \} \setminus G$. The mayor's policy generate a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends of the party affiliation of the councilor. If the mayor's proposal is rejected, a city councilor aligned with the mayor, that would receive $p$ from the policy, now receives zero. On the other hand, a city councilor that belongs to the opposition would receive $-p$ from the mayor's policy, and now receives zero. Although these assumptions are strong, they capture the underlying political dynamics of partisanship: the political preferences in terms of public goods provision are shared by councilors aligned with the mayor. Voting against the mayor's proposals would represent to defy the partisan label.

Lastly, in the \textit{hybrid} reversal mechanism, we combine partisanship with legislature bargaining costs. Councilors in this mechanism receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the non-partisan reversal mechanism takes place. In the mayor's proposal stage, city councilors that belong to the mayor's coalition receive a gain of $p > 0$ when the mayor's policy is implemented. Opposition members, on the other hand, receive $-p$ when the mayor's proposal is implemented. If the mayor's proposal is rejected, as the city council does not control the Executive when the two branches are separated, no public goods are provided ($p=0$). Moreover, in equilibrium, we assume that city councilors would prefer to receive transfers instead of providing public goods. This aligns with the empirical evidence in most developing economies.

The timeline of the game is as follows:

\begin{enumerate}
  \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
  \item The mayor proposes a policy vector $(r, g, x)_M$.
  \item The city council votes the proposal.
  \begin{itemize}
    \item If the council accepts, the policy is implemented and the game ends. 
    \item Otherwise, the reversal policy is implemented.
  \end{itemize}
  \item (Reversal Policy) Depends on which mechanism, we have three different reversal policies. The details are in the following sections.
\end{enumerate}

The solution concept we use in this model is the Sub-game Perfect Nash Equilibrium. A Sub-game Perfect Nash Equilibrium requires that the strategies played are a Nash Equilibrium in each of the subgames of the game. The solution is found using backward induction. In the model with infinitely repeated proposals, we extend the equilibrium concept to require that the equilibrium is Stationary. A Stationary Sub-game Perfect Equilibrium requires that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should accept the same offer at time $k$. Stationarity gives us an objective of finding an offer that would be accepted at any stage in the game. Applying this reasoning, we can find a sequence of offers for each point $k$ in time. For the mayor, the optimal offer is at $k=0$, and this represents a no delay in policy implementation.

\begin{definition}
The equilibrium for the game consists in a sequence of strategic policy vectors $(g^*, r^*, x^*)_k$, indexed in $k \in \{0, 1, \cdots, \infty\}$, such that, at every stage of the game, the mayor and the councilors have no profitable deviations from the equilibrium.
\end{definition}

Moreover, we assume that the players play no dominated strategies, even when there is less than sufficient support for implementing the policy.

### The Mayor's Decision Stage

Solving the game by backward induction requires us to start with the councilor's strategies. However, for exposure convenience, assume at this point that we solved the the game for the councilors, and found the equilibrium cost of govern $C_G(N)$ when there are $N$ city councilors. In the next section, we define $C_G(N)$ for each of the mechanisms using backward induction, and the definitions are well-behaved. In this section, we use this assumption to simplify the exposition.

We now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor. The mayor benefits from public goods provision, as it increases the chances of her reelection. However, she prefers to contribute as minimum as necessary for the public goods, and extract the remaining resources as political rents. The mayor's objective is to maximize her expected utility, subject to the municipal budget constraint.

\[
\begin{aligned}
\max_{r, g} \quad & u(r) + B_M\pi(g)\\
\textrm{s.t.} \quad & r + g + C_G(N) \leq R
\end{aligned}
\]

In equilibrium the budget binds, and the public goods provision maximizes:

\[
\max_{g} \{ u(R - g - C_G(N)) + B_M\pi(g) \}
\]

The first order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equals to the marginal benefits of reelection:

\[
u'(R - g - C_G(N)) = B_M\pi'(g)
\]

This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_G(N)) + B_M\pi''(g^*) < 0$.

\begin{proposition}
The provision of public goods increase with legislature size when the costs of govern decrease with legislature size.
\end{proposition}

\begin{proof}
To prove this result we need to show that the mayor's expected utility satisfy the increasing differences in $g$ and $N$. This would mean that when increasing the size of the council, the optimal solution $g^*$ would also increase. However, as $N$ increases discretely, we cannot take a the cross-partial derivative on $N$ or even use the implicit function theorem. Instead, we use monotone comparative statics to derive these results \citep{milgrom1994monotone}.

The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$,\footnote{Moreover, the requirement that the decision and type space is a complete lattice, is satisfied for $\mathbb{R} \times \mathbb{N}$.} we have:

\[
\mathbb{E}\text{U}(g, N+1) - \mathbb{E}\text{U}(g', N+1) \geq \mathbb{E}\text{U}(g, N) - \mathbb{E}\text{U}(g', N)
\]

After substituting, we have:

\[
u(R - g - C_G(N+1)) + B_M\pi(g) - u(R - g' - C_G(N+1)) - B_M\pi(g') \geq 
u(R - g - C_G(N)) + B_M\pi(g) - u(R - g' - C_G(N)) - B_M\pi(g')
\]

Which is equal to:

\[
u(R - g - C_G(N+1)) - u(R - g' - C_G(N+1)) \geq 
u(R - g - C_G(N)) - u(R - g' - C_G(N))
\]

Multiplying both sides by $\dfrac{1}{g - g'}$ and taking the limit when $g \rightarrow g'$, we have:

\[
u'(R - g - C_G(N+1)) \geq 
u'(R - g - C_G(N))
\]

It is now clear to see that the function satisfies the increasing differences in $g$ and $N$ when the governing costs of a $N+1$-sized city council is lower than the governing costs of a $N$-sized city council:

\[
C_G(N+1) \leq C_G(N)
\]

\end{proof}

This provides us our first empirical hypothesis to test: \textit{if the governing costs decrease when the legislature increases, then the public goods provision increase when the legislature size increase}.

At this stage, we need to solve for existence of these governing costs. Below we show that this proposition is true for the *partisan* and *hybrid* mechanisms, but it is not true for the *non-partisan* mechanism.

### Non-Partisan Reversal Mechanism

In the \textit{non-partisan reversal} mechanism, we assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly. To find the stationary sub-game perfect Nash equilibrium, suppose that there were $k-1$ rejections, and we are at the $k$-th stage in the game. A councilor accepts the proposer's offer if, and only if, to accept the offer at $k$ is better than to wait until the next stage $k+1$. If the offer is $x_i$, then:

\[
x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left( 1 - \dfrac{1}{N} \right)\left[\dfrac{1}{2} x_i \right]
\]

In the left-hand side, we place the offer. In the right-hand side, there are two components. The first is the amount that the councilor $i$ gets when she is the proposer. It is equal to the chance that she is recognized as the proposer times the budget in the next round minus the offers that she has to make to convince half of the councilors. The second part is the gains if when the councilor happens to reject the current received offer, but still receives an offer in the following round. It is equal to the chance that she is not recognized as the proposer times the chance that she receives a transfer times the amount of the transfer. Note that the offer the councilor makes as the proposer is the same as the offer that she wants to receive. This because the city councilors are exchangeable, and the solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, we could have dropped the $i$ in the solution). After some algebra, the offer $x_i$ has to be greater than or equal to:

\[
x_i \geq \dfrac{2 \delta^{k+1}R}{2N + 1} \equiv \underline{x}(k, N)
\]

The proposer always offer the minimum required to get the proposal approved. In the case, the offer at any given stage $k$ is going to be equal to $\underline{x}(k, N)$.

Proceeding backwards, at the mayor's proposal stage $k=0$ and the mayor is going to offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors. In this context, the governing costs for the mayor are:

\[
C_G(N) \ = \ \dfrac{N}{2}\left[\dfrac{2 \delta R }{2N + 1}\right] \ = \ \dfrac{\delta R N}{2N + 1}
\]

\begin{proposition}
In the \textit{non-partisan reversal} mechanism, the governing costs always increase when the size of the legislature increases.
\end{proposition}

\begin{proof}

The difference in costs when there are $N+1$ city councilors versus when there are $N$ city councilors is equal to:

\[
\begin{aligned}
C_G(N+1) - C_G(N) \ = \ & \dfrac{(N+1)\delta R}{2(N+1) + 1} - \dfrac{N \delta R}{2N + 1}\\
 = \ & \dfrac{\delta R}{(2N+3)(2N+1)}  \\
> \ &0
\end{aligned}
\]

Therefore, the costs always increase when the size of the legislature increases.

\end{proof}

\begin{corollary}
In the \textit{non-partisan reversal} mechanism, public goods provision decreases as the legislature size increases.
\end{corollary}

This result is crucial to understand the role of the politics in our model. If the costs of govern increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism. In our case, we show that there is a \textit{political} reason for increasing the public goods provision.

### Partisan Reversal Mechanism

We now look into the other extreme, which is a fully politicized legislature. In this case, when the mayor implements the policy, it generates a value of $p > 0$. A legislator aligned with the mayor receives a benefit $p$ while an opposition legislator receives a cost of $-p$. Moreover, as in the case of the non-partisan reversal, the mayor can choose to distribute $x_i$ private goods for a legislator $i$. In this case, when the policy is implemented, the utility of an aligned legislator is equals to $x_i + p$. When the legislator is not aligned with the mayor, her utility is equals to $x_i - p$. If the policy is not implemented, then we assume a reversal policy of zero in all choice vectors $g = x_i = p = 0$.

A legislator aligned with the mayor always support the mayor's policy, regardless of receiving or not private goods. This because as $p > 0$, the councilor always receive positive benefits from the policy.\footnote{The mayor could even impose a cost to the city councilors aligned with the government. Although this seem unrealistic, it is mostly the case when government-aligned legislators are recognized to draft legislation for the mayor's office, or even take the popular fallout from a failed policy.} However, politicians not aligned with the mayor require a compensation when their votes are needed. In this case, if the mayor's proposal requires the support of an opposition politician, then the mayor compensates the councilor for the policy costs. In such case:

\[
x_i \geq p
\]

Optimality dictates that the mayor offers $x_i = p$ to the opposition legislator. Let $\gamma$ be the ex-ante probability of electing a politician aligned with the mayor. Then, the costs of govern when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor has to compensate minus the amount needed to implement the policy, in this case, half of them:

\[
C_G(N) \ = \ p\left(\dfrac{N}{2} - \gamma N\right)
\]

\begin{proposition}
In the \textit{partisan reversal} mechanism, if the chance of electing a mayor-aligned politician is greater than one-half, then the costs of govern decrease as the legislature size increases.
\end{proposition}

\begin{proof}

The differences in costs when there are $N+1$ versus when there are $N$ legislators are equal to:

\[
\begin{aligned}
C_G(N+1) - C_G(N) \ = \ & p\left(\dfrac{N+1}{2} - \gamma (N+1)\right) - p\left(\dfrac{N}{2} - \gamma N\right) \\
 = \ & p\left( \dfrac{1}{2} - \gamma  \right)
\end{aligned}
\]

Therefore, when $\gamma < \dfrac{1}{2}$, the costs of govern increase. Otherwise, the costs decrease.

\end{proof}

\begin{corollary}
In the \textit{partisan reversal} mechanism, if the chance of electing a mayor-aligned politician is greater than $1/2$, then public goods provision increase as the legislature size increases.
\end{corollary}

This result shows that when the chances of electing an aligned politician is sufficiently high, then the costs of govern decrease. As a response, the public goods provision (and also rents), increase. The rate distribution between these two vectors is determined by the marginal change in the utility from rents and the utility from reelection. In any case, the amount allocated for both increase.

### Hybrid Partisan and Non-partisan Reversal Mechanism

The \textit{hybrid reversal} mechanism combines both partisan and non-partisan motivations. In the hybrid mechanism, a city councilor aligned with the government favors the mayor's offer if:

\[
x_i \geq \dfrac{2\delta R}{2N+1} - p
\]

An opposition politician, on the other hand, favors the mayor's offer if, and only if:

\[
x_i \geq \dfrac{2\delta R}{2N+1} + p
\]

We can decompose these costs in two components. First, the costs in terms of rents. Second, the costs (or benefits) from political alignment. In this context, the governing costs depend on the mayor's offers for councilors in the mayor's coalition versus the mayor's offers for councilors in the opposition. The ex-ante chance of a opposition member be elected is equal to $1-\gamma$, and taking the weighted averages, these costs become:

\[
C_G(N) \ = \ \dfrac{N}{2}\left( \dfrac{2\delta R}{2N+1} - p \right) + \left(\dfrac{N}{2} - \gamma N \right)p
\]

\begin{proposition}
In the \textit{hybrid reversal} mechanism, if $\gamma \leq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right]$, then the costs of govern increase as the legislature size increases. Otherwise, the costs decrease when the legislature size increases.
\end{proposition}

\begin{proof}

The difference in costs when there are $N+1$ city councilors versus the costs when there are $N$ councilors is equal to:

\[
\begin{aligned}
C_G(N+1) - C_G(N) \ = \ & \dfrac{N+1}{2}\left( \dfrac{2\delta R}{2(N+1)+1} - p \right) + \left(\dfrac{N+1}{2} - \gamma (N+1) \right)p \\
& - \dfrac{N}{2}\left( \dfrac{2\delta R}{2N+1} - p \right) - \left(\dfrac{N}{2} - \gamma N \right)p \\
 = \ & \dfrac{\delta R}{(2N+3)(2N+1)}\left[ 1-\gamma (2N+1)(2N+3)p \right]
\end{aligned}
\]

The conditions for the differences in governing costs be decrease when the  legislature size increases is:

\[
\gamma \geq \dfrac{1}{p}\left[\dfrac{1}{(2N+3)(2N+1)}\right] \equiv \underline{\gamma}
\]

\end{proof}

\begin{corollary}
In the \textit{hybrid reversal} mechanism, public goods provision decreases as the legislature size increases.
\end{corollary}

Also, the threshold $\underline{\gamma}$ for the probability of electing a politician aligned with the government is decreasing in both the political value of the mayors policy $p$ and the size of the legislature $N$. This means that higher political values and larger legislatures makes it easier to satisfy the electoral threshold.

### Main Hypotheses

Our model provides two empirically testable hypotheses. Consider a city council comprised of $N$ legislators, that increase its council size to $N+1$. Then:

\begin{enumerate}
  \item[H1. ] The provision of public goods increase when the governing costs decrease with legislature size.
  \item[H2. ] The governing decrease with legislature size when the chance of electing a government aligned legislator is sufficiently high.
\end{enumerate}

In the paper, we show that the provision of education and healthcare improves in Brazil, and this results from the fact that the chances of electing a city councilor aligned with the mayor is of 91%, thanks to the rule of distributing seats adopted in the country.

\newpage

## Variable Sources and Descriptive Statistics
\label{appsources}

We use three information sources, either from Brazilian governmental agencies or available online. Table \ref{varsources} displays the primary sources and their respective URLs.

\begin{sidewaystable}[!htbp] \centering 
\caption{Data Sources} 
\label{varsources}
\scalebox{0.75}{
  \begin{tabular}{@{\extracolsep{5pt}}llll} 
  \\[-1.8ex]\hline\hline \\[-1.8ex] 
  Source Code & \multicolumn{1}{c}{Source Name} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{URL} \\ 
  \hline \\[-1.8ex] 
  & & & \\
  DataSUS & Brazilian Health Ministry Data Service & Collects data on Health Care & \url{http://www.datasus.gov.br} \\
  & & & \\
  IBGE & Brazilian Institute of Geography and Statistics & Collects data Geography, Economics and Demography & \url{http://www.ibge.gov.br} \\ 
  & & & \\
  INEP & Data Service of Ministry of Education & Collects data on performance of Education & \url{http://www.inep.gov.br} \\ 
  & & & \\
  InterLegis & Senate Legislative Data Service & Collect Data on Legislative in Brazil & \url{http://www.interlegis.leg.br} \\
  & & & \\
  IPEA & Brazilian Institute of Applied Economics & Collects data on the Economy & \url{http://www.ipeadata.gov.br} \\ 
  & & & \\
  MDS & Social Security Ministry & Collect data on Social Coverage and Effectiveness of Social Programs & \url{http://www.mds.gov.br} \\ 
  & & & \\
  TSE & Superior Electoral Tribunal & Collects data on elections results & \url{http://www.tse.jus.br} \\
  & & & \\
  \hline\hline \\[-1.8ex] 
  \end{tabular} 
}
\end{sidewaystable}

Now let us define each variable.

### Outcomes Aggregated at the Municipal Level

\begin{itemize}
\item \textbf{Number of Seats 2000}: Number of councilors in the municipality by the 2000 elections (source: TSE).
\item \textbf{Population 2000}: Municipal population according to the 2000 Brazilian Census (source: IBGE).
\item \textbf{Per-Capita GDP Census 2000 (in millions)}: Municipal per-capita GDP computed by the IBGE Census (source: IPEA).
\item \textbf{Proportion of Poverty Census 2000}: Proportion of poverty in the municipality defined as people living on less than R\$ 70.00 a day (source: MDS).
\item \textbf{Number of Seats 2004}: Number of city-councilors in a municipality according to the Electoral Justice decision (source: TSE).
\item \textbf{Infant Mortality 2005--2008}: Infant mortality computed as the number of children born alive that died before reaching one year of age divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
\item \textbf{Post-Natal Mortality Rate 2005--2008}: Infant mortality computed as the number of children born alive that successfully lived 28 days, but died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
\item \textbf{Coverage Family Health Program 2005--2008}: Number of families covered by the Family Health Program (source: DataSUS).
\item \textbf{Prop. Born w. 7+ Pre-Natal 2005--2008}: Proportion of children born who went to seven or more prenatal care consultations (source: DataSUS)
\item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
\item \textbf{Enrollment Middle School 2005--2008}: Number of children enrolled in middle schools, averaged by classroom size (5--9) (source: INEP)
\item \textbf{Quality of Elementary School Index 2005--2008}: IDEB score averaged by schools in the municipality. IDEB scores are composed by the student's grades in math and language, multiplied by an indicator of the distortion between the year the child is supposed to be and the year the child is. The estimators are cleaned to avoid influences of schools and classroom specific effects (source: INEP, years: 2005, 2007).
\item \textbf{Quality of Middle School Index 2005--2008}: IDEB score averaged by schools in the municipality. IDEB scores are composed by the student's grade in math and language, multiplied by a score capturing the distortion between the year the child is supposed to be in, and the year the child is studying. The estimators are cleaned to avoid the influence of schools and classrooms specific effects. (source: INEP, years: 2005, 2007).
\item \textbf{Mayoral Pre-Electoral Coalition Size 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration that were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
\item \textbf{Number of Career Bureaucrats 2005--2008}: Number of career bureaucrats in the municipality. Career bureaucrats cannot be fired by politicians and earn considerably better pensions after retirement (source: IBGE, years: 2005, 2006, and 2008)
\item \textbf{Number of Councilor's Appointed Assistants 2005}: Number of assistants appointed for the councilor cabinet (source: InterLegis)
\item \textbf{Number of Females Elected 2004}: Number of females elected to city council (source: TSE)
\item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to city council. We collected this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: our compilation based on the TSE candidate pictures). 
\item \textbf{Competition per Seat 2004}: Number of people running for city-councilor divided by the number of city councilors in the municipality (source: TSE)
\item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
\end{itemize}

### Legislation Dataset

We coded the legislation approved by the councilors in 64 municipalities that are 10 thousand inhabitants away from the council size thresholds. We classified the legislation in five categories:

\begin{itemize}
\item \textbf{Local Public Goods}: Legislation that provides a service targeted at the individual, group, or geographical level.
\item \textbf{Public Goods or General Legislation}: Legislation that provides a service for the entire municipality, or approves a law that does not discriminate among citizens.
\item \textbf{Oversight}: Legislation that requests information to the mayor's office or the bureaucracy about the provision of services.
\item \textbf{Others}: Legislation that is not classified as Local Public Goods, Public Goods, or Oversight. Usually honors or procedures.
\item \textbf{Education and Health Care}: Legislation about Education or Health Care provision.
\end{itemize}

### Online 2016 Former City Councilors Survey

We run an online survey asking 174 councilors whether helping with [...service...] gives [none, few, some, or many] votes. The services were:

\begin{itemize}
\item \textbf{Help Hospital Admission}: We asked former councilors whether helping with hospital admission gives [none, few, some, many] votes (source: survey).
\item \textbf{Help School Admission}: We asked former councilors whether helping with school admission gives [none, few, some, many] votes (source: survey).
\item \textbf{Help Getting Medication}: We asked former councilors whether helping voters get medication gives [none, few, some, many] votes (source: survey).
\item \textbf{Fix Street Potholes}: We asked former councilors whether pressing the bureaucracy to fix street potholes gives [none, few, some, many] votes (source: survey).
\item \textbf{Other Local Public Goods}: We asked former councilors whether helping voters with local public goods and services such as traffic rules, sewage constructions, potable water, and others, gives [none, few, some, many] votes (source: survey).
\item \textbf{Legislative Duties}: We asked former councilors whether the act to discuss, propose, and vote on legislation gives [none, few, some, many] votes (source: survey).
\item \textbf{Honors Legislation}: We asked former councilors whether proposing bills to praise local celebrities gives [none, few, some, many] votes (source: survey).
\item \textbf{Oversee School Quality}: We asked former councilors whether overseeing school quality gives [none, few, some, many] votes (source: survey).
\item \textbf{Oversee Construction}: We asked former councilors whether overseeing public construction gives [none, few, some, many] votes (source: survey)
\end{itemize}

In this Appendix, we present other questions we asked in the survey. They are meant to improve the knowledge we have about the city councilors perceptions about their representation. We have not added these to the main paper because they were more complimentary and not of general interest. The descriptive statistics of the variables used in the main paper follow in Table \ref{tabdescrvarspaper}.

XXXX CHANGE HERE TABLE BELOW

\begin{table}[htb!]
\centering 
\caption{Summary Statistics} 
\label{tabdescrvarspaper} 
\resizebox{0.9\textwidth}{3.5in}{
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{\fill}}l r r r r r } 
\toprule
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\ 
\midrule 
& \multicolumn{5}{c}{\textbf{Municipal Characteristics}} \\ \cline{2-6}
Number of Seats 2000 & 5,521 & 10.76 & 2.70 & 9 & 21 \\ 
Population 2000 & 5,474 & 22,341.96 & 44,573.67 & 697 & 567,728 \\ 
Per-Capita GDP Census 2000 (in thousands) & 5,474 & 0.13 & 0.46 & 0.00 & 13.57 \\ 
Proportion of Poverty Census 2000 & 5,474 & 46.58 & 22.82 & 2.89 & 93.02 \\ 
Number of Seats 2004 & 5,527 & 9.22 & 0.94 & 9 & 21 \\ 
& \multicolumn{5}{c}{\textbf{Health Care Outcomes}} \\ \cline{2-6}
Infant Mortality 2005-2008 & 13,329 & 20.64 & 13.45 & 1.28 & 209.30 \\
Post-Natal Mortality Rate 2005-2008 & 6,113 & 9.29 & 8.64 & 0.59 & 200.00 \\
Coverage Family Health Program 2005-2008 & 20,577 & 76.97 & 27.39 & 0.00 & 100.00 \\ 
Prop. Born w. $6+$ Pre-Natal 2005-2008 & 16,578 & 54.02 & 24.30 & 0.57 & 100.00 \\ 
& \multicolumn{5}{c}{\textbf{Education Outcomes}} \\ \cline{2-6}
Enrollment Elementary School 2005-2008 & 10,842 & 20.62 & 5.32 & 1.00 & 57.80 \\ 
Enrollment Middle School 2005-2008 & 7,887 & 25.18 & 7.25 & 1.00 & 92.50 \\
Quality of Elementary School Index 2005-2008 & 9,267 & 3.73 & 0.94 & 0.70 & 8.10 \\
Quality of Middle School Index 2005-2008 & 5,566 & 3.21 & 0.76 & 0.30 & 6.60 \\
& \multicolumn{5}{c}{\textbf{Resources and Patronage}} \\ \cline{2-6}
Mayoral Coalition Size 2004 & 5,522 & 4.86 & 1.71 & 0.00 & 17.00 \\ 
Number of Appointed Bureaucrats 2005-2008 & 16,564 & 67.78 & 126.68 & 0 & 2,894 \\ 
Number of Career Bureaucrats 2005-2008 & 16,558 & 436.13 & 698.17 & 0 & 11,633 \\ 
Number Councilor Assistants 2005 & 5,523 & 4.63 & 8.55 & 0 & 213 \\ 
& \multicolumn{5}{c}{\textbf{Representation and Competition}} \\ \cline{2-6}
Proportion Female Elected 2004 & 5,526 & 1.12 & 1.20 & 0.00 & 8.00 \\ 
Proportion Non-White Elected 2004 & 397 & 2.23 & 1.87 & 0.00 & 9.00 \\ 
Competition per Seat 2004 & 5,527 & 6.27 & 3.82 & 1.00 & 25.83 \\ 
Proportion Approved Legislation 2005 & 3,694 & 0.83 & 0.28 & 0.00 & 1.00 \\ 
& \multicolumn{5}{c}{\textbf{Legislation Approved Data}} \\ \cline{2-6}
Legislation -- Local Public Goods & 346,553 & 0.73 & 0.44 & 0 & 1 \\ 
Legislation -- Public Goods & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
Legislation -- Oversight & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
Legislation -- Others & 346,553 & 0.17 & 0.38 & 0 & 1 \\ 
Legislation -- Education and Health & 346,553 & 0.11 & 0.31 & 0 & 1 \\ 
& \multicolumn{5}{c}{\textbf{Survey -- Electoral Attractiveness of Services}} \\ \cline{2-6}
Votes -- Help Hospital Admission & 174 & 0.82 & 0.38 & 0 & 1 \\ 
Votes -- Help School Admission & 174 & 0.59 & 0.49 & 0 & 1 \\ 
Votes -- Help get Medication & 174 & 0.71 & 0.46 & 0 & 1 \\ 
Votes -- Fix Street Potholes & 174 & 0.49 & 0.50 & 0 & 1 \\ 
Votes -- Local Public Goods & 174 & 0.81 & 0.39 & 0 & 1 \\ 
Votes -- Legislive Duties & 174 & 0.22 & 0.42 & 0 & 1 \\ 
Votes -- Honors Legislation & 174 & 0.18 & 0.38 & 0 & 1 \\ 
Votes -- Oversee School Quality & 174 & 0.29 & 0.45 & 0 & 1 \\ 
Votes -- Oversee Construction & 174 & 0.24 & 0.43 & 0 & 1 \\ 
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\textbf{Notes:} The legislation approved dataset has data on 64 of the 202 municipalities 10 thousand inhabitants from the council size thresholds. The survey summary statistics here are unweighted. Numbers of cases vary due to missingness.
\end{tablenotes} 
\end{threeparttable}
}
\end{table}

\newpage

### Threshold Manipulation, Sorting, and Pre-treatment Consistency

The validity of our causal claim relies on three assumptions. First, the impossibility of municipalities to manipulate the placement at the left or right-hand side of the thresholds. Second, that we are consistently comparing municipalities in the same cutoffs. Lastly, that we have no pre-treatment differences in our sample.

For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant in the left or the right of the cutoff. For our research, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.

We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator. We use local polynomial orders from one to four. As the null hypothesis is no manipulation, the p-values for each polynomial order are: local linear (p-value $=0.442$); quadratic (p-value $=0.740$); cubic (p-value $=0.998$); and quartic (p-value $=0.620$). Therefore, there is no manipulation according to \citet{calonico2019regression}.

We also graph the \citet{McCrary2008} test, pooling all the discontinuities. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.

\begin{figure}[htb!]
  \begin{center}
  \begin{minipage}{1 \linewidth}
  \centerline{\includegraphics[width=5in,angle=0]{../figures/McCrary.pdf}}
  \caption{\citet{McCrary2008} manipulation test}
  \bigskip
  \label{manipulationplot}
  \end{minipage}
  \end{center}
\end{figure}

For the second assumption, we know that running RDD in multiple thresholds may lead to inconsistent estimates when there is an imbalance in the running variable's distribution around the cutoffs \citep{Bertanha2015, Cattaneo2016, eggers2018regression}. For example, in our dataset, we have twelve discontinuities, and at each threshold, we have a sharp increase of one councilor, from 9 to 21. When running an RDD on these discontinuities, a consistent estimator should fit an exact change of one councilor. However, if we pool all the discontinuities together with no correction, we find an increase in council size of 1.63 councilors. This imbalance is because when we combine all the discontinuities, we are implying that changes in municipalities right below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members). That is incorrect, not only because we could be comparing a municipality with nine councilors with one with 21 councilors, but also because these municipalities diverge in many other aspects, such as population to GDP per capita.

To avoid this problem, we show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in our case, the population in 2003), improves the consistency and efficiency of the estimates. Relying on this fact, we add five controls to our estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities. The reason for the first variable is the multiple threshold assignments. We add GDP per capita because wealthier cities tend to be more productive and have better public services. The number of seats in 2000 intends to control for the fact that some municipalities could experience a change provoked by the previous council size, confounding our estimates. The year and the northeast dummies serve to improve efficiency. Adding controls improves efficiency in RDD \citep{calonico2019regression} and also enhances the consistency in the multiple thresholds RDD. See the following section for further tests and simulations.

For the last assumption, we should have no changes in pre-treatment covariates. These pre-treatment covariates are variables measured before the primary outcomes. As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.

Table \ref{validitycheck} displays the results of the validity checks. At the top of the table, we run the first-stage regressions, both using and not using the controlling covariates strategy proposed, for both real and the placebo cutoffs. At the bottom, we estimate the pre-treatment covariate balance.

XXXX CHANGE THIS

\begin{table}[htb!] \centering 
  \caption{Research Design Validity Check} 
  \label{validitycheck} 
    \scalebox{0.9}{
  \begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
\toprule
 & \multicolumn{4}{c}{\textbf{Panel A: Validity Check --- First Stage}} \\ \cline{2-5}
   & \multicolumn{1}{c}{\small{(1)}} & 
 \multicolumn{1}{c}{\small{(2)}} & 
 \multicolumn{1}{c}{\small{(3)}} & 
 \multicolumn{1}{c}{\small{(4)}} \\

 & \multicolumn{1}{c}{\small{Additional Num.}} & 
 \multicolumn{1}{c}{\small{Placebo Add.}} & 
 \multicolumn{1}{c}{\small{Additional Num.}} & 
 \multicolumn{1}{c}{\small{Placebo Add.}} \\ 
  & \multicolumn{1}{c}{\small{Seats 2004}} & 
  \multicolumn{1}{c}{\small{Num. Seats 2004}} & 
  \multicolumn{1}{c}{\small{Seats 2004}} & 
  \multicolumn{1}{c}{\small{Num. Seats 2004}} \\
  & \multicolumn{1}{c}{\small{(Without Controls)}} & 
  \multicolumn{1}{c}{\small{(Without Controls)}} & 
  \multicolumn{1}{c}{\small{(With Controls)}} & 
  \multicolumn{1}{c}{\small{(With Controls)}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
\\[-1.8ex] 
 LATE & 1.63$^{***}$ & -0.31$^{**}$ & 1.00$^{***}$ & -0.00 \\ 
  & (0.51) & (0.14) & (0.0004) & (0.0000) \\ 
\hdashline \\[-1.8ex]   
 N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
\midrule 
 & \multicolumn{4}{c}{\textbf{Panel B: Validity Check --- Pre-Treatment Variables}} \\ \cline{2-5}
 & \multicolumn{1}{c}{\small{(5)}} & 
 \multicolumn{1}{c}{\small{(6)}} & 
 \multicolumn{1}{c}{\small{(7)}} & 
 \multicolumn{1}{c}{\small{(8)}} \\
  & \multicolumn{1}{c}{\small{Number of}} & 
 \multicolumn{1}{c}{\small{Population}} & 
 \multicolumn{1}{c}{\small{GDP}} & 
 \multicolumn{1}{c}{\small{\% of Poverty}} \\ 
  & \multicolumn{1}{c}{\small{Seats 2000}} & 
  \multicolumn{1}{c}{\small{2000 Census}} & 
  \multicolumn{1}{c}{\small{2000 Census}} &
   \multicolumn{1}{c}{\small{2000 Census}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
 LATE & 0.17 & -2057.60 & 0.06 & -9.72 \\ 
  & (0.67) & (1926.33) & (0.18) & (6.27) \\ 
  \hdashline \\[-1.8ex]
 N Left & \multicolumn{1}{c}{5178} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} \\ 
N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} \\ 
Eff N Left & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{219} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{194} \\ 
Eff N Right & \multicolumn{1}{c}{147} & \multicolumn{1}{c}{157} & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{142} \\ 
BW Loc Poly & 8.970 & 9.368 & 8.739 & 8.530 \\ 
BW Bias & 13.860 & 15.029 & 14.752 & 13.035 \\ 
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $ ^{***} $ p $ < $ .01; $ ^{**} $ p $ < $ .05; $ ^{*} $ p $ < $ .1. RD local linear estimates using \citet{calonico2019regression} optimal bandwidth quadratic selection and triangular kernel. Robust standard errors, clustered at the municipal level, in parentheses. Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region. \textit{N Left} and \textit{N Right} represent the total number of observation in the left and right sides of the thresholds (untreated). \textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth. \textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE). \textit{BW Bias} is the Bandwidth used to compute the standard errors.
\end{tablenotes}
\end{threeparttable}}
\end{table}

Notice that without controls, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions. After adding covariates, the results improve, and the point estimates are now one for the primary model and zero for the placebo regressions, which are the correct values. Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds. These tests reinforce the validity of our research designs.

\pagebreak

## Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision
\label{appidentif}

The identification strategy requires exogenous changes in the city council size thresholds. Previous to the changes we exploit here, the 1988 Brazilian Constitution states the following distribution of seats per population size, presented in Table \ref{tabcitycouncilsize1988}.

\begin{table}[htp!]
\centering
\caption{City council size from the 1988 Constitution}
\scalebox{0.75}{
\begin{tabular}{rccrrr}
  \hline\hline
 & \multicolumn{1}{c}{Min. Leg.} & \multicolumn{1}{c}{Max. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\ 
 & & & & & \multicolumn{1}{c}{(2001-2004)} \\
  \hline
  1 & 9  & 21 & 0 & 1,000,000 &  5,537 \\ 
  2 & 33 & 41 & 1,000,001 & 5,000,000 & 11 \\ 
  3 & 42 & 55 & 5,000,001 & $\infty$ & 2 \\ 
   \hline\hline
\end{tabular}
}
\label{tabcitycouncilsize1988}
\end{table}

These cutoffs were in place until 2003, when the municipality of Mira Estrela decided to decrease the council size from eleven to nine councilors. The two losing councilors started a judicial contestation that made it to the Supreme Court. The court ruled that the Constitution meant that council size should vary proportionally with population, starting with nine legislators, until the maximum number of councilors, 55. Following this decision, the Superior Electoral Tribunal (TSE) decided the thresholds that should be followed in the 2004 election (Resolution 21,702/2004). According to their decision, the legislature should increase as displayed in Table \ref{tabcitycouncilsize2004all}.

\begin{table}[htp!]
\centering
\caption{City council size thresholds according to TSE resolution 21,702/2004}
\scalebox{0.75}{
\begin{tabular}{rcrrr}
  \hline\hline
 &  \multicolumn{1}{c}{Num. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
 & & & & \multicolumn{1}{c}{(2003 pop. proj.)} \\
  \hline
  1 &  9 & 0 & 47,619 & 5,029 \\ 
  2 &  10 & 47,620 & 95,238 & 317 \\ 
  3 &  11 & 95,239 & 142,857 & 89 \\ 
  4 &  12 & 142,858 & 190,476 & 43 \\ 
  5 &  13 & 190,477 & 238,095 & 30 \\ 
  6 &  14 & 238,096 & 285,714 & 21 \\ 
  7 &  15 & 285,715 & 333,333 & 13 \\ 
  8 &  16 & 333,334 & 380,952 & 13 \\ 
  9 &  17 & 380,953 & 428,571 & 6 \\ 
  10  & 18 & 428,572 & 476,190 & 6 \\ 
  11  & 19 & 476,191 & 523,809 & 4 \\ 
  12  & 20 & 523,810 & 571,428 & 5 \\ 
  13  & 21 & 571,429 & 1,000,000 & 13 \\ 
  14  & 33 & 1,000,001 & 1,121,952 & 1 \\ 
  15  & 34 & 1,121,953 & 1,243,903 & 2 \\ 
  16  & 35 & 1,243,904 & 1,365,854 & 1 \\ 
  17  & 36 & 1,365,855 & 1,487,805 & 2 \\ 
  18  & 37 & 1,487,806 & 1,609,756 & 1 \\ 
  19  & 38 & 1,609,757 & 1,731,707 & 1 \\ 
  20  & 39 & 1,731,708 & 1,853,658 & 0 \\ 
  21  & 40 & 1,853,659 & 1,975,609 & 0 \\ 
  22  & 41 & 1,975,610 & 4,999,999 & 4 \\ 
  23  & 42 & 5,000,000 & 5,119,047 & 0 \\ 
  24  & 43 & 5,119,048 & 5,238,094 & 0 \\ 
  25  & 44 & 5,238,095 & 5,357,141 & 0 \\ 
  26  & 45 & 5,357,142 & 5,476,188 & 0 \\ 
  27  & 46 & 5,476,189 & 5,595,235 & 0 \\ 
  28  & 47 & 5,595,236 & 5,714,282 & 0 \\ 
  29  & 48 & 5,714,283 & 5,833,329 & 0 \\ 
  30  & 49 & 5,833,330 & 5,952,376 & 0 \\ 
  31  & 50 & 5,952,377 & 6,071,423 & 1 \\ 
  32  & 51 & 6,071,424 & 6,190,470 & 0 \\ 
  33  & 52 & 6,190,471 & 6,309,517 & 0 \\ 
  34  & 53 & 6,309,518 & 6,428,564 & 0 \\ 
  35  & 54 & 6,428,565 & 6,547,611 & 1 \\ 
  36  & 55 & 6,547,612 & $\infty$  & 0 \\ 
   \hline\hline
\end{tabular}
}
\label{tabcitycouncilsize2004all}
\end{table}

As there are few municipalities above one million inhabitants, we decided to restrict our attention to municipalities with less than $571,429 + 47,619 = 619,048$ inhabitants. Table \ref{tabcitycouncilsize2004short} displays the frequency of municipality by thresholds used in our paper.

\begin{table}[htp!]
\centering
\caption{City council thresholds used in the paper}
\scalebox{0.85}{
\renewcommand*{\arraystretch}{1.2}
\begin{tabular}{rcrrr}
  \hline \hline
 & \multicolumn{1}{c}{Legislature} & \multicolumn{1}{c}{Min.} & \multicolumn{1}{c}{Max.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
 & \multicolumn{1}{c}{Size} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{(2003 pop.)} \\
  \hline
  1 & 9 & 0 & 47,619 & 5,029 \\ 
  2 & 10 & 47,620 & 95,238 & 317 \\ 
  3 & 11 & 95,239 & 142,857 & 89 \\ 
  4 & 12 & 142,858 & 190,476 & 43 \\ 
  5 & 13 & 190,477 & 238,095 & 30 \\ 
  6 & 14 & 238,096 & 285,714 & 21 \\ 
  7 & 15 & 285,715 & 333,333 & 13 \\ 
  8 & 16 & 333,334 & 380,952 & 13 \\ 
  9 & 17 & 380,953 & 428,571 & 6 \\ 
  10 & 18 & 428,572 & 476,190 & 6 \\ 
  11 & 19 & 476,191 & 523,809 & 4 \\ 
  12 & 20 & 523,810 & 571,428 & 5 \\ 
  13 & 21 & 571,429 & 1,000,000 & 13 \\ 
   \hline \hline
\end{tabular}
}
\label{tabcitycouncilsize2004short}
\end{table}

The Supreme Court ruled that the electoral courts should use the 2003 population projection to assign municipalities to cutoffs. In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) propose the official population projections. Sorting is not an issue for our identification strategy, as IBGE is an insulated bureaucracy, insulated from local influences (see also the McCrary test above).

To provide an overview of the data dispersion, Figure \ref{sampleplot} plots the municipalities by their proximity from the cutoffs. In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds. The darker the color, the closer to the population thresholds. In regression discontinuity, the closer a municipality is to the cutoff, the more influential it is in the estimation. Figure \ref{sampleplot} also shows that our municipalities are reasonably distributed around the whole country.

XXXX CHANGE

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=7in,angle=0]{../figures/samplePlot.pdf}}
      \caption{Municipalities by their Selection Status}
      \bigskip
      \label{sampleplot}
    \end{minipage}
  \end{center}
\end{figure}

\pagebreak

Moreover, we could question whether the discontinuities studied here are sharp or fuzzy. In order to be fuzzy, the laws passed by the Supreme Court had to be contested or not be perfectly enforced. For instance, \citet{cavalcanti2017essays} shows in his second chapter that there has been a misuse of these discontinuities. However, this problem was absent in our RDD, as the problem identified by Cavalcanti was based on the use of thresholds approved in 2009. In our case, we use the thresholds approved in 2003, and until a period before 2009 (in our case, 2008).

\newpage

## Identification Strategy in Multiple Thresholds Regression Discontinuity Design
\label{ISMT}

Usually when carrying out regression discontinuity with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes. Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$. The outcome variable is assumed to be $Y$. In the pooled model, the Local Average Treatment Effect is:

\[
LATE_{nocontrols} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C \right]
\]

Nevertheless, this may be problematic as the municipal characteristics in each cutoff may vary from cutoff to cutoff. The population imbalance certainly carries out heterogeneity, in the way shown by \citet{Cattaneo2016}. To ensure we have comparability, and that we estimate the average LATE for all cutoffs, avoiding most of the heterogeneity, we propose to add a set of controls denoted by $Z_i$ that vary between cutoffs. For instance, the population that determines the change from one threshold to another also determines all the cutoffs. As the population varies smoothly around each cutoff, it makes it a perfect control to add. The new estimator is:

\[
LATE_{controls} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C, Z_i \right]
\]

We control for Population, GDP, a dummy for the Northeast States, seats before the 2003 decision, and year. All these control variables are smooth in each cutoff, but are significantly different from cutoff to cutoff, making them adequate control variables for our case \citep{calonico2019regression}. To perform the estimations, we use a triangular kernel, which places more weight on the municipalities that are closer to each cutoff. To compute the optimal bandwidth, we use the \citet{CCT2014} method. To study the sensitivity to the bandwidth choice, we vary the bandwidth from 50\% to 200\% of the optimal bandwidth size. We also use cluster-robust standard errors at the municipal level.

However, as it is uncommon for a regression discontinuity to use control variables, some readers may ask why in this case is it advisable? To answer this question, we run a series of simulations to show that controlling for the variable that determines the assignment not only helps improve the consistency of our estimates but also improves their efficiency.

Consider the data distributed in one of the four forms depicted by Figure \ref{simRDdd}. We add nine thresholds, at 0.1, 0.2, and so on until 0.9, and we create six types of outcomes. The first three outcomes are sharp changes. In the first, we add variation from one to 10, with one step for each change. In the second, we add 1 in the first cut, zero in the second cut, and -1 in the third cut, repeating this pattern for the remaining cutoffs. The estimated change should be equal to zero. In the third model, we add one in the first cut, $1+0.9$ in the second cut, $1+0.9+0.8$ in the third cut, and so on until the last cutoff. This is intended to simulate a diminishing effect from one cutoff to the other. The last three outcomes are the same as depicted here, added by a Normal random disturbance, mean zero, and variance 0.01. We then run a thousand Monte Carlo simulation for each combination, $4 \times 6 \times 2 = 48$ in total, fitting a regression with and without the running variable as a control.

XXXX CHANGE

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{0.9\linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/simdistrRDD.pdf}}
      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
      \bigskip
      \label{simRDdd}
    \end{minipage}
  \end{center}
\end{figure}

\pagebreak

A consistent estimator should fit one in the first and fourth data distribution.  In the second and fifth, the change should be of $(1, 0, -1, 1, 0, -1, 1, 0, -1)$, and the average change here is equal to zero. In the third and sixth models the change should be equal to $(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)$, and the average change should be equal to $0.5$. The first three models should present a more efficient estimation than the last three models. We display the results in Figure \ref{estimDGP}, showing that the controlled models are more consistent and efficient.

XXXX CHANGE

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=4.5in,angle=0]{../figures/estimsRDD.pdf}}
      \caption{Estimations for the Different Data Generating Processes}
      \bigskip
      \label{estimDGP}
    \end{minipage}
  \end{center}
\end{figure}

\newpage

## Placebo Regressions for the Aggregated Mechanism Outcomes
\label{placmechmain}

Here we present the placebo regressions for the mechanism-aggregated outcomes. In Panel A of the main paper, we run the regression on alternative explanations. As we can see, the only female changed significantly, but the change is statistically expected in at least 10\% of cases. For non-white, we have not collected data on non-white legislators in the placebo cutoffs; therefore, we leave it blank. In Panel B, we have the placebo regressions for the primary mechanism: resource access and patronage. As expected, the placebo regressions were not statistically significant.

XXXX CHANGE

\begin{table}[!htbp] \centering 
\caption{Mechanism -- Aggregate Municipal Level Regressions} 
\label{placresmechreg1} 
\scalebox{0.9}{
\begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l R R R R }
\toprule
 & \multicolumn{4}{c}{\textbf{Panel A: Representation and Elections -- Placebo Cutoffs}} \\ \cline{2-5}
& \multicolumn{2}{c}{\textbf{Representation}} & 
\multicolumn{2}{c}{\textbf{Elections \& Leg. Productivity}}\\ \cline{2-3}\cline{4-5}
 & \multicolumn{1}{c}{\small{Num. Female}} & 
 \multicolumn{1}{c}{\small{Num. Non-white}} &
  \multicolumn{1}{c}{\small{Candidates}} & 
  \multicolumn{1}{c}{\small{Prop. Laws}} \\ 
   & \multicolumn{1}{c}{\small{Councilors}} & 
 \multicolumn{1}{c}{\small{Councilors}} &
  \multicolumn{1}{c}{\small{Per Seat}} & 
  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
  LATE & 0.65$^{**}$ &  & -0.72 & -0.001 \\ 
  & (0.27) &  & (0.48) & (0.06) \\ 
  N Left & 4620 &  & 4621 & 2991 \\ 
  N Right & 906 &  & 906 & 703 \\ 
  Eff N Left & 412 &  & 567 & 356 \\ 
  Eff N Right & 297 &  & 347 & 229 \\ 
  BW Loc Poly & 4.861 &  & 6.113 & 5.58 \\ 
  BW Bias & 8.775 &  & 10.345 & 8.896 \\ 
\midrule
 & \multicolumn{4}{c}{\textbf{Panel B: Resource Access and Patronage -- Placebo Cutoffs}} \\ \cline{2-5}
 & \multicolumn{1}{c}{\small{Mayoral}} & 
 \multicolumn{1}{c}{\small{Num. Politically}} & 
 \multicolumn{1}{c}{\small{Num. Career}} & 
 \multicolumn{1}{c}{\small{Num. Councilor}} \\
 & \multicolumn{1}{c}{\small{Coalition Size}} & 
 \multicolumn{1}{c}{\small{Appointed Empl.}} & 
 \multicolumn{1}{c}{\small{Bureaucrats}} & 
 \multicolumn{1}{c}{\small{Assistants}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
 LATE & 0.12 & 3.77 & 115.67 & -2.17 \\ 
 & (0.34) & (17.20) & (79.96) & (1.81) \\ 
 N Left & 4618 & 13855 & 13850 & 4618 \\ 
 N Right & 904 & 2709 & 2708 & 905 \\ 
 Eff N Left & 644 & 1123 & 1464 & 592 \\ 
 Eff N Right & 388 & 825 & 957 & 361 \\ 
 BW Loc Poly & 6.730 & 4.475 & 5.461 & 6.279 \\ 
 BW Bias & 10.421 & 7.600 & 9.999 & 10.944 \\ 
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1. RD estimates using \citet{CCT2014} optimal bandwidth selection and triangular kernel. Robust standard errors, clustered at the municipal level, in parenthesis. Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
\end{tablenotes}
\end{threeparttable}}
\end{table}

\newpage

## Sensitivity Analysis for Bandwidth Selection
\label{sensffapp}

We present here the sensitivity to the bandwidth selection. Following the suggestions of \citet{Bueno2015}, we vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.

XXXX CHANGE

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=5in,angle=0]{../figures/bwSens.pdf}}
      \caption{Bandwidth Sensitivity -- Main Models}
      \bigskip
      \label{graphbw}
    \end{minipage}
  \end{center}
\end{figure}

In Figure \ref{placgraphbw}, we run the same bandwidth analysis for the placebo outcomes. The results, as expected, show mostly insignificant results.

\pagebreak

XXXX CHANGE

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[width=5in,angle=0]{../figures/placBwSens.pdf}}
      \caption{Placebo Regressions -- Bandwidth Sensitivity}
      \bigskip
      \label{placgraphbw}
    \end{minipage}
  \end{center}
\end{figure}

\newpage

## Sensitivity to Different States in the Analysis
\label{sensstate}

The literature considers that some states are more prone to inefficiencies than the rest of the country. Moreover, some states had such poor Health Care and Education systems that they could be driving the results by themselves. As a consequence, our results could be a byproduct of structural changes in crucial states, instead of in council size. We run the analysis dropping one state at a time, to investigate this statewide heterogeneity. The results are in Figures \ref{graphsensstatedrop1},\ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.

To interpret the results, first, note that most coefficients remain around the same value as before the robustness checks. The exceptions are with the Family Health Program, which improves without Para\'{i}ba but decreases significantly without Bahia, both northeastern states. In the placebo, the FHP coverage increases when we remove Bahia and decrease when we add S\~{a}o Paulo. Otherwise, note that all the other variables remain unchanged, except for gender. Gender changes because there were laws during this period mandating a minimum amount of female candidates. It is expected that one variable changes as a response to randomness.

\pagebreak

XXXX CHANGE

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens1.pdf}}
      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
      \bigskip
      \label{graphsensstatedrop1}
    \end{minipage}
  \end{center}
\end{figure}

\pagebreak

XXXX CHANGE

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens2.pdf}}
      \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
      \bigskip
      \label{graphsensstatedrop2}
    \end{minipage}
  \end{center}
\end{figure}

\pagebreak

XXXX CHANGE

\begin{figure}[htb!]
  \begin{center}
      \centerline{\includegraphics[width=5in,angle=0]{../figures/placDropStateSens1.pdf}}
      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
      \bigskip
      \label{placgraphsensstatedrop1}
  \end{center}
\end{figure}

\pagebreak

XXXX CHANGE

\begin{figure}[htb!]
  \begin{center}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/placDropStateSens2.pdf}}
      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
      \bigskip
      \label{placgraphsensstatedrop2}
  \end{center}
\end{figure}

\newpage

## Sensitivity to the Functional Form Analysis
\label{sensfuncform}

In the paper, we run all the regressions using local linear polynomials. \citet{GelmanImbens2014} show that local linear and quadratic polynomials are better in terms of consistency than cubic and quartic.

However, we run here all the models using polynomials from local linear to a quartic, showing that our results are robust to different regression functional forms. With two exceptions, the results are mostly consistent. First, quadratic and cubic polynomials make the significance go away in some models. Second, quartic polynomials seem to make the Family Health Program (FHP) significant and negative, which goes in line with our theoretical predictions. Figures \ref{graphsensff} and \ref{placgraphsensff} present the results for the real and the placebo cutoffs.

\pagebreak

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,angle=0]{../figures/ffSens.pdf}}
      \caption{Sensitivity Analysis for the Functional Form}
      \bigskip
      \label{graphsensff}
    \end{minipage}
  \end{center}
\end{figure}

\pagebreak

\begin{figure}[htb!]
  \begin{center}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/placFfSens.pdf}}
      \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
      \bigskip
      \label{placgraphsensff}
  \end{center}
\end{figure}

\newpage

## Sensitivity to Covariates
\label{senstcovapp}

The control variables play an essential role in our model. As we argued before, without controls, the first stage is inconsistent, and we may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.

However, if the selection of controls makes the models overestimate quantities in the directions our narrative emphasizes, this would pose a considerable credibility issue for our analysis. To study the sensitivity to controls, we run the same regressions for all possible control combinations. Figure \ref{graphsenscontrol} displays the results for this sensitivity test.\footnote{In the Figure, \textit{NC} stands for No Controls. The controls used are \textit{gdp}, the municipal GDP in a given year; \textit{nseats2000}, the number of seats before the 2003 Supreme Court decision; \textit{northeast}, a dummy variable for Northeast Brazil; \textit{pop2003\_2}, population in 2003 (underscore 2 means that is population by thousands); and \textit{year}.}

\begin{landscape}
\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=6in,angle=0]{../figures/sensCov.pdf}}
      \caption{Sensitivity Analysis for the Control Variable's Choices}
\bigskip
\label{graphsenscontrol}
\end{minipage}
\end{center}
\end{figure}
\end{landscape}

For instance, changes in controls have a substantial effect on the detected differences in the Family Health Program coverage, as well as in Elementary Education Quality.

In our view, our choice was the most conservative, as the Full Model is significant when most of the combinations also are significant. Otherwise, our model is not significant when most combinations are also insignificant. Regarding the point estimates, our analysis chooses the smaller coefficient sizes systematically for the significant variables.

We also plot sensitivity tests to covariates in the placebo regressions in Figures \ref{placsenscov1} and \ref{placsenscov2}. The theoretical expectations here are that most of these outcomes would fail, and the graphs indeed confirm these expectations.

\pagebreak

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens1Cov.pdf}}
\caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
\bigskip
\label{placsenscov1}
\end{center}
\end{figure}

\pagebreak

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens2Cov.pdf}}
\caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
\bigskip
\label{placsenscov2}
\end{center}
\end{figure}

\newpage

\subsection{Sensitivity to Additional Cutoffs\label{senscutapp}}

To study the sensitivity to the number of cutoffs, as well as a possibility of diminishing returns from the additional legislator, we run regressions limiting the population sizes to half the cutoffs, from the second cutoff to the last. This strategy is similar to adding one cutoff at a time. The results are stable and do not change our main conclusions. Moreover, there is no increasing or decreasing pattern, which would indicate that differential returns are occurring. Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs, while Figures \ref{placsenscut1} and \ref{placsenscut2} present the same results for the placebo cutoffs.

\pagebreak

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts1.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
\bigskip
\label{senscut1}
\end{center}
\end{figure}

\pagebreak

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts2.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
\bigskip
\label{senscut2}
\end{center}
\end{figure}

\pagebreak

\begin{figure}[htb!]
\begin{center}
\begin{minipage}{0.8 \linewidth}
\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts1.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
\bigskip
\label{placsenscut1}
\end{minipage}
\end{center}
\end{figure}

\pagebreak

\begin{figure}[htb!]
\begin{center}
\begin{minipage}{0.8 \linewidth}
\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts2.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
\bigskip
\label{placsenscut2}
\end{minipage}
\end{center}
\end{figure}

\newpage

## Mayor's Characteristics, Revenues, and Transfers from the Central Government

Two alternative explanations could confound our results. First, the selection of the mayor could be affected by the city council size, and then the welfare improve by the quality of the mayor, and not by the partisan mechanism described. Second, the partisan mechanism could be confounded by an argument similar to the @Weingastetal1981 ``law of 1/n'', and the improvements in welfare could have been a result of higher revenues. This section shows that none of these concerns are true in our case.

\subsubsection{Mayoral characteristics}

We select four characteristics: gender, schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008. The results show no variation on council size and mayoral characteristics.

\begin{table}[!htbp] \centering 
\caption{Mayoral Characteristics} 
\label{appmaychar} 
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
  \\[-1.8ex]\hline \\[-1.8ex] 
  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w. College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\ 
  \hline \\[-1.8ex] 
  LATE & 0.07 & -0.06 & -0.09 & 0.06 \\ 
  & (0.08) & (0.13) & (0.10) & (0.14) \\ 
  N Left & 5069 & 5069 & 5184 & 5183 \\ 
  N Right & 335 & 335 & 343 & 343 \\ 
  Eff N Left & 299 & 226 & 192 & 231 \\ 
  Eff N Right & 184 & 154 & 141 & 159 \\ 
  BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\ 
  BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\ 
  \hline \\[-1.8ex] 
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
  \end{tabular} }
\end{table}

\begin{table}[!htbp] \centering 
\caption{Mayoral characteristics -- Placebo} 
\label{placappmaychar} 
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
  \\[-1.8ex]\hline \\[-1.8ex] 
  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w. College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\ 
  \hline \\[-1.8ex] 
  LATE & 0.03 & 0.04 & 0.08 & -0.07 \\ 
  & (0.05) & (0.08) & (0.07) & (0.08) \\ 
  N Left & 4526 & 4526 & 4621 & 4620 \\ 
  N Right & 878 & 878 & 906 & 906 \\ 
  Eff N Left & 567 & 707 & 683 & 759 \\ 
  Eff N Right & 342 & 406 & 397 & 427 \\ 
  BW Loc Poly & 6.197 & 7.413 & 7.006 & 7.71 \\ 
  BW Bias & 10.241 & 12.64 & 13.536 & 12.648 \\ 
  \hline \\[-1.8ex] 
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
  \end{tabular} }
\end{table}

\subsubsection{Revenues and Transfers}

We run the regressions on federal transfers and revenue raised within the municipalities. There is only a small effect on education transfer, barely significant at 10%. The other indicators remain insignificant. Note that the placebo are significant, and this actually reinforce the claim that the education effect may be spurious.

\begin{table}[!htbp] \centering 
\caption{Transfers and Revenue} 
\label{apptrev} 
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
  \\[-1.8ex]\hline \\[-1.8ex] 
  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
  \hline \\[-1.8ex] 
  LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\ 
  & (0.04) & (0.03) & (0.10) & (0.04) \\ 
  N Left & 15555 & 15555 & 15460 & 14668 \\ 
  N Right & 1029 & 1029 & 1028 & 998 \\ 
  Eff N Left & 804 & 258 & 349 & 626 \\ 
  Eff N Right & 516 & 273 & 333 & 442 \\ 
  BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\ 
  BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\ 
  \hline \\[-1.8ex] 
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
  \end{tabular} }
\end{table}

\begin{table}[!htbp] \centering 
\caption{Transfers and Revenue -- Placebo} 
\label{plactrev} 
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
  \\[-1.8ex]\hline \\[-1.8ex] 
  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
  \hline \\[-1.8ex] 
  LATE & 0.07$^{**}$ & 0.04 & 0.03 & 0.07$^{**}$ \\ 
  & (0.03) & (0.03) & (0.06) & (0.03) \\ 
  N Left & 13865 & 13865 & 13776 & 13103 \\ 
  N Right & 2719 & 2719 & 2712 & 2563 \\ 
  Eff N Left & 807 & 636 & 1928 & 848 \\ 
  Eff N Right & 619 & 544 & 1163 & 611 \\ 
  BW Loc Poly & 3.418 & 3.028 & 6.738 & 3.67 \\ 
  BW Bias & 6.021 & 5.36 & 10.871 & 6.222 \\ 
  \hline \\[-1.8ex] 
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
  \end{tabular} }
\end{table}

\newpage

\subsection{Legislation Dataset\label{legdfr}}

In the Fall of 2018, we collected the data on the legislation approved by the city council of 64 municipalities 10 thousand inhabitants away from the thresholds. There are 202 municipalities at a 10 thousand inhabitants distance from the cutoff, but only 64 had information on the legislation for the period between 2005 to 2008.

To classify the legislation, we hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machines algorithm to the remaining 99\% cases. First, we train and test the accuracy of the SVM classifier on 80\% of the dataset. Then, we ran the training on the full hand-coded data and predicted the remaining.\footnote{We tested SVM, Naive-Bayes, Random Forests, and Neural Networks. We choose SVM as it gives the highest prediction rate. We are using a simple bag-of-words classifier, with the R package RTextTools \citep{collingwood2013rtexttools}.}

We hand-coded using five characteristics:

\begin{enumerate}
\item \textbf{Local Public Goods}: Whether the bills provided a local public good or service. Bills here are, for example, proposals to fix street potholes, staff a given health clinic, purchase equipment to a given school. To lay on this category, the service should have been targeted for a fraction of the population.
\item \textbf{Public Goods and Legislation}: Whether a bill is about a municipal public good (e.g., improving education), or about legislation that does not discriminate against any citizen within the polity (general law). 
\item \textbf{Oversight}: Legislation requesting information on the status of service provision.
\item \textbf{Others}: Legislation that is not categorized as any of the previous three listed. Legislation here includes honors to notable citizens and procedure legislation, among others.
\item \textbf{Health Care and Education}: Bills on education and health care, broadly defined.
\end{enumerate}

We run the SVM on the hand-coded data. Table \ref{accurClassif} shows the classification accuracy for each of the variables that we hand-coded. In all models, we set cost equals 10 to avoid overfitting.

\begin{table}
\centering
\caption{Accuracy SVM Classifier (tested in 20\% of the data)}
\label{accurClassif}
\begin{tabular}{lc} 
\hline
\textbf{Variable}            & \textbf{Accuracy}  \\ 
\hline
Local Public Goods           & 93.8               \\
Public Goods and Legislation & 94.2               \\
Oversight                    & 94.9               \\
Others                       & 93.5               \\
Education and Health Care    & 92.5               \\
\hline
\end{tabular}
\end{table}

After we classify all the bills, the frequency in each category was added to the main paper. We also add the productivity per legislator, consisting of a ratio of the legislation approved in the municipality in the four-year term, divided by the council size. As expected, the results changed little from when we considered the absolute values.

\newpage

\subsection{City Councilors Survey\label{appsurv}}

From November 21st to December 1st, 2016, we surveyed former city councilors that served in the 2005 to 2008 period. We asked them questions regarding how mayors secure electoral support, which services are common in the city councilor's practice, and which services give the highest electoral yield.

We used 3,240 emails from politicians that ran in the 2016 election, filtering the politicians that hold public office in 2005. In December 1st we closed the pool, having 174 responses. Figure \ref{geodistrsurv} displays a distribution of responses.

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrRespSurvey.pdf}}
      \caption{Geographical Distribution of Survey Responses}
      \bigskip
      \label{geodistrsurv}
    \end{minipage}
  \end{center}
\end{figure}

\pagebreak

To weight the survey, we use the Legislative Census, which was conducted ran in 2005 by the Brazilian Senate company \textit{Interlegis} to improve the quality of the legislative. We use the categories of Brazilian region, legislature size (9 to 15 or more), gender, and age less than 39, re-weighting the collected data to match the population proportions. We use the proportions on each bin to weight the graphs and statistics generated after the raking process.\footnote{The R package \textit{survey} describes in detail the raking process \citep{lumley2004analysis}. In summary, it iterates the post-stratification procedure until the sample marginals match the population marginals for all variables.} Table \ref{tabweight} shows the sample, population, and weighted proportions.

\begin{table}[htp!]
\centering
\caption{Proportions for each bin used in the weighting process}
\label{tabweight}
\begin{tabular}{lccc}
\hline
& Sample & Population & Weighted \\
& Proportions & Proportions. & Proportions \\
\hline
\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
\textbf{Region = CENTRO-OESTE} & 0.11         & 0.08       & 0.08           \\
\textbf{Region = NORDESTE}     & 0.33         & 0.32       & 0.32           \\
\textbf{Region = NORTE}        & 0.05         & 0.08       & 0.08           \\
\textbf{Region = SUDESTE}      & 0.30         & 0.30       & 0.30           \\
\textbf{Region = SUL}          & 0.20         & 0.21       & 0.21           \\ \hline
\end{tabular}
\end{table}

Note that the algorithm performed well, with minimal differences occurring only after the third decimal place.

The questions of interest for this research, asked in the survey were:

\begin{enumerate}
    \item No Brasil é comum que o prefeito tenha de negociar para ter maioria na Câmara de Vereadores. Com que frequência, o(a) Sr(a) acha que o prefeito usa os seguintes dispositivos para conseguir apoio?
    \item Quais dessas atividades o(a) Sr(a) acredita serem mais comuns no trabalho da maioria dos vereadores?
    \item Quais dessas atividades o(a) Sr(a) acredita que ajudam mais um vereador durante a eleição?
\end{enumerate}

A free translation to English would be:

\begin{enumerate}
    \item In Brazil, it is common that mayors negotiate the majority within the city council. What is the frequency that mayors use the following services in exchange for support?
    \item Which of those activities do city councilors perform the most in their representation practices?
    \item Which of the following activities do you believe helps city councilors the most in elections?
\end{enumerate}

The second question is essential, as it reports whether councilors do the activities that give more electoral yield. Figure \ref{commonservice} shows the results for each of the activities we studied the electoral yield.

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6.5in,angle=0]{../figures/commonJobsCouncilors.pdf}}
      \caption{City Councilor's Common Activities}
\bigskip
\label{commonservice}
\end{minipage}
\end{center}
\end{figure}

The last question measures the willingness of mayors to give services to city councilors. This question is relevant, as mayors control most of the bureaucracy and the mediation of services requires a good relationship with mayors. Figure \ref{mayorneg} shows the results for the mayoral activities.

\begin{figure}[htb!]
\begin{center}
\begin{minipage}{1 \linewidth}
\centerline{\includegraphics[width=6.5in,angle=0]{../figures/strategySupportMayors.pdf}}
\caption{Mayor negotiated services in exchange of support}
\bigskip
\label{mayorneg}
\end{minipage}
\end{center}
\end{figure}

Therefore, both Figures show that councilors do perform the tasks that give the most electoral yield. The exception is the category of honor legislation, which most legislators seem to perform, even though they acknowledge that it provides little electoral returns.

Regarding the services that mayors use to negotiate with the coalition, note that jobs in exchange of support are the highest ranked strategy by councilors. Our results capture that, as an increase in city council size has a positive effect on the number of appointed employees in the municipality.

### 2021-08-20 article/article.Rmd
structure

---
title:  |
        | Legislature Size and Welfare:
        | Evidence from Brazil
author: 
  - Gabriel Cepaluni[^gabriel]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
date: \today
thanks: "We thank Cedric Antunes, Victor Araujo, Eric Arias, Taylor Boas, Natalia Bueno, Andrea Freitas, Saad Gulzar, James Mahon, Lucas Novaes, Nelson Ruiz, Catarina Roman, David Skarbek, and Denis Stukal for their valuable comments. We also thank the participants of seminars and conferences at CEPESP, CUNY, INSPER, IPSA, LACEA, LASA, MPSA, Notre Dame, NYU, PUC Chile, SPSA, and Uppsala. We gratefully acknowledge the financial support of the São Paulo Research Foundation (FAPESP), grant number 2017/07290-5. All materials required to replicate this study are available at <https://github.com/umbertomig/legislature-size-welfare>."
abstract: "What is the effect of legislature size on social welfare? While the literature suggests that increasing the number of legislators broadens political representation and raises government expenditures, its implications for public service provision remain understudied. In this paper, we exploit exogenous changes in city-council size in Brazil and show that adding a legislator increases education and healthcare indicators. XXXX Education quality and preventive health care remain unaffected, but primary school enrolment and infant mortality significantly improve. To investigate the mechanism, we surveyed former councillors and analysed 346,553 bills proposed between 2005 and 2008. This analysis shows that politicians prefer to provide private and targeted goods instead of public goods. This paper has implications for the design of legislative institutions."
abstractspacing: double
keywords: Legislature size; Legislative politics; Public goods provision; Regression discontinuity design; Brazil
jelcodes: HXXXX
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# XXXX
```

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.

[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.

\newpage

# Introduction
\label{sec:intro}

Legislative institutions are crucial for welfare and service provision in democratic countries. Historically, the division of power and the birth of a representative government placed the legislatures at the center of popular consent \citep{north1989constitutions}. In modern democracies, most countries have assemblies at all levels of government. These institutions affect the information and quality of legislation \citep{krehbiel2010information}, check and veto the other political powers \citep{tsebelis2002veto}, and influence policymaking \citep{weingast1988industrial, north1989constitutions, auriol2012optimal}. Moreover, they also determine taxation, government expenditure \citep{Weingastetal1981, PrimoSnyder2008, stasavage2011states}, and oversee service provision \citep{mccubbins1984congressional, poulsen2018political}.

Regardless of differences in electoral rules, social composition, and procedures, all legislatures share one feature: more than one representative composes them. Legislature size relates to collective action problems \citep{crain1979cost, rogers2002free}, government spending \citep{Weingastetal1981, PrimoSnyder2008}, and representation \citep{allenrepresentation}, but how these components affect welfare remain understudied. On the one hand, enlarged legislatures increase government spending and lawmaking, and this may improve some services \citep{Weingastetal1981, }. On the other hand, adding a legislator can increase the number of veto players and broaden the collective action problems, hindering service provision. Therefore, larger legislatures have an ambiguous effect on welfare, and XXXX.

In this paper, we propose a theory of legislature size and welfare that takes into account two crucial components: the XXXX and the partisan affiliation of the legislators.

XXXX Umberto: Parei aqui.

This paper fills this gap by studying the effects of legislature size on service provision. Assuming that politicians want to further their careers, we argue that two variables determine service provision: the perceived importance of the service by voters and the politician's capacity to claim credit for its provision. Politicians perform a simple cost-benefit analysis: if providing a service results in high electoral yield, and it is easy to claim credit for, politicians will produce this service abundantly. When a service is hard to claim credit for, politicians only invest their time if it is highly preferred by voters. Finally, when services are both hard to claim credit for and of low importance to voters, they are placed at the bottom of the politicians' priorities.

To test this theory, we exploit an exogenous variation in Brazilian city council sizes. In 2004, the judiciary reinterpreted the constitution, unexpectedly changing the number of city councilors in Brazilian municipalities. Before the decision, towns could freely choose their legislature size, but in March 2004, the Superior Electoral Court created population thresholds, adding one councilor for each set of 47,619 inhabitants. Around the cutoffs, this decision represents an exogenous change in city council size, allowing us to investigate the welfare effects of increasing the legislatures in Brazil.

Studying the 2005 to 2008 Brazilian mayoral term, when the ruling was in effect, we find improvements in health care and education. Increasing the council size by one legislator lowers infant mortality by 1.99 per one thousand infants born and increases elementary school enrollment by 2.58 children in kindergarten classrooms. However, the additional legislator had no influence on preventive health care and education quality. [] Voters place a high electoral premium on hospital care and mediating school enrollment is relatively easy to claim credit for. In line with our theoretical model, these services should improve with legislative size. On the other hand, preventive health care is harder to claim credit for, and school quality improvements are expensive and pay off only in the long-run. Thus, these services remain unchanged with larger legislatures.

Finally, we present three sets of evidence that the results are consistent with the micro-level representation practices of city councilors. First, we show that the new councilor has access to government resources and uses public office appointments to mediate service provision. They have a 91\% chance of belonging to the mayoral coalition, and they appoint an average of 105 extra bureaucrats for many positions at the mayor's office, having loyal workers inside the municipal bureaucracy. Second, we analyzed 346,553 bills approved by city councilors in municipalities close to the council size thresholds. In line with our theory, we find that councilors prefer to provide targeted goods (72.9\% of all bills), as they satisfy the populations' needs and are easier to credit claim. Finally, we ran an online survey among the councilors during the period, showing that most councilors believe that voters prefer targeted services (68.8\%) to lawmaking (24.6\%) and oversight (30\%).\footnote{Councilors were able to select multiple categories, so the sum can be over 100\%.} We also refute three alternative explanations: increased representation of women and non-white legislators, change in electoral competitiveness, and a larger average of approved legislation by each councilor.

# Legislature Size, Legislative Support, and Welfare
\label{sec:theory}

What is the effect of larger legislatures on public service provision? The most striking feature of a legislature is the fact that decisions are undertaken collectively. Legislators have to propose changes in the status-quo, agree upon what they want to decide, evaluate proposals put forward by mayors, discuss and improve the proposals, and decide which changes they will carry on.

In this sense, legislature size is critical in determining the efficiency of the decision-making process. Upon adding a new city councilor, the most simple change is the increased production capability. Legislative production, analogous to what happens in firms, may increase when adding an extra legislator \citep{crain1979cost, crain1982team, rogers2002free}. For instance, suppose that working full time, politicians can approve five bills a month. Ten politicians can together approve 50 bills, while 11 can pass 55. This increases the number of measures adopted, and if laws enact services to constituencies, then we shall witness an increase in service provision.\footnote{An alternative explanation relates to the Condorcet Jury Theorem. In these models, there is a binary choice, with one of them being ex-ante the best. If legislators access the best choice with a probability higher than 0.5, more legislators will increase the change of selecting the best choice \citep{myerson1998extended}. However, this logic assumes that politicians choose among exogenously provided proposals, which makes sense in the case of a jury, but is somewhat uncommon for legislatures. \citet{auriol2012optimal} compute the optimal size of chambers considering that this is the solution to the interplay between specialization costs and citizens' preferences.}

However, increasing the size of legislatures also carries considerable costs. Larger legislatures can raise the transaction costs \citep{weingast1988industrial}, increase collective action problems \citep{crain1979cost}, and make  forming majorities more costly \citep{crain1982team}. These negative features, together with the fact that legislators may free-ride on each others' proposals, may decrease legislative productivity. For instance, if decisions need a majority or qualified majority to be approved, more legislators create a perverse incentive, increasing the difficulty of approval. Moreover, legislators are pressured to provide targeted services for their constituencies at the expense of the entire polity \citep{Weingastetal1981, PrimoSnyder2008}, and this can raise inefficiencies in expenditure allocation. Additionally, transaction costs within legislatures may increase the difficulty of passing bills \citep{weingast1988industrial, baron1989bargaining}. Therefore, it is unclear whether and how larger legislatures impact lawmaking and service provision.

In our view, to understand the effects of larger legislatures, we need to consider the political motivations behind the legislator's work. While an extra politician may increase the productivity frontier of a legislature, the types of services that will be favored remain unclear. To understand the political motivations, we need a theory that accounts for the cost-benefit calculations performed by politicians.

When deciding which service to prioritize, politicians look into two dimensions of the service provision. First, the competition with other legislators motivates politicians to provide services that they believe voters want, regardless of whether these policies improve long-term welfare. For instance, suppose that there are three services, organized hypothetically based on beliefs about which of these three voters are more likely to reward:\footnote{Note that there is a difference between \textit{what voters want} and what \textit{politicians believe voters want}. Although politicians and brokers mostly access voter's beliefs accurately \citep{FinanSchechter2012, Stokesetal2013}, the crucial signal that a politician gets is vote shares, which are aggregated. It is hard to disentangle which service generated the highest electoral yield for the politician. Therefore, the politician's beliefs play an essential role in the services that they prioritize.} improving a local health clinic (most preferred), building a playground (second most preferred), or increasing the quality of education (least preferable). Politicians seeking recognition will mostly want to improve the health care system, which they believe will most benefit their electoral yields. After getting this done, they will shift efforts toward the playground construction and finally to education quality. Therefore, increasing legislature size will disproportionately increase the provision of services that the politicians believe voters prefer and will reward the most in the polls.

Second, to get reelected, besides providing the services that voters prefer, politicians have to take credit for facilitating provision \citep{fiorina1987personal, gulzar2017politicians, nielsen2017politicians, silva2017clarity}. Typically, the services that are easiest in terms of credit claiming are either providing local public goods, such as improving a neighborhood health clinic, or purely clientelistic and personalistic services \citep{Weingastetal1981, kuschnir2000cotidiano, Stokes2005, nichter2011electoral, Stokesetal2013, luna2014segmented, vieira2015clientelismo, bertholini2018pork}. This explains why clientelism and pork-barrel are persistent in democratic polities. Table \ref{tabcli} summarizes the incentives.

\begin{table}[htp!]
\centering
\caption{Effects of Legislature Size on Service Provision}
\label{tabcli}
\scalebox{1}{%
\begin{tabular}{@{}lcc@{}}
\toprule
& \textbf{Hard for Credit Claim} & \textbf{Easy for Credit Claim} \\ 
\midrule
\multirow{3}{*}{\textbf{Low ranked by voters}} & No changes & None or mild \\
& or deterioration & improvements \\
& (Preventive Health)  & (Honors bills) \\[0.5em]
\multirow{3}{*}{\textbf{High ranked by Voters}} & Mild to low & Mild to strong \\ 
& improvement & improvement \\
& (Infant Mortality)  & (School Enrollment) \\
\bottomrule
\end{tabular}
}
\end{table}

These two dimensions provide a simple yet powerful guide of the politicians' incentives. When voter places a high premium on the provision of a given service, and it is easy to claim credit for the provision, politicians will concentrate their efforts in providing it. The more politicians, the higher the provision of the service. Consider, for instance, constituency service, such as getting a child enrolled at a public school. The voters highly rank service such as this, and the politicians can break the school access directly, getting all the credit for the provision. Therefore, these services tend to increase, up to the point of being over provided.

When a service is hard to credit claim, to be provided, it has to be highly ranked by the voters. Consider services that decrease infant mortality. Although policies in this direction might be harder to be directly associated with one given politician, every politician wants to be known as the ones that diminished infant mortality. The death of a child has devastating effects over a polity, and no politician wants to be associated with it. On the other hand, every parent would be extremely thankful for the politicians that improved health care and saved their child. Moreover, politicians might facilitate access to medication and hospitals, which in turn is easier for credit claiming. Therefore, these services will have anywhere from modest to substantial improvements.

Suppose now that service is secure to credit claim for, but gives low electoral yield. In this case, although the provision can be unquestionably traced back to the legislator, voters care little about the provision. For instance, honors and appraisal legislation are very common in Brazilian municipalities. However, they are perceived by politicians as low electoral yield, but the legislator that proposed the homage usually gets associated with it. These types of legislation increase with legislature size, but their effect on welfare is negligible.

Finally, services that are difficult to credit-claim, or that politicians believe that voters care very little about, are expected to receive little invested effort from politicians. For instance, consider preventive health care. Preventive care refers to health measures, such as prenatal care or vaccination, undertaken to lower the chances or the severity of a disease(s) in the future. However, it is a compounded chance: the voter has to consume the service, but its effectiveness depends on voters getting sick. Nowadays, we are witnessing how hard it is to vaccinate children, despite all the scientific evidence demonstrating its effectiveness. Moreover, rational voters may fail to punish politicians for low investments in preventive public policies, such as natural disasters or climate change mitigation \citep{gailmard2019preventing}. Hence, voters might also not punish politicians for low investments in preventive health care because they might only observe whether a politician properly invested in preventive public policies in cases of emergency. Therefore, we shall expect little to no improvement in these types of services with larger legislatures.

In sum, these considerations suggest that instead of looking for overall positive or negative effects, the effects of legislature size should manifest diversely, conditional on the type of service studied. The most significant changes should be expected in services that voters want and that are easier to claim credit for. Services with only one of these characteristics will be intermediate in terms of their priority and efforts exerted by politicians in their provision and will improve with less intensity. Services hard to credit claim and low ranked by voters will tend to be unaffected or under-provided by lawmakers.

# Background on the Brazilian Case
\label{sec:background}

In 2004, Brazil comprised 5,560 municipalities. According to the Brazilian Constitution, each city must provide healthcare, primary education, transportation, and infrastructure to its citizens. Municipalities have the authority to enact local laws and collect taxes on housing and services. However, their room for fiscal manipulation is limited. On average, municipal taxes account for only 5\% of the local budgets, while mandatory transfers from state and federal governments correspond to the remaining 95\%. This reduces the ability of municipal legislators to effectively influence local spending, what makes improvements in local services dependent only on the efforts of city-level politicians. XXXX

With regards to their political organisation, municipalities have one mayor and one city council. Citizens choose their representatives by direct vote in the same election. Mayors are in charge of organising the provision of public services, as well as proposing laws and amendments to the tax code. Proposals submitted by the mayor are subject to the approval of the city council. Councillors, in turn, have two primary duties. First, they should discuss and vote legislation put forward by the mayors or by their peers. Second, they oversee the public budget and sanction mayors who do not comply with fiscal legislation. Councillors also provide an array of public and personal services for their constituents, such as helping voters access public hospitals, facilitating school enrolment, and even paying their voters' utility bills \citep{nichter2011electoral, AlmeidaFelix2012}.

Until 2004, there was no specific regulation on the size of city councils. The 1988 Brazilian Constitution set only broad guidelines about the number of council seats in each municipality, which allowed cities to determine how many legislators they should have in their local chambers. This led to severe imbalances in the proportion of representatives per citizen across the country. For instance, the Nova Russas municipality had 30,009 inhabitants and 21 councillors, which accounts for one legislator per 1,429 citizens. In contrast, the city of Sorocaba had only 15 councillors for 528,735 inhabitants, that is, one legislator per 35,249 citizens. In 2003, this malapportionment problem gained national visibility when Mira Estrela, a small municipality with only 2,651 residents, reduced its city council from 11 to 9 seats because of fiscal considerations. The change motivated a legal dispute that reached the Brazilian Supreme Court. The Court favoured the city's decision and ruled that the size of every local council should correspond to precise population thresholds.

Following the ruling of the Supreme Court, in March 2004 the Brazilian Electoral Court established a series of population cutoffs for all municipal legislatures. The Court specified that, following the Brazilian Constitution, cities with up to one million residents should have between 9 and 21 legislators. The number of seats was allocated as follows. Each city starts with 9 councillors, then adds one legislator for every 47,619 inhabitants until their councils reach 21 members. This threshold implies that cities with a population between 571,428 and one million should all the same number of legislators, that is, 21 of them. Conversely, cities between one and four million inhabitants should have at least 33 councillors, and this number increases up to 41 members following the previous formula of one additional legislator per 47,619 inhabitants.

This decision makes Brazil the ideal testing ground for our theory. Although an endogenous decision motivated the Electoral Court ruling, the population cutoffs created sharp discontinuities in the distribution of local council seats. That is, cities close to the cutoffs had very similar characteristics, but those which were just above the threshold gained a new legislator. Moreover, cities could not self-select into any group, as their population estimates were calculated using the 2003 projections by the Brazilian Census Bureau (IBGE). This change in council size also happened only seven months before the election, making it impossible for candidates to adjust their service provision strategies for the 2004 election. Therefore, the ruling allows us to study the effect of larger legislatures on public service provision during the 2005-2008 term while holding all else constant.

\section{Empirical Strategy}
\label{sec:empstrat}

\subsection{Methodology}
\label{sub:methods}

We employ a regression discontinuity design (RDD) using the population thresholds established by the 2004 Superior Electoral Court resolution as treatment indicators. Figure \ref{fig:runningvarplot} displays the distribution of municipalities within each city council size. These population thresholds remained in effect until 2009, when Congress amended the Brazilian Constitution. This study covers the period between 2005 and 2008, which constitutes the full mayoral and city-council term following the 2004 Brazilian elections.

\vspace{.5cm}

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrSeats.pdf}}
      \caption{Distribution of Municipalities by Population and City Council Size}
      \bigskip
      \label{fig:runningvarplot}
    \end{minipage}
  \end{center}
\end{figure}

Our identification strategy relies on three assumptions. First, we assume that no municipality self-selected into each side of the discontinuity. Second, as we run a sharp RDD, we also assume that council size increases precisely as the law mandates. Third, our design assumes that the pre-treatment variables, collected before the 2003 Supreme Court decision, were not affected by the 2004 ruling on council size. In the online appendix, we test these assumptions by building an estimator that balances the local average treatment effects (LATE). Our estimate is an extension of RDD and uses covariates to balance the multiple cutoff differences. Additionally, we propose a placebo test in which we run the same models with fake cutoffs around the original thresholds. Our balance and placebo tests indicate that the assumptions underlying the analyses are indeed met.

% Subsection: Variables
\subsection{Variables and Data Sources}
\label{sub:sources}

We use four groups of city-level variables in our models. The first group includes pre-treatment control variables that were not affected by the 2004 council size resolution. We add them to the models to improve the balance between treated and non-treated units. The covariates are: 1) the number of council seats in the previous term; 2) city population; 3) city GDP; 4) the proportion of low-income families in each municipality. The data come from the Superior Electoral Court (Tribunal Superior Eleitoral--TSE) and the 2000 Brazilian census.

We employ a second set of variables to quantify social welfare. They are our outcomes of interest. Our main focus here is on the impact of legislature size on education and healthcare, which are the two most important public services the municipal government should provide to citizens. We measure access to education with the average enrolment in primary (K--4) and secondary (5--8) public schools. We assess education quality with the Education Development Index (\'Indice de Desenvolvimento da Educa\c{c}\~{a}o B\'asica--IDEB), which the Ministry of Education has issued biannually since 2007. The index is a weighted average of student scores in Portuguese and Mathematics (0--10) multiplied by the harmonic mean of public school promotion rates in a given year (0--100). To test the effect of the 2004 ruling on healthcare, we mapped the coverage of the Family Health Programme, a local-level primary care policy, and the proportion of pregnant women who attended more than six pre-natal consultations. We also gather data on post-neonatal mortality\footnote{Post-neonatal mortality rate is the probability of dying between 28 days and one year of life, expressed per 1,000 live births.} to assess healthcare quality. The source of all variables is the Brazilian Ministry of Health Data Centre (DataSUS).

Next, we look into municipal data, city councillors' characteristics, approved legislation, and an online survey with 174 former city councillors that served during the 2005--2008 term to test our proposed micro-level mechanisms\footnote{We also analysed 108 structured interviews conducted by \citet{lopez2017legisladores} at the Brazilian Economics Planning Institute (IPEA) in 2009. The authors asked councillors about their daily work. The interviews reinforced the idea that councillors see private goods provision as more electorally profitable than formal lawmaking or executive policy oversight.}. The municipal data contains: 1) the number of councillors belonging to the pre-electoral mayoral coalition; 2) the councillor's gender and race; 3) the number of mayor-appointed, councillor-appointed, and career civil servants. All variables come from the Superior Electoral Court and the Brazilian Institute for Geography and Statistics.

Lastly, we also collect 346,553 bills from cities whose populations lie within 10 thousand inhabitants from the 2004 population thresholds. We selected 64 out of 202 municipalities whose voting records were available online. We evaluate information regarding proposal types, discriminating between local and municipal public goods, oversight, and other legislative activity. While local public goods consist of services targeting personal, group, or neighbourhood levels, municipal public goods comprise laws and policies covering the entire municipality. Examples of the first are investing in a given public health clinic, requesting school bureaucracy to accommodate an extra child, and renovating sewage and fixing potholes on a given street\footnote{Our theory does not differentiate between clientelism and service provision, as it is hard to disentangle legislator's intentions. On the one hand, a voter may request a particular service, such as fixing a pothole. Attending this request can be interpreted as a clientelistic practice, despite their non-excludable benefits to the adjoining neighborhood. On the other hand, upon request, facilitating hospital admission is a very particularized service, thus likely to fall under clientelistic logic. Saying this is vote-buying can be imprecise, as service provision might simply be a way of signaling responsiveness to the electorate's demands and efficacy. \citet{kuschnir2000cotidiano}'s qualitative work shows the Silveira Family in Rio de Janeiro aided the community they represented regardless of political preference. As a result, when one of the family members ran in an election, he had the highest vote share ever seen in Rio de Janeiro.}. As for the latter, examples are to ameliorate education by capacitating public teachers, and to raise public health care standards through city-wide vaccination campaigns. Oversight bills are accountability and transparency mechanisms meant to keep public services undertaken by the bureaucracy in check. Other legislation comprises bills that do not fit in the previous categories. Examples are changes in street names, motions to honour citizens or groups, and legislative and internal city council procedures.

Together, this evidence provides a clear picture of representation patterns in Brazil, from municipal welfare consequences to their micro-level mechanisms. Summary statistics follow in the online supplemental materials.

# Results

% Session: Results
\section{Results}
\label{sec:outcomes}

\subsection{The Effect of Legislature Size on Service Provision}
\label{sub:effects}

We study the impact of legislatures on two services: education and health care. We collect eight indicators: four in education, and four in health care.

\begin{sidewaystable}[!htbp] \centering 
  \caption{Public Service Outcomes} 
  \label{tab:outcomes} 
\scalebox{0.9}{
\begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c c c c c }
\toprule
& \multicolumn{4}{c}{\textbf{Education Outcomes}} & \multicolumn{4}{c}{\textbf{Health Care Outcomes}}  \\ \cline{2-5} \cline{6-9}
  & \multicolumn{1}{c}{\small{(1)}} & 
 \multicolumn{1}{c}{\small{(2)}} & 
 \multicolumn{1}{c}{\small{(3)}} & 
 \multicolumn{1}{c}{\small{(4)}} & 
 \multicolumn{1}{c}{\small{(5)}} & 
 \multicolumn{1}{c}{\small{(6)}} & 
 \multicolumn{1}{c}{\small{(7)}} & 
 \multicolumn{1}{c}{\small{(8)}} \\
 & \multicolumn{1}{c}{\small{Average}} & 
 \multicolumn{1}{c}{\small{Average}} & 
 \multicolumn{1}{c}{\small{Elem. School}} & 
 \multicolumn{1}{c}{\small{Middle School}} &
\multicolumn{1}{c}{\small{Infant}} & 
 \multicolumn{1}{c}{\small{Post-Natal}} & 
 \multicolumn{1}{c}{\small{Cov. Family}} & 
 \multicolumn{1}{c}{\small{Pr. Born w. 6+}} \\ 
 & \multicolumn{1}{c}{\small{Enroll. K-4}} & 
 \multicolumn{1}{c}{\small{Enroll. 5-8}} & 
 \multicolumn{1}{c}{\small{Quality Index}} & 
 \multicolumn{1}{c}{\small{Quality Index}} &
 \multicolumn{1}{c}{\small{Mortality}} & 
 \multicolumn{1}{c}{\small{Mort. Rate}} & 
 \multicolumn{1}{c}{\small{Health Program}} & 
 \multicolumn{1}{c}{\small{Pre-Natal Consult.}}\\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-7} \cline{8-8} \cline{9-9}
 LATE & 2.58$^{***}$ & -0.01 & -0.04 & -0.11 & -1.99$^{**}$ & -0.90$^{*}$ & -1.67 & -4.23 \\ 
    & (0.81) & (1.07) & (0.13) & (0.11) & (0.78) & (0.48) & (2.09) & (4.01) \\
  \hdashline \\[-1.8ex] 
 N Left & \multicolumn{1}{c}{10156} & \multicolumn{1}{c}{7306} & \multicolumn{1}{c}{8597} & \multicolumn{1}{c}{5037} &
 \multicolumn{1}{c}{12299} & \multicolumn{1}{c}{5441} & \multicolumn{1}{c}{19280} & \multicolumn{1}{c}{15548} \\ 
 N Right & \multicolumn{1}{c}{686} & \multicolumn{1}{c}{581} & \multicolumn{1}{c}{670} & \multicolumn{1}{c}{529} & \multicolumn{1}{c}{1030} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{1297} & \multicolumn{1}{c}{1030} \\ 
 Eff N Left & \multicolumn{1}{c}{196} & \multicolumn{1}{c}{475} & \multicolumn{1}{c}{387} & \multicolumn{1}{c}{279} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{314} & \multicolumn{1}{c}{281} & \multicolumn{1}{c}{615} \\ 
 Eff N Right & \multicolumn{1}{c}{202} & \multicolumn{1}{c}{312} & \multicolumn{1}{c}{283} & \multicolumn{1}{c}{195} & \multicolumn{1}{c}{390} & \multicolumn{1}{c}{242} & \multicolumn{1}{c}{301} & \multicolumn{1}{c}{438} \\ 
 BW Loc Poly & 5.132 & 11.208 & 8.724 & 7.824 
 7.720 & 7.183 & 4.185 & 8.891 \\ 
 BW Bias & 10.615 & 16.694 & 15.186 & 13.714 
 12.289 & 10.726 & 8.310 & 15.007 \\ 
\midrule 
 & \multicolumn{4}{c}{\textbf{Education Outcomes -- Placebo Cutoffs}} & \multicolumn{4}{c}{\textbf{Health Care Outcomes -- Placebo Cutoffs}}\\ \cline{2-5} \cline{6-9}
  & \multicolumn{1}{c}{\small{(9)}} & 
 \multicolumn{1}{c}{\small{(10)}} & 
 \multicolumn{1}{c}{\small{(11)}} & 
 \multicolumn{1}{c}{\small{(12)}} & 
 \multicolumn{1}{c}{\small{(13)}} & 
 \multicolumn{1}{c}{\small{(14)}} & 
 \multicolumn{1}{c}{\small{(15)}} & 
 \multicolumn{1}{c}{\small{(16)}} \\
 & \multicolumn{1}{c}{\small{Average}} & 
 \multicolumn{1}{c}{\small{Average}} & 
 \multicolumn{1}{c}{\small{Elem. School}} & 
 \multicolumn{1}{c}{\small{Middle School}}&
 \multicolumn{1}{c}{\small{Infant}} & 
 \multicolumn{1}{c}{\small{Post-Natal}} & 
 \multicolumn{1}{c}{\small{Cov. Family}} & 
 \multicolumn{1}{c}{\small{Pr. Born w. 6+}}\\ 
 & \multicolumn{1}{c}{\small{Enroll. K-4}} & 
 \multicolumn{1}{c}{\small{Enroll. 5-8}} & 
 \multicolumn{1}{c}{\small{Quality Index}} & 
 \multicolumn{1}{c}{\small{Quality Index}} &
 \multicolumn{1}{c}{\small{Mortality}} & 
 \multicolumn{1}{c}{\small{Mort. Rate}} & 
 \multicolumn{1}{c}{\small{Health Program}} & 
 \multicolumn{1}{c}{\small{Pre-Natal Consult.}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-7} \cline{8-8} \cline{9-9}
  LATE & 0.45 & 0.97 & -0.10 & -0.12
  & -1.14 & -0.25 & 1.85 & -2.22 \\ 
  & (0.61) & (0.98) & (0.11) & (0.09)
  & (1.05) & (0.65) & (1.25) & (2.92) \\ 
  \hdashline \\[-1.8ex]   
 N Left & \multicolumn{1}{c}{9040} & \multicolumn{1}{c}{6350} & \multicolumn{1}{c}{7529} & \multicolumn{1}{c}{4243} & \multicolumn{1}{c}{10614} & \multicolumn{1}{c}{4449} & \multicolumn{1}{c}{17198} & \multicolumn{1}{c}{13861} \\ 
 N Right & \multicolumn{1}{c}{1802} & \multicolumn{1}{c}{1537} & \multicolumn{1}{c}{1738} & \multicolumn{1}{c}{1323} & \multicolumn{1}{c}{2715} & \multicolumn{1}{c}{1664} & \multicolumn{1}{c}{3379} & \multicolumn{1}{c}{2717} \\ 
 Eff N Left & \multicolumn{1}{c}{1186} & \multicolumn{1}{c}{1138} & \multicolumn{1}{c}{1202} & \multicolumn{1}{c}{931} & \multicolumn{1}{c}{1213} & \multicolumn{1}{c}{775} & \multicolumn{1}{c}{2575} & \multicolumn{1}{c}{1575} \\ 
 Eff N Right & \multicolumn{1}{c}{724} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{734} & \multicolumn{1}{c}{580} & \multicolumn{1}{c}{890} & \multicolumn{1}{c}{557} & \multicolumn{1}{c}{1483} & \multicolumn{1}{c}{1004} \\ 
 BW Loc Poly & 6.325 & 6.975 & 6.686 & 7.198 
 & 4.840 & 5.360 & 6.999 & 5.796 \\ 
 BW Bias & 9.860 & 12.598 & 10.029 & 11.004 
 & 7.268 & 7.943 & 11.213 & 9.559 \\ 
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1. RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel. Robust standard errors, clustered at the municipal level, are in parentheses. The control variables are: population, GDP per capita, number of seats in 2000, year, and a dummy for the northeast region. \textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated). \textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth. \textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE). \textit{BW Bias} is the bandwidth used to compute the standard errors.
\end{tablenotes}
\end{threeparttable}}
\end{sidewaystable}

XXXX Rewrite all this!

Each of the outcomes is further divided into two groups. In the first group, we include services that are easier to provide or credit claim, or both. These services are preferred by the electorate and have an intensive advertising effect for the councillor. In this category, we have school enrollment and infant mortality. In the second group are services either considered less critical by voters or harder to credit claim. They are harder to translate into votes or to target and advertise. In our models, we use preventive health care and quality of education to illustrate. According to our theory, we expect that increasing legislature size has a positive effect on desirable services that are easy to target.

Table \ref{tab:outcomes} presents the results for education and health care outcomes. The data shows that, with the addition of a city councillor, enrollment in elementary schools increased by 2.58 children on average per school. This represents a change of around 0.20 standard deviations. From 5th to 8th grades, council size has no effect on school enrollment. Due to high dropout rates at this stage, spots for extra students remain vacant. Results are insignificant for quality indicators.\footnote{As education quality improves in the medium to long term, we look into the 2015 education quality index in the Online Supplemental Materials. Effects are null, pointing to no delayed benefits.} As expected, the placebo regressions are also insignificant.

Although Brazil achieved universal elementary school enrolment, enrolling a child in public school is particularly difficult in the early years. At the same time, taking care of small children is a considerable burden for poor households. Citizens thus reach out to councillors who can pressure school's bureaucracy to accommodate an extra child. Such an effort has virtually no cost to the politician, and grants her direct recognition, benefiting her electorally.

Consequences for infant mortality rates are also substantial. 1.99 deaths per 1,000 children born are prevented with every extra legislator. This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations. Moreover, post-neonatal mortality decreases by 0.90 casualties per 1,000 births, which improves health care by 0.14 standard deviations. As expected, placebo regressions were statistically insignificant. However, the Family Health Program coverage and the proportion of children born with more than six prenatal consultations seems to decrease. This apparent inconsistency with the other indicators will be discussed further in the text.

% Sub-Section: Mechanisms
\subsection{Applying the Mechanism and Testing Hypotheses}
\label{sub:mechanism}

We test our hypotheses in Table \ref{tab:mechanism-reg} dividing the municipal outcome data in two panels. In Panel A, we counter alternative explanations for our mechanism. In Panel B, we present evidence that corroborates our arguments.  
\begin{table}[!htbp] \centering 
  \caption{Mechanism Regressions -- Aggregated Municipal Level Outcomes} 
  \label{tab:mechanism-reg} 
\scalebox{0.9}{
\begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
\toprule
& \multicolumn{4}{c}{\textbf{Panel A: Representation, Competition, and Legislation Approval}} \\ \cline{2-5}
 & \multicolumn{1}{c}{\small{(1)}} 
 & \multicolumn{1}{c}{\small{(2)}} 
 & \multicolumn{1}{c}{\small{(3)}} 
 & \multicolumn{1}{c}{\small{(4)}} \\
 & \multicolumn{1}{c}{\small{Num. Female}} & 
 \multicolumn{1}{c}{\small{Num. Non-white}} &
  \multicolumn{1}{c}{\small{Candidates}} & 
  \multicolumn{1}{c}{\small{Prop. Laws}} \\ 
   & \multicolumn{1}{c}{\small{councillors}} & 
 \multicolumn{1}{c}{\small{councillors}} &
  \multicolumn{1}{c}{\small{Per Seat}} & 
  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
 LATE & 0.22 & 0.60 & -0.19 & -0.02 \\ 
  & (0.38) & (0.85) & (1.11) & (0.08) \\ 
  \hdashline \\[-1.8ex] 
 N Left & \multicolumn{1}{c}{5183} & \multicolumn{1}{c}{239} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{3424} \\ 
N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{158} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{270} \\ 
Eff N Left & \multicolumn{1}{c}{194} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{179} & \multicolumn{1}{c}{227} \\ 
Eff N Right & \multicolumn{1}{c}{144} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{132} & \multicolumn{1}{c}{142} \\ 
BW Loc Poly & 8.564 & 2.954 & 8.126 & 11.080 \\ 
BW Bias & 13.569 & 4.917 & 12.049 & 16.921 \\[1.0ex] 
\midrule 
& \multicolumn{4}{c}{\textbf{Panel B: Access to Resources and Patronage}} \\ \cline{2-5}
 & \multicolumn{1}{c}{\small{(5)}} 
 & \multicolumn{1}{c}{\small{(6)}} 
 & \multicolumn{1}{c}{\small{(7)}} 
 & \multicolumn{1}{c}{\small{(8)}} \\
 & \multicolumn{1}{c}{\small{Mayoral}} & 
 \multicolumn{1}{c}{\small{Num. Politically}} & 
 \multicolumn{1}{c}{\small{Num. Career}} & 
 \multicolumn{1}{c}{\small{Num. councillor}} \\
 & \multicolumn{1}{c}{\small{Coalition Size}} & 
 \multicolumn{1}{c}{\small{Appointed Empl.}} & 
 \multicolumn{1}{c}{\small{Bureaucrats}} & 
 \multicolumn{1}{c}{\small{Assistants}} \\[1ex]  \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
 LATE & 0.91$^{*}$ & 105.09$^{*}$ & 71.57 & 2.09 \\ 
  & (0.50) & (62.12) & (218.12) & (4.37) \\ 
    \hdashline \\[-1.8ex] 
 N Left & \multicolumn{1}{c}{5168} & \multicolumn{1}{c}{15536} & \multicolumn{1}{c}{15531} & \multicolumn{1}{c}{5179} \\ 
N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1028} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{344} \\ 
Eff N Left & \multicolumn{1}{c}{240} & \multicolumn{1}{c}{351} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{99} \\ 
Eff N Right & \multicolumn{1}{c}{161} & \multicolumn{1}{c}{334} & \multicolumn{1}{c}{388} & \multicolumn{1}{c}{101} \\ 
BW Loc Poly & 9.906 & 6.019 & 7.695 & 5.134 \\ 
BW Bias & 15.846 & 10.170 & 11.780 & 8.902 \\ 
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1. RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel. Robust standard errors, clustered at the municipal level, in parentheses. Controls: population; GDP per capita; number of seats in 2000; year; and dummy for northeast region. \textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated). \textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth. \textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE). \textit{BW Bias} is the Bandwidth used to compute the standard errors.
\end{tablenotes}
\end{threeparttable}}
\end{table}

Panel A (Table \ref{mechreg1}) tests perspectives proposed by the literature. One of them is that better representation of under-served groups could broaden health care and education provision \citep{pande2003can, chattopadhyay2004women, chin2011redistributive, duflo2012women}. However, columns (1) and (2) show that neither gender nor representation of non-white legislators significantly improves public service provision for minorities. Alternatively, enhanced competition is also thought to improve responsiveness, alleviating the principal-agent problem between voters and politicians. Yet, we show that competition (3) or bills approval (4) remain unchanged when we increase council size.

Panel B (Table \ref{mechreg1}) illustrates our mechanism. Column (5) shows that there is a 91\% chance of the extra legislator belonging to the mayoral coalition. This suggests that these additions will likely enhance welfare effects due to increased governability\footnote{It is possible that the new coalition councillor facilitates mayor's lawmaking process. Indeed, we might actually be estimating the effects of mayors on policy-making. Their relationship with the central government is fundamental for service provision \citep{bueno2018bypassing}. In the Online Supplemental Materials, we investigate whether mayoral and council party composition vary across cities, and find that it remains unchanged around the thresholds.}. Column (6) demonstrates that adding one councillor increases the number of appointed employees by 105 with a standard deviation of over 0.30. This attests councillors' strong ties with the administration and facilitates service provision.

Additionally, we consider the number of career employees\footnote{Career bureaucrats have to undergo rigorous selection that prevents them from being fired for political reasons.} and find that improvements in state capacity and welfare are not consequences of bureaucratic agency. Column (7) points that the number of career bureaucrats does not significantly explain access to resources. Finally, adding a legislator has a null effect on the average number of appointed cabinet employees (column (8)).

\subsection{Disaggregating Data on Approved Legislation and City councillor Survey}
\label{sub:survey}

To evidence our mechanism's operation in city councillors' ordinary legislative activities, we examine two datasets: one composed by the approved bills, and the other by answers to the online survey. Figure \ref{LEGAPPR} showcases the results of the analysis of approved legislation.

\begin{figure}[htb!]
  \begin{center}
  \caption{Legislation Approved in Municipalities Closer to the City Council Thresholds}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/lawsApproved.pdf}}
      \bigskip
      \label{LEGAPPR}
    \end{minipage}
  \end{center}
\end{figure}

As previously argued, lawmakers decide on service provision based on the feasibility of credit-claiming. The top-two preferred legislation categories share this feature. In addition,\textit{local public goods} carries high electoral yield, which explains it ranking above \textit{others}. Graph 2A (Figure \ref{LEGAPPR}) presents the frequency of approved proposals. The overwhelming majority belongs to \textit{local public goods} (72.9\%), followed by \textit{others} (17.4\%).\footnote{Note that the sum is below 100\%. This is due to the SVM algorithm classifying around 3.5\% of laws as belonging to none of the categories above. For more information, see \citet{collingwood2013rtexttools}.} Graph 2B (Figure \ref{LEGAPPR}) depicts the average number of bills per legislator and, evidently, reflects the same pattern: \textit{local public goods} also amount to the highest, at 290.7 (S.E. 56.95), and \textit{others} follows with 77.6 (S.E. 15.50). Measuring the production of each representative builds on the idea that adding legislators – who provide more services – generates greater welfare.

Health care and education services, which compose 11.1\% of total approved bills (44.3 per legislator), are mainly addressed through \textit{local public goods}. According to Graph 2C (Figure \ref{LEGAPPR}), they represent 80.6\% of proposals in these sectors, followed by \textit{municipal public goods} (7.8\%). Productivity follows the same pattern (Graph 2D, Figure \ref{LEGAPPR}). Legislators propose 36.4 (in absolute terms) of the first, and 4.2 of the latter. Therefore, not only in general, but also specifically for education and health care, \textit{local public goods} are the preferred choice of councillors in Brazilian municipal chambers.

In our online survey with former city councillors, we asked about their legislative activity, the amount of votes it yielded, and how they negotiated with the mayor. While most results are in the Online Supplemental Materials, Figure \ref{survelec} displays the services councillors believe to generate the highest electoral results.

\begin{figure}[htb!]
  \begin{center}
  \caption{Electoral Attractiveness of Councilor's Activities and Practices}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/elecYieldJobsCouncilors.pdf}}
      \bigskip
      \label{survelec}
    \end{minipage}
  \end{center}
\end{figure}

The service that best secures votes, according to 84.3\% of the interviewed, is access to hospital facilities; to 56.0\%, it is school admission; and to 71.0\%, it is access to medication. 82.6\% of respondents confirm that local public goods are electorally beneficial, and 50.2\% indicated that, namely, fixing potholes on public roads resulting in some or many votes. Second in their evaluation is public school quality oversight (34.7\%), followed by  reported public construction oversight (25.3\%). These last two services, despite being preferred by voters and easy to credit-claim, require more investment. Coordination costs related to mayor negotiation and bureaucratic mediation also force them to recur to less demanding options, for instance, honors legislation. This is likely the reason why more approved bills fall under the \textit{others} label than under \textit{oversight}.

\section{Discussion}

%CLIENTELISM

Although city councillors should have governing advantages for being the closest representatives to citizens, the literature often presents them as inefficient and clientelistic \citep{Castroetal2009, AlmeidaFelix2012, leal2012coronelismo}. This proximity to the community results in better informed decision-making and accountability. However, it also creates perverse incentives to corruption, patronage and overprovision of electorally beneficial services. Poor management could be driven by private interests, or by limitations restraining governability. It is unrealistic to think that all politicians have free rein to approve and implement policies at their will. Bureaucracy and strong executives balance the assembly, who, in turn, develops strategies to enforce its will.

A councillor can only provide services which she can control or influence. In a Brazilian municipality, mayors directly control budget and staff allocation. Consequently, councillors must side with the mayor to participate in policy-making. Efforts towards establishing alliances start in the pre-electoral coalition period. If a candidate is part of the mayoral coalition, she credibly signals being able to deliver her platform promises. As the Electoral Justice allocates seats according to vote shares (D'Hondt method), pre-electoral coalitions have advantages since extremely popular candidates' votes thrust smaller candidates into office. Pre-electoral coalitions become crucial for mayors' governability after the election.

Bureaucrats also mediate most of the access to resources, and may filter councillor's demands, either for or against them. To influence service provision, city councillors sometimes recur to patronage, which is a strategy mobilized to ensure collaborative administrations. It is characterized by the employment of bureaucrats attached to an incumbent's personal figure. These politically-appointed employees have incentives to support the councillor's interests unconditionally \citep{Robinson2013}. Loyalty of the administration – through patronage or not – thus appears as fundamental in the political game.

Another limitation to representative agency is based on perception, as politicians imperfectly observe voters' preferences. The online survey provides us with clues on how councillor's beliefs could translate into their policy choices. \textit{Local public goods} is the preferred type of legislation across sources. We assembled five specific welfare-improving policies into the \textit{local public goods} category (Figure \ref{survelec}), namely \textit{hospital admission aid} (84.3\% answered it gives some to many votes), \textit{other local public goods} (82.6\%), \textit{access to medication} (71.0\%), \textit{school admission aid} (56.0\%), and \textit{street repairs} (50.2\%). They all pushed down remaining categories. \textit{School quality oversight} places second at overwhelming distance (34.7\%). In the approved legislation dataset (Graph 2A, Figure \ref{LEGAPPR}), \textit{local public goods} is equally favoured (72.9\%), followed by \textit{others} legislation (17.4\%), which we know to represent mostly honors bills.

If councillors aim for reelection, why do approved legislation frequencies not reflect answers to the survey? Comparison points to an inconsistency that circles back to the aforementioned limitations. Since negative exposure of executive and bureaucratic underachievement tensions political coalitions, and is less attractive to voters than policy-making. Logically, councillors will dedicate more to \textit{local public goods} than to \textit{oversight}. This does not attest their lack of competence, efficiency or honesty, but rather evidences the hardship of coordinating efforts and collectively making decisions under diverging goals and interests.

# Conclusion
\label{sec:conclusion}

In this paper, we argue that political motivation determines the services that gain traction with larger legislatures. Councillors, guided by reelection, invest in policies they believe voters want and for which credit-claiming is feasible. Consequently, many essential welfare services are underprovided, giving place to locally-targeted policies. For instance, our theory explains why patterns of poor education persist in developing countries. In 2000, among the 32 countries that participated in the OECD's \textit{Programme for International Student Assessment} (PISA), Brazil ranked last. Between 2006 and 2015, there were virtually no improvements in scores. Counterintuitively, school enrolment was close to 99\% since 2010. Although desired by voters, ameliorating education quality is difficult to trace back to specific politicians. In this logic, they have incentives to target education through tangible yet low-reaching measures, such as raising the amount of children attending schools.

We run a RDD to capture the effect of adding representatives to a municipal council. We focus on the effects of exogenously imposing thresholds to chamber sizes. We compare cities with similar populations, but located on different sides of the cutoff. We also collect data on the approved legislation during the 2005-2008 term, and perform an online survey with former representatives. Empirically, larger municipal chambers prevents death in infancy and stimulate educational enrollment. These changes do not, however, coincide with improvements in education and health care quality. We find that councillors prefer investing in local public goods, and they access resources via attachment to mayors and through bureaucratic mediation.

Our study has implications for policy-making and for the literature on distributive politics. First, we provide tools to predict welfare effects of changing the number of seats in municipal councils. We also contribute to comprehend the strategies politicians may use to adapt to these modifications. For example, an extra legislator will hardly add diversity to council activities, since there is a 91\% probability she will integrate the mayoral coalition. As for academia, we offer a simple theory to understand the underprovision of essential public goods as education and health care. We add complexity to the common belief that politicians in developing countries are purely clientelistic, inefficient or dishonest. We conclude that the political architecture of the assembly floor creates perverse incentives.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

### 2021-08-20 article/article.Rmd
editing and adding old info main paper

@@
 title:  |
-        | Legislature Size and Welfare:
-        | Evidence from Brazil
+        | Electoral Systems, Competition, and Incentives for Corruption
 author: 
-  - Gabriel Cepaluni[^gabriel]
-  - Danilo Freire[^danilo]
   - Umberto Mignozzetti[^umberto]
 date: \today
-thanks: "We thank Cedric Antunes, Victor Araujo, Eric Arias, Taylor Boas, Natalia Bueno, Andrea Freitas, Saad Gulzar, James Mahon, Lucas Novaes, Nelson Ruiz, Catarina Roman, David Skarbek, and Denis Stukal for their valuable comments.
-We also thank the participants of seminars and conferences at CEPESP, CUNY, INSPER, IPSA, LACEA, LASA, MPSA, Notre Dame, NYU, PUC Chile, SPSA, and Uppsala.
-We gratefully acknowledge the financial support of the São Paulo Research Foundation (FAPESP), grant number 2017/07290-5.
-All materials required to replicate this study are available at <https://github.com/umbertomig/legislature-size-welfare>."
-abstract: "What is the effect of legislature size on social welfare?
-While the literature suggests that increasing the number of legislators broadens political representation and raises government expenditures, its implications for public service provision remain understudied.
-In this paper, we exploit exogenous changes in city-council size in Brazil and show that adding a legislator increases education and healthcare indicators.
-XXXX Education quality and preventive health care remain unaffected, but primary school enrolment and infant mortality significantly improve.
-To investigate the mechanism, we surveyed former councillors and analysed 346,553 bills proposed between 2005 and 2008.
-This analysis shows that politicians prefer to provide private and targeted goods instead of public goods.
-This paper has implications for the design of legislative institutions."
+thanks: "I thank Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Adam Przeworski, Howard Rosenthal, Renard Sexton, Denis Stukal, and Scott Tyson for their comments.
+I also thank participants at APSA, MPSA, NYU PE Seminar, and SPSA.
+All materials required to replicate this study are available at <https://github.com/umbertomig/electoral-systems-corruption>."
+abstract: "This is my abstract."
 abstractspacing: double
-keywords: Legislature size; Legislative politics; Public goods provision; Regression discontinuity design; Brazil
-jelcodes: HXXXX
+keywords: Political Corruption; District Magnitude; Single-member districts; Multi-member districts; Welfare; Brazil
+#jelcodes: HXXXX
 fontsize: 11pt
@@
 
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
-
-[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
-
 \newpage
@@
 
-Legislative institutions are crucial for welfare and service provision in democratic countries.
-Historically, the division of power and the birth of a representative government placed the legislatures at the center of popular consent \citep{north1989constitutions}.
-In modern democracies, most countries have assemblies at all levels of government.
-These institutions affect the information and quality of legislation \citep{krehbiel2010information}, check and veto the other political powers \citep{tsebelis2002veto}, and influence policymaking \citep{weingast1988industrial, north1989constitutions, auriol2012optimal}.
-Moreover, they also determine taxation, government expenditure \citep{Weingastetal1981, PrimoSnyder2008, stasavage2011states}, and oversee service provision \citep{mccubbins1984congressional, poulsen2018political}.
+Here goes the intro.
 
-Regardless of differences in electoral rules, social composition, and procedures, all legislatures share one feature: more than one representative composes them.
-Legislature size relates to collective action problems \citep{crain1979cost, rogers2002free}, government spending \citep{Weingastetal1981, PrimoSnyder2008}, and representation \citep{allenrepresentation}, but how these components affect welfare remain understudied.
-On the one hand, enlarged legislatures increase government spending and lawmaking, and this may improve some services \citep{Weingastetal1981, }.
-On the other hand, adding a legislator can increase the number of veto players and broaden the collective action problems, hindering service provision.
-Therefore, larger legislatures have an ambiguous effect on welfare, and XXXX.
-
-In this paper, we propose a theory of legislature size and welfare that takes into account two crucial components: the XXXX and the partisan affiliation of the legislators.
-
-XXXX Umberto: Parei aqui.
-
-This paper fills this gap by studying the effects of legislature size on service provision.
-Assuming that politicians want to further their careers, we argue that two variables determine service provision: the perceived importance of the service by voters and the politician's capacity to claim credit for its provision.
-Politicians perform a simple cost-benefit analysis: if providing a service results in high electoral yield, and it is easy to claim credit for, politicians will produce this service abundantly.
-When a service is hard to claim credit for, politicians only invest their time if it is highly preferred by voters.
-Finally, when services are both hard to claim credit for and of low importance to voters, they are placed at the bottom of the politicians' priorities.
-
-To test this theory, we exploit an exogenous variation in Brazilian city council sizes.
-In 2004, the judiciary reinterpreted the constitution, unexpectedly changing the number of city councilors in Brazilian municipalities.
-Before the decision, towns could freely choose their legislature size, but in March 2004, the Superior Electoral Court created population thresholds, adding one councilor for each set of 47,619 inhabitants.
-Around the cutoffs, this decision represents an exogenous change in city council size, allowing us to investigate the welfare effects of increasing the legislatures in Brazil.
-
-Studying the 2005 to 2008 Brazilian mayoral term, when the ruling was in effect, we find improvements in health care and education.
-Increasing the council size by one legislator lowers infant mortality by 1.99 per one thousand infants born and increases elementary school enrollment by 2.58 children in kindergarten classrooms.
-However, the additional legislator had no influence on preventive health care and education quality.
-[] Voters place a high electoral premium on hospital care and mediating school enrollment is relatively easy to claim credit for.
-In line with our theoretical model, these services should improve with legislative size.
-On the other hand, preventive health care is harder to claim credit for, and school quality improvements are expensive and pay off only in the long-run.
-Thus, these services remain unchanged with larger legislatures.
-
-Finally, we present three sets of evidence that the results are consistent with the micro-level representation practices of city councilors.
-First, we show that the new councilor has access to government resources and uses public office appointments to mediate service provision.
-They have a 91\% chance of belonging to the mayoral coalition, and they appoint an average of 105 extra bureaucrats for many positions at the mayor's office, having loyal workers inside the municipal bureaucracy.
-Second, we analyzed 346,553 bills approved by city councilors in municipalities close to the council size thresholds.
-In line with our theory, we find that councilors prefer to provide targeted goods (72.9\% of all bills), as they satisfy the populations' needs and are easier to credit claim.
-Finally, we ran an online survey among the councilors during the period, showing that most councilors believe that voters prefer targeted services (68.8\%) to lawmaking (24.6\%) and oversight (30\%).\footnote{Councilors were able to select multiple categories, so the sum can be over 100\%.} We also refute three alternative explanations: increased representation of women and non-white legislators, change in electoral competitiveness, and a larger average of approved legislation by each councilor.
-
-# Legislature Size, Legislative Support, and Welfare
+# Theory
 \label{sec:theory}
 
-What is the effect of larger legislatures on public service provision?
-The most striking feature of a legislature is the fact that decisions are undertaken collectively.
-Legislators have to propose changes in the status-quo, agree upon what they want to decide, evaluate proposals put forward by mayors, discuss and improve the proposals, and decide which changes they will carry on.
-
-In this sense, legislature size is critical in determining the efficiency of the decision-making process.
-Upon adding a new city councilor, the most simple change is the increased production capability.
-Legislative production, analogous to what happens in firms, may increase when adding an extra legislator \citep{crain1979cost, crain1982team, rogers2002free}.
-For instance, suppose that working full time, politicians can approve five bills a month.
-Ten politicians can together approve 50 bills, while 11 can pass 55.
-This increases the number of measures adopted, and if laws enact services to constituencies, then we shall witness an increase in service provision.\footnote{An alternative explanation relates to the Condorcet Jury Theorem.
-In these models, there is a binary choice, with one of them being ex-ante the best.
-If legislators access the best choice with a probability higher than 0.5, more legislators will increase the change of selecting the best choice \citep{myerson1998extended}.
-However, this logic assumes that politicians choose among exogenously provided proposals, which makes sense in the case of a jury, but is somewhat uncommon for legislatures.
-\citet{auriol2012optimal} compute the optimal size of chambers considering that this is the solution to the interplay between specialization costs and citizens' preferences.}
-
-However, increasing the size of legislatures also carries considerable costs.
-Larger legislatures can raise the transaction costs \citep{weingast1988industrial}, increase collective action problems \citep{crain1979cost}, and make  forming majorities more costly \citep{crain1982team}.
-These negative features, together with the fact that legislators may free-ride on each others' proposals, may decrease legislative productivity.
-For instance, if decisions need a majority or qualified majority to be approved, more legislators create a perverse incentive, increasing the difficulty of approval.
-Moreover, legislators are pressured to provide targeted services for their constituencies at the expense of the entire polity \citep{Weingastetal1981, PrimoSnyder2008}, and this can raise inefficiencies in expenditure allocation.
-Additionally, transaction costs within legislatures may increase the difficulty of passing bills \citep{weingast1988industrial, baron1989bargaining}.
-Therefore, it is unclear whether and how larger legislatures impact lawmaking and service provision.
-
-In our view, to understand the effects of larger legislatures, we need to consider the political motivations behind the legislator's work.
-While an extra politician may increase the productivity frontier of a legislature, the types of services that will be favored remain unclear.
-To understand the political motivations, we need a theory that accounts for the cost-benefit calculations performed by politicians.
-
-When deciding which service to prioritize, politicians look into two dimensions of the service provision.
-First, the competition with other legislators motivates politicians to provide services that they believe voters want, regardless of whether these policies improve long-term welfare.
-For instance, suppose that there are three services, organized hypothetically based on beliefs about which of these three voters are more likely to reward:\footnote{Note that there is a difference between \textit{what voters want} and what \textit{politicians believe voters want}.
-Although politicians and brokers mostly access voter's beliefs accurately \citep{FinanSchechter2012, Stokesetal2013}, the crucial signal that a politician gets is vote shares, which are aggregated.
-It is hard to disentangle which service generated the highest electoral yield for the politician.
-Therefore, the politician's beliefs play an essential role in the services that they prioritize.} improving a local health clinic (most preferred), building a playground (second most preferred), or increasing the quality of education (least preferable).
-Politicians seeking recognition will mostly want to improve the health care system, which they believe will most benefit their electoral yields.
-After getting this done, they will shift efforts toward the playground construction and finally to education quality.
-Therefore, increasing legislature size will disproportionately increase the provision of services that the politicians believe voters prefer and will reward the most in the polls.
-
-Second, to get reelected, besides providing the services that voters prefer, politicians have to take credit for facilitating provision \citep{fiorina1987personal, gulzar2017politicians, nielsen2017politicians, silva2017clarity}.
-Typically, the services that are easiest in terms of credit claiming are either providing local public goods, such as improving a neighborhood health clinic, or purely clientelistic and personalistic services \citep{Weingastetal1981, kuschnir2000cotidiano, Stokes2005, nichter2011electoral, Stokesetal2013, luna2014segmented, vieira2015clientelismo, bertholini2018pork}.
-This explains why clientelism and pork-barrel are persistent in democratic polities.
-Table \ref{tabcli} summarizes the incentives.
-
-\begin{table}[htp!]
-\centering
-\caption{Effects of Legislature Size on Service Provision}
-\label{tabcli}
-\scalebox{1}{%
-\begin{tabular}{@{}lcc@{}}
-\toprule
-& \textbf{Hard for Credit Claim} & \textbf{Easy for Credit Claim} \\ 
-\midrule
-\multirow{3}{*}{\textbf{Low ranked by voters}} & No changes & None or mild \\
-& or deterioration & improvements \\
-& (Preventive Health)  & (Honors bills) \\[0.5em]
-\multirow{3}{*}{\textbf{High ranked by Voters}} & Mild to low & Mild to strong \\ 
-& improvement & improvement \\
-& (Infant Mortality)  & (School Enrollment) \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-These two dimensions provide a simple yet powerful guide of the politicians' incentives.
-When voter places a high premium on the provision of a given service, and it is easy to claim credit for the provision, politicians will concentrate their efforts in providing it.
-The more politicians, the higher the provision of the service.
-Consider, for instance, constituency service, such as getting a child enrolled at a public school.
-The voters highly rank service such as this, and the politicians can break the school access directly, getting all the credit for the provision.
-Therefore, these services tend to increase, up to the point of being over provided.
-
-When a service is hard to credit claim, to be provided, it has to be highly ranked by the voters.
-Consider services that decrease infant mortality.
-Although policies in this direction might be harder to be directly associated with one given politician, every politician wants to be known as the ones that diminished infant mortality.
-The death of a child has devastating effects over a polity, and no politician wants to be associated with it.
-On the other hand, every parent would be extremely thankful for the politicians that improved health care and saved their child.
-Moreover, politicians might facilitate access to medication and hospitals, which in turn is easier for credit claiming.
-Therefore, these services will have anywhere from modest to substantial improvements.
-
-Suppose now that service is secure to credit claim for, but gives low electoral yield.
-In this case, although the provision can be unquestionably traced back to the legislator, voters care little about the provision.
-For instance, honors and appraisal legislation are very common in Brazilian municipalities.
-However, they are perceived by politicians as low electoral yield, but the legislator that proposed the homage usually gets associated with it.
-These types of legislation increase with legislature size, but their effect on welfare is negligible.
-
-Finally, services that are difficult to credit-claim, or that politicians believe that voters care very little about, are expected to receive little invested effort from politicians.
-For instance, consider preventive health care.
-Preventive care refers to health measures, such as prenatal care or vaccination, undertaken to lower the chances or the severity of a disease(s) in the future.
-However, it is a compounded chance: the voter has to consume the service, but its effectiveness depends on voters getting sick.
-Nowadays, we are witnessing how hard it is to vaccinate children, despite all the scientific evidence demonstrating its effectiveness.
-Moreover, rational voters may fail to punish politicians for low investments in preventive public policies, such as natural disasters or climate change mitigation \citep{gailmard2019preventing}.
-Hence, voters might also not punish politicians for low investments in preventive health care because they might only observe whether a politician properly invested in preventive public policies in cases of emergency.
-Therefore, we shall expect little to no improvement in these types of services with larger legislatures.
-
-In sum, these considerations suggest that instead of looking for overall positive or negative effects, the effects of legislature size should manifest diversely, conditional on the type of service studied.
-The most significant changes should be expected in services that voters want and that are easier to claim credit for.
-Services with only one of these characteristics will be intermediate in terms of their priority and efforts exerted by politicians in their provision and will improve with less intensity.
-Services hard to credit claim and low ranked by voters will tend to be unaffected or under-provided by lawmakers.
+Here goes the theory.
 
@@
 
-In 2004, Brazil comprised 5,560 municipalities.
-According to the Brazilian Constitution, each city must provide healthcare, primary education, transportation, and infrastructure to its citizens.
-Municipalities have the authority to enact local laws and collect taxes on housing and services.
-However, their room for fiscal manipulation is limited.
-On average, municipal taxes account for only 5\% of the local budgets, while mandatory transfers from state and federal governments correspond to the remaining 95\%.
-This reduces the ability of municipal legislators to effectively influence local spending, what makes improvements in local services dependent only on the efforts of city-level politicians.
-XXXX
-
-With regards to their political organisation, municipalities have one mayor and one city council.
-Citizens choose their representatives by direct vote in the same election.
-Mayors are in charge of organising the provision of public services, as well as proposing laws and amendments to the tax code.
-Proposals submitted by the mayor are subject to the approval of the city council.
-Councillors, in turn, have two primary duties.
-First, they should discuss and vote legislation put forward by the mayors or by their peers.
-Second, they oversee the public budget and sanction mayors who do not comply with fiscal legislation.
-Councillors also provide an array of public and personal services for their constituents, such as helping voters access public hospitals, facilitating school enrolment, and even paying their voters' utility bills \citep{nichter2011electoral, AlmeidaFelix2012}.
-
-Until 2004, there was no specific regulation on the size of city councils.
-The 1988 Brazilian Constitution set only broad guidelines about the number of council seats in each municipality, which allowed cities to determine how many legislators they should have in their local chambers.
-This led to severe imbalances in the proportion of representatives per citizen across the country.
-For instance, the Nova Russas municipality had 30,009 inhabitants and 21 councillors, which accounts for one legislator per 1,429 citizens.
-In contrast, the city of Sorocaba had only 15 councillors for 528,735 inhabitants, that is, one legislator per 35,249 citizens.
-In 2003, this malapportionment problem gained national visibility when Mira Estrela, a small municipality with only 2,651 residents, reduced its city council from 11 to 9 seats because of fiscal considerations.
-The change motivated a legal dispute that reached the Brazilian Supreme Court.
-The Court favoured the city's decision and ruled that the size of every local council should correspond to precise population thresholds.
-
-Following the ruling of the Supreme Court, in March 2004 the Brazilian Electoral Court established a series of population cutoffs for all municipal legislatures.
-The Court specified that, following the Brazilian Constitution, cities with up to one million residents should have between 9 and 21 legislators.
-The number of seats was allocated as follows.
-Each city starts with 9 councillors, then adds one legislator for every 47,619 inhabitants until their councils reach 21 members.
-This threshold implies that cities with a population between 571,428 and one million should all the same number of legislators, that is, 21 of them.
-Conversely, cities between one and four million inhabitants should have at least 33 councillors, and this number increases up to 41 members following the previous formula of one additional legislator per 47,619 inhabitants.
-
-This decision makes Brazil the ideal testing ground for our theory.
-Although an endogenous decision motivated the Electoral Court ruling, the population cutoffs created sharp discontinuities in the distribution of local council seats.
-That is, cities close to the cutoffs had very similar characteristics, but those which were just above the threshold gained a new legislator.
-Moreover, cities could not self-select into any group, as their population estimates were calculated using the 2003 projections by the Brazilian Census Bureau (IBGE).
-This change in council size also happened only seven months before the election, making it impossible for candidates to adjust their service provision strategies for the 2004 election.
-Therefore, the ruling allows us to study the effect of larger legislatures on public service provision during the 2005-2008 term while holding all else constant.
-
-\section{Empirical Strategy}
-\label{sec:empstrat}
-
-\subsection{Methodology}
-\label{sub:methods}
-
-We employ a regression discontinuity design (RDD) using the population thresholds established by the 2004 Superior Electoral Court resolution as treatment indicators.
-Figure \ref{fig:runningvarplot} displays the distribution of municipalities within each city council size.
-These population thresholds remained in effect until 2009, when Congress amended the Brazilian Constitution.
-This study covers the period between 2005 and 2008, which constitutes the full mayoral and city-council term following the 2004 Brazilian elections.
-
-\vspace{.5cm}
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrSeats.pdf}}
-      \caption{Distribution of Municipalities by Population and City Council Size}
-      \bigskip
-      \label{fig:runningvarplot}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-Our identification strategy relies on three assumptions.
-First, we assume that no municipality self-selected into each side of the discontinuity.
-Second, as we run a sharp RDD, we also assume that council size increases precisely as the law mandates.
-Third, our design assumes that the pre-treatment variables, collected before the 2003 Supreme Court decision, were not affected by the 2004 ruling on council size.
-In the online appendix, we test these assumptions by building an estimator that balances the local average treatment effects (LATE).
-Our estimate is an extension of RDD and uses covariates to balance the multiple cutoff differences.
-Additionally, we propose a placebo test in which we run the same models with fake cutoffs around the original thresholds.
-Our balance and placebo tests indicate that the assumptions underlying the analyses are indeed met.
-
-% Subsection: Variables
-\subsection{Variables and Data Sources}
-\label{sub:sources}
-
-We use four groups of city-level variables in our models.
-The first group includes pre-treatment control variables that were not affected by the 2004 council size resolution.
-We add them to the models to improve the balance between treated and non-treated units.
-The covariates are: 1) the number of council seats in the previous term; 2) city population; 3) city GDP; 4) the proportion of low-income families in each municipality.
-The data come from the Superior Electoral Court (Tribunal Superior Eleitoral--TSE) and the 2000 Brazilian census.
-
-We employ a second set of variables to quantify social welfare.
-They are our outcomes of interest.
-Our main focus here is on the impact of legislature size on education and healthcare, which are the two most important public services the municipal government should provide to citizens.
-We measure access to education with the average enrolment in primary (K--4) and secondary (5--8) public schools.
-We assess education quality with the Education Development Index (\'Indice de Desenvolvimento da Educa\c{c}\~{a}o B\'asica--IDEB), which the Ministry of Education has issued biannually since 2007.
-The index is a weighted average of student scores in Portuguese and Mathematics (0--10) multiplied by the harmonic mean of public school promotion rates in a given year (0--100).
-To test the effect of the 2004 ruling on healthcare, we mapped the coverage of the Family Health Programme, a local-level primary care policy, and the proportion of pregnant women who attended more than six pre-natal consultations.
-We also gather data on post-neonatal mortality\footnote{Post-neonatal mortality rate is the probability of dying between 28 days and one year of life, expressed per 1,000 live births.} to assess healthcare quality.
-The source of all variables is the Brazilian Ministry of Health Data Centre (DataSUS).
-
-Next, we look into municipal data, city councillors' characteristics, approved legislation, and an online survey with 174 former city councillors that served during the 2005--2008 term to test our proposed micro-level mechanisms\footnote{We also analysed 108 structured interviews conducted by \citet{lopez2017legisladores} at the Brazilian Economics Planning Institute (IPEA) in 2009.
-The authors asked councillors about their daily work.
-The interviews reinforced the idea that councillors see private goods provision as more electorally profitable than formal lawmaking or executive policy oversight.}.
-The municipal data contains: 1) the number of councillors belonging to the pre-electoral mayoral coalition; 2) the councillor's gender and race; 3) the number of mayor-appointed, councillor-appointed, and career civil servants.
-All variables come from the Superior Electoral Court and the Brazilian Institute for Geography and Statistics.
-
-Lastly, we also collect 346,553 bills from cities whose populations lie within 10 thousand inhabitants from the 2004 population thresholds.
-We selected 64 out of 202 municipalities whose voting records were available online.
-We evaluate information regarding proposal types, discriminating between local and municipal public goods, oversight, and other legislative activity.
-While local public goods consist of services targeting personal, group, or neighbourhood levels, municipal public goods comprise laws and policies covering the entire municipality.
-Examples of the first are investing in a given public health clinic, requesting school bureaucracy to accommodate an extra child, and renovating sewage and fixing potholes on a given street\footnote{Our theory does not differentiate between clientelism and service provision, as it is hard to disentangle legislator's intentions.
-On the one hand, a voter may request a particular service, such as fixing a pothole.
-Attending this request can be interpreted as a clientelistic practice, despite their non-excludable benefits to the adjoining neighborhood.
-On the other hand, upon request, facilitating hospital admission is a very particularized service, thus likely to fall under clientelistic logic.
-Saying this is vote-buying can be imprecise, as service provision might simply be a way of signaling responsiveness to the electorate's demands and efficacy.
-\citet{kuschnir2000cotidiano}'s qualitative work shows the Silveira Family in Rio de Janeiro aided the community they represented regardless of political preference.
-As a result, when one of the family members ran in an election, he had the highest vote share ever seen in Rio de Janeiro.}.
-As for the latter, examples are to ameliorate education by capacitating public teachers, and to raise public health care standards through city-wide vaccination campaigns.
-Oversight bills are accountability and transparency mechanisms meant to keep public services undertaken by the bureaucracy in check.
-Other legislation comprises bills that do not fit in the previous categories.
-Examples are changes in street names, motions to honour citizens or groups, and legislative and internal city council procedures.
-
-Together, this evidence provides a clear picture of representation patterns in Brazil, from municipal welfare consequences to their micro-level mechanisms.
-Summary statistics follow in the online supplemental materials.
+Here goes the bozo.
 
 # Results
+\label{sec:results}
 
-% Session: Results
-\section{Results}
-\label{sec:outcomes}
+Here goes the results.
 
-\subsection{The Effect of Legislature Size on Service Provision}
-\label{sub:effects}
+# Discussion
+\label{sec:discussion}
 
-We study the impact of legislatures on two services: education and health care. We collect eight indicators: four in education, and four in health care.
-
-\begin{sidewaystable}[!htbp] \centering 
-  \caption{Public Service Outcomes} 
-  \label{tab:outcomes} 
-\scalebox{0.9}{
-\begin{threeparttable}
-\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c c c c c }
-\toprule
-& \multicolumn{4}{c}{\textbf{Education Outcomes}} & \multicolumn{4}{c}{\textbf{Health Care Outcomes}}  \\ \cline{2-5} \cline{6-9}
-  & \multicolumn{1}{c}{\small{(1)}} & 
- \multicolumn{1}{c}{\small{(2)}} & 
- \multicolumn{1}{c}{\small{(3)}} & 
- \multicolumn{1}{c}{\small{(4)}} & 
- \multicolumn{1}{c}{\small{(5)}} & 
- \multicolumn{1}{c}{\small{(6)}} & 
- \multicolumn{1}{c}{\small{(7)}} & 
- \multicolumn{1}{c}{\small{(8)}} \\
- & \multicolumn{1}{c}{\small{Average}} & 
- \multicolumn{1}{c}{\small{Average}} & 
- \multicolumn{1}{c}{\small{Elem. School}} & 
- \multicolumn{1}{c}{\small{Middle School}} &
-\multicolumn{1}{c}{\small{Infant}} & 
- \multicolumn{1}{c}{\small{Post-Natal}} & 
- \multicolumn{1}{c}{\small{Cov. Family}} & 
- \multicolumn{1}{c}{\small{Pr. Born w. 6+}} \\ 
- & \multicolumn{1}{c}{\small{Enroll. K-4}} & 
- \multicolumn{1}{c}{\small{Enroll. 5-8}} & 
- \multicolumn{1}{c}{\small{Quality Index}} & 
- \multicolumn{1}{c}{\small{Quality Index}} &
- \multicolumn{1}{c}{\small{Mortality}} & 
- \multicolumn{1}{c}{\small{Mort. Rate}} & 
- \multicolumn{1}{c}{\small{Health Program}} & 
- \multicolumn{1}{c}{\small{Pre-Natal Consult.}}\\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-7} \cline{8-8} \cline{9-9}
- LATE & 2.58$^{***}$ & -0.01 & -0.04 & -0.11 & -1.99$^{**}$ & -0.90$^{*}$ & -1.67 & -4.23 \\ 
-    & (0.81) & (1.07) & (0.13) & (0.11) & (0.78) & (0.48) & (2.09) & (4.01) \\
-  \hdashline \\[-1.8ex] 
- N Left & \multicolumn{1}{c}{10156} & \multicolumn{1}{c}{7306} & \multicolumn{1}{c}{8597} & \multicolumn{1}{c}{5037} &
- \multicolumn{1}{c}{12299} & \multicolumn{1}{c}{5441} & \multicolumn{1}{c}{19280} & \multicolumn{1}{c}{15548} \\ 
- N Right & \multicolumn{1}{c}{686} & \multicolumn{1}{c}{581} & \multicolumn{1}{c}{670} & \multicolumn{1}{c}{529} & \multicolumn{1}{c}{1030} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{1297} & \multicolumn{1}{c}{1030} \\
- Eff N Left & \multicolumn{1}{c}{196} & \multicolumn{1}{c}{475} & \multicolumn{1}{c}{387} & \multicolumn{1}{c}{279} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{314} & \multicolumn{1}{c}{281} & \multicolumn{1}{c}{615} \\
- Eff N Right & \multicolumn{1}{c}{202} & \multicolumn{1}{c}{312} & \multicolumn{1}{c}{283} & \multicolumn{1}{c}{195} & \multicolumn{1}{c}{390} & \multicolumn{1}{c}{242} & \multicolumn{1}{c}{301} & \multicolumn{1}{c}{438} \\
- BW Loc Poly & 5.132 & 11.208 & 8.724 & 7.824 
- 7.720 & 7.183 & 4.185 & 8.891 \\ 
- BW Bias & 10.615 & 16.694 & 15.186 & 13.714 
- 12.289 & 10.726 & 8.310 & 15.007 \\ 
-\midrule 
- & \multicolumn{4}{c}{\textbf{Education Outcomes -- Placebo Cutoffs}} & \multicolumn{4}{c}{\textbf{Health Care Outcomes -- Placebo Cutoffs}}\\ \cline{2-5} \cline{6-9}
-  & \multicolumn{1}{c}{\small{(9)}} & 
- \multicolumn{1}{c}{\small{(10)}} & 
- \multicolumn{1}{c}{\small{(11)}} & 
- \multicolumn{1}{c}{\small{(12)}} & 
- \multicolumn{1}{c}{\small{(13)}} & 
- \multicolumn{1}{c}{\small{(14)}} & 
- \multicolumn{1}{c}{\small{(15)}} & 
- \multicolumn{1}{c}{\small{(16)}} \\
- & \multicolumn{1}{c}{\small{Average}} & 
- \multicolumn{1}{c}{\small{Average}} & 
- \multicolumn{1}{c}{\small{Elem. School}} & 
- \multicolumn{1}{c}{\small{Middle School}}&
- \multicolumn{1}{c}{\small{Infant}} & 
- \multicolumn{1}{c}{\small{Post-Natal}} & 
- \multicolumn{1}{c}{\small{Cov. Family}} & 
- \multicolumn{1}{c}{\small{Pr. Born w. 6+}}\\ 
- & \multicolumn{1}{c}{\small{Enroll. K-4}} & 
- \multicolumn{1}{c}{\small{Enroll. 5-8}} & 
- \multicolumn{1}{c}{\small{Quality Index}} & 
- \multicolumn{1}{c}{\small{Quality Index}} &
- \multicolumn{1}{c}{\small{Mortality}} & 
- \multicolumn{1}{c}{\small{Mort. Rate}} & 
- \multicolumn{1}{c}{\small{Health Program}} & 
- \multicolumn{1}{c}{\small{Pre-Natal Consult.}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-7} \cline{8-8} \cline{9-9}
-  LATE & 0.45 & 0.97 & -0.10 & -0.12
-  & -1.14 & -0.25 & 1.85 & -2.22 \\ 
-  & (0.61) & (0.98) & (0.11) & (0.09)
-  & (1.05) & (0.65) & (1.25) & (2.92) \\ 
-  \hdashline \\[-1.8ex]   
- N Left & \multicolumn{1}{c}{9040} & \multicolumn{1}{c}{6350} & \multicolumn{1}{c}{7529} & \multicolumn{1}{c}{4243} & \multicolumn{1}{c}{10614} & \multicolumn{1}{c}{4449} & \multicolumn{1}{c}{17198} & \multicolumn{1}{c}{13861} \\
- N Right & \multicolumn{1}{c}{1802} & \multicolumn{1}{c}{1537} & \multicolumn{1}{c}{1738} & \multicolumn{1}{c}{1323} & \multicolumn{1}{c}{2715} & \multicolumn{1}{c}{1664} & \multicolumn{1}{c}{3379} & \multicolumn{1}{c}{2717} \\
- Eff N Left & \multicolumn{1}{c}{1186} & \multicolumn{1}{c}{1138} & \multicolumn{1}{c}{1202} & \multicolumn{1}{c}{931} & \multicolumn{1}{c}{1213} & \multicolumn{1}{c}{775} & \multicolumn{1}{c}{2575} & \multicolumn{1}{c}{1575} \\
- Eff N Right & \multicolumn{1}{c}{724} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{734} & \multicolumn{1}{c}{580} & \multicolumn{1}{c}{890} & \multicolumn{1}{c}{557} & \multicolumn{1}{c}{1483} & \multicolumn{1}{c}{1004} \\
- BW Loc Poly & 6.325 & 6.975 & 6.686 & 7.198 
- & 4.840 & 5.360 & 6.999 & 5.796 \\ 
- BW Bias & 9.860 & 12.598 & 10.029 & 11.004 
- & 7.268 & 7.943 & 11.213 & 9.559 \\ 
-\bottomrule
-\end{tabularx}
-\begin{tablenotes}
-\small
-\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1.
-RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel.
-Robust standard errors, clustered at the municipal level, are in parentheses.
-The control variables are: population, GDP per capita, number of seats in 2000, year, and a dummy for the northeast region.
-\textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated).
-\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
-\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
-\textit{BW Bias} is the bandwidth used to compute the standard errors.
-\end{tablenotes}
-\end{threeparttable}}
-\end{sidewaystable}
-
-XXXX Rewrite all this!
-
-Each of the outcomes is further divided into two groups.
-In the first group, we include services that are easier to provide or credit claim, or both.
-These services are preferred by the electorate and have an intensive advertising effect for the councillor.
-In this category, we have school enrollment and infant mortality.
-In the second group are services either considered less critical by voters or harder to credit claim.
-They are harder to translate into votes or to target and advertise.
-In our models, we use preventive health care and quality of education to illustrate.
-According to our theory, we expect that increasing legislature size has a positive effect on desirable services that are easy to target.
-
-Table \ref{tab:outcomes} presents the results for education and health care outcomes.
-The data shows that, with the addition of a city councillor, enrollment in elementary schools increased by 2.58 children on average per school.
-This represents a change of around 0.20 standard deviations.
-From 5th to 8th grades, council size has no effect on school enrollment.
-Due to high dropout rates at this stage, spots for extra students remain vacant.
-Results are insignificant for quality indicators.\footnote{As education quality improves in the medium to long term, we look into the 2015 education quality index in the Online Supplemental Materials.
-Effects are null, pointing to no delayed benefits.} As expected, the placebo regressions are also insignificant.
-
-Although Brazil achieved universal elementary school enrolment, enrolling a child in public school is particularly difficult in the early years.
-At the same time, taking care of small children is a considerable burden for poor households.
-Citizens thus reach out to councillors who can pressure school's bureaucracy to accommodate an extra child.
-Such an effort has virtually no cost to the politician, and grants her direct recognition, benefiting her electorally.
-
-Consequences for infant mortality rates are also substantial.
-1.99 deaths per 1,000 children born are prevented with every extra legislator.
-This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations.
-Moreover, post-neonatal mortality decreases by 0.90 casualties per 1,000 births, which improves health care by 0.14 standard deviations.
-As expected, placebo regressions were statistically insignificant.
-However, the Family Health Program coverage and the proportion of children born with more than six prenatal consultations seems to decrease.
-This apparent inconsistency with the other indicators will be discussed further in the text.
-
-% Sub-Section: Mechanisms
-\subsection{Applying the Mechanism and Testing Hypotheses}
-\label{sub:mechanism}
-
-We test our hypotheses in Table \ref{tab:mechanism-reg} dividing the municipal outcome data in two panels.
-In Panel A, we counter alternative explanations for our mechanism.
-In Panel B, we present evidence that corroborates our arguments.
-\begin{table}[!htbp] \centering 
-  \caption{Mechanism Regressions -- Aggregated Municipal Level Outcomes} 
-  \label{tab:mechanism-reg} 
-\scalebox{0.9}{
-\begin{threeparttable}
-\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
-\toprule
-& \multicolumn{4}{c}{\textbf{Panel A: Representation, Competition, and Legislation Approval}} \\ \cline{2-5}
- & \multicolumn{1}{c}{\small{(1)}} 
- & \multicolumn{1}{c}{\small{(2)}} 
- & \multicolumn{1}{c}{\small{(3)}} 
- & \multicolumn{1}{c}{\small{(4)}} \\
- & \multicolumn{1}{c}{\small{Num. Female}} & 
- \multicolumn{1}{c}{\small{Num. Non-white}} &
-  \multicolumn{1}{c}{\small{Candidates}} & 
-  \multicolumn{1}{c}{\small{Prop. Laws}} \\ 
-   & \multicolumn{1}{c}{\small{councillors}} & 
- \multicolumn{1}{c}{\small{councillors}} &
-  \multicolumn{1}{c}{\small{Per Seat}} & 
-  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.22 & 0.60 & -0.19 & -0.02 \\ 
-  & (0.38) & (0.85) & (1.11) & (0.08) \\ 
-  \hdashline \\[-1.8ex] 
- N Left & \multicolumn{1}{c}{5183} & \multicolumn{1}{c}{239} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{3424} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{158} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{270} \\ 
-Eff N Left & \multicolumn{1}{c}{194} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{179} & \multicolumn{1}{c}{227} \\ 
-Eff N Right & \multicolumn{1}{c}{144} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{132} & \multicolumn{1}{c}{142} \\ 
-BW Loc Poly & 8.564 & 2.954 & 8.126 & 11.080 \\ 
-BW Bias & 13.569 & 4.917 & 12.049 & 16.921 \\[1.0ex] 
-\midrule 
-& \multicolumn{4}{c}{\textbf{Panel B: Access to Resources and Patronage}} \\ \cline{2-5}
- & \multicolumn{1}{c}{\small{(5)}} 
- & \multicolumn{1}{c}{\small{(6)}} 
- & \multicolumn{1}{c}{\small{(7)}} 
- & \multicolumn{1}{c}{\small{(8)}} \\
- & \multicolumn{1}{c}{\small{Mayoral}} & 
- \multicolumn{1}{c}{\small{Num. Politically}} & 
- \multicolumn{1}{c}{\small{Num. Career}} & 
- \multicolumn{1}{c}{\small{Num. councillor}} \\
- & \multicolumn{1}{c}{\small{Coalition Size}} & 
- \multicolumn{1}{c}{\small{Appointed Empl.}} & 
- \multicolumn{1}{c}{\small{Bureaucrats}} & 
- \multicolumn{1}{c}{\small{Assistants}} \\[1ex]  \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.91$^{*}$ & 105.09$^{*}$ & 71.57 & 2.09 \\ 
-  & (0.50) & (62.12) & (218.12) & (4.37) \\ 
-    \hdashline \\[-1.8ex] 
- N Left & \multicolumn{1}{c}{5168} & \multicolumn{1}{c}{15536} & \multicolumn{1}{c}{15531} & \multicolumn{1}{c}{5179} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1028} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{344} \\ 
-Eff N Left & \multicolumn{1}{c}{240} & \multicolumn{1}{c}{351} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{99} \\ 
-Eff N Right & \multicolumn{1}{c}{161} & \multicolumn{1}{c}{334} & \multicolumn{1}{c}{388} & \multicolumn{1}{c}{101} \\ 
-BW Loc Poly & 9.906 & 6.019 & 7.695 & 5.134 \\ 
-BW Bias & 15.846 & 10.170 & 11.780 & 8.902 \\ 
-\bottomrule
-\end{tabularx}
-\begin{tablenotes}
-\small
-\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1.
-RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel.
-Robust standard errors, clustered at the municipal level, in parentheses.
-Controls: population; GDP per capita; number of seats in 2000; year; and dummy for northeast region.
-\textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated).
-\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
-\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
-\textit{BW Bias} is the Bandwidth used to compute the standard errors.
-\end{tablenotes}
-\end{threeparttable}}
-\end{table}
-
-Panel A (Table \ref{mechreg1}) tests perspectives proposed by the literature.
-One of them is that better representation of under-served groups could broaden health care and education provision \citep{pande2003can, chattopadhyay2004women, chin2011redistributive, duflo2012women}.
-However, columns (1) and (2) show that neither gender nor representation of non-white legislators significantly improves public service provision for minorities.
-Alternatively, enhanced competition is also thought to improve responsiveness, alleviating the principal-agent problem between voters and politicians.
-Yet, we show that competition (3) or bills approval (4) remain unchanged when we increase council size.
-
-Panel B (Table \ref{mechreg1}) illustrates our mechanism.
-Column (5) shows that there is a 91\% chance of the extra legislator belonging to the mayoral coalition.
-This suggests that these additions will likely enhance welfare effects due to increased governability\footnote{It is possible that the new coalition councillor facilitates mayor's lawmaking process.
-Indeed, we might actually be estimating the effects of mayors on policy-making.
-Their relationship with the central government is fundamental for service provision \citep{bueno2018bypassing}.
-In the Online Supplemental Materials, we investigate whether mayoral and council party composition vary across cities, and find that it remains unchanged around the thresholds.}.
-Column (6) demonstrates that adding one councillor increases the number of appointed employees by 105 with a standard deviation of over 0.30.
-This attests councillors' strong ties with the administration and facilitates service provision.
-
-Additionally, we consider the number of career employees\footnote{Career bureaucrats have to undergo rigorous selection that prevents them from being fired for political reasons.} and find that improvements in state capacity and welfare are not consequences of bureaucratic agency.
-Column (7) points that the number of career bureaucrats does not significantly explain access to resources.
-Finally, adding a legislator has a null effect on the average number of appointed cabinet employees (column (8)).
-
-\subsection{Disaggregating Data on Approved Legislation and City councillor Survey}
-\label{sub:survey}
-
-To evidence our mechanism's operation in city councillors' ordinary legislative activities, we examine two datasets: one composed by the approved bills, and the other by answers to the online survey.
-Figure \ref{LEGAPPR} showcases the results of the analysis of approved legislation.
-
-\begin{figure}[htb!]
-  \begin{center}
-  \caption{Legislation Approved in Municipalities Closer to the City Council Thresholds}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/lawsApproved.pdf}}
-      \bigskip
-      \label{LEGAPPR}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-As previously argued, lawmakers decide on service provision based on the feasibility of credit-claiming.
-The top-two preferred legislation categories share this feature.
-In addition,\textit{local public goods} carries high electoral yield, which explains it ranking above \textit{others}.
-Graph 2A (Figure \ref{LEGAPPR}) presents the frequency of approved proposals.
-The overwhelming majority belongs to \textit{local public goods} (72.9\%), followed by \textit{others} (17.4\%).\footnote{Note that the sum is below 100\%.
-This is due to the SVM algorithm classifying around 3.5\% of laws as belonging to none of the categories above.
-For more information, see \citet{collingwood2013rtexttools}.} Graph 2B (Figure \ref{LEGAPPR}) depicts the average number of bills per legislator and, evidently, reflects the same pattern: \textit{local public goods} also amount to the highest, at 290.7 (S.E.
-56.95), and \textit{others} follows with 77.6 (S.E.
-15.50).
-Measuring the production of each representative builds on the idea that adding legislators – who provide more services – generates greater welfare.
-
-Health care and education services, which compose 11.1\% of total approved bills (44.3 per legislator), are mainly addressed through \textit{local public goods}.
-According to Graph 2C (Figure \ref{LEGAPPR}), they represent 80.6\% of proposals in these sectors, followed by \textit{municipal public goods} (7.8\%).
-Productivity follows the same pattern (Graph 2D, Figure \ref{LEGAPPR}).
-Legislators propose 36.4 (in absolute terms) of the first, and 4.2 of the latter.
-Therefore, not only in general, but also specifically for education and health care, \textit{local public goods} are the preferred choice of councillors in Brazilian municipal chambers.
-
-In our online survey with former city councillors, we asked about their legislative activity, the amount of votes it yielded, and how they negotiated with the mayor.
-While most results are in the Online Supplemental Materials, Figure \ref{survelec} displays the services councillors believe to generate the highest electoral results.
-
-\begin{figure}[htb!]
-  \begin{center}
-  \caption{Electoral Attractiveness of Councilor's Activities and Practices}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/elecYieldJobsCouncilors.pdf}}
-      \bigskip
-      \label{survelec}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-The service that best secures votes, according to 84.3\% of the interviewed, is access to hospital facilities; to 56.0\%, it is school admission; and to 71.0\%, it is access to medication.
-82.6\% of respondents confirm that local public goods are electorally beneficial, and 50.2\% indicated that, namely, fixing potholes on public roads resulting in some or many votes.
-Second in their evaluation is public school quality oversight (34.7\%), followed by  reported public construction oversight (25.3\%).
-These last two services, despite being preferred by voters and easy to credit-claim, require more investment.
-Coordination costs related to mayor negotiation and bureaucratic mediation also force them to recur to less demanding options, for instance, honors legislation.
-This is likely the reason why more approved bills fall under the \textit{others} label than under \textit{oversight}.
-
-\section{Discussion}
-
-%CLIENTELISM
-
-Although city councillors should have governing advantages for being the closest representatives to citizens, the literature often presents them as inefficient and clientelistic \citep{Castroetal2009, AlmeidaFelix2012, leal2012coronelismo}.
-This proximity to the community results in better informed decision-making and accountability.
-However, it also creates perverse incentives to corruption, patronage and overprovision of electorally beneficial services.
-Poor management could be driven by private interests, or by limitations restraining governability.
-It is unrealistic to think that all politicians have free rein to approve and implement policies at their will.
-Bureaucracy and strong executives balance the assembly, who, in turn, develops strategies to enforce its will.
-
-A councillor can only provide services which she can control or influence.
-In a Brazilian municipality, mayors directly control budget and staff allocation.
-Consequently, councillors must side with the mayor to participate in policy-making.
-Efforts towards establishing alliances start in the pre-electoral coalition period.
-If a candidate is part of the mayoral coalition, she credibly signals being able to deliver her platform promises.
-As the Electoral Justice allocates seats according to vote shares (D'Hondt method), pre-electoral coalitions have advantages since extremely popular candidates' votes thrust smaller candidates into office.
-Pre-electoral coalitions become crucial for mayors' governability after the election.
-
-Bureaucrats also mediate most of the access to resources, and may filter councillor's demands, either for or against them.
-To influence service provision, city councillors sometimes recur to patronage, which is a strategy mobilized to ensure collaborative administrations.
-It is characterized by the employment of bureaucrats attached to an incumbent's personal figure.
-These politically-appointed employees have incentives to support the councillor's interests unconditionally \citep{Robinson2013}.
-Loyalty of the administration – through patronage or not – thus appears as fundamental in the political game.
-
-Another limitation to representative agency is based on perception, as politicians imperfectly observe voters' preferences.
-The online survey provides us with clues on how councillor's beliefs could translate into their policy choices.
-\textit{Local public goods} is the preferred type of legislation across sources.
-We assembled five specific welfare-improving policies into the \textit{local public goods} category (Figure \ref{survelec}), namely \textit{hospital admission aid} (84.3\% answered it gives some to many votes), \textit{other local public goods} (82.6\%), \textit{access to medication} (71.0\%), \textit{school admission aid} (56.0\%), and \textit{street repairs} (50.2\%).
-They all pushed down remaining categories.
-\textit{School quality oversight} places second at overwhelming distance (34.7\%).
-In the approved legislation dataset (Graph 2A, Figure \ref{LEGAPPR}), \textit{local public goods} is equally favoured (72.9\%), followed by \textit{others} legislation (17.4\%), which we know to represent mostly honors bills.
-
-If councillors aim for reelection, why do approved legislation frequencies not reflect answers to the survey?
-Comparison points to an inconsistency that circles back to the aforementioned limitations.
-Since negative exposure of executive and bureaucratic underachievement tensions political coalitions, and is less attractive to voters than policy-making.
-Logically, councillors will dedicate more to \textit{local public goods} than to \textit{oversight}.
-This does not attest their lack of competence, efficiency or honesty, but rather evidences the hardship of coordinating efforts and collectively making decisions under diverging goals and interests.
-
-# Conclusion
-\label{sec:conclusion}
-
-In this paper, we argue that political motivation determines the services that gain traction with larger legislatures.
-Councillors, guided by reelection, invest in policies they believe voters want and for which credit-claiming is feasible.
-Consequently, many essential welfare services are underprovided, giving place to locally-targeted policies.
-For instance, our theory explains why patterns of poor education persist in developing countries.
-In 2000, among the 32 countries that participated in the OECD's \textit{Programme for International Student Assessment} (PISA), Brazil ranked last.
-Between 2006 and 2015, there were virtually no improvements in scores.
-Counterintuitively, school enrolment was close to 99\% since 2010.
-Although desired by voters, ameliorating education quality is difficult to trace back to specific politicians.
-In this logic, they have incentives to target education through tangible yet low-reaching measures, such as raising the amount of children attending schools.
-
-We run a RDD to capture the effect of adding representatives to a municipal council.
-We focus on the effects of exogenously imposing thresholds to chamber sizes.
-We compare cities with similar populations, but located on different sides of the cutoff.
-We also collect data on the approved legislation during the 2005-2008 term, and perform an online survey with former representatives.
-Empirically, larger municipal chambers prevents death in infancy and stimulate educational enrollment.
-These changes do not, however, coincide with improvements in education and health care quality.
-We find that councillors prefer investing in local public goods, and they access resources via attachment to mayors and through bureaucratic mediation.
-
-Our study has implications for policy-making and for the literature on distributive politics.
-First, we provide tools to predict welfare effects of changing the number of seats in municipal councils.
-We also contribute to comprehend the strategies politicians may use to adapt to these modifications.
-For example, an extra legislator will hardly add diversity to council activities, since there is a 91\% probability she will integrate the mayoral coalition.
-As for academia, we offer a simple theory to understand the underprovision of essential public goods as education and health care.
-We add complexity to the common belief that politicians in developing countries are purely clientelistic, inefficient or dishonest.
-We conclude that the political architecture of the assembly floor creates perverse incentives.
+Here goes the discussion.
 

### 2021-08-20 article/article.Rmd
adding old content article

@@
 
-Here goes the intro.
+The design of electoral institutions is key for political accountability and representation \citep{cox1997making, manin1999elections, carey2011electoral, shugart2017votes, taylor2017impact}.
+Electoral rules influence incentives that politicians face when they are in office, public service provision, reelection and survival in office, campaign strategies, and incumbency advantages, among other characteristics.
+One particular consequence of electoral rules is their effect on corruption \citep{Persson2003, Kunicova2005, chang2007electoral, charron2011party, alfano2014electoral, schleiter2014party, xezonakis2015can, schwindt2016corruption}.
 
-# Theory
-\label{sec:theory}
+Despite the large body of literature on incentives that electoral system creates for corruption, two problems remain sparse.
+On the one hand, the roles of challengers in coping or boosting corruption incentives remain unclear.
+Although challengers are not the politicians that embezzle money, their campaign strategies may not only communicate with voters about her platform but also hold the incumbent's accountable by exposing their malfeasances once in office.\footnote{According to  \citet{polborn2006informative}, negative campaign is useful as it reveals information about candidates that they would now be willing to reveal by themselves.
+This paper rationalizes the idea that negative campaign, such as exposing a corrupt past, maybe even desirable from the perspective of voter's welfare.}
 
-Here goes the theory.
+On the other hand, despite the richness of the empirical literature on electoral systems and corruption, it frequently finds mixed results regarding the impact of district size, the pool of competitors, parties, and other electoral characteristics on corruption.
+For instance, \citet{Persson2003} show that closed-list Proportional Representation (PR) increases corruption by making voters less capable of punishing politicians, and single-member districts (SMD) may not be best for corruption as it poses significant entry barriers to honest politicians.
+However, \citet{chang2007electoral} demonstrate that, when controlling for the district magnitude, open-list PR performs worse in large-magnitude districts compared with closed-list PR (and vice-versa for small magnitude districts), showing that the results are highly non-monotone.
+Also, while \citet{charron2011party} shows that more competition increases corruption, specially in single-member district countries, \citet{schleiter2014party} and \citet{schleiter2016party} argue that party competition and party institutionalization increase the availability of credible alternatives against corrupt politicians, decreasing corruption.
+Moreover, \citet{tavits2007clarity, potter2011curbing} and \citet{schwindt2016corruption} show that clarity of responsibility is essential for corruption outcomes, as it limits the capacity for politicians to hide behind the political system, making them more accountable for bad outcomes.\footnote{For a summary of the clarity of responsibility and elections see \citet{silva2017clarity}.} Therefore, findings on the corruption-electoral systems literature are mostly contradictory, and this claims for a stronger theoretical foundation that conciliates differences in empirical models and their institutional and behavioral incentives.
 
-# Background on the Brazilian Case
-\label{sec:background}
+This paper provides a rigorous micro-foundation for one facet of the corruption-electoral system nexus.
+I build a model on corruption incentives considering the two main set of players in this strategic interaction: incumbents and challengers.
+Incumbents choose policy investments, with the possibility to add kickbacks to the optimal required values.
+Challengers observe the total investment and choose a proportion of their campaign to devote for exposing the incumbents' corruption.
+Solving the model presents the determinants for the corruption levels: the \textit{free-riding} incentives caused by the number of competitors, and the \textit{coordination failures} caused by the number of incumbents.
 
-Here goes the bozo.
+Polities with an open entry may attract many challengers, and even though challengers benefit from the use of negative campaign, they prefer to let the other challengers expose the corrupt politician: free-riders avoid the costs of exposing the corrupt politicians while benefiting from the increased winning chances.
+Additionally, polities with many incumbents, such as proportional representation systems, add coordination failures to the top of the free-riding incentives: when there are many challengers and incumbents, challengers may happen to expose the same politician, leaving other incumbents without proper denouncing.\footnote{Although a system that has many incumbents is not a perfect representation of PR systems, a perfect PR representation would make the model considerably harder to understand, without changing the qualitative characteristic of its results.
+Moreover, our approach is similar to \citet{Myerson1993}, with the key difference that we do not assume the existence of a behaviorally non-corrupt politician.
+In this sense, this is a moral hazard model, while Myerson's is an adverse selection model.} This possibility makes incumbents more prone to pocket even more money than when there is only free-riding caused by a large pool of challengers.
+In sum, these collective action problems determine the incentives that challengers have to expose incumbents, therefore impacting the incentives for corruption.
 
-# Results
+The results here suggest that the least corrupt system is the single-member district with restrictions for contest office and the most corrupt system is proportional representation with weak parties and personalistic voting (open-lists).
+However, as changes in electoral systems reflect more profound trade-offs, sometimes polities may decide that multi-member districts trumps single-member districts, as their primary objective is to accommodate social cleavages or improve the representation of minorities.\footnote{See \citet{carey2011electoral} for a discussion about the possibility of an optimal trade-off between representation and accountability, where PR in small districts seem to be the best for maximizing representation without lowering accountability considerably.} The historical development of each polity determines these trade-offs and the relative importance of representation, accountability, corruption, and other related components.
+My argument in this paper is that if corruption is a problem that the polity wants to fight, and if politicians want to limit corruption by reforming the electoral system, then they should raise entry barriers and decrease district size.
+Additionally, I discuss many extensions that shed light on the micro-level electoral institutions affecting the collective action problems.
+Rules such as run-offs, proportional representation thresholds, or even laws that bar convicted politicians to contest offices are sometimes proposed as a method to lower corruption.
+Again, institutions that lower competition and district size decrease political corruption.
+
+The last session of the paper shows that our claims hold empirically, by exploiting two quasi-experimental shocks in district size and competition in Brazil.
+First, I show that run-off and candidacy impact on corruption.
+Second, I show that exogenous thresholds for legislature size influences candidacy and district size, impact on corruption.
+This paper builds upon \citet{ferraz2011electoral}, \citet{avis2016government}, and \citet{britto2016corruption} findings, providing a theoretical explanation for their results.
+These results provide a solid empirical test for my model, showing that the electoral rules and competitiveness consistently affect corruption levels, in one of the most corrupt democracies in the world.
+
+# Corruption, politics, and institutions
+\label{sec:theorytext}
+
+In modern societies, elections select representatives, that carry out the interests of voters \citep{pitkin1967concept, manin1997principles}.
+Representation creates a principal-agent problem as the elected have the latitude to implement or not the voters' preferences \citep{manin1999elections}.
+As there exist many methods and rules to elect politicians, these rules affect the extent through which politicians perceive themselves as accountable to voters in several forms \citep{LizzeriPersico2001, grofman2016perspectives}.
+
+For instance, consider the differences in representation generated by multi-member and single-member districts.
+In single-member districts, only one representative gets elected, and she represents the district majority.
+In homogeneous districts, single-member districts with majoritarian rule capture the social and racial composition precisely.
+However, when there is considerable heterogeneity, such as social, racial, or religious cleavages, single-member districts may under-represent those cleavages.
+In these cases, multi-member districts are preferable concerning representation, as they tend to reflect the actual proportions of these cleavages more closely.
+
+However, electoral institutions embed more profound trade-offs in every dimension they affect \citep{grofman1986electoral, carey2011electoral, grofman2016perspectives}.
+Multi-member districts favor representation but also translate into a more significant number of parties, increasing the governing costs \citep{duverger1959political, fujiwara2011regression}.
+Single-member districts, on the other hand, tend to produce fewer represented parties, lowering the governing costs.
+
+One dimension affected by the electoral rules is the electoral campaigns.
+Every politician divides their campaign roughly in two basic strategies: positive campaign, where they present their political platform for voters; and negative campaign, where they campaign against their opponents, aiming to affect the voter's perceptions regarding other candidates \citep{harrington1996spatial, polborn2006informative, walter2014stakes}.
+Although voters and politicians may perceive positive campaign as less controversial, negative campaigns are also essential, primarily when they aim to expose a corrupt politician \citep{polborn2006informative, FerrazFinan2008, avis2016government}.
+In this sense, to understand how electoral systems affect corruption, we need to explore the effects of electoral rules on incentives for challengers to expose corrupt incumbents.
+
+Exposing corrupt politicians consumes campaign resources, and the aim is to change the voters' perspectives about another politician.
+However, the electoral rules affect the number of politicians, either incumbent or challengers, running in the election.
+In this sense, like any other situation where there are many politicians, collective action problems affect the willingness to campaign against a corrupt incumbent \citep{olson2009logic, ostrom2015governing}.
+These collective action problems will determine the incentives that challengers face when they are willing to expose corrupt incumbent(s).
+
+For the scope of this paper, two types of collective action problems matter when studying electoral rules: free-riding and coordination failures.
+First, electoral rules influence the incentives that candidates have to free ride on others candidates' negative campaigns.
+The free-riding here entails a situation where a candidate does not pay the costs of negative campaigning but benefit from the negative campaigning undertaken by the other candidates.
+
+Second, electoral institutions may cause coordination failures, as candidates would be better-off exposing only one incumbent at a time, but as they cannot perfectly coordinate, they end up targeting the same incumbent more than one time.
+If we consider that the likelihood of exposure has decreasing returns, meaning that the more negative campaigning politicians make, the lower the effects of additional negative campaigning, inefficient targeting lowers the effectiveness of corruption exposures.
+A summary of these two effects on different electoral rules follows in Table \ref{tabcor2x2}.
+
+\begin{table}[htp!]
+\centering
+\caption{Effects of Competition and District Size on Corruption}
+\label{tabcor2x2}
+\scalebox{1}{%
+\begin{tabular}{@{}lcc@{}}
+\toprule
+& \textbf{Single-Member} & \textbf{Multi-Member} \\ 
+& \textbf{Districts} & \textbf{Districts} \\ 
+\midrule
+\textbf{One Challenger} & Low Incentives & Moderate Incentives \\
+\textbf{Per Seat} & for Corruption & for Corruption \\
+ & (No Free-Riding or Coord. Probl.) & (Coordination Problems) \\[0.5em]
+\textbf{Multiple Challengers} & Moderate Incentives & High Incentives \\ 
+\textbf{Per Seat} & for Corruption & for Corruption \\
+ & (Free-Riding Problems) & (Free-Riding + Coord. Probl.) \\
+\bottomrule
+\end{tabular}
+}
+\end{table}
+
+Regarding corruption incentives, single-member districts with one challenger running are the least corrupt systems.
+The reason here is that any negative campaign that harms the incumbent also increases the challenger's electoral perspective.
+In this sense, no free-riding or coordination failures happen, and the incentives to expose corrupt politicians are at the maximum.
+This explains why majoritarian systems with run-off are effective in lowering corruption: the run-off makes the election to polarize, eliminating the free-riding and coordination failures \citep{ferraz2011electoral}.
+
+Adding more challengers create a free-riding problem, as challengers may benefit when other fellow challengers investigate the incumbent.
+This result points to the direction that more competition increases corruption, agreeing with the majority of the empirical findings \citep{Charron2011}.\footnote{A few papers, such as \citet{Persson2003}, argue that competition is positive, as it presents lower entry barriers, and therefore, credible alternatives against corrupt politicians.
+Despite their findings, most of the literature shows a negative influence of competition.
+However, at the party level, competition seems to provide positive results \citep{schleiter2014party}.}
+
+Adding more seats and more challengers further reduce the incentives to expose corrupt politicians, and the reason is twofold.
+First, adding more seats create free-riding incentives, as it increases the absolute number of competitors, even when the ratio of competitors-per-seat is kept constant.
+Second, adding more seats increase the likelihood of coordination failure, as the same incumbent may be exposed more than once while others may be not exposed at all.
+These two effects lower the incentives for exposing corrupt politicians, and they reasonably explain why countries with open-list proportional representation systems are endemic corrupt \citep{Myerson1993, ames1995electoral, mello2018brazil}.
+
+However, the cases reported above may be considered \textit{pure forms}, that vary with the particular characteristics of each system.
+Consider, for instance, three variants of these simple electoral rules.
+First, consider that party lists may be open or closed, and this affects the strength of a party.
+Closed lists empower party leaders, and may have a positive effect on coordination, lowering corruption.
+\citet{chang2007electoral} find that there exists a threshold where closed-list proportional representation systems become less corrupt than open-list proportional representation systems.
+\citet{schleiter2016party}, along with similar lines, argue that stronger parties are better to decrease political corruption.
+
+This list can be extended, as there are many types of political rules.
+Ultimately, they will be closer to one of the forms in Table \ref{tabcor2x2}.
+The main conclusion is that larger the number of incumbents or number of challengers, the more the collective action problem in the exposure of corrupt politicians.\footnote{Moreover, the mechanism in play may not be the same as the exposed here, and the diminished incidence of corruption could be caused not because challengers investigate more, but because of some other feature.
+Here in this paper, I abstract from these other possibilities in order to explore the role of challengers in the diverse electoral systems.}
+
+# Formal Model
+\label{sec:theorymodel}
+
+Let a strategic interaction between three players: an incumbent politician ($I$), a challenger politician ($C$), and a representative voter ($V$).
+
+The incumbent $I$ has a fixed budget of $A$ units, to invest in service provision.
+The level of expenditure required to provide the public goods is a random variable $\eta \in [0, A]$, where $f(\eta)$ an increasing probability density function.
+The randomness reflects the idea that changes in real-world conditions influence the amount needed for service provision.
+The incumbent knows the optimal investment level, making it her private information.
+If incumbents were honest, they would invest the needed amount to provide the services ($\eta$), but in this model, the incumbent invests the optimal amount plus some value, that she intends to pocket.
+The utility from pocketing money is described by $u(e_i-\eta)$, which $u$ is a strictly concave utility function, and $e_i$ represents the service expenditure by an incumbent $i$.\footnote{This assumption matches a frequent empirical regularity in the political environment, especially in new democracies: corruption tend to be over-investments, meaning that politicians add kickbacks and gifts to procurement contracts, receiving benefits them.
+Usually, what happens is not that voters fail to receive the services, it is that those services cost much more than their market value.
+For instance, \citet{Bandiera2009} estimated that the waste in procurement account for around 2\% of the Italian GDP.}
+
+After the service provision period, the electoral stage starts with the incumbent and the challenger campaigning.
+The challenger and the voters do not observe the optimal service investment level, but the challenger observes the amount of money invested by the incumbent politician ($e_i$, for all $i$).
+The challenger faces no entry costs and has the opportunity to use the negative campaign to convince the voters that the incumbent has embezzled public funds.\footnote{ This assumption is strong, as many papers demonstrated the effect of quality and service provision on the decision to challenge an incumbent \citep{Gordonetal2007, ashworth2008electoral, gordon2009voter, hall2015much}.
+In this paper, I endogenously fix the number of incumbents and challengers, as the critical point here is to study how the number of politicians influences incentives.
+In the Appendix, I extend the model to have a pool of possible challengers that have their entry costs a random variable.
+In the extension, the total pool of likely entrants becomes the critical variable, holding all qualitative findings here unchanged.
+Therefore, to fix the number of entrants is easier to understand, and represents a class of models that preserve the characteristics of our results, than we adopt this approach in the main text.
+Also, for the entry decision in economics, see \citet{Milgrom1982, Nti1989}.} If she decides to use all of her campaign resources to expose the corrupt politician, she pays a cost $c>0$.
+Her chances of success depend on the strength of the corruption evidence, plus other environmental facts, such as how much control over information incumbents have \citet{ferraz2011electoral, boas2011controlling}, credibility perceived by the voter \citep{polborn2006informative, AshworthShotts2011}, access to privileged information, and the challengers' competence to spread the information among voters.
+I assume that these factors are captured by a corruption detection technology, a function $\lambda(.)$ that is increasing on the amount embezzled by the incumbents.
+It increases with the amount embezzled, as the more money the incumbent pockets, the easier to convince voters that there is hard evidence of malfeasance undertaken by the incumbents.\footnote{There are two ways to interpret the hard evidence detection technology.
+First, it can be exposure of hard corruption evidence that was brought by a law enforcement agency, such as the FBI in the US or the General Comptroller Agency in Brazil.
+Second, it can be information uncovered during the campaign process by candidates or former allies that turned to the opposition.
+Either way, we consider that the process is noisy, but more substantial sums of money embezzled makes its detection easier.}
+
+Finally, as the voters' decisions are sequentially rational, upon observing hard corruption evidence, they punish the incumbent electing the challenger.
+Otherwise, the claim that the incumbent is corrupt is interpreted as a cheap talk by the voters.\footnote{Note that it is not ex-ante rational to always dismiss (never dismiss) the politicians, even when the voters know that politicians are corrupt.
+This because always dismissing (never dismissing) would generate equilibrium where politicians always spend the total amount of resources, regardless of how much is needed to provide the services.} Thus, the voter only punishes the incumbent when the challenger presents and convinces the voters that there is hard evidence of malfeasance.
+The game then ends, and payoffs are realized.
+The timeline for this model is as follows:
+
+\begin{enumerate}
+ \item Nature draws the optimal investment level to provide the public services.
+ \item The incumbent observes the optimal investment level and choose the expenditure.
+ \item The election starts with the challenger choosing her campaign strategy.
+ \item Voters observe the campaign and choose whether to retain or dismiss the incumbent.
+\end{enumerate}
+
+The strategic decisions in this game are the expenditure level chosen by the incumbent ($\varepsilon$), the fraction of time that the challenger invests in exposing the corrupt incumbent ($\varphi$), and the voter's decision to retain or dismiss the incumbent.
+Condensing the discussion above, we have the following expected utility functions.
+For the incumbents:
+
+\[
+U_i (\varepsilon_i; \ \eta, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) \ = \ u(\varepsilon_i - \eta) + B \ \Prob (\upsilon_i = 1 \ | \ \psi, \dd) 
+\]
+
+Where $B$ is the reward for staying in office (assumed the same for every player) and $\Prob (\upsilon_i = 1 \ | \ \psi, \dd)$ is the probability of being retained, given $\psi$ and the exposure profile $\dd$.
+For a challenger $j$:
+
+\[
+U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}) \ = \ B \int_{0}^A \Prob (\upsilon_j = 1 \ | \ \eta, \bveps^{*}, \bvphi^{*})\mu(\eta|\bveps^{*}) d\mu(\eta) - c \sum_{i=1}^K \varphi_{ij}(\psi, \bveps^{*})
+\]
+
+With $c > 0$ being the cost of performing one full corruption exposure.
+Notice that the total amount spent on exposing corrupt politicians will be the sum of the amounts spent on each exposure.
+The representative voter's expected utility is equal to:
+
+\[
+U_V (\psi, \dd, \bups) \ = \ \indf \{\psi=G \}r_G
+\]
+
+Where $\indf$ is the indicator function for $\psi=G$ and $r_G$ the value of the public good for the voter.
+Notice that no $\psi=B$ is observed on the equilibrium path, as under-spending is a dominated strategy.
+
+Any retention rule selected for the voters is sequentially rational because there is no uncertainty about the results when they cast their votes.
+I impose the retention rule for the voter to be to dismiss all incumbents when $\psi=B$ or replace incumbents that were successfully exposed by challengers when $\psi=G$.
+This rule is ex-post efficient as over-dismissal would make incumbents pocket all the money regardless of $\eta$.
+
+I solve this game for a \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}, and as this is a signaling game, I also use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}.\footnote{The restriction imposed by the universal divinity requires that the challengers, facing a deviation from the equilibrium path, put probability one on the type that is more likely to deviate.
+Moreover, as we have a continuum of types, we use the approach by \citet{Malaith1987}, which consists in finding the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.}
+
+\begin{definition}
+ \label{def_eqn}
+ A Perfect Bayesian Equilibrium for the game described, with $|I|=K$ and $|C|=L$, $K$ and $L$ in $\mathbb{N}$, type space $T=[0,A]$, consists in optimal strategies $\bveps^{*}$, $\bvphi^{*}$, $\bups^{*}$ and beliefs $\mu^*$, that satisfy
+ \begin{enumerate}
+  \item $\forall t_i \in T$, $\varepsilon^{*}_i(t_i)$ maximizes $ U_i (\varepsilon_i; \ t_i, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) $ $\forall i \in \{1, \cdots, K\}$.
+  \item $\forall \bveps \in \left[0,A \right]^K $ and $\psi \in \{B, \ G \}$, $\bvphi^{*}_j(\bveps, \psi)$ maximizes $ U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}, \ \mu^*) $, $\forall j \in \{1, \cdots, L\}$
+  \item $\forall \psi \in \{B, \ G \}$ and $\dd \in \{0,1\}^L$, $\bups^{*}(\psi, \dd)$ maximizes $ U_V (\psi, \dd, \bups^*) $.
+  \item The beliefs are derived using Bayes rule whenever possible, and for all $\varepsilon_i$ that are off-the-equilibrium path, $\mu^*(t_i| \varepsilon_i)>0$ (in fact, 1) only if $\widehat{\varepsilon}_i \in \arg \min_{t_i} p(t_i, \widehat{\varepsilon}_i)$, where $ p(t_i, \widehat{\varepsilon}_i)$ is the profit from deviating from $\varepsilon_i$ to $\tilde{\varepsilon}_i$ for a type $t_i$.
+ \end{enumerate}
+\end{definition}
+
+Note four characteristics of the model proposed.
+First, the incumbent politicians always embezzle some amount in equilibrium.
+Second, conditional on the benefits from holding office, to spend less than the optimal investment is harmful to the incumbent.
+In concrete terms, this means that politicians' first aim is to be elected.
+If the voter always dismisses the politician, then the politician will always say that the good costs $A$.
+Third, the voters always receive the public goods, regardless of the amount of money embezzled.
+The voter decides to punish the corrupt incumbent to discipline the incumbent's behavior, minimizing the rents extracted.
+Finally, this model has no ideological proximity, or affinity between the voter and any of the politicians: the paper aims to explore the incentives for corruption, not the trade-offs between ideology and corruption.
+Ideology is vital to understand why voters may not want to punish a corrupt politician, but this is not the main point of this paper, and adding this to the paper only blurs the logic of the argument.
+I now solve the model for the scenarios relevant to this paper.
+
+\subsection{One incumbent and one challenger}
+
+Applying backward induction, the voters retain the incumbent if the policy result was good and no corruption was exposed.
+From the challenger's perspective, as there is no cost of entry, she decides whether to invest or not her campaign resources in exposing the incumbent.
+She does so when the expected utility of exposing is higher than or equal the expected utility of not exposing, given her beliefs about the real value of $\eta$.
+Thus:
+
+\[
+B \int_{t_i \in T} \Prob (\bups = (0,1)\ | \ \eta, \varepsilon^*, \varphi)\mu^*(t_i|\varepsilon^*) d\mu - c \varphi(\psi, \varepsilon^*) \geq 0
+\]
+
+Rearranging and applying the fact that $ \Prob(\bups = (0,1) | \varepsilon^*, \varphi ( \psi, \varepsilon^*), \eta) = \varphi(\psi, \varepsilon^*) \lambda(\varepsilon^*-\eta) $ and $\mu^*(t_i | \varepsilon^*) = \mu(\eta) = \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta}$ yields to:
+
+\[
+B \varphi(\psi, \varepsilon^*) \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta - c \varphi(\psi, \varepsilon^*)
+\]
+
+Isolating $\varphi(\psi, \varepsilon^*)$, let $\lambda_\varepsilon = \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta$ and $Q(B, c) = \dfrac{c}{B}$.
+Sequential rationality implies three distinct decisions: first, the challenger exposes the corrupt incumbent for sure whenever $\lambda_\varepsilon > Q(B, c)$; second, the challenger never exposes the corrupt incumbent when $ \lambda_\varepsilon < Q(B, c)$; and finally, the challenger is indifferent between exposing or not the corrupt incumbent when $\lambda_\varepsilon = Q(B, c)$.
+Optimality suggests that incumbent politicians will calibrate their rent extraction in order to make challengers indifferent between investigating or not.\footnote{To avoid a trivial equilibrium we assume that $Q < \dfrac{\int_0^A \lambda(A - \eta)f(\eta) d\eta}{\int_0^Af(\eta)d\eta} = Q^*$.
+If $Q \geq Q^*$, then the only equilibrium is to play $A$ regardless of $\eta$, and there will be no exposures.}
+
+In this situation, there exists $\overline{\eta}$ such that:
+
+\[
+\lambda_A = \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta)f(\eta) d\eta}{\int_{\overline{\eta}}^Af(\eta)d\eta} = Q(B, c)
+\]
+
+This equation represents the upper limit in the incumbent politician's strategy when the randomly drawn optimal expenditure is too close to the maximum expenditure.
+In these situations is more profitable for them to play $A$.
+We say that the threshold for this case is $\overline{\eta}$.
+
+Now, let $\delta(\varepsilon)$ the probability function that characterizes the amount of negative campaign chosen by the challenger when $\varepsilon \in [ 0, \ \overline{\eta}]$.
+The optimal $\varepsilon$ solves the equation $\lambda_\varepsilon = Q(B, c)$, making the challenger indifferent between exposing or not the incumbent's corruption.
+As $\lambda(.)$ has an inverse function, the optimal strategy for the incumbent is:
+
+\begin{equation*}
+\varepsilon^*(\eta) \ = \ \eta + \lambda^{-1}\left(\dfrac{c}{B}\right)
+\end{equation*}
+
+Therefore, the optimal strategy for the incumbent politician is to add a kickback $\kappa$ to the cost for providing the public good.
+The incumbent devises the optimal kickback to make the challenger indifferent between expose or not the corrupt incumbent.
+The optimal kickback is increasing in the cost of the negative campaign and decreasing in the benefit of holding office.
+
+The incumbent, on the other hand, only plays this strategy when it is incentive compatible for her.
+To be an optimal response, it should be a $\arg \max$ for $U_I$.
+Taking the derivative of $U_I$, and setting it to zero gives us the following differential equation for $\delta(\varepsilon)$:
+
+\[
+\dfrac{d \delta}{d \varepsilon} + \delta(\varepsilon)\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)} = \frac{1}{B}\frac{u^{'}(\kappa)}{\lambda(\kappa)}
+\]
+
+Under the boundary condition $\delta(\kappa)=0$.
+The equation is a well defined first order differential equation that has a straightforward unique solution determined by the boundary condition.
+Solving for $\delta(\varepsilon)$, we have:
+
+\[
+\delta(\varepsilon) = \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right)
+\]
+
+Combining all these results together gives us the following lemma:
+
+\begin{lemma}
+ \label{lemma_m1}
+ A Perfect Bayesian Equilibrium for the game when there is one incumbent and one challenger is a pair of strategies and beliefs such that the optimal strategies are
+ \begin{enumerate}
+  \item For the incumbent 
+  \[
+   \varepsilon^{*}(\eta) \quad = \quad \twopd{\eta + \kappa}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
+  \]
+  \item For the challenger
+  \[
+   \varphi^*(\varepsilon) \quad = \quad \threepdo{0}{\varepsilon < \kappa}{\delta(\varepsilon)}{\kappa \leq \varepsilon \leq \overline{\eta}}{\delta(A)}
+  \]
+ \item And the voter replaces the incumbent if there is evidence of corruption.
+ \end{enumerate}
+ Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
+ \[
+ \kappa = \lambda^{-1}\left(\dfrac{c}{B}\right)
+ \]
+ The upper threshold, $\overline{\eta}$, satisfies 
+ \[
+ \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta) f(\eta) d\eta}{\int_{\overline{\eta}}^A f(\eta)d\eta} - \dfrac{c}{B} = 0
+ \]
+ \[
+ \delta(\varepsilon) \ = \ \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right) 
+ \]
+ And the beliefs are updated using Bayes rule whenever possible.
+\end{lemma}
+
+The remainder of the proof and the demonstration that this strategy is indeed an equilibrium is in the Appendix.
+Note three critical features on this equilibrium.
+First, an increase in the value of office ($B$) decreases the kickbacks extracted and the amount of negative campaign.
+Decreases kickbacks because it becomes more profitable to be reelected vis-a-vis extract rents, and lowers the amount of negative campaign because there are fewer opportunities to detect corrupt behavior.
+Second, increasing the costs of exposing corruption ($c$) increases the kickbacks and decreases the amount of exposure in equilibrium.
+Finally, increasing the gains from extracting rents (increasing $u'$) does not change the amount of extraction, but increases the amount of negative campaign, as a form to cope with the possibility of deviating from the equilibrium.
+These results are intuitive but demonstrate that the model follows a reasonable logic.
+
+\subsection{One incumbent and many challengers}
+
+Let $|I|=1$ and $|C|=L$.
+Starting with the voters, their optimal strategy is to retain the incumbent if the incumbent provides the public good and no corruption has been uncovered.
+If the voters dismiss the incumbent, they randomly select a challenger with equal probability.\footnote{One might think that an optimal scheme would be to reward the challengers that uncovered the corruption scandal.
+The problem with this consideration is twofold: first, once the corruption has been detected, all challengers could use these facts in their campaigns, making the corruption exposure a ``non-excludable good.'' Second, even if we consider that challengers inherit the votes from the exposed incumbent, the collective action remains, as every challenger will have incentives for negative campaign, but if all do, the voter will keep choosing by chance.
+The equilibrium changes slightly but qualitatively, it is still worse than just one challenger.}
+
+Challengers observe $\psi$ and $\varepsilon$ and have to simultaneously compute the time to invest in negative campaign $\varphi_i$.
+As challengers have the same utility function, we solve for a symmetric equilibrium.
+Let $\lambda(\varepsilon-\eta) = \lambda_\varepsilon$.
+If we have $k$ players investing in a negative campaign against the incumbent politician, the probability that the incumbent gets successfully exposed and lose the election is:
+
+\[
+f(\varphi, x) = \sum_{k=0}^{L-1} {L \choose k} \varphi^k (1-\varphi)^{L-1-k} \cdot (1 - (1-\lambda_\varepsilon)^{k+x})
+\]
+
+So when $i$ decides to commit all her resources in a negative campaign, we let $x=1$ in $f$. This strategy allows us to compute the expected utility for the challenger $i$ as:
+
+\[
+\frac{B}{L}\int_0^A f(\varphi, 0) \mu(\eta|\varepsilon) d\mu + \varphi_i  \left[\frac{B}{L} \int_0^A \left( f(\varphi, 1)-f(\varphi, 0) \right) \mu(\eta|\varepsilon) d\mu - c \right]
+\]
+
+Sequential rationality requires that $\varphi_i > 0$ when this quantity is greater than zero, and zero otherwise.
+After some algebra, we can rewrite the critical term in the decision process as an equation $G$:
+
+\[
+G(\lambda, \varphi; L) = (1-\varphi\lambda_\varepsilon)^{L-1}\lambda_\varepsilon - Q(B, c) L
+\]
+
+Where $Q$ is defined as in the previous section: $Q(B,c) = \dfrac{c}{B}$.
+This equation yields to the optimal $\varepsilon$.
+The problem is that we will have, for each value of $\varepsilon$, a corresponding optimal value of $\varphi$, and vice-versa.
+As the incumbent plays first, she can choose the max-min value for $\lambda$, which is the maximum value for $\varepsilon$ that still delivers the lowest $\varphi$ possible.
+For a numerical example, if we assume $Q=0.15$ and $L$ ranging from $1$ to $5$, we can have a contour for the possible values for $\lambda$ in Figure \ref{fig_m2_1}.
+
+\begin{figure}[htb!]
+ \centering 
+ \includegraphics{figm21.pdf}
+ \caption{Contour plot for $G=0$ when $Q=0.15$ and $L$ ranges from $1$ to $5$}
+ \label{fig_m2_1}
+\end{figure}
+
+Making $G=0$ yields to the following optimal incumbent expenditure strategy:
+
+\[
+\varepsilon^*(\eta) = \eta + \lambda^{-1}\left( Q(B, c)\cdot L \right) = \eta + \kappa(L)
+\]
+
+Again, the actual value required to provide the service plus a kickback comprises the incumbent strategy.
+The kickback has the same characteristics expressed in the case with one challenger, except now it is augmented linearly by the number of challengers contesting the seat.
+In order to this expenditure profile be incentive compatible it has to satisfy the following differential equation in $\delta(\varepsilon)$:
+
+\[
+\delta^{'}(\varepsilon)-\delta(\varepsilon)\dfrac{\lambda^{'}(\kappa(L))}{\lambda(\kappa(L))} \ = \ \dfrac{u^{'}(\kappa(L))}{BQ(B, c)L^2}
+\]
+
+With the boundary condition $\delta(\kappa(L))=0$, we have the following optimal exposure strategy:
+\[
+\delta(\varepsilon) \ = \ \dfrac{u^{'}(\kappa(L))}{BQ(B, c)L^2} \left( 1- e^{\frac{\lambda^{'}(\kappa(L))}{\lambda(\kappa(L))}(\kappa(L)-\varepsilon)}\right)
+\]
+
+Collecting all the results leads us to the following Lemma.
+
+\begin{lemma}
+ \label{lemma_m2}
+ A Perfect Bayesian Equilibrium for the game when there is one incumbent and $L$ challengers is a pair of strategies and beliefs such that
+ \begin{enumerate}
+  \item For the incumbent
+  \[
+  \varepsilon^{*}(\eta) \quad = \quad \twopd{\eta + \kappa (L)}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
+  \]
+  \item For each of the challengers
+  \[
+  \varphi^*(\varepsilon) \quad = \quad \threepdo{0}{\varepsilon < \kappa(L)}{\delta(\varepsilon)}{\varepsilon \in [\underline{\eta}, \ \overline{\eta}]}{\delta(A)}
+  \]
+  \item And the voter dismiss the incumbent if there is evidence of corruption, electing one of the $L$ challengers with probability $1/L$.
+ \end{enumerate}
+ Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
+ \[
+ \kappa(L) = \lambda^{-1}\left(L\dfrac{c}{B}\right)
+ \]
+ And the $\delta(.)$ defined as in the Appendix.
+\end{lemma}
+
+The proof with the step-by-step derivations is in the Appendix.
+Note here that all the comparative statics with relation to the benefit from holding office, the costs of exposing corrupt politicians, and the utility of rent extractions remain unchanged.
+The fundamental differences here are the effect of the number of challengers: it increases the kickbacks while decreasing the incentives for investigating the corrupt incumbent.
+The reason is intuitive: the more challenger added, the more the collective action problem faced by the challengers.
+For every individual challenger, it is better to let someone else pay the cost of a negative campaign but if all challengers reason similarly no exposures are performed in equilibrium.
+Thus, adding challengers increase the incentives for corruption.
+
+\subsection{Many incumbents and challengers}
+
+In multi-member districts there are more than one incumbent.
+All proportional representation countries, and most non-Westminster democracies use some variety of multi-member districts to elect representatives to their parliaments.\footnote{Proportional representation systems elect many representatives within a district, but also use apportionment rules to ensure proportional distribution of votes to parties.
+With the only difference that the apportionment rules may generate a few differences in the translation between votes and seats, in general, our representation encompasses the main features in a PR systems.} The following Lemma summarizes the case when there are many incumbents and many challengers.
+
+\begin{lemma}
+ \label{lemma_m3}
+ A Perfect Bayesian Equilibrium for the game when there are $K$ incumbents and $L$ challengers is a pair of strategies and beliefs such that
+ \begin{enumerate}
+  \item For the Incumbent
+  \[
+  \varepsilon^{*}(\eta) \ = \ \twopd{\eta + \kappa(L+K)}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
+  \]
+  \item For the Challenger
+  \[
+  \varphi^*(\varepsilon) \ = \ \threepdo{0}{\varepsilon < \kappa(L+K)}{\delta(\varepsilon)}{\varepsilon \in [\kappa(L+K), \overline{\eta}]}{\delta(A)}
+  \]
+  \item The voters dismiss the corrupt incumbents, choosing randomly the substitutes among the $L$ challengers.
+ \end{enumerate}
+ Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
+ \[
+ \kappa(L+K) = \lambda^{-1}\left((L+K)\dfrac{c}{B}\right)
+ \]
+ And the $\delta(.)$ defined as in the Appendix.
+\end{lemma}
+
+The full derivation resembles the case with many challengers, and we leave for the Appendix.
+Qualitatively, the addition of more incumbents aggravate the collective action problems in two aspects.
+First, we have the free-riding problem, as politicians prefer to leave others to pay the exposing costs.
+Second, the absence of coordination among rival politicians increases the chances that challengers target some incumbents more than others.
+
+\subsection{Summarizing the effects of the number of incumbents and challengers}
+
+The following corollary summarizes the effects found above:
+
+\begin{corollary}
+Let the strategic interaction as summarized in the previous Lemmas.
+Then, increasing the number of challengers increases the incentives for corruption, as it promotes free-riding in the corruption exposures by challengers.
+Increasing the number of incumbents increases even further the incentives for corruption by promoting free-riding and coordination failures in the corruption exposures.
+\end{corollary}
+
+In equilibrium, the situation that induces the major incentive to embezzle is when we add challengers and incumbents simultaneously.
+Lowering the amount of either one of them, we also decrease the incentives for corruption, as denouncing the wrongdoing by incumbents become more profitable for challengers.
+
+To summarize the discussion in the previous Lemmas, we have the following testable hypothesis:
+
+\begin{enumerate}
+ \item[H. 1] Increasing the number of seats, keeping all other characteristics constant, increase corruption.
+ \item[H. 2] Increasing the number of competitors, keeping all other characteristics constant, increase corruption.
+\end{enumerate}
+
+These hypothesis can be rephrased in terms of the incentives they produce for challengers to use corruption information against incumbents.
+However, phrased in terms of corruption incentives they have the advantage to lead to testable implications.
+
+# Corruption and XXXX: Evidence from Brazilian and Italian Municipalities
 \label{sec:results}
 
-Here goes the results.
+Empirical evidence shows that electoral rules affect corruption.
+However, papers present often-contradictory evidence, due to the difficulty of isolating the causes of corruption using observational data.
+To remedy this gap, I study two quasi-natural experiments in the Brazilian context: the exogenous population thresholds for the legislature size and competition \citep{cepaluni2015politicians, britto2016corruption} and population threshold for run-off \citep{ferraz2011electoral, fujiwara2011regression}.\footnote{Some of these results were found originally by \citet{ferraz2011electoral} for runoff, and by \citet{britto2016corruption} for legislature size.
+I replicate their findings, mainly confirming their original assessment, and providing microfoundations for their results.} The results confirm that competitiveness and district sizes are key for corruption.
+
+\subsection{Data, Sources of Variation, and Identification Strategy}
+
+To construct the dependent variable, I use two different codings for the Brazilian Municipal Audit program.
+This program was launched in 2003 by the Brazilian Federal government, and since 2004 it consists of a federal audit of a random lottery of 60 municipalities.
+Federal auditors go to each selected town collecting evidence of inefficiencies and corruption with the use of federal transfers.
+\citet{brollo2013political} and \citet{avelino2016replication} coded these lotteries, each with a different focus.
+\citet{brollo2013political} coded the lotteries 2 to 29, looking for \textit{broad} irregularities (incompetence) and \textit{narrow} irregularities (corruption).
+\citet{avelino2016replication} coded the lotteries 8 to 33, with the focus on health care transfers, coding the \textit{frequency} of detected malfeasance events, and the \textit{amount} involved.
+
+I use two population thresholds as an exogenous variation for competition, legislature size (city council district size), and competition in single-member district elections (mayoral elections).
+First, in 2004, the Brazilian Electoral Court ruled that the 29th Federal Constitution article that assumes a range from 9 to 21 city councilors for municipalities with less than a million inhabitants be miss-interpreted by towns.
+The court suggested that each municipal council should start with nine councilors, adding one councilor for every 47,619 inhabitants, which is the ratio of a million divided by 21 councilors.
+The electoral justice enforced the population thresholds for the council during two terms: 2004 and 2008.
+In 2009, the Congress amended the constitution, changing the council sizes and other council characteristics \citep{cepaluni2015politicians, britto2016corruption}.
+We use these thresholds as a shock on district size, and also on the competition.
+This because district size varies sharply with legislature size, pushing competition to also increase with these threshold variations.
+Second, the Brazilian electoral law mandates that municipalities with more than 200 thousand inhabitants should have a run-off for their mayoral elections \citep{fujiwara2011regression}.
+This emulates a single-member district with one competitor dispute (run-off), versus a single-member district with more than one competitor (no run-off).
+Figure \ref{empstrat} illustrates the empirical strategy.
+
+\begin{figure}[htp!]
+    \centering
+    \begin{tikzpicture}
+      \node[block] (a) {Run-off\\ threshold};
+      \node[block, below =2cm of a] (b) {Council size\\ thresholds};
+      \node[block, right =2cm of a] (c) {Competition\\ mayors' offices};
+      \node[block, below =2cm of c] (d) {Competition\\ city councils};
+      \node[block, below =2cm of d] (e) {City council \\ sizes};
+      \node[block, right =2cm of d] (f) {Corruption\\ measurements};
+
+      \draw[line] (a.east) -- (c.west);
+      \draw[line] (b.east) -- (d.west);
+      \draw[line] (b.south) |- (e.west);
+
+      \draw[line] (c.east) -| (f.north);
+      \draw[line] (d.east) -- (f.west);
+      \draw[line] (e.east) -| (f.south);
+
+      \node[container, fit=(a) (b)] (es) {};
+      \node at (es.north west) [above right,node distance=0 and 0] {Exogenous Shocks};
+
+      \node[container, fit=(c) (d)] (trc) {};
+      \node at (trc.north west) [above right,node distance=0 and 0] {Competitiveness};
+
+      \node[container, fit=(e)] (trd) {};
+      \node at (trd.north west) [above right,node distance=0 and 0] {District Size};
+    \end{tikzpicture}
+    \caption{Empirical strategy}
+    \label{empstrat}
+\end{figure}
+
+The model starts with the institution design to measure the corruption impacts, but the empirical strategy abstracts away from the precise formulation in order to estimate the model.
+There are two key changed features.
+First, it assumes that competition relates to district size.
+Second, it abstracts the role of challengers, assuming that it is working on the background as postulated by the formal model.
+For the first caveat, I also run robustness checks, splitting the sample into above and below the median competition per seat, and the results remain as postulated (above the median the coefficient is more significant).
+For the second point, I show in the appendix qualitative evidence that negative campaign and corruption claims, especially aimed against mayors, are considerably larger in run-off municipalities, compared with municipalities closer to the run-off thresholds.
+
+\subsection{Results}
+
+On the top of Figure \ref{figregcoef} I apply the empirical strategy for \citet{brollo2013political} \textit{broad} and \textit{narrow} irregularities detection, and below I estimate the same models for \citet{avelino2016replication} data on incidence and amount of discovered malfeasance on health care transfers.
+To keep our approach consistent, I limit the data to the 2005-2008 mayoral term.
+The results follow below.
+
+\begin{figure}[!htb]
+ \centering 
+ \includegraphics[width=1\textwidth]{graphCoefs.pdf}
+ \caption{Regression coefficients for interplay between electoral systems, competition, and corruption}
+ \label{figregcoef}
+\end{figure}
+
+I divide the results into four quadrants, plotting the coefficients for each model I run, based on the strategy presented in Figure \ref{empstrat}.\footnote{ I run an instrumental variable regression using the legislator threshold cutoffs as an exogenous shock for candidacy, regression discontinuity design for city council size, and t-test, selecting the municipalities close to the run-off cutoff, for a run-off.
+The reason for not running an RDD for the run-off is the fact that there were too few cases in the right-hand size (municipalities with more than 200 thousand voters).
+To emulate an RDD result I restrict the sample to the municipalities with 50 thousand voters around the 200 thousand run-off threshold.} In the top-left, the broad corruption findings represent inefficiency detection.
+As the model has no prior hypothesis on inefficiency, I keep it here as a placebo check, in order to study a possible oversensitivity of the empirical model.
+As the Figure shows, no coefficient is significant for inefficiency detection.
+
+In the top-right I present the results for \citet{brollo2013political} narrow corruption charges.
+These estimates work as expected: more competition and larger district sizes increase the chance of detect corruption 24\% and 56\%, respectively.
+Run-off decreases the amount of corruption 67\%.
+
+In the bottom-left we examine the \citet{avelino2016replication} frequency of detected corruption in health care.\footnote{ Health care is a good outcome of studying corruption incidence because it consumes a considerable portion of the municipal budget (around 25\%), and most voters in Brazil reward handsomely a good public healthcare administration \citep{fujiwara2015voting}.} As we can see, one standard deviation increase in candidates running for mayor and council increase in 20\% and 12\% the frequency of detected malfeasance, respectively.\footnote{ One standard deviation for the competition variables is 1.04 and 4.6 competitors for mayor and city council, respectively.
+See the Appendix for the full list of descriptive statistics.} The other coefficients are in the predicted direction, but not significant at 10 or 5\% levels.
+
+Finally, in the bottom right we have the fraction of healthcare investments where the auditors detected incidences of corruption.
+Consistent with the model predictions, adding one standard deviation of mayoral and city council competitors increase the investments with corruption irregularities by 15\% and 9\%, respectively.
+Having run-off decreases the investments with corruption by 47\%.
+The city council size coefficient is in the predicted direction, but not significant at the conventional levels.
+
+In sum, the empirical results largely confirm the hypotheses \textbf{H1} and \textbf{H2} derived from the formal model.
+In the appendix we run a few robustness and placebo checks, to test whether the findings here are resistant to small specification changes.
+All results remain consistent and significant in the majority of the different specifications.
 
@@
 
-Here goes the discussion.
+This paper lays out the micro-foundations for the relation between corruption and electoral rules.
+It shows that challengers and incumbents have different incentives to investigate or engage in corruption activity in equilibrium.
+It also tests the theory using quasi-experimental variation, showing that the incentives generated by the institutions key for political corruption.
+
+Electoral systems are embedded into an array of trade-offs, and also generate many other political and representational effects within the society.
+Majoritarian systems are great for accountability, as they foster clarity of responsibility \citep{tavits2007clarity, xezonakis2015can}, and as this paper shows, they also promote lower levels of corruption.
+However, they also tend to be highly polarizing and have a considerable amount of wasted votes, which grow steadily with the number of candidates credibly competing for the seat.
+On the other extreme, proportional representation systems ensure less wasted votes, but parties proliferate on it.
+It quickly becomes ungovernable without broad coalitions and inter-party agreements, which are usually rigged by corruption in developing economies \citep{mello2018brazil}.
+
+To some extent, this paper delivers a very synthetic result: the incentives for engagement and for exposing corrupt behavior are dependent on the collective action problems generated within the political system.
+The results favor single-member districts with just one competitor when it comes to corruption.
+However, in between the extremes of single-member districts and full open-list proportional representation, some institutions work positively in fighting corruption.
+
+First, the existence of run-offs, such as in the French parliament, improves corruption outcomes without artificially limit the number of competitors.
+The run-off compensates the predatory competition that happens in the first round, and politicians may work to expose corruption by incumbents, lowering the incentives to corrupt behavior.
+
+Second, threshold laws, which are harmful to the inclusion of different cleavages, may help to avoid predatory competition, decreasing corruption.
+Third, the results here tend to favor findings such as \citet{schleiter2014party} and \citet{schleiter2016party}, which claim that strengthening parties in proportional representation systems decrease political corruption, suggesting that closed lists may be better for lowering corruption.
+In my model, the rationale is because strong parties may efficiently coordinate the corruption exposures, aiming at taking down not only a single politician but also an entire corrupt rival party.
+Stronger parties improve coordination and lower free-riding, especially when there are a limited number of parties.
+
+Finally, small district sizes in proportional representation, such as in the Chilean electoral system, maybe not only positive for the interplay between representation and accountability \citep{carey2011electoral}, but also in lowering corruption, when compared with large district proportional representation.
+The Brazilian system, with weak parties, open-list proportional representation, and large district sizes (varying between 8 and 70 legislators) proves that corruption can easily become endemic, with considerable negative impact on the quality of democracy and accountability \citep{avis2016government, mello2018brazil}.
 

### 2021-08-20 article/article.Rmd
adding abstract, updating references

@@
 Second, adding more seats increase the likelihood of coordination failure, as the same incumbent may be exposed more than once while others may be not exposed at all.
-These two effects lower the incentives for exposing corrupt politicians, and they reasonably explain why countries with open-list proportional representation systems are endemic corrupt \citep{Myerson1993, ames1995electoral, mello2018brazil}.
+These two effects lower the incentives for exposing corrupt politicians, and they reasonably explain why countries with open-list proportional representation systems are endemic corrupt \citep{Myerson1993, ames1995electoral}.
 
@@
 On the other extreme, proportional representation systems ensure less wasted votes, but parties proliferate on it.
-It quickly becomes ungovernable without broad coalitions and inter-party agreements, which are usually rigged by corruption in developing economies \citep{mello2018brazil}.
+It quickly becomes ungovernable without broad coalitions and inter-party agreements, which are usually rigged by corruption in developing economies.
 
@@
 Finally, small district sizes in proportional representation, such as in the Chilean electoral system, maybe not only positive for the interplay between representation and accountability \citep{carey2011electoral}, but also in lowering corruption, when compared with large district proportional representation.
-The Brazilian system, with weak parties, open-list proportional representation, and large district sizes (varying between 8 and 70 legislators) proves that corruption can easily become endemic, with considerable negative impact on the quality of democracy and accountability \citep{avis2016government, mello2018brazil}.
+The Brazilian system, with weak parties, open-list proportional representation, and large district sizes (varying between 8 and 70 legislators) proves that corruption can easily become endemic, with considerable negative impact on the quality of democracy and accountability \citep{avis2016government}.
 

### 2021-08-21 appendix/appendix.Rmd
appendix structure

@@
 title: |
-       | Supplementary Materials for "Legislature Size and Welfare: Evidence from Brazil"
+       | Supplementary Materials for "Electoral Systems, Competition, and Incentives for Corruption"
 author:
-  - Gabriel Cepaluni[^gabriel]
-  - Danilo Freire[^danilo]
   - Umberto Mignozzetti[^umberto]
@@
 
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
-
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
-
-[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
 
 \appendix
-\addtocounter{section}{2}
 
@@
 
-## A Model of Legislature Size and Service Provision
-
-### Primitives of the Model
-
-Consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors, indexed in $i \in \{1, 2, \cdots, N \}$.
-The mayor is the head of the local executive branch, and has the prerogative of proposing a vector of policies, that is voted by the city councilors.
-Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors \textbf{x}.
-
-The city council votes the mayor's proposal and if they accept it, it is implemented.
-Otherwise, a reversal policy takes place.
-Reversal policy in this context means that the mayor's proposal failed to secure majority of council votes.
-The decision process leaves the mayor's office, and either immediately stops or it is transferred to the council.
-The types of reversal policies are crucial for our argument, as it changes the relative strength of the council in their bargaining with the mayor.
-We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan affiliation; a \textit{partisan} reversal mechanism, where the council is divided in supporters and non-supporters of the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan with non-partisan features.
-In the main paper, we focus on the hybrid model, as it is the more realistic scenario.
-Despite that, comparing the partisan and non-partisan reversal mechanisms illustrate clearly our argument that the partisan a mechanism is what drives our results.
-
-To govern, the mayor has to convince at least half of the city councilors to support her policy proposals.
-Similar to \citet{buenodemesquita2005logic}, we assume that the selectorate, i.e.
-the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors.
-The winning coalition, which is the minimum number of members that have to be convinced to implement the policy, is equal to half of the selectorate $N/2$.
-City councilors are moved by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}.
-We leave the definition of these transfers open, as this facilitates the relation with several instruments that mayors can use to pressure city councilors.
-To illustrate, examples of transfers are granting electoral favors, spending in areas that the councilor has political or personal interests, granting portfolio and public jobs within the municipal bureaucracy, or even campaign contributions and bribes.
-The use of transfers to affect the councilors' choices and generate a governing cost of $C_G$.
-The governing costs vary with the reversal mechanism and the legislature size.
-
-Finally, after paying the costs of govern, the mayor proposes a level of public goods provision ($g$) and rents ($r$).
-Public goods provision help the mayor to get reelected.
-Rents are for direct mayor's consumption, and does not contribute to the mayor's electoral success.
-This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection.
-Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.\footnote{In technical terms, $u'>0$ and $\pi'>0$; and $u''<0$ and $\pi''<0$.} The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
-This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office.
-We assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to say that mayors have a strong preference to be reelected.
-If the mayor's policy proposal is approved, then the expected utility for the mayor is:
-
-\[
-\mathbb{E}U(r, g) \ = \ u(r) + B_M\pi(g)
-\]
-
-The policy choices of the mayor are subject to the municipal budget constraint.
-The municipality has $R > 0$ resources, and cannot run debts, meaning that the budget has to be balanced.
-We also assume that there are enough resources for the mayor to govern.
-
-Let $C_G$ be the costs of govern. The budget balance constraint requires the offers that the mayor makes to the city councilors satisfy the following inequality:
-
-\[
-r + g + C_G \ \leq \ R
-\]
-
-The expected utility for the city councilors depend on the reversal policy.
-As discussed, we explore three different mechanisms.
-First, in \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminish by a factor of $\delta \in (0,1)$ and the selection of one councilor randomly.
-The randomly selected councilor becomes the new proposer.
-If her proposal is accepted, it is implemented.
-If it is rejected, the budget shrinks again by a factor $\delta$, and another city councilor is recognized to make the proposal.
-The process repeats, until one proposal is finally accepted.
-
-In the second reversal mode, the \textit{partisan} reversal mechanism, we assume that each councilor has a party affiliation.
-Party affiliations are mutually exclusive (a councilor cannot belong to two parties at once).
-If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
-Otherwise, the city councilor belongs to the opposition $O  = \{1, 2, \cdots, N \} \setminus G$.
-The mayor's policy generate a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends of the party affiliation of the councilor.
-If the mayor's proposal is rejected, a city councilor aligned with the mayor, that would receive $p$ from the policy, now receives zero.
-On the other hand, a city councilor that belongs to the opposition would receive $-p$ from the mayor's policy, and now receives zero.
-Although these assumptions are strong, they capture the underlying political dynamics of partisanship: the political preferences in terms of public goods provision are shared by councilors aligned with the mayor.
-Voting against the mayor's proposals would represent to defy the partisan label.
-
-Lastly, in the \textit{hybrid} reversal mechanism, we combine partisanship with legislature bargaining costs.
-Councilors in this mechanism receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the non-partisan reversal mechanism takes place.
-In the mayor's proposal stage, city councilors that belong to the mayor's coalition receive a gain of $p > 0$ when the mayor's policy is implemented.
-Opposition members, on the other hand, receive $-p$ when the mayor's proposal is implemented.
-If the mayor's proposal is rejected, as the city council does not control the Executive when the two branches are separated, no public goods are provided ($p=0$).
-Moreover, in equilibrium, we assume that city councilors would prefer to receive transfers instead of providing public goods.
-This aligns with the empirical evidence in most developing economies.
-
-The timeline of the game is as follows:
+# Formal Model
+\label{app:specs}
+
+Consider three sets of players: a set of incumbents $ I \ = \ \{ I_1, \ \cdots, \ I_K \}$, a set of challengers $C \ = \ \{ C_1, \ \cdots, \ C_L \}$, and a continuum of $V$ voters.
+
+Each incumbent has a budget of $A$ units, that has to be invested in public goods.
+The level of expenditure necessary to provide the goods is a random variable $\eta \in [0,A]$, where $\eta \sim f(\eta)$, and $f$ is a weakly increasing PDF function with CDF $F$.
+If the public goods are successfully provided, we say that the policy result is good ($\psi = G$).
+Otherwise, we say the policy result is bad ($\psi = B$).
+
+Let $\e$ be the vector of expenditures enacted by the incumbents.
+The public goods are provided whenever $K \cdot \eta \leq \sum_i e_i$, where $K$ represents number of incumbents.
+I assume that all incumbents observe the true $\eta$, and it is common-knowledge among them.
+
+After choosing the expenditures, the public goods provision is realized and is common knowledge to all players.
+Now the campaign stage starts.
+Challengers face no running costs, and although they do not observe $\eta$, they know $\e$ and $\psi$.\footnote{This assumption does not change the game because an entry cost would only shift the equilibrium, preserving its qualitative characteristics.}
+
+Upon observing $\e$ and $\psi$, challengers update their beliefs about $\eta$, and decide simultaneously weather to use negative campaign against the incumbents, paying a cost of $c \in \mathbb{R}_{+}$ whenever they use their full resources to expose a corrupt incumbent.
+After their decisions, the result is a vector $\dd \in \{0,1\}^{K}$ of sucessfully exposed corrupt incumbents, for each incumbent $i$ in $\{1, \cdots, K\}$.
+The probability that challenger $j$ investigating $i$ credibly communicate the $i$'s true corruption engagement to the voter is $\lambda: [0,A] \rightarrow [0,1]$.
+I assume $\lambda(0) = 0$ and $\lambda^{'} > 0$.
+Therefore, the probability of being credibly exposed depends on the distance between the optimal expenditure and the amount spend by the incumbent.
+
+Finally, the voters have to decide whether to retain or dismiss the incumbents, upon observing $\psi$ and $\dd$.
+Their choices are summarized in a vector $\bups \in \{0,1\}^{K+L}$, where $1$ means that the politician is elected (or reelected, in case of an incumbent) and $0$, meaning not elected.
+We have that $\sum_i \upsilon_i = K$, and when the voter is asked to decide, she cannot change the results of $\psi$ and $\dd$.
+The voters' decisions are always sequentially rational.
+Therefore, I impose that they behave optimally by dismissing an incumbent $j$ that were credibly related with corruption, or all incumbents, when $\psi=B$.
+
+The time-line of the game is as follows:
 
 \begin{enumerate}
-  \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
-  \item The mayor proposes a policy vector $(r, g, x)_M$.
-  \item The city council votes the proposal.
-  \begin{itemize}
-    \item If the council accepts, the policy is implemented and the game ends. 
-    \item Otherwise, the reversal policy is implemented.
-  \end{itemize}
-  \item (Reversal Policy) Depends on which mechanism, we have three different reversal policies. The details are in the following sections.
+ \item The nature draws $\eta$;
+ \item Each incumbent observes $\eta$ and chooses, simultaneously, $\e$;
+ \item $\psi$ is realized. Challengers choose, also simultaneously, whether to invest resources to expose corrupt incumbents;
+ \item The vector of successfully exposed incumbents $\dd$ are realized. The voter chooses $\bups(\psi, \ \dd)$ and the game ends.
 \end{enumerate}
 
-The solution concept we use in this model is the Sub-game Perfect Nash Equilibrium.
-A Sub-game Perfect Nash Equilibrium requires that the strategies played are a Nash Equilibrium in each of the subgames of the game.
-The solution is found using backward induction.
-In the model with infinitely repeated proposals, we extend the equilibrium concept to require that the equilibrium is Stationary.
-A Stationary Sub-game Perfect Equilibrium requires that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should accept the same offer at time $k$.
-Stationarity gives us an objective of finding an offer that would be accepted at any stage in the game.
-Applying this reasoning, we can find a sequence of offers for each point $k$ in time.
-For the mayor, the optimal offer is at $k=0$, and this represents a no delay in policy implementation.
+An incumbent $i$'s strategy is defined as:
+
+\[
+\varepsilon_i:[0,A] \rightarrow [0,A] 
+\]
+
+And the challenger $j$'s strategy is defined as:
+
+\[
+\bvphi_j:\{G, \ B \} \times [0,A]^K \rightarrow [0,1]^K
+\]
+
+Representing the amount of time invested by each challenger $j \in \{1, \cdots , L \}$ to expose an incumbent $i$.
+Notice that $\bvphi_j$ is a vector of size $K$, where each component is the probability of exposing one of the incumbents.
+For the representative voter we have:
+
+\[
+\bups:\{G, \ B \} \times \{0, \ 1 \}^{K} \rightarrow \{0, \ 1 \}^{K+L}
+\]
+
+That represents the decision to retain or dismiss each politician, with their replacement. The expected utilities for each player are, for the incumbents:
+
+\[
+U_i (\varepsilon_i; \ \eta, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) \ = \ u(\varepsilon_i - \eta) + B \ \Prob (\upsilon_i = 1 \ | \ \psi, \dd) 
+\]
+
+Where $B$ is the reward for staying in office (assumed the same for every player) and $\Prob (\upsilon_i = 1 \ | \ \psi, \dd)$ is the probability of being retained, given $\psi$ and the exposure profile $\dd$.
+For the challenger $j$:
+
+\[
+U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}) \ = \ B \int_{0}^A \Prob (\upsilon_j = 1 \ | \ \eta, \bveps^{*}, \bvphi^{*})\mu(\eta|\bveps^{*}) d\mu(\eta) - c \sum_{i=1}^K \varphi_{ij}(\psi, \bveps^{*})
+\]
+
+With $c > 0$ being the cost of performing one full corruption exposure.
+Notice that the total amount spent on exposing corrupt politicians will be the sum of the amounts spent on each exposure.
+The representative voter's expected utility is defined as:
+
+\[
+U_V (\psi, \dd, \bups) \ = \ \indf \{\psi=G \}r_G
+\]
+
+Where $\indf$ is the indicator function for $\psi=G$ and $r_G$ the value of the public good for the voter.
+Notice that no $\psi=B$ is observed on the equilibrium path, as underspending is a dominated strategy.
+
+Also, any retention rule selected for the voters is sequentially rational, because there is no uncertainty about the results when they vote.
+I choose the optimal rule for the voter as dismiss all incumbents when $\psi=B$ or replace incumbents that were successfully exposed by challengers when $\psi=G$.
+This rule is ex-post efficient as over-dismissal would make incumbents to pocket all the money regardless of $\eta$.
+
+Finally, I solve for the \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}. A perfect Bayesian equilibrium consists in a pair of strategies and beliefs such that:
+
+\begin{enumerate}
+ \item In each information set, the decision should be sequentially rational;
+ \item Each strategy is compatible with its beliefs concerning the behavior on and off the equilibrium path.
+\end{enumerate}
+
+Also, as this is a signaling game, I use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}.\footnote{The restriction imposed by the universal divinity requires that the challengers, facing a deviation from the equilibrium path, put probability one on the type that are more likely to deviate.
+Moreover, as we have a continuum of types in one of the types dimensions, we use the approach by \citet{Malaith1987}, which consists in find the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.}
 
 \begin{definition}
-The equilibrium for the game consists in a sequence of strategic policy vectors $(g^*, r^*, x^*)_k$, indexed in $k \in \{0, 1, \cdots, \infty\}$, such that, at every stage of the game, the mayor and the councilors have no profitable deviations from the equilibrium.
+ \label{def_eqn}
+ A Perfect Bayesian Equilibrium for the game described, with $|I|=K$ and $|C|=L$, $K$ and $L$ in $\mathbb{N}$, type space $T=[0,A]$, consists in optimal strategies $\bveps^{*}$, $\bvphi^{*}$, $\bups^{*}$ and beliefs $\mu^*$, that satisfy
+ \begin{enumerate}
+  \item $\forall t_i \in T$, $\varepsilon^{*}_i(t_i)$ maximizes $ U_i (\varepsilon_i; \ t_i, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) $ $\forall i \in \{1, \cdots, K\}$.
+  \item $\forall \bveps \in \left[0,A \right]^K $ and $\psi \in \{B, \ G \}$, $\bvphi^{*}_j(\bveps, \psi)$ maximizes $ U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}, \ \mu^*) $, $\forall j \in \{1, \cdots, L\}$
+  \item $\forall \psi \in \{B, \ G \}$ and $\dd \in \{0,1\}^L$, $\bups^{*}(\psi, \dd)$ maximizes $ U_V (\psi, \dd, \bups^*) $.
+  \item The beliefs are derived using Bayes rule whenever possible, and for all $\varepsilon_i$ that are off-the-equilibrium path, $\mu^*(t_i| \varepsilon_i)>0$ (in fact, 1) only if $\widehat{\varepsilon}_i \in \arg \min_{t_i} p(t_i, \widehat{\varepsilon}_i)$, where $ p(t_i, \widehat{\varepsilon}_i)$ is the profit from deviating from $\varepsilon_i$ to $\tilde{\varepsilon}_i$ for a type $t_i$.
+ \end{enumerate}
 \end{definition}
 
-Moreover, we assume that the players play no dominated strategies, even when there is less than sufficient support for implementing the policy.
-
-### The Mayor's Decision Stage
-
-Solving the game by backward induction requires us to start with the councilor's strategies.
-However, for exposure convenience, assume at this point that we solved the the game for the councilors, and found the equilibrium cost of govern $C_G(N)$ when there are $N$ city councilors.
-In the next section, we define $C_G(N)$ for each of the mechanisms using backward induction, and the definitions are well-behaved.
-In this section, we use this assumption to simplify the exposition.
-
-We now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
-The mayor benefits from public goods provision, as it increases the chances of her reelection.
-However, she prefers to contribute as minimum as necessary for the public goods, and extract the remaining resources as political rents.
-The mayor's objective is to maximize her expected utility, subject to the municipal budget constraint.
-
-\[
-\begin{aligned}
-\max_{r, g} \quad & u(r) + B_M\pi(g)\\
-\textrm{s.t.} \quad & r + g + C_G(N) \leq R
-\end{aligned}
-\]
-
-In equilibrium the budget binds, and the public goods provision maximizes:
-
-\[
-\max_{g} \{ u(R - g - C_G(N)) + B_M\pi(g) \}
-\]
-
-The first order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equals to the marginal benefits of reelection:
-
-\[
-u'(R - g - C_G(N)) = B_M\pi'(g)
-\]
-
-This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_G(N)) + B_M\pi''(g^*) < 0$.
-
-\begin{proposition}
-The provision of public goods increase with legislature size when the costs of govern decrease with legislature size.
-\end{proposition}
+## Single-Member Districts with One Challenger
+
+Let $|I|=1$ and $|C|=1$. Solving the game backwards, the voters retain the incumbent if the policy result was good and no corruption was exposed.
+
+From the challenger's perspective, as there is no cost of entry, she decides whether to invest her campaign resources in exposing the incumbent.
+She does so when the expected utility of exposing is greater than or equal the expected utility of not exposing, given her beliefs about the true value of $\eta$.
+Thus:
+
+\[
+B \int_{t_i \in T} \Prob (\bups = (0,1)\ | \ \eta, \varepsilon^*, \varphi)\mu^*(t_i|\varepsilon^*) d\mu - c \varphi(\psi, \varepsilon^*) \geq 0
+\]
+
+Rearranging and applying the fact that $ \Prob(\bups = (0,1) | \varepsilon^*, \varphi ( \psi, \varepsilon^*), \eta) = \varphi(\psi, \varepsilon^*) \lambda(\varepsilon^*-\eta) $ and $\mu^*(t_i | \varepsilon^*) = \mu(\eta) = \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta}$,
+
+\[
+B \varphi(\psi, \varepsilon^*) \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta - c \varphi(\psi, \varepsilon^*)
+\]
+
+Isolating $\varphi(\psi, \varepsilon^*)$, letting $\lambda_\varepsilon = \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta$ and $Q(B, c) = \dfrac{c}{B}$, we see that sequential rationality implies that the challenger expose corrupt incumbents for sure whenever $\lambda_\varepsilon > Q(B, c)$, never expose corruption when $ \lambda_\varepsilon < Q(B, c)$, and is indifferent when $\lambda_\varepsilon = Q(B, c)$.
+
+Now let $\dfrac{\int_0^A \lambda(A - \eta)f(\eta) d\eta}{\int_0^Af(\eta)d\eta} = Q^*$.
+If $Q \geq Q^*$, we have only one equilibrium, which will be to play $A$ regardless of $\eta$.
+And there will be no exposures in equilibrium, as they are too expensive to be performed.
+To avoid this situation, we impose the following condition:
+
+\begin{assumption}\label{assExist}
+We assume $B$ and $c$ are restricted in such a way that $Q<Q^*$.
+\end{assumption}
+
+Given this assumption, there exists $\overline{\eta}$ such that
+
+\[
+\lambda_A = \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta)f(\eta) d\eta}{\int_{\overline{\eta}}^Af(\eta)d\eta} = Q(B, c)
+\]
+
+In equilibrium, we seek for roots to the equation $\lambda_A-Q(B, c)$.
+These roots are well characterized, as if $\overline{\eta}=0$, $\lambda_A - Q (B, c) \geq 0$ and if $\overline{\eta}=0$, $\lambda_A=0$ and so the value is negative.
+As this function is continuous, by the intermediate value theorem, we have a root, that we call $\overline{\eta}$.
+The monotonicity of $f$ also ensures that each root is unique.
+
+$\overline{\eta}$ has an intuitive interpretation: it is the minimal value for $\eta$ such that above this value, the incumbent always prefers to play $A$ regardless of $\eta$.
+
+Now, let a probability function $\delta(\varepsilon)$ to characterize the equilibrium amount of negative campaign when $\varepsilon \in [ 0, \ \overline{\eta}]$.
+The optimal $\varepsilon$ solves the equation $\lambda_\varepsilon = Q(B, c)$, making the challenger indifferent between exposing or not the incumbent's corruption.
+As $\lambda(.)$ has a well defined inverse function, the optimal strategy for the incumbent is:
+
+\begin{equation*}
+\varepsilon^*(\eta) \ = \ \eta + \lambda^{-1}\left(\dfrac{c}{B}\right)
+\end{equation*}
+
+Therefore, the required value plus a kickback $\kappa$ defined as $\kappa = \lambda^{-1}\left(\dfrac{c}{B}\right)$, whenever $\eta \in [0, \overline{\eta}]$, and $A$ otherwise.
+
+Now, reasoning backwards, the incumbent only plays this strategy when it is incentive compatible for her, and to be an optimal response, it should be an $\arg \max$ of $U_I$.
+Taking the derivative of $U_I$ and setting it to zero gives us the following differential equation for $\delta(\varepsilon)$:
+
+\[
+\dfrac{d \delta}{d \varepsilon} + \delta(\varepsilon)\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)} = \frac{1}{B}\frac{u^{'}(\kappa)}{\lambda(\kappa)}
+\]
+
+Under the boundary condition that $\delta(\kappa)=0$.
+This represents a well defined first order differential equation, that has an straightforward unique solution determined by the boundary condition.
+Solving for $\delta(\varepsilon)$, we have:
+
+\[
+\delta(\varepsilon) = \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right)
+\]
+
+Combining all these results together  us the following lemma.
+
+\begin{lemma}
+ \label{lemma_m1}
+ A Perfect Bayesian Equilibrium for the game when $|I|=1$ and $|C|=1$ is a pair of strategies and beliefs such that the optimal strategies are
+ \begin{enumerate}
+  \item For the incumbent
+  \[
+  \varepsilon^{*}(\eta) \ = \ \twopdo{\eta + \kappa}{\eta \leq \overline{\eta}}{A}
+  \]
+  \item For the challenger
+  \[
+  \varphi^*(\varepsilon) \ = \ \threepdo{0}{\varepsilon < \kappa}{\delta(\varepsilon)}{\varepsilon \in [\kappa, \overline{\eta}]}{\delta(A)}
+  \]
+  \item And for the voter, retain the incumbent if $\dd=0$ and $\psi=G$ and dismiss otherwise.
+ \end{enumerate}
+ With 
+ \[
+ \delta(\varepsilon) = \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right)
+ \]
+ and
+ \[
+ \kappa = \lambda^{-1}\left(\dfrac{c}{B}\right)
+ \]
+ And the optimal beliefs updated by Bayes rule whenever possible, with the out-of-the path beliefs restricted by the Universal Divinity Criteria.
+\end{lemma}
 
 \begin{proof}
-To prove this result we need to show that the mayor's expected utility satisfy the increasing differences in $g$ and $N$.
-This would mean that when increasing the size of the council, the optimal solution $g^*$ would also increase.
-However, as $N$ increases discretely, we cannot take a the cross-partial derivative on $N$ or even use the implicit function theorem.
-Instead, we use monotone comparative statics to derive these results \citep{milgrom1994monotone}.
-
-The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$,\footnote{Moreover, the requirement that the decision and type space is a complete lattice, is satisfied for $\mathbb{R} \times \mathbb{N}$.} we have:
-
-\[
-\mathbb{E}\text{U}(g, N+1) - \mathbb{E}\text{U}(g', N+1) \geq \mathbb{E}\text{U}(g, N) - \mathbb{E}\text{U}(g', N)
-\]
-
-After substituting, we have:
-
-\[
-u(R - g - C_G(N+1)) + B_M\pi(g) - u(R - g' - C_G(N+1)) - B_M\pi(g') \geq 
-u(R - g - C_G(N)) + B_M\pi(g) - u(R - g' - C_G(N)) - B_M\pi(g')
-\]
-
-Which is equal to:
-
-\[
-u(R - g - C_G(N+1)) - u(R - g' - C_G(N+1)) \geq 
-u(R - g - C_G(N)) - u(R - g' - C_G(N))
-\]
-
-Multiplying both sides by $\dfrac{1}{g - g'}$ and taking the limit when $g \rightarrow g'$, we have:
-
-\[
-u'(R - g - C_G(N+1)) \geq 
-u'(R - g - C_G(N))
-\]
-
-It is now clear to see that the function satisfies the increasing differences in $g$ and $N$ when the governing costs of a $N+1$-sized city council is lower than the governing costs of a $N$-sized city council:
-
-\[
-C_G(N+1) \leq C_G(N)
-\]
+
+Let $\varepsilon^*$ and $\varphi^*$ as defined in the Lemma \ref{lemma_m1}.
+To show the existence and the characteristics of the separating equilibrium, following \citet{Malaith1987} we need to prove the following Claim:
+
+\begin{claimnn}\label{claim1}
+The expenditure in weakly increasing in the type $t_i \in T$
+\end{claimnn}
+
+\begin{proof}[Proof of Claim \ref{claim1}]
+First, notice that the type space $T$ is a compact set, and thus a complete lattice. Then:
+
+\[
+\dfrac{\partial^2 U}{\partial \varepsilon \partial \eta} = -u^{''} + B(\varphi(\varepsilon)\lambda^{''} + \varphi^{'}(\varepsilon)\lambda^{'}) 
+\]
+
+And so, as $\lambda$ is weakly increasing, $\lambda^{''}>0$ and $u$ is concave, $U$ satisfies the increasing differences properties in $\varepsilon$ and $t$.
+As $T$ is a lattice, we have that $\varepsilon^{*}(\eta)$, which is a maximum for $U_I(t_i, \varepsilon(t_i) )$, is also weakly increasing in $\eta$.\footnote{See \citet{MilgromShannon1994}, theorem 6.}
 
@@
 
-This provides us our first empirical hypothesis to test: \textit{if the governing costs decrease when the legislature increases, then the public goods provision increase when the legislature size increase}.
-
-At this stage, we need to solve for existence of these governing costs.
-Below we show that this proposition is true for the *partisan* and *hybrid* mechanisms, but it is not true for the *non-partisan* mechanism.
-
-### Non-Partisan Reversal Mechanism
-
-In the \textit{non-partisan reversal} mechanism, we assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
-To find the stationary sub-game perfect Nash equilibrium, suppose that there were $k-1$ rejections, and we are at the $k$-th stage in the game.
-A councilor accepts the proposer's offer if, and only if, to accept the offer at $k$ is better than to wait until the next stage $k+1$.
-If the offer is $x_i$, then:
-
-\[
-x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left( 1 - \dfrac{1}{N} \right)\left[\dfrac{1}{2} x_i \right]
-\]
-
-In the left-hand side, we place the offer.
-In the right-hand side, there are two components.
-The first is the amount that the councilor $i$ gets when she is the proposer.
-It is equal to the chance that she is recognized as the proposer times the budget in the next round minus the offers that she has to make to convince half of the councilors.
-The second part is the gains if when the councilor happens to reject the current received offer, but still receives an offer in the following round.
-It is equal to the chance that she is not recognized as the proposer times the chance that she receives a transfer times the amount of the transfer.
-Note that the offer the councilor makes as the proposer is the same as the offer that she wants to receive.
-This because the city councilors are exchangeable, and the solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, we could have dropped the $i$ in the solution).
-After some algebra, the offer $x_i$ has to be greater than or equal to:
-
-\[
-x_i \geq \dfrac{2 \delta^{k+1}R}{2N + 1} \equiv \underline{x}(k, N)
-\]
-
-The proposer always offer the minimum required to get the proposal approved. In the case, the offer at any given stage $k$ is going to be equal to $\underline{x}(k, N)$.
-
-Proceeding backwards, at the mayor's proposal stage $k=0$ and the mayor is going to offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors.
-In this context, the governing costs for the mayor are:
-
-\[
-C_G(N) \ = \ \dfrac{N}{2}\left[\dfrac{2 \delta R }{2N + 1}\right] \ = \ \dfrac{\delta R N}{2N + 1}
-\]
-
-\begin{proposition}
-In the \textit{non-partisan reversal} mechanism, the governing costs always increase when the size of the legislature increases.
-\end{proposition}
+As I derived the optimal strategies for the incumbent and challenger's strategies, it remains to show that no type $t_i \in T$ have incentives to deviate.
+Define the profit that a type $t_i$ gains when she deviates from $\varepsilon(t_i)$ to $\tilde{\varepsilon}$ as:
+
+\[
+p(t_i, \varepsilon(t_i), \varphi, \tilde{\varepsilon}) \ = \ u (\varepsilon(t_i) - \eta) + B \left( \varphi(\tilde{\varepsilon})\lambda(\varepsilon(t_i)-\eta) - \varphi(\varepsilon(t_i))\lambda(\varepsilon(t_i)-\eta) \right)
+\]
+
+Now consider the following Claim:
+
+\begin{claimnn}\label{claim2}
+No type has incentive to deviate from the equilibrium enunciated in Lemma \ref{lemma_m1}.
+\end{claimnn}
+
+\begin{proof}[Proof of the Claim \ref{claim2}]
+
+Let $t_i = \eta$. We then have that
+
+\[
+\dfrac{\partial p}{\partial \eta} \ = \ \left(\dfrac{\partial \varepsilon}{\partial \eta} - 1 \right) (u^{'}(\varepsilon-\eta) - B\varphi(\varepsilon)\lambda^{'}(\varepsilon-\eta))
+ - B \varphi(\tilde{\varepsilon})\lambda^{'}(\varepsilon-\eta)) - \dfrac{\partial \varepsilon}{\partial \eta} B \varphi^{'}(\varepsilon)\lambda(\tilde{\varepsilon}-\eta) - u^{'}(\varepsilon-\eta)
+\]
+
+Applying the fact that $\dfrac{\partial}{\partial \varepsilon}\left[ \varphi(\varepsilon) \lambda(\varepsilon - \eta) \right] = \dfrac{u^{'}(\varepsilon(\tilde{\eta})-\eta)}{B}$:
+
+\[
+\dfrac{\partial p}{\partial \eta} \ = \ -u^{'}(\varepsilon-\eta) + B(\varphi(\varepsilon)\lambda^{'}(\varepsilon-\eta) - \varphi(\tilde{\varepsilon}) \lambda(\tilde{\varepsilon} - \eta))
+\]
+
+And as long as the challenger plays $\varphi^*$, that is increasing on $\varepsilon$, the $ \dfrac{\partial p}{\partial \eta} < 0 $. Thus, $t_i$ has no incentives to deviate from $\varepsilon(\eta)$.
+
+\end{proof}
+
+For the voter, the optimal $\bups$ is $\bups=(1,0)$ when $\psi=G$ and $\dd=0$ and $\bups=(0,1)$ otherwise.
+
+The beliefs are derived using Bayes rule:
+
+\[
+\mu(\eta | \varepsilon) = \dfrac{f(\eta)}{\int_\kappa^\varepsilon f(\eta) d\eta}
+\]
+
+As no discontinuity is present inside the interval $[\kappa, \overline{\eta}]$, the set of players who deviate under these strategies is a measure zero set.
+So, $(\varepsilon^*, \ \varphi^*, \ \bups^*, \ \mu^* )$, as defined in the Lemma \ref{lemma_m1} are a Perfect Bayesian Equilibrium for the game.
+
+\end{proof}
+
+## Single-member District with Many Challengers
+
+Let $|I|=1$ and $|C|=L$.
+Solving backwards, the optimal strategy for the voters is to retain the incumbent if the public goods were successfully provided and no corruption was successfully uncovered.
+If the voters dismiss the incumbent, they randomly select a challenger among all challengers.
+
+One might think that an optimal scheme would be to reward the challengers that uncovered the corruption scandal.
+The problem with this consideration is twofold: first, once the corruption has been detected, all challengers could use these facts in their campaigns, making the corruption exposure a non-excludable public good.
+Second, even if we consider that challengers inherit the votes from the exposed incumbent, the collective action remains, as every challenger will have incentives for negative campaign, but if all do, the voter will keep choosing by chance.
+The equilibrium changes slightly but qualitatively, it is still worse than just one challenger.
+
+Challengers observe $\psi$ and $\varepsilon$, and have to simultaneously compute the negative campaign investment $\varphi_i$.
+As challengers have the same utility function, we solve for a symmetric equilibrium.\footnote{As the payoffs and costs are symmetric here, the symmetric Nash equilibrium is the adequate choice for this problem.
+If we had heterogeneity on challengers, induced by ideological preferences of the electorate, or other characteristics, the symmetry assumption would not be well suited.}
+
+Let $\lambda(\varepsilon-\eta) = \lambda_\varepsilon$. If we have $k$ players investing in negative campaign against the incument politician, the probability that the incumbent loses the election is:
+
+\[
+\Prob(\text{success} | \text{k exp.})  \ = \ 1 - (1-\lambda_\varepsilon)^k
+\]
+
+Let $\varphi$ the probability that all players but $i$, invest in negative campaign. Then, the chance of having $k$ players investing in exposing the corrupt incumbent among the $L-1$ players is:
+
+\[
+\Prob( \text{k exp.}) \ = \ {L \choose k} \varphi^k (1-\varphi)^{L-1-k}
+\]
+
+And the composite probability of losing an election is given by:
+
+\[
+f(\varphi, x) = \sum_{k=0}^{L-1} {L \choose k} \varphi^k (1-\varphi)^{L-1-k} \cdot (1 - (1-\lambda_\varepsilon)^{k+x})
+\]
+
+And when $i$ invests in negative campaign, we let $x=1$ in $f$. This allows us to compute the expected utility for the challenger $i$ as:
+
+\[
+\varphi_i \left[\frac{B}{L}\int_0^A f(\varphi, 1) \mu(\eta|\varepsilon) d\mu \right] + (1-\varphi_i)\left[\frac{B}{L} \int_0^A f(\varphi, 0) \mu(\eta|\varepsilon) d\mu \right] - \varphi_i c
+\]
+
+And some algebra yields to:
+
+\[
+\frac{B}{L}\int_0^A f(\varphi, 0) \mu(\eta|\varepsilon) d\mu + \varphi_i  \left[\frac{B}{L} \int_0^A \left( f(\varphi, 1)-f(\varphi, 0) \right) \mu(\eta|\varepsilon) d\mu - c \right]
+\]
+
+The challenger $i$ exposes the incumbent whenever the term in the right-hand side is positive. Solving for $f$, taking the difference and applying to the problem gives us:
+
+\[
+\frac{B}{L} \int_0^A \left( (1-\varphi\lambda_\varepsilon)^{L-1}\lambda_\varepsilon \right) \mu(\eta|\varepsilon) d\mu - c
+\]
+
+And the sequential rationality imposes us that $\varphi_i \geq 0$ when this quantity is positive, and $0$ otherwise. The upper bound in the equilibrium is:
+
+\[
+\dfrac{\int_{\bar{\eta}}^A \left( (1-\varphi\lambda_A)^{L-1}\lambda_A \right) f(\eta) d\eta}{\int_{\bar{\eta}}^A f(\eta) d\eta} = L\dfrac{c}{B}
+\]
+
+And yields to:
+
+\[
+\int_0^{\bar{\eta}} \left((1-\varphi\lambda_\varepsilon)^{L-1}\lambda_\varepsilon - L\dfrac{c}{B} \right) \mu(\eta|\varepsilon) d\mu = 0
+\]
+
+Let us denote as $G$ the following equation:
+
+\[
+G(\lambda, \varphi; L) = (1-\varphi\lambda_\varepsilon)^{L-1}\lambda_\varepsilon - Q(B, c) L
+\]
+
+Where $Q$ is defined as in the previous section: $Q(B,c) = \dfrac{c}{B}$.
+The optimal $\varepsilon$ can be derived from this equation.
+The problem is that we will have, for each value of $\varepsilon$ a corresponding optimal value of $\varphi$, and vice-versa.
+As the incumbent plays first, she can choose the max-min value for $\lambda$, which is the maximum value for $\varepsilon$ that still delivers the lowest $\varphi$ possible.
+For a numerical example, if we assume $Q=0.15$ and $L$ ranging from $1$ to $5$, we can have a contour for the possible values for $\lambda$ in Figure \ref{fig_m2_1}.
+
+\begin{figure}[htb!]
+ \centering 
+ \includegraphics{1figs/figm21.pdf}
+ \caption{Contour plot for $G=0$ when $Q=0.15$ and $L$ ranges from $1$ to $5$}
+ \label{fig_m2_1}
+\end{figure}
+
+And we have the following optimal incumbent expenditure strategy:
+
+\[
+\varepsilon^*(\eta) \ = \ \eta + \lambda^{-1}\left( Q(B, c)\cdot L \right) \ = \ \eta + \kappa(L)
+\]
+
+Again, the incumbent strategy is comprised of the actual value required to provide the service plus a kickback. However, now the kickback is augmented by the number of challengers contesting the seat.
+
+Again, this expenditure has to be incentive compatible in order to the incumbent prefer it. Thus, it has to satisfy the following differential equation in $\delta(\varepsilon)$:
+
+\[
+u^{'}(\varepsilon-\eta) - BL(1-\delta(\varepsilon)\lambda(\varepsilon-\eta))^{L-1} (\delta^{'}(\varepsilon)\lambda(\varepsilon-\eta)-\delta(\varepsilon)\lambda(\varepsilon-\eta)^{'}) = 0
+\]
+
+But making $G=0$ yield to $(1-\delta(\varepsilon)\lambda(\varepsilon-\eta))^{L-1} = L\frac{Q(B,c)}{\lambda(\varepsilon-\eta)}$.
+Applying these results on the previous equations leads to the following differential equation:
+
+\[
+\delta^{'}(\varepsilon)-\delta(\varepsilon)\dfrac{\lambda^{'}(\kappa(L))}{\lambda(\kappa(L))} \ = \ \dfrac{u^{'}(\kappa(L))}{BQ(B, c)L^2}
+\]
+
+With the boundary condition $\delta(\kappa(L))=0$. Thus:
+
+\[
+\delta(\varepsilon) \ = \ \dfrac{u^{'}(\kappa(L))}{BQ(B, c)L^2} \left( 1- e^{\frac{\lambda^{'}(\kappa(L))}{\lambda(\kappa(L))}(\kappa(L)-\varepsilon)}\right)
+\]
+
+\begin{lemma}
+ \label{lemma_m2}
+ A Perfect Bayesian Equilibrium for the game when $|I|=1$ and $|C|=L$ is a pair of strategies and beliefs such that the optimal strategies are
+ \begin{enumerate}
+  \item For the Incumbent
+  \begin{equation*}
+  \varepsilon^{*}(\eta) \ = \ \twopd{\eta + \kappa(L)}{\eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
+  \end{equation*}
+  \item For the Challenger
+  \[
+  \varphi^*(\varepsilon) \quad = \quad \threepdo{0}{\varepsilon < \kappa(L)}{\delta(\varepsilon)}{\varepsilon \in [\kappa(L), \overline{\eta}]}{\delta(A)}
+  \]
+  \item And the voters retain the incumbent if $d=0$ and $\psi=G$.
+ \end{enumerate}
+ And the optimal beliefs are the same as in the previous Lemma.
+\end{lemma}
 
@@
 
-The difference in costs when there are $N+1$ city councilors versus when there are $N$ city councilors is equal to:
-
-\[
-\begin{aligned}
-C_G(N+1) - C_G(N) \ = \ & \dfrac{(N+1)\delta R}{2(N+1) + 1} - \dfrac{N \delta R}{2N + 1}\\
- = \ & \dfrac{\delta R}{(2N+3)(2N+1)}  \\
-> \ &0
-\end{aligned}
-\]
-
-Therefore, the costs always increase when the size of the legislature increases.
+The results in this Lemma follow analogously from the previous Lemma.
+
+As we are defining a symmetric equilibrium, we have $\varphi_i = \varphi$, $\forall i \in \{1, \cdots, L\}$. Similarly to the previous Lemma, suppose we have an optimal deviation:
+
+\[
+\dfrac{\partial}{\partial \tilde{\eta}} = \dfrac{\partial \varepsilon}{\partial \tilde{\eta}} \left( u^{'}(\varepsilon(\tilde{\eta})-\eta) - B L (1-\varphi(\varepsilon)\lambda(\varepsilon(\tilde{\eta})-\eta))^{L-1} \dfrac{\partial}{\partial \varepsilon}(\varphi(\varepsilon)\lambda(\varepsilon(\tilde{\eta})-\eta)) \right) = 0
+\]
+
+And as $ \dfrac{\partial \varepsilon}{\partial \tilde{\eta}}>0$, we should have that
+
+\[
+\dfrac{\partial}{\partial \varepsilon} (\varphi (\varepsilon) \lambda (\varepsilon (\eta)-\eta)) = \dfrac{u^{'}(\varepsilon(\eta)-\eta)}{B L (1-\varphi(\varepsilon)\lambda(\varepsilon(\eta)-\eta))^{L-1}}
+\]
+
+And the profit from deviate is:
+
+\[
+p(t_i, \varepsilon(t_i), \tilde{\varepsilon}) \ = \ u(\varepsilon-\eta) + B\left[ (1-\varphi(\varepsilon)\lambda(\varepsilon-\eta))^L - (1-\varphi(\tilde{\varepsilon})\lambda(\tilde{\varepsilon}-\eta))^L\right]
+\]
+
+Taking the derivative yields to:
+
+\[
+\dfrac{\partial p}{\partial \eta} \ = \ u^{'}(\varepsilon-\eta) - LB(1-\varphi(\tilde{\varepsilon})\lambda(\tilde{\varepsilon}-\eta))^{L-1}\varphi(\tilde{\varepsilon})\lambda^{'}(\tilde{\varepsilon}) \ < \ 0
+\]
+
+Therefore, no type has incentives to deviate from the equilibrium. The beliefs are computed with a similar method from Lemma \ref{lemma_m1}.
 
@@
 
-\begin{corollary}
-In the \textit{non-partisan reversal} mechanism, public goods provision decreases as the legislature size increases.
-\end{corollary}
-
-This result is crucial to understand the role of the politics in our model.
-If the costs of govern increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
-In our case, we show that there is a \textit{political} reason for increasing the public goods provision.
-
-### Partisan Reversal Mechanism
-
-We now look into the other extreme, which is a fully politicized legislature.
-In this case, when the mayor implements the policy, it generates a value of $p > 0$.
-A legislator aligned with the mayor receives a benefit $p$ while an opposition legislator receives a cost of $-p$.
-Moreover, as in the case of the non-partisan reversal, the mayor can choose to distribute $x_i$ private goods for a legislator $i$.
-In this case, when the policy is implemented, the utility of an aligned legislator is equals to $x_i + p$.
-When the legislator is not aligned with the mayor, her utility is equals to $x_i - p$.
-If the policy is not implemented, then we assume a reversal policy of zero in all choice vectors $g = x_i = p = 0$.
-
-A legislator aligned with the mayor always support the mayor's policy, regardless of receiving or not private goods.
-This because as $p > 0$, the councilor always receive positive benefits from the policy.\footnote{The mayor could even impose a cost to the city councilors aligned with the government.
-Although this seem unrealistic, it is mostly the case when government-aligned legislators are recognized to draft legislation for the mayor's office, or even take the popular fallout from a failed policy.} However, politicians not aligned with the mayor require a compensation when their votes are needed.
-In this case, if the mayor's proposal requires the support of an opposition politician, then the mayor compensates the councilor for the policy costs.
-In such case:
-
-\[
-x_i \geq p
-\]
-
-Optimality dictates that the mayor offers $x_i = p$ to the opposition legislator.
-Let $\gamma$ be the ex-ante probability of electing a politician aligned with the mayor.
-Then, the costs of govern when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor has to compensate minus the amount needed to implement the policy, in this case, half of them:
-
-\[
-C_G(N) \ = \ p\left(\dfrac{N}{2} - \gamma N\right)
-\]
-
-\begin{proposition}
-In the \textit{partisan reversal} mechanism, if the chance of electing a mayor-aligned politician is greater than one-half, then the costs of govern decrease as the legislature size increases.
-\end{proposition}
-
-\begin{proof}
-
-The differences in costs when there are $N+1$ versus when there are $N$ legislators are equal to:
-
-\[
-\begin{aligned}
-C_G(N+1) - C_G(N) \ = \ & p\left(\dfrac{N+1}{2} - \gamma (N+1)\right) - p\left(\dfrac{N}{2} - \gamma N\right) \\
- = \ & p\left( \dfrac{1}{2} - \gamma  \right)
-\end{aligned}
-\]
-
-Therefore, when $\gamma < \dfrac{1}{2}$, the costs of govern increase. Otherwise, the costs decrease.
+And as the key result for the paper is that more challengers represent a larger larger expenditure proposals:
+
+\begin{claim}
+ \label{claim_veps}
+ Let $\eta$ fixed. $\varepsilon^*(\eta; \ L)$ is increasing on $L$
+\end{claim}
+
+\begin{proof}[Proof of Claim \ref{claim_veps}]
+
+Taking the derivative of $\varepsilon^*(\eta; L)$ on $L$ yields to:
+
+\begin{eqnarray*}
+\dfrac{\partial \varepsilon^*(\eta; L)}{\partial L} & = & \dfrac{\partial}{\partial L} \left[ \eta + \lambda^{-1} (Q(B,c) \cdot L) \right] \\
+& = & \frac{Q(B,c)}{\lambda^{'}(\kappa(L))}
+\end{eqnarray*}
+
+And as $\lambda^{'}>0$ and $Q>0$, then $\dfrac{\partial \varepsilon^*(\eta, L)}{\partial L}>0$.
 
@@
 
-\begin{corollary}
-In the \textit{partisan reversal} mechanism, if the chance of electing a mayor-aligned politician is greater than $1/2$, then public goods provision increase as the legislature size increases.
-\end{corollary}
-
-This result shows that when the chances of electing an aligned politician is sufficiently high, then the costs of govern decrease.
-As a response, the public goods provision (and also rents), increase.
-The rate distribution between these two vectors is determined by the marginal change in the utility from rents and the utility from reelection.
-In any case, the amount allocated for both increase.
-
-### Hybrid Partisan and Non-partisan Reversal Mechanism
-
-The \textit{hybrid reversal} mechanism combines both partisan and non-partisan motivations. In the hybrid mechanism, a city councilor aligned with the government favors the mayor's offer if:
-
-\[
-x_i \geq \dfrac{2\delta R}{2N+1} - p
-\]
-
-An opposition politician, on the other hand, favors the mayor's offer if, and only if:
-
-\[
-x_i \geq \dfrac{2\delta R}{2N+1} + p
-\]
-
-We can decompose these costs in two components.
-First, the costs in terms of rents.
-Second, the costs (or benefits) from political alignment.
-In this context, the governing costs depend on the mayor's offers for councilors in the mayor's coalition versus the mayor's offers for councilors in the opposition.
-The ex-ante chance of a opposition member be elected is equal to $1-\gamma$, and taking the weighted averages, these costs become:
-
-\[
-C_G(N) \ = \ \dfrac{N}{2}\left( \dfrac{2\delta R}{2N+1} - p \right) + \left(\dfrac{N}{2} - \gamma N \right)p
-\]
-
-\begin{proposition}
-In the \textit{hybrid reversal} mechanism, if $\gamma \leq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right]$, then the costs of govern increase as the legislature size increases.
-Otherwise, the costs decrease when the legislature size increases.
-\end{proposition}
-
-\begin{proof}
-
-The difference in costs when there are $N+1$ city councilors versus the costs when there are $N$ councilors is equal to:
-
-\[
-\begin{aligned}
-C_G(N+1) - C_G(N) \ = \ & \dfrac{N+1}{2}\left( \dfrac{2\delta R}{2(N+1)+1} - p \right) + \left(\dfrac{N+1}{2} - \gamma (N+1) \right)p \\
-& - \dfrac{N}{2}\left( \dfrac{2\delta R}{2N+1} - p \right) - \left(\dfrac{N}{2} - \gamma N \right)p \\
- = \ & \dfrac{\delta R}{(2N+3)(2N+1)}\left[ 1-\gamma (2N+1)(2N+3)p \right]
-\end{aligned}
-\]
-
-The conditions for the differences in governing costs be decrease when the  legislature size increases is:
-
-\[
-\gamma \geq \dfrac{1}{p}\left[\dfrac{1}{(2N+3)(2N+1)}\right] \equiv \underline{\gamma}
-\]
-
-\end{proof}
-
-\begin{corollary}
-In the \textit{hybrid reversal} mechanism, public goods provision decreases as the legislature size increases.
-\end{corollary}
-
-Also, the threshold $\underline{\gamma}$ for the probability of electing a politician aligned with the government is decreasing in both the political value of the mayors policy $p$ and the size of the legislature $N$.
-This means that higher political values and larger legislatures makes it easier to satisfy the electoral threshold.
-
-### Main Hypotheses
-
-Our model provides two empirically testable hypotheses. Consider a city council comprised of $N$ legislators, that increase its council size to $N+1$. Then:
-
+## Multi-member Districts with Many Challengers
+
+Consider now an election with $K$ incumbents and $L$ challengers.
+Solving backwards, the voters reelect a given incumbent $i$ if the public goods were successfully provided, and no corruption was exposed.
+
+Challengers then decide whom to expose with negative campaign.
+They can choose to expose each one of the $K$ incumbents.
+In a logic similar to the previous Lemmas, we have that the optimal investment is:
+
+\[
+\varepsilon^{*}(\eta) \ = \ \eta + \lambda^{-1} ((L+K)\dfrac{c}{B}) \ = \ \eta + \kappa(K+L)
+\]
+
+And $\delta(.)$ defined in the similar mode as before.
+
+\begin{lemma}
+ \label{lemma_m4}
+ A Perfect Bayesian Equilibrium for the game when $|I|=K$ and $|C|=L$ will be such as the strategies for the players are:
  \begin{enumerate}
-  \item[H1. ] The provision of public goods increase when the governing costs decrease with legislature size.
-  \item[H2. ] The governing decrease with legislature size when the chance of electing a government aligned legislator is sufficiently high.
+  \item For each of the incumbents:
+  \[
+  \varepsilon^{*}(\eta) \ = \ \twopdo{\eta + \kappa(L+K)}{\eta \leq \overline{\eta}}{A}
+  \]
+  \item For each of the challengers:
+  \[
+  \varphi^*(\varepsilon) \ = \ \threepdo{0}{\varepsilon < \kappa(L+K)}{\delta(\varepsilon)}{\varepsilon \in [\kappa(L+K), \overline{\eta}]}{\delta(A)}
+  \]
+  \item For the voters, retain the incumbents that $d=0$ when $\psi=G$, dismissing otherwise.
  \end{enumerate}
-
-In the paper, we show that the provision of education and healthcare improves in Brazil, and this results from the fact that the chances of electing a city councilor aligned with the mayor is of 91%, thanks to the rule of distributing seats adopted in the country.
-
-\newpage
-
-## Variable Sources and Descriptive Statistics
-\label{appsources}
-
-We use three information sources, either from Brazilian governmental agencies or available online. Table \ref{varsources} displays the primary sources and their respective URLs.
-
-\begin{sidewaystable}[!htbp] \centering 
-\caption{Data Sources} 
-\label{varsources}
-\scalebox{0.75}{
-  \begin{tabular}{@{\extracolsep{5pt}}llll} 
-  \\[-1.8ex]\hline\hline \\[-1.8ex] 
-  Source Code & \multicolumn{1}{c}{Source Name} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{URL} \\ 
-  \hline \\[-1.8ex] 
-  & & & \\
-  DataSUS & Brazilian Health Ministry Data Service & Collects data on Health Care & \url{http://www.datasus.gov.br} \\
-  & & & \\
-  IBGE & Brazilian Institute of Geography and Statistics & Collects data Geography, Economics and Demography & \url{http://www.ibge.gov.br} \\ 
-  & & & \\
-  INEP & Data Service of Ministry of Education & Collects data on performance of Education & \url{http://www.inep.gov.br} \\ 
-  & & & \\
-  InterLegis & Senate Legislative Data Service & Collect Data on Legislative in Brazil & \url{http://www.interlegis.leg.br} \\
-  & & & \\
-  IPEA & Brazilian Institute of Applied Economics & Collects data on the Economy & \url{http://www.ipeadata.gov.br} \\ 
-  & & & \\
-  MDS & Social Security Ministry & Collect data on Social Coverage and Effectiveness of Social Programs & \url{http://www.mds.gov.br} \\ 
-  & & & \\
-  TSE & Superior Electoral Tribunal & Collects data on elections results & \url{http://www.tse.jus.br} \\
-  & & & \\
-  \hline\hline \\[-1.8ex] 
+ And the optimal beliefs are uptadated by Bayes rule, whenever possible.
+\end{lemma}
+
+The proof is similar to the previous proofs, and is available upon request.
+
+# Model Extensions
+
+## Run-offs
+
+Run-off works in this model as a two-stage election, with the first election a contest with one incumbent and many challengers, and then a contest with two politicians.
+The behavioral rule assumed for the voters imply here that voters will send the incumbent and challenger to the run-off if no corruption was exposed in the first round.
+In equilibrium, challengers take this into consideration, not investing any resources in negative campaign in the first round.
+However, the run-off emulates a single-member district election with the incumbent and a challenger.
+This system is the most effective in coping corruption, accoding to Lemma \ref{lemma_m1}.
+
+## Parties
+
+Strong parties can change the game substantially by coordinate the investigations.
+They can optimally decide to invest the resources aiming at maximizing the changes of exposure.
+The logic with district size and competition reverts to parties, instead of candidates.
+Few strong parties can successfully coordinate the exposures, lowering the equilibrium corruption.
+
+# Empirical Analysis
+
+## Data Sources
+
+I use data from Brazil for the 2004 municipal election, coupled with the corruption investigation performed by a Federal Random Audit program.
+The corruption investigations are performed on federal transfers, but these compose the majority of the municipal budgets in Brazil.
+Table \ref{tabsourc} provide a list of data sources, that can easily searched online.
+
+The summary statistics follow below:
+
+```
+require(foreign)
+require(fBasics)
+require(rdrobust)
+require(AER)
+require(tidyverse)
+require(ggplot2)
+require(broom)
+require(gridExtra)
+
+dat <- read.dta('EISC.dta')
+dat$nCandCC_by10 <- dat$nCandCC/10
+dat$nCandCC <- NULL
+res <- data.frame(round(t(basicStats(dat)[c("Mean", "Stdev", "Median", "Minimum", "Maximum", "nobs"),]), digits=3))
+names(res) <- c("Mean", "SD", "Med", "Min", "Max", "N")
+res
+
+stdzy <- function(x) {
+  z <- (x-mean(x, na.rm = T))/sd(x, na.rm = T)
+  return(z)
+}
+
+# Extract coeffs
+extr_coef_rdr <- function(obj, name = 'RD Robust') {
+  return(data.frame(term = name, estimate = round(obj$coef[3], digits=3), std.error = round(obj$se[3], digits=3) ))
+}
+
+extr_coef_ttest <- function(obj, name = 'T Test') {
+  cfs = obj$estimate[2]-obj$estimate[1]
+  stde = abs((cfs)*(1/obj$statistic))
+  res <- data.frame(term = name, 
+                    estimate = round(cfs, digits=3), 
+                    std.error = round(stde, digits=3))
+  row.names(res) <- NULL
+  return(res)
+}
+
+extr_coef_ivreg <- function(obj, name = 'IV Regression') {
+  return(data.frame(term = name, 
+                    estimate = round(obj$coefficients[2,1], digits=3),
+                    std.error = round(obj$coefficients[2,2], digits=3)))
+}
+```
+
+And the data sources are:
+
+\usepackage{lscape}
+\begin{landscape}
+\begin{table}[htp!]
+\centering
+\caption{Data sources used in empirical section}
+\label{tabsourc}
+\scalebox{0.8}{
+\begin{tabular}{llcl}
+\hline
+\multicolumn{1}{c}{\textbf{Variable}} & \multicolumn{1}{c}{\textbf{Description}} & \textbf{Source} & \multicolumn{1}{c}{\textbf{URLs}} \\ \hline
+ibge\_code & \begin{tabular}[c]{@{}l@{}}6-digit Brazilian Geography and Statistics \\ Institute municipal identifier\end{tabular} & IBGE & https://cidades.ibge.gov.br \\
+year & Year &  &  \\
+lottery & \begin{tabular}[c]{@{}l@{}}Number draw from CGU \\ (Brazilian General Comptroller)\end{tabular} & CGU & http://www.cgu.gov.br \\
+broad & \begin{tabular}[c]{@{}l@{}}Brollo et al (2013) broad \\ detected irregularities\end{tabular} & \begin{tabular}[c]{@{}c@{}}CGU\\ + processing\end{tabular} & \begin{tabular}[c]{@{}l@{}}https://www.aeaweb.org/articles?id=10.1257/aer.103.5.1759\\ http://www.cgu.gov.br\end{tabular} \\
+narrow & \begin{tabular}[c]{@{}l@{}}Brollo et al (2013) corruption \\ detected\end{tabular} & \begin{tabular}[c]{@{}c@{}}CGU\\ + processing\end{tabular} & \begin{tabular}[c]{@{}l@{}}https://www.aeaweb.org/articles?id=10.1257/aer.103.5.1759\\ http://www.cgu.gov.br\end{tabular} \\
+ind\_corrup\_n & \begin{tabular}[c]{@{}l@{}}Avelino et al (2016) fraction of detected \\ irregularities\end{tabular} & \begin{tabular}[c]{@{}c@{}}CGU\\ + processing\end{tabular} & https://doi.org/10.7910/DVN/MJWO0X \\
+ind\_corrup\_m & \begin{tabular}[c]{@{}l@{}}Avelino et al (2016) monetary amount \\ of detected irregularities\end{tabular} & \begin{tabular}[c]{@{}c@{}}CGU\\ + processing\end{tabular} & https://doi.org/10.7910/DVN/MJWO0X \\
+nCandMayor & \begin{tabular}[c]{@{}l@{}}Number of candidates running for \\ 2004 mayoral election\end{tabular} & TSE & http://www.cepesp.io \\
+runningCC & \begin{tabular}[c]{@{}l@{}}Distance from 2003 TSE council \\ size decision and 2003 IBGE population\end{tabular} & \begin{tabular}[c]{@{}c@{}}TSE + IBGE\\ + processing\end{tabular} & http://www.cepesp.io \\
+fakeRunningCC & \begin{tabular}[c]{@{}l@{}}Placebo distance from 2003 TSE \\ council size decision and 2003 IBGE population\end{tabular} & \begin{tabular}[c]{@{}c@{}}TSE + IBGE\\ + processing\end{tabular} & http://www.cepesp.io \\
+pop & \begin{tabular}[c]{@{}l@{}}Population projection for the \\ research period\end{tabular} & IBGE & https://cidades.ibge.gov.br \\
+validVotes\_by100k & \begin{tabular}[c]{@{}l@{}}Number of voters by municipality \\ (divided by 100 thousands)\end{tabular} & TSE & http://www.tse.jus.br \\
+distValidVotes200k & \begin{tabular}[c]{@{}l@{}}Distance from the 200 thousands \\ run-off cutoff\end{tabular} & TSE + processing & http://www.tse.jus.br \\
+distValidVotes150k & \begin{tabular}[c]{@{}l@{}}Placebo distance from the 200 \\ thousands run-off cutoff (placebo as 150k)\end{tabular} & TSE + processing & http://www.tse.jus.br \\
+distValidVotes250k & \begin{tabular}[c]{@{}l@{}}Placebo distance from the 200 \\ thousands run-off cutoff (placebo as 250k)\end{tabular} & TSE + processing & http://www.tse.jus.br \\
+year\_2005 & Dummy for year = 2005 &  &  \\
+year\_2006 & Dummy for year = 2006 &  &  \\
+year\_2007 & Dummy for year = 2007 &  &  \\
+year\_2008 & Dummy for year = 2008 &  &  \\
+nCandCC\_by10 & \begin{tabular}[c]{@{}l@{}}Number of candidates running \\ for city council (divided by 10)\end{tabular} & TSE & http://www.tse.jus.br \\ \hline
 \end{tabular}
 }
-\end{sidewaystable}
-
-Now let us define each variable.
-
-### Outcomes Aggregated at the Municipal Level
-
-\begin{itemize}
-\item \textbf{Number of Seats 2000}: Number of councilors in the municipality by the 2000 elections (source: TSE).
-\item \textbf{Population 2000}: Municipal population according to the 2000 Brazilian Census (source: IBGE).
-\item \textbf{Per-Capita GDP Census 2000 (in millions)}: Municipal per-capita GDP computed by the IBGE Census (source: IPEA).
-\item \textbf{Proportion of Poverty Census 2000}: Proportion of poverty in the municipality defined as people living on less than R\$ 70.00 a day (source: MDS).
-\item \textbf{Number of Seats 2004}: Number of city-councilors in a municipality according to the Electoral Justice decision (source: TSE).
-\item \textbf{Infant Mortality 2005--2008}: Infant mortality computed as the number of children born alive that died before reaching one year of age divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
-\item \textbf{Post-Natal Mortality Rate 2005--2008}: Infant mortality computed as the number of children born alive that successfully lived 28 days, but died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
-\item \textbf{Coverage Family Health Program 2005--2008}: Number of families covered by the Family Health Program (source: DataSUS).
-\item \textbf{Prop. Born w. 7+ Pre-Natal 2005--2008}: Proportion of children born who went to seven or more prenatal care consultations (source: DataSUS)
-\item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
-\item \textbf{Enrollment Middle School 2005--2008}: Number of children enrolled in middle schools, averaged by classroom size (5--9) (source: INEP)
-\item \textbf{Quality of Elementary School Index 2005--2008}: IDEB score averaged by schools in the municipality.
-IDEB scores are composed by the student's grades in math and language, multiplied by an indicator of the distortion between the year the child is supposed to be and the year the child is.
-The estimators are cleaned to avoid influences of schools and classroom specific effects (source: INEP, years: 2005, 2007).
-\item \textbf{Quality of Middle School Index 2005--2008}: IDEB score averaged by schools in the municipality.
-IDEB scores are composed by the student's grade in math and language, multiplied by a score capturing the distortion between the year the child is supposed to be in, and the year the child is studying.
-The estimators are cleaned to avoid the influence of schools and classrooms specific effects.
-(source: INEP, years: 2005, 2007).
-\item \textbf{Mayoral Pre-Electoral Coalition Size 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
-\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration that were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
-\item \textbf{Number of Career Bureaucrats 2005--2008}: Number of career bureaucrats in the municipality.
-Career bureaucrats cannot be fired by politicians and earn considerably better pensions after retirement (source: IBGE, years: 2005, 2006, and 2008)
-\item \textbf{Number of Councilor's Appointed Assistants 2005}: Number of assistants appointed for the councilor cabinet (source: InterLegis)
-\item \textbf{Number of Females Elected 2004}: Number of females elected to city council (source: TSE)
-\item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to city council.
-We collected this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: our compilation based on the TSE candidate pictures).
-\item \textbf{Competition per Seat 2004}: Number of people running for city-councilor divided by the number of city councilors in the municipality (source: TSE)
-\item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
-\end{itemize}
-
-### Legislation Dataset
-
-We coded the legislation approved by the councilors in 64 municipalities that are 10 thousand inhabitants away from the council size thresholds. We classified the legislation in five categories:
-
-\begin{itemize}
-\item \textbf{Local Public Goods}: Legislation that provides a service targeted at the individual, group, or geographical level.
-\item \textbf{Public Goods or General Legislation}: Legislation that provides a service for the entire municipality, or approves a law that does not discriminate among citizens.
-\item \textbf{Oversight}: Legislation that requests information to the mayor's office or the bureaucracy about the provision of services.
-\item \textbf{Others}: Legislation that is not classified as Local Public Goods, Public Goods, or Oversight. Usually honors or procedures.
-\item \textbf{Education and Health Care}: Legislation about Education or Health Care provision.
-\end{itemize}
-
-### Online 2016 Former City Councilors Survey
-
-We run an online survey asking 174 councilors whether helping with [...service...] gives [none, few, some, or many] votes. The services were:
-
-\begin{itemize}
-\item \textbf{Help Hospital Admission}: We asked former councilors whether helping with hospital admission gives [none, few, some, many] votes (source: survey).
-\item \textbf{Help School Admission}: We asked former councilors whether helping with school admission gives [none, few, some, many] votes (source: survey).
-\item \textbf{Help Getting Medication}: We asked former councilors whether helping voters get medication gives [none, few, some, many] votes (source: survey).
-\item \textbf{Fix Street Potholes}: We asked former councilors whether pressing the bureaucracy to fix street potholes gives [none, few, some, many] votes (source: survey).
-\item \textbf{Other Local Public Goods}: We asked former councilors whether helping voters with local public goods and services such as traffic rules, sewage constructions, potable water, and others, gives [none, few, some, many] votes (source: survey).
-\item \textbf{Legislative Duties}: We asked former councilors whether the act to discuss, propose, and vote on legislation gives [none, few, some, many] votes (source: survey).
-\item \textbf{Honors Legislation}: We asked former councilors whether proposing bills to praise local celebrities gives [none, few, some, many] votes (source: survey).
-\item \textbf{Oversee School Quality}: We asked former councilors whether overseeing school quality gives [none, few, some, many] votes (source: survey).
-\item \textbf{Oversee Construction}: We asked former councilors whether overseeing public construction gives [none, few, some, many] votes (source: survey)
-\end{itemize}
-
-In this Appendix, we present other questions we asked in the survey.
-They are meant to improve the knowledge we have about the city councilors perceptions about their representation.
-We have not added these to the main paper because they were more complimentary and not of general interest.
-The descriptive statistics of the variables used in the main paper follow in Table \ref{tabdescrvarspaper}.
-
-XXXX CHANGE HERE TABLE BELOW
-
-\begin{table}[htb!]
-\centering 
-\caption{Summary Statistics} 
-\label{tabdescrvarspaper} 
-\resizebox{0.9\textwidth}{3.5in}{
-\begin{threeparttable}
-\begin{tabular}{@{\extracolsep{\fill}}l r r r r r } 
-\toprule
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\ 
-\midrule 
-& \multicolumn{5}{c}{\textbf{Municipal Characteristics}} \\ \cline{2-6}
-Number of Seats 2000 & 5,521 & 10.76 & 2.70 & 9 & 21 \\ 
-Population 2000 & 5,474 & 22,341.96 & 44,573.67 & 697 & 567,728 \\ 
-Per-Capita GDP Census 2000 (in thousands) & 5,474 & 0.13 & 0.46 & 0.00 & 13.57 \\ 
-Proportion of Poverty Census 2000 & 5,474 & 46.58 & 22.82 & 2.89 & 93.02 \\ 
-Number of Seats 2004 & 5,527 & 9.22 & 0.94 & 9 & 21 \\ 
-& \multicolumn{5}{c}{\textbf{Health Care Outcomes}} \\ \cline{2-6}
-Infant Mortality 2005-2008 & 13,329 & 20.64 & 13.45 & 1.28 & 209.30 \\
-Post-Natal Mortality Rate 2005-2008 & 6,113 & 9.29 & 8.64 & 0.59 & 200.00 \\
-Coverage Family Health Program 2005-2008 & 20,577 & 76.97 & 27.39 & 0.00 & 100.00 \\ 
-Prop. Born w. $6+$ Pre-Natal 2005-2008 & 16,578 & 54.02 & 24.30 & 0.57 & 100.00 \\ 
-& \multicolumn{5}{c}{\textbf{Education Outcomes}} \\ \cline{2-6}
-Enrollment Elementary School 2005-2008 & 10,842 & 20.62 & 5.32 & 1.00 & 57.80 \\ 
-Enrollment Middle School 2005-2008 & 7,887 & 25.18 & 7.25 & 1.00 & 92.50 \\
-Quality of Elementary School Index 2005-2008 & 9,267 & 3.73 & 0.94 & 0.70 & 8.10 \\
-Quality of Middle School Index 2005-2008 & 5,566 & 3.21 & 0.76 & 0.30 & 6.60 \\
-& \multicolumn{5}{c}{\textbf{Resources and Patronage}} \\ \cline{2-6}
-Mayoral Coalition Size 2004 & 5,522 & 4.86 & 1.71 & 0.00 & 17.00 \\ 
-Number of Appointed Bureaucrats 2005-2008 & 16,564 & 67.78 & 126.68 & 0 & 2,894 \\ 
-Number of Career Bureaucrats 2005-2008 & 16,558 & 436.13 & 698.17 & 0 & 11,633 \\ 
-Number Councilor Assistants 2005 & 5,523 & 4.63 & 8.55 & 0 & 213 \\ 
-& \multicolumn{5}{c}{\textbf{Representation and Competition}} \\ \cline{2-6}
-Proportion Female Elected 2004 & 5,526 & 1.12 & 1.20 & 0.00 & 8.00 \\ 
-Proportion Non-White Elected 2004 & 397 & 2.23 & 1.87 & 0.00 & 9.00 \\ 
-Competition per Seat 2004 & 5,527 & 6.27 & 3.82 & 1.00 & 25.83 \\ 
-Proportion Approved Legislation 2005 & 3,694 & 0.83 & 0.28 & 0.00 & 1.00 \\ 
-& \multicolumn{5}{c}{\textbf{Legislation Approved Data}} \\ \cline{2-6}
-Legislation -- Local Public Goods & 346,553 & 0.73 & 0.44 & 0 & 1 \\ 
-Legislation -- Public Goods & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
-Legislation -- Oversight & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
-Legislation -- Others & 346,553 & 0.17 & 0.38 & 0 & 1 \\ 
-Legislation -- Education and Health & 346,553 & 0.11 & 0.31 & 0 & 1 \\ 
-& \multicolumn{5}{c}{\textbf{Survey -- Electoral Attractiveness of Services}} \\ \cline{2-6}
-Votes -- Help Hospital Admission & 174 & 0.82 & 0.38 & 0 & 1 \\ 
-Votes -- Help School Admission & 174 & 0.59 & 0.49 & 0 & 1 \\ 
-Votes -- Help get Medication & 174 & 0.71 & 0.46 & 0 & 1 \\ 
-Votes -- Fix Street Potholes & 174 & 0.49 & 0.50 & 0 & 1 \\ 
-Votes -- Local Public Goods & 174 & 0.81 & 0.39 & 0 & 1 \\ 
-Votes -- Legislive Duties & 174 & 0.22 & 0.42 & 0 & 1 \\ 
-Votes -- Honors Legislation & 174 & 0.18 & 0.38 & 0 & 1 \\ 
-Votes -- Oversee School Quality & 174 & 0.29 & 0.45 & 0 & 1 \\ 
-Votes -- Oversee Construction & 174 & 0.24 & 0.43 & 0 & 1 \\ 
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\small
-\textbf{Notes:} The legislation approved dataset has data on 64 of the 202 municipalities 10 thousand inhabitants from the council size thresholds.
-The survey summary statistics here are unweighted.
-Numbers of cases vary due to missingness.
-\end{tablenotes} 
-\end{threeparttable}
-}
 \end{table}
-
-\newpage
-
-### Threshold Manipulation, Sorting, and Pre-treatment Consistency
-
-The validity of our causal claim relies on three assumptions.
-First, the impossibility of municipalities to manipulate the placement at the left or right-hand side of the thresholds.
-Second, that we are consistently comparing municipalities in the same cutoffs.
-Lastly, that we have no pre-treatment differences in our sample.
-
-For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant in the left or the right of the cutoff.
-For our research, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
-
-We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
-We use local polynomial orders from one to four.
-As the null hypothesis is no manipulation, the p-values for each polynomial order are: local linear (p-value $=0.442$); quadratic (p-value $=0.740$); cubic (p-value $=0.998$); and quartic (p-value $=0.620$).
-Therefore, there is no manipulation according to \citet{calonico2019regression}.
-
-We also graph the \citet{McCrary2008} test, pooling all the discontinuities. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
-
-\begin{figure}[htb!]
-  \begin{center}
-  \begin{minipage}{1 \linewidth}
-  \centerline{\includegraphics[width=5in,angle=0]{../figures/McCrary.pdf}}
-  \caption{\citet{McCrary2008} manipulation test}
-  \bigskip
-  \label{manipulationplot}
-  \end{minipage}
-  \end{center}
-\end{figure}
-
-For the second assumption, we know that running RDD in multiple thresholds may lead to inconsistent estimates when there is an imbalance in the running variable's distribution around the cutoffs \citep{Bertanha2015, Cattaneo2016, eggers2018regression}.
-For example, in our dataset, we have twelve discontinuities, and at each threshold, we have a sharp increase of one councilor, from 9 to 21.
-When running an RDD on these discontinuities, a consistent estimator should fit an exact change of one councilor.
-However, if we pool all the discontinuities together with no correction, we find an increase in council size of 1.63 councilors.
-This imbalance is because when we combine all the discontinuities, we are implying that changes in municipalities right below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
-That is incorrect, not only because we could be comparing a municipality with nine councilors with one with 21 councilors, but also because these municipalities diverge in many other aspects, such as population to GDP per capita.
-
-To avoid this problem, we show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in our case, the population in 2003), improves the consistency and efficiency of the estimates.
-Relying on this fact, we add five controls to our estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
-The reason for the first variable is the multiple threshold assignments.
-We add GDP per capita because wealthier cities tend to be more productive and have better public services.
-The number of seats in 2000 intends to control for the fact that some municipalities could experience a change provoked by the previous council size, confounding our estimates.
-The year and the northeast dummies serve to improve efficiency.
-Adding controls improves efficiency in RDD \citep{calonico2019regression} and also enhances the consistency in the multiple thresholds RDD.
-See the following section for further tests and simulations.
-
-For the last assumption, we should have no changes in pre-treatment covariates.
-These pre-treatment covariates are variables measured before the primary outcomes.
-As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.
-
-Table \ref{validitycheck} displays the results of the validity checks.
-At the top of the table, we run the first-stage regressions, both using and not using the controlling covariates strategy proposed, for both real and the placebo cutoffs.
-At the bottom, we estimate the pre-treatment covariate balance.
-
-XXXX CHANGE THIS
-
-\begin{table}[htb!] \centering 
-  \caption{Research Design Validity Check} 
-  \label{validitycheck} 
-    \scalebox{0.9}{
-  \begin{threeparttable}
-\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
-\toprule
- & \multicolumn{4}{c}{\textbf{Panel A: Validity Check --- First Stage}} \\ \cline{2-5}
-   & \multicolumn{1}{c}{\small{(1)}} & 
- \multicolumn{1}{c}{\small{(2)}} & 
- \multicolumn{1}{c}{\small{(3)}} & 
- \multicolumn{1}{c}{\small{(4)}} \\
-
- & \multicolumn{1}{c}{\small{Additional Num.}} & 
- \multicolumn{1}{c}{\small{Placebo Add.}} & 
- \multicolumn{1}{c}{\small{Additional Num.}} & 
- \multicolumn{1}{c}{\small{Placebo Add.}} \\ 
-  & \multicolumn{1}{c}{\small{Seats 2004}} & 
-  \multicolumn{1}{c}{\small{Num. Seats 2004}} & 
-  \multicolumn{1}{c}{\small{Seats 2004}} & 
-  \multicolumn{1}{c}{\small{Num. Seats 2004}} \\
-  & \multicolumn{1}{c}{\small{(Without Controls)}} & 
-  \multicolumn{1}{c}{\small{(Without Controls)}} & 
-  \multicolumn{1}{c}{\small{(With Controls)}} & 
-  \multicolumn{1}{c}{\small{(With Controls)}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
-\\[-1.8ex] 
- LATE & 1.63$^{***}$ & -0.31$^{**}$ & 1.00$^{***}$ & -0.00 \\ 
-  & (0.51) & (0.14) & (0.0004) & (0.0000) \\ 
-\hdashline \\[-1.8ex]   
- N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
-Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
-Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
-BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
-BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
-\midrule 
- & \multicolumn{4}{c}{\textbf{Panel B: Validity Check --- Pre-Treatment Variables}} \\ \cline{2-5}
- & \multicolumn{1}{c}{\small{(5)}} & 
- \multicolumn{1}{c}{\small{(6)}} & 
- \multicolumn{1}{c}{\small{(7)}} & 
- \multicolumn{1}{c}{\small{(8)}} \\
-  & \multicolumn{1}{c}{\small{Number of}} & 
- \multicolumn{1}{c}{\small{Population}} & 
- \multicolumn{1}{c}{\small{GDP}} & 
- \multicolumn{1}{c}{\small{\% of Poverty}} \\ 
-  & \multicolumn{1}{c}{\small{Seats 2000}} & 
-  \multicolumn{1}{c}{\small{2000 Census}} & 
-  \multicolumn{1}{c}{\small{2000 Census}} &
-   \multicolumn{1}{c}{\small{2000 Census}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.17 & -2057.60 & 0.06 & -9.72 \\ 
-  & (0.67) & (1926.33) & (0.18) & (6.27) \\ 
-  \hdashline \\[-1.8ex]
- N Left & \multicolumn{1}{c}{5178} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} \\ 
-Eff N Left & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{219} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{194} \\ 
-Eff N Right & \multicolumn{1}{c}{147} & \multicolumn{1}{c}{157} & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{142} \\ 
-BW Loc Poly & 8.970 & 9.368 & 8.739 & 8.530 \\ 
-BW Bias & 13.860 & 15.029 & 14.752 & 13.035 \\ 
-\bottomrule
-\end{tabularx}
-\begin{tablenotes}
-\small
-\item \textbf{Note:} $ ^{***} $ p $ < $ .01; $ ^{**} $ p $ < $ .05; $ ^{*} $ p $ < $ .1.
-RD local linear estimates using \citet{calonico2019regression} optimal bandwidth quadratic selection and triangular kernel.
-Robust standard errors, clustered at the municipal level, in parentheses.
-Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
-\textit{N Left} and \textit{N Right} represent the total number of observation in the left and right sides of the thresholds (untreated).
-\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
-\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
-\textit{BW Bias} is the Bandwidth used to compute the standard errors.
-\end{tablenotes}
-\end{threeparttable}}
-\end{table}
-
-Notice that without controls, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
-After adding covariates, the results improve, and the point estimates are now one for the primary model and zero for the placebo regressions, which are the correct values.
-Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds.
-These tests reinforce the validity of our research designs.
-
-\pagebreak
-
-## Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision
-\label{appidentif}
-
-The identification strategy requires exogenous changes in the city council size thresholds.
-Previous to the changes we exploit here, the 1988 Brazilian Constitution states the following distribution of seats per population size, presented in Table \ref{tabcitycouncilsize1988}.
-
-\begin{table}[htp!]
-\centering
-\caption{City council size from the 1988 Constitution}
-\scalebox{0.75}{
-\begin{tabular}{rccrrr}
-  \hline\hline
- & \multicolumn{1}{c}{Min. Leg.} & \multicolumn{1}{c}{Max. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\ 
- & & & & & \multicolumn{1}{c}{(2001-2004)} \\
-  \hline
-  1 & 9  & 21 & 0 & 1,000,000 &  5,537 \\ 
-  2 & 33 & 41 & 1,000,001 & 5,000,000 & 11 \\ 
-  3 & 42 & 55 & 5,000,001 & $\infty$ & 2 \\ 
-   \hline\hline
-\end{tabular}
-}
-\label{tabcitycouncilsize1988}
-\end{table}
-
-These cutoffs were in place until 2003, when the municipality of Mira Estrela decided to decrease the council size from eleven to nine councilors.
-The two losing councilors started a judicial contestation that made it to the Supreme Court.
-The court ruled that the Constitution meant that council size should vary proportionally with population, starting with nine legislators, until the maximum number of councilors, 55.
-Following this decision, the Superior Electoral Tribunal (TSE) decided the thresholds that should be followed in the 2004 election (Resolution 21,702/2004).
-According to their decision, the legislature should increase as displayed in Table \ref{tabcitycouncilsize2004all}.
-
-\begin{table}[htp!]
-\centering
-\caption{City council size thresholds according to TSE resolution 21,702/2004}
-\scalebox{0.75}{
-\begin{tabular}{rcrrr}
-  \hline\hline
- &  \multicolumn{1}{c}{Num. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
- & & & & \multicolumn{1}{c}{(2003 pop. proj.)} \\
-  \hline
-  1 &  9 & 0 & 47,619 & 5,029 \\ 
-  2 &  10 & 47,620 & 95,238 & 317 \\ 
-  3 &  11 & 95,239 & 142,857 & 89 \\ 
-  4 &  12 & 142,858 & 190,476 & 43 \\ 
-  5 &  13 & 190,477 & 238,095 & 30 \\ 
-  6 &  14 & 238,096 & 285,714 & 21 \\ 
-  7 &  15 & 285,715 & 333,333 & 13 \\ 
-  8 &  16 & 333,334 & 380,952 & 13 \\ 
-  9 &  17 & 380,953 & 428,571 & 6 \\ 
-  10  & 18 & 428,572 & 476,190 & 6 \\ 
-  11  & 19 & 476,191 & 523,809 & 4 \\ 
-  12  & 20 & 523,810 & 571,428 & 5 \\ 
-  13  & 21 & 571,429 & 1,000,000 & 13 \\ 
-  14  & 33 & 1,000,001 & 1,121,952 & 1 \\ 
-  15  & 34 & 1,121,953 & 1,243,903 & 2 \\ 
-  16  & 35 & 1,243,904 & 1,365,854 & 1 \\ 
-  17  & 36 & 1,365,855 & 1,487,805 & 2 \\ 
-  18  & 37 & 1,487,806 & 1,609,756 & 1 \\ 
-  19  & 38 & 1,609,757 & 1,731,707 & 1 \\ 
-  20  & 39 & 1,731,708 & 1,853,658 & 0 \\ 
-  21  & 40 & 1,853,659 & 1,975,609 & 0 \\ 
-  22  & 41 & 1,975,610 & 4,999,999 & 4 \\ 
-  23  & 42 & 5,000,000 & 5,119,047 & 0 \\ 
-  24  & 43 & 5,119,048 & 5,238,094 & 0 \\ 
-  25  & 44 & 5,238,095 & 5,357,141 & 0 \\ 
-  26  & 45 & 5,357,142 & 5,476,188 & 0 \\ 
-  27  & 46 & 5,476,189 & 5,595,235 & 0 \\ 
-  28  & 47 & 5,595,236 & 5,714,282 & 0 \\ 
-  29  & 48 & 5,714,283 & 5,833,329 & 0 \\ 
-  30  & 49 & 5,833,330 & 5,952,376 & 0 \\ 
-  31  & 50 & 5,952,377 & 6,071,423 & 1 \\ 
-  32  & 51 & 6,071,424 & 6,190,470 & 0 \\ 
-  33  & 52 & 6,190,471 & 6,309,517 & 0 \\ 
-  34  & 53 & 6,309,518 & 6,428,564 & 0 \\ 
-  35  & 54 & 6,428,565 & 6,547,611 & 1 \\ 
-  36  & 55 & 6,547,612 & $\infty$  & 0 \\ 
-   \hline\hline
-\end{tabular}
-}
-\label{tabcitycouncilsize2004all}
-\end{table}
-
-As there are few municipalities above one million inhabitants, we decided to restrict our attention to municipalities with less than $571,429 + 47,619 = 619,048$ inhabitants.
-Table \ref{tabcitycouncilsize2004short} displays the frequency of municipality by thresholds used in our paper.
-
-\begin{table}[htp!]
-\centering
-\caption{City council thresholds used in the paper}
-\scalebox{0.85}{
-\renewcommand*{\arraystretch}{1.2}
-\begin{tabular}{rcrrr}
-  \hline \hline
- & \multicolumn{1}{c}{Legislature} & \multicolumn{1}{c}{Min.} & \multicolumn{1}{c}{Max.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
- & \multicolumn{1}{c}{Size} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{(2003 pop.)} \\
-  \hline
-  1 & 9 & 0 & 47,619 & 5,029 \\ 
-  2 & 10 & 47,620 & 95,238 & 317 \\ 
-  3 & 11 & 95,239 & 142,857 & 89 \\ 
-  4 & 12 & 142,858 & 190,476 & 43 \\ 
-  5 & 13 & 190,477 & 238,095 & 30 \\ 
-  6 & 14 & 238,096 & 285,714 & 21 \\ 
-  7 & 15 & 285,715 & 333,333 & 13 \\ 
-  8 & 16 & 333,334 & 380,952 & 13 \\ 
-  9 & 17 & 380,953 & 428,571 & 6 \\ 
-  10 & 18 & 428,572 & 476,190 & 6 \\ 
-  11 & 19 & 476,191 & 523,809 & 4 \\ 
-  12 & 20 & 523,810 & 571,428 & 5 \\ 
-  13 & 21 & 571,429 & 1,000,000 & 13 \\ 
-   \hline \hline
-\end{tabular}
-}
-\label{tabcitycouncilsize2004short}
-\end{table}
-
-The Supreme Court ruled that the electoral courts should use the 2003 population projection to assign municipalities to cutoffs.
-In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) propose the official population projections.
-Sorting is not an issue for our identification strategy, as IBGE is an insulated bureaucracy, insulated from local influences (see also the McCrary test above).
-
-To provide an overview of the data dispersion, Figure \ref{sampleplot} plots the municipalities by their proximity from the cutoffs.
-In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds.
-The darker the color, the closer to the population thresholds.
-In regression discontinuity, the closer a municipality is to the cutoff, the more influential it is in the estimation.
-Figure \ref{sampleplot} also shows that our municipalities are reasonably distributed around the whole country.
-
-XXXX CHANGE
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=7in,angle=0]{../figures/samplePlot.pdf}}
-      \caption{Municipalities by their Selection Status}
-      \bigskip
-      \label{sampleplot}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-Moreover, we could question whether the discontinuities studied here are sharp or fuzzy.
-In order to be fuzzy, the laws passed by the Supreme Court had to be contested or not be perfectly enforced.
-For instance, \citet{cavalcanti2017essays} shows in his second chapter that there has been a misuse of these discontinuities.
-However, this problem was absent in our RDD, as the problem identified by Cavalcanti was based on the use of thresholds approved in 2009.
-In our case, we use the thresholds approved in 2003, and until a period before 2009 (in our case, 2008).
-
-\newpage
-
-## Identification Strategy in Multiple Thresholds Regression Discontinuity Design
-\label{ISMT}
-
-Usually when carrying out regression discontinuity with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes.
-Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$.
-The outcome variable is assumed to be $Y$.
-In the pooled model, the Local Average Treatment Effect is:
-
-\[
-LATE_{nocontrols} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C \right]
-\]
-
-Nevertheless, this may be problematic as the municipal characteristics in each cutoff may vary from cutoff to cutoff.
-The population imbalance certainly carries out heterogeneity, in the way shown by \citet{Cattaneo2016}.
-To ensure we have comparability, and that we estimate the average LATE for all cutoffs, avoiding most of the heterogeneity, we propose to add a set of controls denoted by $Z_i$ that vary between cutoffs.
-For instance, the population that determines the change from one threshold to another also determines all the cutoffs.
-As the population varies smoothly around each cutoff, it makes it a perfect control to add.
-The new estimator is:
-
-\[
-LATE_{controls} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C, Z_i \right]
-\]
-
-We control for Population, GDP, a dummy for the Northeast States, seats before the 2003 decision, and year.
-All these control variables are smooth in each cutoff, but are significantly different from cutoff to cutoff, making them adequate control variables for our case \citep{calonico2019regression}.
-To perform the estimations, we use a triangular kernel, which places more weight on the municipalities that are closer to each cutoff.
-To compute the optimal bandwidth, we use the \citet{CCT2014} method.
-To study the sensitivity to the bandwidth choice, we vary the bandwidth from 50\% to 200\% of the optimal bandwidth size.
-We also use cluster-robust standard errors at the municipal level.
-
-However, as it is uncommon for a regression discontinuity to use control variables, some readers may ask why in this case is it advisable?
-To answer this question, we run a series of simulations to show that controlling for the variable that determines the assignment not only helps improve the consistency of our estimates but also improves their efficiency.
-
-Consider the data distributed in one of the four forms depicted by Figure \ref{simRDdd}.
-We add nine thresholds, at 0.1, 0.2, and so on until 0.9, and we create six types of outcomes.
-The first three outcomes are sharp changes.
-In the first, we add variation from one to 10, with one step for each change.
-In the second, we add 1 in the first cut, zero in the second cut, and -1 in the third cut, repeating this pattern for the remaining cutoffs.
-The estimated change should be equal to zero.
-In the third model, we add one in the first cut, $1+0.9$ in the second cut, $1+0.9+0.8$ in the third cut, and so on until the last cutoff.
-This is intended to simulate a diminishing effect from one cutoff to the other.
-The last three outcomes are the same as depicted here, added by a Normal random disturbance, mean zero, and variance 0.01.
-We then run a thousand Monte Carlo simulation for each combination, $4 \times 6 \times 2 = 48$ in total, fitting a regression with and without the running variable as a control.
-
-XXXX CHANGE
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{0.9\linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/simdistrRDD.pdf}}
-      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
-      \bigskip
-      \label{simRDdd}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-A consistent estimator should fit one in the first and fourth data distribution.
-In the second and fifth, the change should be of $(1, 0, -1, 1, 0, -1, 1, 0, -1)$, and the average change here is equal to zero.
-In the third and sixth models the change should be equal to $(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)$, and the average change should be equal to $0.5$.
-The first three models should present a more efficient estimation than the last three models.
-We display the results in Figure \ref{estimDGP}, showing that the controlled models are more consistent and efficient.
-
-XXXX CHANGE
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=4.5in,angle=0]{../figures/estimsRDD.pdf}}
-      \caption{Estimations for the Different Data Generating Processes}
-      \bigskip
-      \label{estimDGP}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\newpage
-
-## Placebo Regressions for the Aggregated Mechanism Outcomes
-\label{placmechmain}
-
-Here we present the placebo regressions for the mechanism-aggregated outcomes.
-In Panel A of the main paper, we run the regression on alternative explanations.
-As we can see, the only female changed significantly, but the change is statistically expected in at least 10\% of cases.
-For non-white, we have not collected data on non-white legislators in the placebo cutoffs; therefore, we leave it blank.
-In Panel B, we have the placebo regressions for the primary mechanism: resource access and patronage.
-As expected, the placebo regressions were not statistically significant.
-
-XXXX CHANGE
-
-\begin{table}[!htbp] \centering 
-\caption{Mechanism -- Aggregate Municipal Level Regressions} 
-\label{placresmechreg1} 
-\scalebox{0.9}{
-\begin{threeparttable}
-\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l R R R R }
-\toprule
- & \multicolumn{4}{c}{\textbf{Panel A: Representation and Elections -- Placebo Cutoffs}} \\ \cline{2-5}
-& \multicolumn{2}{c}{\textbf{Representation}} & 
-\multicolumn{2}{c}{\textbf{Elections \& Leg. Productivity}}\\ \cline{2-3}\cline{4-5}
- & \multicolumn{1}{c}{\small{Num. Female}} & 
- \multicolumn{1}{c}{\small{Num. Non-white}} &
-  \multicolumn{1}{c}{\small{Candidates}} & 
-  \multicolumn{1}{c}{\small{Prop. Laws}} \\ 
-   & \multicolumn{1}{c}{\small{Councilors}} & 
- \multicolumn{1}{c}{\small{Councilors}} &
-  \multicolumn{1}{c}{\small{Per Seat}} & 
-  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
-  LATE & 0.65$^{**}$ &  & -0.72 & -0.001 \\ 
-  & (0.27) &  & (0.48) & (0.06) \\ 
-  N Left & 4620 &  & 4621 & 2991 \\ 
-  N Right & 906 &  & 906 & 703 \\ 
-  Eff N Left & 412 &  & 567 & 356 \\ 
-  Eff N Right & 297 &  & 347 & 229 \\ 
-  BW Loc Poly & 4.861 &  & 6.113 & 5.58 \\ 
-  BW Bias & 8.775 &  & 10.345 & 8.896 \\ 
-\midrule
- & \multicolumn{4}{c}{\textbf{Panel B: Resource Access and Patronage -- Placebo Cutoffs}} \\ \cline{2-5}
- & \multicolumn{1}{c}{\small{Mayoral}} & 
- \multicolumn{1}{c}{\small{Num. Politically}} & 
- \multicolumn{1}{c}{\small{Num. Career}} & 
- \multicolumn{1}{c}{\small{Num. Councilor}} \\
- & \multicolumn{1}{c}{\small{Coalition Size}} & 
- \multicolumn{1}{c}{\small{Appointed Empl.}} & 
- \multicolumn{1}{c}{\small{Bureaucrats}} & 
- \multicolumn{1}{c}{\small{Assistants}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.12 & 3.77 & 115.67 & -2.17 \\ 
- & (0.34) & (17.20) & (79.96) & (1.81) \\ 
- N Left & 4618 & 13855 & 13850 & 4618 \\ 
- N Right & 904 & 2709 & 2708 & 905 \\ 
- Eff N Left & 644 & 1123 & 1464 & 592 \\ 
- Eff N Right & 388 & 825 & 957 & 361 \\ 
- BW Loc Poly & 6.730 & 4.475 & 5.461 & 6.279 \\ 
- BW Bias & 10.421 & 7.600 & 9.999 & 10.944 \\ 
-\bottomrule
-\end{tabularx}
-\begin{tablenotes}
-\small
-\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1.
-RD estimates using \citet{CCT2014} optimal bandwidth selection and triangular kernel.
-Robust standard errors, clustered at the municipal level, in parenthesis.
-Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
-\end{tablenotes}
-\end{threeparttable}}
-\end{table}
-
-\newpage
-
-## Sensitivity Analysis for Bandwidth Selection
-\label{sensffapp}
-
-We present here the sensitivity to the bandwidth selection. Following the suggestions of \citet{Bueno2015}, we vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.
-
-XXXX CHANGE
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=5in,angle=0]{../figures/bwSens.pdf}}
-      \caption{Bandwidth Sensitivity -- Main Models}
-      \bigskip
-      \label{graphbw}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-In Figure \ref{placgraphbw}, we run the same bandwidth analysis for the placebo outcomes. The results, as expected, show mostly insignificant results.
-
-\pagebreak
-
-XXXX CHANGE
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[width=5in,angle=0]{../figures/placBwSens.pdf}}
-      \caption{Placebo Regressions -- Bandwidth Sensitivity}
-      \bigskip
-      \label{placgraphbw}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\newpage
-
-## Sensitivity to Different States in the Analysis
-\label{sensstate}
-
-The literature considers that some states are more prone to inefficiencies than the rest of the country.
-Moreover, some states had such poor Health Care and Education systems that they could be driving the results by themselves.
-As a consequence, our results could be a byproduct of structural changes in crucial states, instead of in council size.
-We run the analysis dropping one state at a time, to investigate this statewide heterogeneity.
-The results are in Figures \ref{graphsensstatedrop1},\ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.
-
-To interpret the results, first, note that most coefficients remain around the same value as before the robustness checks.
-The exceptions are with the Family Health Program, which improves without Para\'{i}ba but decreases significantly without Bahia, both northeastern states.
-In the placebo, the FHP coverage increases when we remove Bahia and decrease when we add S\~{a}o Paulo.
-Otherwise, note that all the other variables remain unchanged, except for gender.
-Gender changes because there were laws during this period mandating a minimum amount of female candidates.
-It is expected that one variable changes as a response to randomness.
-
-\pagebreak
-
-XXXX CHANGE
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens1.pdf}}
-      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
-      \bigskip
-      \label{graphsensstatedrop1}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-XXXX CHANGE
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens2.pdf}}
-      \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
-      \bigskip
-      \label{graphsensstatedrop2}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-XXXX CHANGE
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=5in,angle=0]{../figures/placDropStateSens1.pdf}}
-      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
-      \bigskip
-      \label{placgraphsensstatedrop1}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-XXXX CHANGE
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/placDropStateSens2.pdf}}
-      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
-      \bigskip
-      \label{placgraphsensstatedrop2}
-  \end{center}
-\end{figure}
-
-\newpage
-
-## Sensitivity to the Functional Form Analysis
-\label{sensfuncform}
-
-In the paper, we run all the regressions using local linear polynomials.
-\citet{GelmanImbens2014} show that local linear and quadratic polynomials are better in terms of consistency than cubic and quartic.
-
-However, we run here all the models using polynomials from local linear to a quartic, showing that our results are robust to different regression functional forms.
-With two exceptions, the results are mostly consistent.
-First, quadratic and cubic polynomials make the significance go away in some models.
-Second, quartic polynomials seem to make the Family Health Program (FHP) significant and negative, which goes in line with our theoretical predictions.
-Figures \ref{graphsensff} and \ref{placgraphsensff} present the results for the real and the placebo cutoffs.
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{../figures/ffSens.pdf}}
-      \caption{Sensitivity Analysis for the Functional Form}
-      \bigskip
-      \label{graphsensff}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/placFfSens.pdf}}
-      \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
-      \bigskip
-      \label{placgraphsensff}
-  \end{center}
-\end{figure}
-
-\newpage
-
-## Sensitivity to Covariates
-\label{senstcovapp}
-
-The control variables play an essential role in our model.
-As we argued before, without controls, the first stage is inconsistent, and we may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
-
-However, if the selection of controls makes the models overestimate quantities in the directions our narrative emphasizes, this would pose a considerable credibility issue for our analysis.
-To study the sensitivity to controls, we run the same regressions for all possible control combinations.
-Figure \ref{graphsenscontrol} displays the results for this sensitivity test.\footnote{In the Figure, \textit{NC} stands for No Controls.
-The controls used are \textit{gdp}, the municipal GDP in a given year; \textit{nseats2000}, the number of seats before the 2003 Supreme Court decision; \textit{northeast}, a dummy variable for Northeast Brazil; \textit{pop2003\_2}, population in 2003 (underscore 2 means that is population by thousands); and \textit{year}.}
-
-\begin{landscape}
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=6in,angle=0]{../figures/sensCov.pdf}}
-      \caption{Sensitivity Analysis for the Control Variable's Choices}
-\bigskip
-\label{graphsenscontrol}
-\end{minipage}
-\end{center}
-\end{figure}
 \end{landscape}
 
-For instance, changes in controls have a substantial effect on the detected differences in the Family Health Program coverage, as well as in Elementary Education Quality.
-
-In our view, our choice was the most conservative, as the Full Model is significant when most of the combinations also are significant.
-Otherwise, our model is not significant when most combinations are also insignificant.
-Regarding the point estimates, our analysis chooses the smaller coefficient sizes systematically for the significant variables.
-
-We also plot sensitivity tests to covariates in the placebo regressions in Figures \ref{placsenscov1} and \ref{placsenscov2}.
-The theoretical expectations here are that most of these outcomes would fail, and the graphs indeed confirm these expectations.
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens1Cov.pdf}}
-\caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
-\bigskip
-\label{placsenscov1}
-\end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens2Cov.pdf}}
-\caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
-\bigskip
-\label{placsenscov2}
-\end{center}
-\end{figure}
-
-\newpage
-
-\subsection{Sensitivity to Additional Cutoffs\label{senscutapp}}
-
-To study the sensitivity to the number of cutoffs, as well as a possibility of diminishing returns from the additional legislator, we run regressions limiting the population sizes to half the cutoffs, from the second cutoff to the last.
-This strategy is similar to adding one cutoff at a time.
-The results are stable and do not change our main conclusions.
-Moreover, there is no increasing or decreasing pattern, which would indicate that differential returns are occurring.
-Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs, while Figures \ref{placsenscut1} and \ref{placsenscut2} present the same results for the placebo cutoffs.
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts1.pdf}}
-\caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
-\bigskip
-\label{senscut1}
-\end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts2.pdf}}
-\caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
-\bigskip
-\label{senscut2}
-\end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\begin{minipage}{0.8 \linewidth}
-\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts1.pdf}}
-\caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
-\bigskip
-\label{placsenscut1}
-\end{minipage}
-\end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\begin{minipage}{0.8 \linewidth}
-\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts2.pdf}}
-\caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
-\bigskip
-\label{placsenscut2}
-\end{minipage}
-\end{center}
-\end{figure}
-
-\newpage
-
-## Mayor's Characteristics, Revenues, and Transfers from the Central Government
-
-Two alternative explanations could confound our results.
-First, the selection of the mayor could be affected by the city council size, and then the welfare improve by the quality of the mayor, and not by the partisan mechanism described.
-Second, the partisan mechanism could be confounded by an argument similar to the @Weingastetal1981 ``law of 1/n'', and the improvements in welfare could have been a result of higher revenues.
-This section shows that none of these concerns are true in our case.
-
-\subsubsection{Mayoral characteristics}
-
-We select four characteristics: gender, schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
-The results show no variation on council size and mayoral characteristics.
-
-\begin{table}[!htbp] \centering 
-\caption{Mayoral Characteristics} 
-\label{appmaychar} 
-\resizebox{\textwidth}{!}{
-  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-  \\[-1.8ex]\hline \\[-1.8ex] 
-  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
-College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
-  \hline \\[-1.8ex] 
-  LATE & 0.07 & -0.06 & -0.09 & 0.06 \\ 
-  & (0.08) & (0.13) & (0.10) & (0.14) \\ 
-  N Left & 5069 & 5069 & 5184 & 5183 \\ 
-  N Right & 335 & 335 & 343 & 343 \\ 
-  Eff N Left & 299 & 226 & 192 & 231 \\ 
-  Eff N Right & 184 & 154 & 141 & 159 \\ 
-  BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\ 
-  BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\ 
-  \hline \\[-1.8ex] 
-  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-  \end{tabular} }
-\end{table}
-
-\begin{table}[!htbp] \centering 
-\caption{Mayoral characteristics -- Placebo} 
-\label{placappmaychar} 
-\resizebox{\textwidth}{!}{
-  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-  \\[-1.8ex]\hline \\[-1.8ex] 
-  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
-College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
-  \hline \\[-1.8ex] 
-  LATE & 0.03 & 0.04 & 0.08 & -0.07 \\ 
-  & (0.05) & (0.08) & (0.07) & (0.08) \\ 
-  N Left & 4526 & 4526 & 4621 & 4620 \\ 
-  N Right & 878 & 878 & 906 & 906 \\ 
-  Eff N Left & 567 & 707 & 683 & 759 \\ 
-  Eff N Right & 342 & 406 & 397 & 427 \\ 
-  BW Loc Poly & 6.197 & 7.413 & 7.006 & 7.71 \\ 
-  BW Bias & 10.241 & 12.64 & 13.536 & 12.648 \\ 
-  \hline \\[-1.8ex] 
-  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-  \end{tabular} }
-\end{table}
-
-\subsubsection{Revenues and Transfers}
-
-We run the regressions on federal transfers and revenue raised within the municipalities.
-There is only a small effect on education transfer, barely significant at 10%.
-The other indicators remain insignificant.
-Note that the placebo are significant, and this actually reinforce the claim that the education effect may be spurious.
-
-\begin{table}[!htbp] \centering 
-\caption{Transfers and Revenue} 
-\label{apptrev} 
-\resizebox{\textwidth}{!}{
-  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-  \\[-1.8ex]\hline \\[-1.8ex] 
-  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
-  \hline \\[-1.8ex] 
-  LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\ 
-  & (0.04) & (0.03) & (0.10) & (0.04) \\ 
-  N Left & 15555 & 15555 & 15460 & 14668 \\ 
-  N Right & 1029 & 1029 & 1028 & 998 \\ 
-  Eff N Left & 804 & 258 & 349 & 626 \\ 
-  Eff N Right & 516 & 273 & 333 & 442 \\ 
-  BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\ 
-  BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\ 
-  \hline \\[-1.8ex] 
-  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-  \end{tabular} }
-\end{table}
-
-\begin{table}[!htbp] \centering 
-\caption{Transfers and Revenue -- Placebo} 
-\label{plactrev} 
-\resizebox{\textwidth}{!}{
-  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-  \\[-1.8ex]\hline \\[-1.8ex] 
-  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
-  \hline \\[-1.8ex] 
-  LATE & 0.07$^{**}$ & 0.04 & 0.03 & 0.07$^{**}$ \\ 
-  & (0.03) & (0.03) & (0.06) & (0.03) \\ 
-  N Left & 13865 & 13865 & 13776 & 13103 \\ 
-  N Right & 2719 & 2719 & 2712 & 2563 \\ 
-  Eff N Left & 807 & 636 & 1928 & 848 \\ 
-  Eff N Right & 619 & 544 & 1163 & 611 \\ 
-  BW Loc Poly & 3.418 & 3.028 & 6.738 & 3.67 \\ 
-  BW Bias & 6.021 & 5.36 & 10.871 & 6.222 \\ 
-  \hline \\[-1.8ex] 
-  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-  \end{tabular} }
-\end{table}
-
-\newpage
-
-\subsection{Legislation Dataset\label{legdfr}}
-
-In the Fall of 2018, we collected the data on the legislation approved by the city council of 64 municipalities 10 thousand inhabitants away from the thresholds.
-There are 202 municipalities at a 10 thousand inhabitants distance from the cutoff, but only 64 had information on the legislation for the period between 2005 to 2008.
-
-To classify the legislation, we hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machines algorithm to the remaining 99\% cases.
-First, we train and test the accuracy of the SVM classifier on 80\% of the dataset.
-Then, we ran the training on the full hand-coded data and predicted the remaining.\footnote{We tested SVM, Naive-Bayes, Random Forests, and Neural Networks.
-We choose SVM as it gives the highest prediction rate.
-We are using a simple bag-of-words classifier, with the R package RTextTools \citep{collingwood2013rtexttools}.}
-
-We hand-coded using five characteristics:
-
-\begin{enumerate}
-\item \textbf{Local Public Goods}: Whether the bills provided a local public good or service.
-Bills here are, for example, proposals to fix street potholes, staff a given health clinic, purchase equipment to a given school.
-To lay on this category, the service should have been targeted for a fraction of the population.
-\item \textbf{Public Goods and Legislation}: Whether a bill is about a municipal public good (e.g., improving education), or about legislation that does not discriminate against any citizen within the polity (general law).
-\item \textbf{Oversight}: Legislation requesting information on the status of service provision.
-\item \textbf{Others}: Legislation that is not categorized as any of the previous three listed. Legislation here includes honors to notable citizens and procedure legislation, among others.
-\item \textbf{Health Care and Education}: Bills on education and health care, broadly defined.
-\end{enumerate}
-
-We run the SVM on the hand-coded data.
-Table \ref{accurClassif} shows the classification accuracy for each of the variables that we hand-coded.
-In all models, we set cost equals 10 to avoid overfitting.
-
-\begin{table}
-\centering
-\caption{Accuracy SVM Classifier (tested in 20\% of the data)}
-\label{accurClassif}
-\begin{tabular}{lc} 
-\hline
-\textbf{Variable}            & \textbf{Accuracy}  \\ 
-\hline
-Local Public Goods           & 93.8               \\
-Public Goods and Legislation & 94.2               \\
-Oversight                    & 94.9               \\
-Others                       & 93.5               \\
-Education and Health Care    & 92.5               \\
-\hline
-\end{tabular}
-\end{table}
-
-After we classify all the bills, the frequency in each category was added to the main paper.
-We also add the productivity per legislator, consisting of a ratio of the legislation approved in the municipality in the four-year term, divided by the council size.
-As expected, the results changed little from when we considered the absolute values.
-
-\newpage
-
-\subsection{City Councilors Survey\label{appsurv}}
-
-From November 21st to December 1st, 2016, we surveyed former city councilors that served in the 2005 to 2008 period.
-We asked them questions regarding how mayors secure electoral support, which services are common in the city councilor's practice, and which services give the highest electoral yield.
-
-We used 3,240 emails from politicians that ran in the 2016 election, filtering the politicians that hold public office in 2005.
-In December 1st we closed the pool, having 174 responses.
-Figure \ref{geodistrsurv} displays a distribution of responses.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrRespSurvey.pdf}}
-      \caption{Geographical Distribution of Survey Responses}
-      \bigskip
-      \label{geodistrsurv}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-To weight the survey, we use the Legislative Census, which was conducted ran in 2005 by the Brazilian Senate company \textit{Interlegis} to improve the quality of the legislative.
-We use the categories of Brazilian region, legislature size (9 to 15 or more), gender, and age less than 39, re-weighting the collected data to match the population proportions.
-We use the proportions on each bin to weight the graphs and statistics generated after the raking process.\footnote{The R package \textit{survey} describes in detail the raking process \citep{lumley2004analysis}.
-In summary, it iterates the post-stratification procedure until the sample marginals match the population marginals for all variables.} Table \ref{tabweight} shows the sample, population, and weighted proportions.
-
-\begin{table}[htp!]
-\centering
-\caption{Proportions for each bin used in the weighting process}
-\label{tabweight}
-\begin{tabular}{lccc}
-\hline
-& Sample & Population & Weighted \\
-& Proportions & Proportions. & Proportions \\
-\hline
-\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
-\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
-\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
-\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
-\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
-\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
-\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
-\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
-\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
-\textbf{Region = CENTRO-OESTE} & 0.11         & 0.08       & 0.08           \\
-\textbf{Region = NORDESTE}     & 0.33         & 0.32       & 0.32           \\
-\textbf{Region = NORTE}        & 0.05         & 0.08       & 0.08           \\
-\textbf{Region = SUDESTE}      & 0.30         & 0.30       & 0.30           \\
-\textbf{Region = SUL}          & 0.20         & 0.21       & 0.21           \\ \hline
-\end{tabular}
-\end{table}
-
-Note that the algorithm performed well, with minimal differences occurring only after the third decimal place.
-
-The questions of interest for this research, asked in the survey were:
-
-\begin{enumerate}
-    \item No Brasil é comum que o prefeito tenha de negociar para ter maioria na Câmara de Vereadores.
-Com que frequência, o(a) Sr(a) acha que o prefeito usa os seguintes dispositivos para conseguir apoio?
-    \item Quais dessas atividades o(a) Sr(a) acredita serem mais comuns no trabalho da maioria dos vereadores?
-    \item Quais dessas atividades o(a) Sr(a) acredita que ajudam mais um vereador durante a eleição?
-\end{enumerate}
-
-A free translation to English would be:
-
-\begin{enumerate}
-    \item In Brazil, it is common that mayors negotiate the majority within the city council. What is the frequency that mayors use the following services in exchange for support?
-    \item Which of those activities do city councilors perform the most in their representation practices?
-    \item Which of the following activities do you believe helps city councilors the most in elections?
-\end{enumerate}
-
-The second question is essential, as it reports whether councilors do the activities that give more electoral yield.
-Figure \ref{commonservice} shows the results for each of the activities we studied the electoral yield.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6.5in,angle=0]{../figures/commonJobsCouncilors.pdf}}
-      \caption{City Councilor's Common Activities}
-\bigskip
-\label{commonservice}
-\end{minipage}
-\end{center}
-\end{figure}
-
-The last question measures the willingness of mayors to give services to city councilors.
-This question is relevant, as mayors control most of the bureaucracy and the mediation of services requires a good relationship with mayors.
-Figure \ref{mayorneg} shows the results for the mayoral activities.
-
-\begin{figure}[htb!]
-\begin{center}
-\begin{minipage}{1 \linewidth}
-\centerline{\includegraphics[width=6.5in,angle=0]{../figures/strategySupportMayors.pdf}}
-\caption{Mayor negotiated services in exchange of support}
-\bigskip
-\label{mayorneg}
-\end{minipage}
-\end{center}
-\end{figure}
-
-Therefore, both Figures show that councilors do perform the tasks that give the most electoral yield.
-The exception is the category of honor legislation, which most legislators seem to perform, even though they acknowledge that it provides little electoral returns.
-
-Regarding the services that mayors use to negotiate with the coalition, note that jobs in exchange of support are the highest ranked strategy by councilors.
-Our results capture that, as an increase in city council size has a positive effect on the number of appointed employees in the municipality.
+## Estimated Models
+
+I run three models.
+First, a RDD for the city council size.
+Second, I tried a RDD for the run-off thresholds, but the number of cases on the right hand side is too small, and the RDD is unidentified.
+To avoid this problem, I run a t-test comparing the cases on the left with the cases on the right, restricting the sample for the municipalities around 50 thousands away from the cutoff (for identification purposes).
+
+For \citet{brollo2013political} broad irregularities:
+
+```
+trs = .5 # Chosen to make the computations feasible
+aux <- rdrobust(dat$broad, dat$runningCC, covs = dat[,c('pop','year_2006','year_2007','year_2008', 'lottery')])
+
+coefs <- extr_coef_rdr(aux, name = 'Council Size (RDD)')
+
+aux <- t.test(dat$broad[abs(dat$distValidVotes200k)<trs]~as.numeric(dat$distValidVotes200k[abs(dat$distValidVotes200k)<trs]>0))
+
+coefs <- rbind(coefs, extr_coef_ttest(aux, 'Run-off (T-test)'))
+
+aux <- summary(ivreg(broad~stdzy(nCandMayor)+pop+factor(year)|runningCC+pop+factor(year), data=dat), vcov = sandwich, df = Inf, diagnostics = TRUE)
+
+coefs <- rbind(coefs, extr_coef_ivreg(aux, name = 'Cand. Mayor (IVreg)'))
+
+aux <- summary(ivreg(broad~stdzy(nCandCC_by10)+pop+factor(year)|runningCC+pop+factor(year), data=dat), vcov = sandwich, df = Inf, diagnostics = TRUE)
+
+coefs <- rbind(coefs, extr_coef_ivreg(aux, name = 'Cand. Council (IVreg)'))
+
+coefs
+coefs$model = 'Broad inefficiencies'
+totalModel <- coefs
+```
+
+For \citet{brollo2013political} narrow (corruption) irregularities:
+
+```
+aux <- rdrobust(dat$narrow, dat$runningCC, covs = dat[,c('pop','year_2006','year_2007','year_2008', 'lottery')])
+
+coefs <- extr_coef_rdr(aux, name = 'Council Size (RDD)')
+
+aux <- t.test(dat$narrow[abs(dat$distValidVotes200k)<trs]~as.numeric(dat$distValidVotes200k[abs(dat$distValidVotes200k)<trs]>0))
+
+coefs <- rbind(coefs, extr_coef_ttest(aux, 'Run-off (T-test)'))
+
+aux <- summary(ivreg(narrow~stdzy(nCandMayor)+pop+factor(year)|runningCC+pop+factor(year), data=dat), vcov = sandwich, df = Inf, diagnostics = TRUE)
+
+coefs <- rbind(coefs, extr_coef_ivreg(aux, name = 'Cand. Mayor (IVreg)'))
+
+aux <- summary(ivreg(narrow~stdzy(nCandCC_by10)+pop+factor(year)|runningCC+pop+factor(year), data=dat), vcov = sandwich, df = Inf, diagnostics = TRUE)
+
+coefs <- rbind(coefs, extr_coef_ivreg(aux, name = 'Cand. Council (IVreg)'))
+coefs
+
+coefs$model = 'Narrow corruption'
+totalModel <- rbind(coefs, totalModel)
+```
+
+```
+p <- ggplot(totalModel, aes(term, estimate))+
+  geom_point()+
+  geom_pointrange(aes(ymin = estimate - 1.64*std.error, 
+                      ymax = estimate + 1.64*std.error), size = 0.5)+
+  geom_pointrange(aes(ymin = estimate - 1.96*std.error, 
+                      ymax = estimate + 1.96*std.error), 
+                  size = 0.35, linetype = 2)+
+  geom_text(aes(label = round(estimate, digits=2)), nudge_x = 0.25) + 
+  scale_x_discrete("") +
+  theme_bw() +
+  geom_hline(yintercept = 0, linetype = 3) +
+  coord_flip(ylim = c(-1, 1)) + ylab(NULL)+
+  theme(text = element_text(size=12))+
+  facet_grid(~model)
+```
+
+For \citet{avelino2016replication} incidence of corruption in health care transfers:
+
+```
+aux <- rdrobust(dat$ind_corrup_n, dat$runningCC, covs = dat[,c('pop','year_2006','year_2007','year_2008', 'lottery')])
+
+coefs <- extr_coef_rdr(aux, name = 'Council Size (RDD)')
+
+aux <- t.test(dat$ind_corrup_n[abs(dat$distValidVotes200k)<trs]~as.numeric(dat$distValidVotes200k[abs(dat$distValidVotes200k)<trs]>0))
+
+coefs <- rbind(coefs, extr_coef_ttest(aux, 'Run-off (T-test)'))
+
+aux <- summary(ivreg(ind_corrup_n~stdzy(nCandMayor)+pop+factor(year)|runningCC+pop+factor(year), data=dat), vcov = sandwich, df = Inf, diagnostics = TRUE)
+
+coefs <- rbind(coefs, extr_coef_ivreg(aux, name = 'Cand. Mayor (IVreg)'))
+
+aux <- summary(ivreg(ind_corrup_n~stdzy(nCandCC_by10)+pop+factor(year)|runningCC+pop+factor(year), data=dat), vcov = sandwich, df = Inf, diagnostics = TRUE)
+
+coefs <- rbind(coefs, extr_coef_ivreg(aux, name = 'Cand. Council (IVreg)'))
+
+coefs
+coefs$model = 'Pct. corruption health'
+totalModel <- coefs
+```
+
+For \citet{avelino2016replication} amount of corruption in health care transfers (divided by the total transfers):
+
+```
+aux <- rdrobust(dat$ind_corrup_m, dat$runningCC, covs = dat[,c('pop','year_2006','year_2007','year_2008', 'lottery')])
+
+coefs <- extr_coef_rdr(aux, name = 'Council Size (RDD)')
+
+aux <- t.test(dat$ind_corrup_m[abs(dat$distValidVotes200k)<trs]~as.numeric(dat$distValidVotes200k[abs(dat$distValidVotes200k)<trs]>0))
+
+coefs <- rbind(coefs, extr_coef_ttest(aux, 'Run-off (T-test)'))
+
+aux <- summary(ivreg(ind_corrup_m~stdzy(nCandMayor)+pop+factor(year)|runningCC+pop+factor(year), data=dat), vcov = sandwich, df = Inf, diagnostics = TRUE)
+
+coefs <- rbind(coefs, extr_coef_ivreg(aux, name = 'Cand. Mayor (IVreg)'))
+
+aux <- summary(ivreg(ind_corrup_m~stdzy(nCandCC_by10)+pop+factor(year)|runningCC+pop+factor(year), data=dat), vcov = sandwich, df = Inf, diagnostics = TRUE)
+
+coefs <- rbind(coefs, extr_coef_ivreg(aux, name = 'Cand. Council (IVreg)'))
+
+coefs
+coefs$model = 'Tot. Amt. corrup. health'
+totalModel <- rbind(coefs, totalModel)
+```
+
+And the coefficient plots:
+
+```
+p2 <- ggplot(totalModel, aes(term, estimate))+
+  geom_point()+
+  geom_pointrange(aes(ymin = estimate - 1.64*std.error, 
+                      ymax = estimate + 1.64*std.error), size = 0.5)+
+  geom_pointrange(aes(ymin = estimate - 1.96*std.error, 
+                      ymax = estimate + 1.96*std.error), 
+                  size = 0.35, linetype = 2)+
+  geom_text(aes(label = round(estimate, digits=2)), nudge_x = 0.25) + 
+  scale_x_discrete("") +
+  theme_bw() +
+  geom_hline(yintercept = 0, linetype = 3) +
+  coord_flip(ylim = c(-1, 1)) + ylab(NULL)+
+  theme(text = element_text(size=12))+
+  facet_grid(~model)
+
+grid.arrange(p, p2, ncol = 1)
+```
+
+## Robustness Checks
+
+For the RDD estimates I run the same models, now with a fake cutoff. The results follow below:
+
+```
+aux <- rdrobust(dat$broad, dat$fakeRunningCC, covs = dat[,c('pop','year_2006','year_2007','year_2008')])
+
+coefs <- extr_coef_rdr(aux, name = 'broad')
+
+aux <- rdrobust(dat$narrow, dat$fakeRunningCC, covs = dat[,c('pop','year_2006','year_2007','year_2008')])
+
+coefs <- rbind(coefs, extr_coef_rdr(aux, name = 'narrow'))
+
+aux <- rdrobust(dat$ind_corrup_n, dat$fakeRunningCC, covs = dat[,c('pop','year_2006','year_2007','year_2008')])
+
+coefs <- rbind(coefs, extr_coef_rdr(aux, name = 'freqCorrupHealth'))
+
+aux <- rdrobust(dat$ind_corrup_m, dat$fakeRunningCC, covs = dat[,c('pop','year_2006','year_2007','year_2008')])
+
+coefs <- rbind(coefs, extr_coef_rdr(aux, name = 'amtCorrupHealth'))
+
+p <- ggplot(coefs, aes(term, estimate))+
+  geom_point()+
+  geom_pointrange(aes(ymin = estimate - 1.64*std.error, 
+                      ymax = estimate + 1.64*std.error), size = 0.5)+
+  geom_pointrange(aes(ymin = estimate - 1.96*std.error, 
+                      ymax = estimate + 1.96*std.error), 
+                  size = 0.35, linetype = 2)+
+  geom_text(aes(label = round(estimate, digits=2)), nudge_x = 0.25) + 
+  scale_x_discrete("") +
+  theme_bw() +
+  geom_hline(yintercept = 0, linetype = 3) +
+  coord_flip(ylim = c(-1, 1)) + ylab(NULL)+
+  theme(text = element_text(size=12))
+p
+```
+
+And as we can see, most of the placebo RDD tests failed, as expected.
+The only significant result is the amount of health care corruption, and in the wrong direction.
+For the run-off cutoffs, we did not use RDD because the number of cases in each side is small.
+We run a robustness with a fake cutoff for 150 thousand (50 thousand voters below the actual threshold).
+The results follow below:
+
+```
+aux <- t.test(dat$broad[abs(dat$distValidVotes150k)<trs]~as.numeric(dat$distValidVotes150k[abs(dat$distValidVotes150k)<trs]>0))
+
+coefs <- extr_coef_ttest(aux, 'broad (below)')
+
+aux <- t.test(dat$narrow[abs(dat$distValidVotes150k)<trs]~as.numeric(dat$distValidVotes150k[abs(dat$distValidVotes150k)<trs]>0))
+
+coefs <- rbind(coefs, extr_coef_ttest(aux, 'narrow (below)'))
+
+aux <- t.test(dat$ind_corrup_n[abs(dat$distValidVotes150k)<trs]~as.numeric(dat$distValidVotes150k[abs(dat$distValidVotes150k)<trs]>0))
+
+coefs <- rbind(coefs, extr_coef_ttest(aux, 'freqCorrupHealth (below)'))
+
+aux <- t.test(dat$ind_corrup_m[abs(dat$distValidVotes150k)<trs]~as.numeric(dat$distValidVotes150k[abs(dat$distValidVotes150k)<trs]>0))
+
+coefs <- rbind(coefs, extr_coef_ttest(aux, 'amtCorrupHealth (below)'))
+
+p <- ggplot(coefs, aes(term, estimate))+
+  geom_point()+
+  geom_pointrange(aes(ymin = estimate - 1.64*std.error, 
+                      ymax = estimate + 1.64*std.error), size = 0.5)+
+  geom_pointrange(aes(ymin = estimate - 1.96*std.error, 
+                      ymax = estimate + 1.96*std.error), 
+                  size = 0.35, linetype = 2)+
+  geom_text(aes(label = round(estimate, digits=2)), nudge_x = 0.25) + 
+  scale_x_discrete("") +
+  theme_bw() +
+  geom_hline(yintercept = 0, linetype = 3) +
+  coord_flip(ylim = c(-1, 1)) + ylab(NULL)+
+  theme(text = element_text(size=12))
+p
+```
+
+And the placebo failed, as expected, for all models. We choose a window of 50 thousand voters, as restricting more would make the estimation infeasible.
+
+\clearpage

### 2021-08-22 appendix/appendix.Rmd
commit app

@@
 
-Consider three sets of players: a set of incumbents $ I \ = \ \{ I_1, \ \cdots, \ I_K \}$, a set of challengers $C \ = \ \{ C_1, \ \cdots, \ C_L \}$, and a continuum of $V$ voters.
+Consider a strategic interaction with three sets of players: a set of incumbents $ I \ = \ \{ I_1, \ \cdots, \ I_K \}$ and a set of challengers $C \ = \ \{ C_1, \ \cdots, \ C_L \}$, and a representative voter $V$.
 

### 2021-08-23 article/article.Rmd
Intro first para

@@
 
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
 
@@
 
-The design of electoral institutions is key for political accountability and representation \citep{cox1997making, manin1999elections, carey2011electoral, shugart2017votes, taylor2017impact}.
-Electoral rules influence incentives that politicians face when they are in office, public service provision, reelection and survival in office, campaign strategies, and incumbency advantages, among other characteristics.
-One particular consequence of electoral rules is their effect on corruption \citep{Persson2003, Kunicova2005, chang2007electoral, charron2011party, alfano2014electoral, schleiter2014party, xezonakis2015can, schwindt2016corruption}.
+Corruption is one of the most prevalent and harmful diseases of developing countries.
+Corruption lowers public goods provision \citep{banerjee201227, beekman2014corruption}, decreases foreign investments \citep{habib2002corruption}, stunt economic growth \citep{mauro1995corruption, grundler2019corruption}, and affects human capital investments \citep{ferraz2012corrupting}.
+Corruption also have nefarious effects on trust \citep{sole2018trust}, attitudes toward political parties \citep{winters2015political}, and fuels the distrust in the political system \citep{mignozzetti2019brazil}.
+Investigating institutional designs that lower corruption is essential to improve short and long-term welfare.
+
+One crucial feature of political corruption is that it is perpetrated by politicians.
+While bureaucratic corruption may be more frequent, it is also easier to sanction and XXXX \citep{XXXX}.
+Political corruption, on the other hand, involves higher rents \citep{XXXX}, has a more disruptive effects on the political system \citep{XXXX}, and frequently goes unpunished \citep{XXXX}.
+For instance, one of the major corruption scandals in Brazil, the Car Wash operation, involved politicians in XXXX parties, and amounted to XXXX in rents and XXXX.
+The efforts to punish the politicians involved failed as the last two presidents undercut the ability of the public prosecutors of XXXX.
+
+This prompts the question: is there a XXXX in the design of the political system that could lower the incentives for political corruption?
+
+As politicians are the XXXX of political corruption, understanding the incentives they face for reelection could help XXXX to XXXX, lowering their incentives to engage in corruption.
+
+The design of electoral systems affect several XXXX, such as accountability and representation XXXX \citep{XXXX}, public service provision XXXX, reelection and survival in office XXXX, campaign strategies XXXX, incumbency advantages XXXX, among other XXXX.
+The same incentives that promote service provision and accountability could be manipulated to deliver lower political corruption.
+However,
+
+This idea have been XXXX by scholars XXXX.
+One important XXXX is the impact of XXXX on political corruption.
+, one particular XXXX is the impact particular consequence of electoral rules is their effect on corruption \citep{Persson2003, Kunicova2005, chang2007electoral, charron2011party, alfano2014electoral, schleiter2014party, xezonakis2015can, schwindt2016corruption}.
+
+Scholars have been investigating the correlation between features in the electoral system and corruption, but to this date, there is no consensual prescription about the use of electoral rules to lower political corruption.
+For instance, XXXX.
 

### 2021-08-24 article/article.Rmd
intro advancing

--- 2021-08-20 article/article.Rmd
@@
 date: \today
-thanks: "I thank Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Adam Przeworski, Howard Rosenthal, Renard Sexton, Denis Stukal, and Scott Tyson for their comments.
-I also thank participants at APSA, MPSA, NYU PE Seminar, and SPSA.
+thanks: "I thank Livio DiLonardo, Sandy Gordon, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Adam Przeworski, Howard Rosenthal, Renard Sexton, Denis Stukal, and Scott Tyson for their comments.
+I also thank participants at APSA, MPSA, and SPSA.
 All materials required to replicate this study are available at <https://github.com/umbertomig/electoral-systems-corruption>."
-abstract: "This is my abstract."
+abstract: "What are the effects of electoral systems and competition on political corruption?
+In this paper, I propose a formal model of political corruption where incumbents decide how much kickbacks to add in the XXXX, and challengers may run anti-corruption campaigns against the incumbents.
+To understand how institutions and competition affect the results, I study two benchmarks: in the first, called the non-excludable anti-corruption campaign, successful exposure of an incumbent opens her seats to all other competitors.
+In the second benchmark, the excludable anti-corruption campaign, the politician successfully exposing the corruption signals competence, and voters tend to prefer her vis-a-vis the other challengers.
+When anti-corruption campaigns are non-excludable, an increase in the number of challengers or incumbents monotonically raises corruption.
+However, when anti-corruption campaigns are excludable, the number of challengers is endogenously limited.
+The excludability makes the free-riding in corruption exposure disappear.
+When I increase the number of incumbents, corruption rises less than in the non-excludable benchmark.
+These predictions hold empirically using quasi-experimental data from Brazilian and Italian municipalities.
+This study has implications for the design of electoral institutions and entry barriers in democratic elections."
 abstractspacing: double
@@
 
-The design of electoral institutions is key for political accountability and representation \citep{cox1997making, manin1999elections, carey2011electoral, shugart2017votes, taylor2017impact}.
-Electoral rules influence incentives that politicians face when they are in office, public service provision, reelection and survival in office, campaign strategies, and incumbency advantages, among other characteristics.
-One particular consequence of electoral rules is their effect on corruption \citep{Persson2003, Kunicova2005, chang2007electoral, charron2011party, alfano2014electoral, schleiter2014party, xezonakis2015can, schwindt2016corruption}.
+Corruption is one of the most prevalent and harmful diseases of developing countries.
+Corruption lowers public goods provision \citep{banerjee201227, beekman2014corruption}, decreases foreign investments \citep{habib2002corruption}, stunt economic growth \citep{mauro1995corruption, grundler2019corruption}, and affects human capital investments \citep{ferraz2012corrupting}.
+Corruption also have detrimental effects on trust \citep{you2018trust}, attitudes toward political parties \citep{winters2015political}, and fuels the distrust in the political system \citep{mignozzetti2019brazil}.
+The International Transparency estimates that corruption is responsible for $1.23 trillion US dollars every year, a sum that could lift 1.4 billion people out of the extreme poverty for consecutive six years \citep{fleming2019corruption}.
 
-Despite the large body of literature on incentives that electoral system creates for corruption, two problems remain sparse.
-On the one hand, the roles of challengers in coping or boosting corruption incentives remain unclear.
-Although challengers are not the politicians that embezzle money, their campaign strategies may not only communicate with voters about her platform but also hold the incumbent's accountable by exposing their malfeasances once in office.\footnote{According to  \citet{polborn2006informative}, negative campaign is useful as it reveals information about candidates that they would now be willing to reveal by themselves.
-This paper rationalizes the idea that negative campaign, such as exposing a corrupt past, maybe even desirable from the perspective of voter's welfare.}
+One crucial distinction in corruption activity is the actor that is perpetrating corruption.
+While bureaucratic corruption may be more frequent, it is also easier to sanction and to punish.
+Political corruption, on the other hand, involves higher rents than bribes to services.
+They are usually associated with large government contracts and procurement \citep{broms2019political}, have a more disruptive effects on the trust in political institutions \citep{sole2018trust}, divert the bureaucracy toward rent seeking \citep{brierley2020unprincipled}.
+For instance, one of the major corruption scandals in the world, the Car Wash scandal in Brazil, involved more than 50 politicians, several high level bureaucrats, and about five billion US dollars in kickbacks \citep{watts2017operation}.
+Political corruption is intricate also because the electoral sanctioning often fails \citep{klavsnja2017uninformed, canete2020voting, janezic2020eliciting}.
+However, as elections are the primary mechanism to sanction corrupt politicians, are there electoral system features that could improve the sanctioning and lower corruption?
 
-On the other hand, despite the richness of the empirical literature on electoral systems and corruption, it frequently finds mixed results regarding the impact of district size, the pool of competitors, parties, and other electoral characteristics on corruption.
-For instance, \citet{Persson2003} show that closed-list Proportional Representation (PR) increases corruption by making voters less capable of punishing politicians, and single-member districts (SMD) may not be best for corruption as it poses significant entry barriers to honest politicians.
-However, \citet{chang2007electoral} demonstrate that, when controlling for the district magnitude, open-list PR performs worse in large-magnitude districts compared with closed-list PR (and vice-versa for small magnitude districts), showing that the results are highly non-monotone.
-Also, while \citet{charron2011party} shows that more competition increases corruption, specially in single-member district countries, \citet{schleiter2014party} and \citet{schleiter2016party} argue that party competition and party institutionalization increase the availability of credible alternatives against corrupt politicians, decreasing corruption.
-Moreover, \citet{tavits2007clarity, potter2011curbing} and \citet{schwindt2016corruption} show that clarity of responsibility is essential for corruption outcomes, as it limits the capacity for politicians to hide behind the political system, making them more accountable for bad outcomes.\footnote{For a summary of the clarity of responsibility and elections see \citet{silva2017clarity}.} Therefore, findings on the corruption-electoral systems literature are mostly contradictory, and this claims for a stronger theoretical foundation that conciliates differences in empirical models and their institutional and behavioral incentives.
+In this paper, I investigate the interplay between the number of incumbents in a polity, the number of competitors challenging those incumbents, and the incentives incumbents have for engaging in corruption.
+I propose a model where incumbents know the optimal level of investment required for public goods provision, but challengers only see the amount that incumbents spend.
+Incumbents have privileged information because they are inside the government, and receive information from governmental agencies.
+When they propose an investment higher than the optimal amount, the public goods is provided, and they pocket the difference between the optimal amount and their proposed expenditure.
+Thus, in this paper, the difference between the optimal and the proposed investment is the definition of political corruption.
 
-This paper provides a rigorous micro-foundation for one facet of the corruption-electoral system nexus.
-I build a model on corruption incentives considering the two main set of players in this strategic interaction: incumbents and challengers.
-Incumbents choose policy investments, with the possibility to add kickbacks to the optimal required values.
-Challengers observe the total investment and choose a proportion of their campaign to devote for exposing the incumbents' corruption.
-Solving the model presents the determinants for the corruption levels: the \textit{free-riding} incentives caused by the number of competitors, and the \textit{coordination failures} caused by the number of incumbents.
+Challengers have incomplete information about the required investment in public goods provision, but they may run a negative campaigning against incumbents.
+Challengers have a prior expectation regarding the optimal investments, and naturally, they know that the higher the level of investment proposed, the more the chances that incumbents are extracting rents.
+They decide to run a negative campaign that aims to gather and expose information supporting that a given incumbent is corrupt.
+To run a negative campaign is costly, both in terms of gathering information to prove that the incumbent is dishonest, and also in terms of XXXX.
+The extent through which the negative campaign is successful depends on the rents extracted by incumbents: While voters know that challengers may accuse an honest incumbent of corruption, the amount of evidence shown to voters can tilt the perception that a given incumbent is honest, triggering his or her dismissal.
 
-Polities with an open entry may attract many challengers, and even though challengers benefit from the use of negative campaign, they prefer to let the other challengers expose the corrupt politician: free-riders avoid the costs of exposing the corrupt politicians while benefiting from the increased winning chances.
-Additionally, polities with many incumbents, such as proportional representation systems, add coordination failures to the top of the free-riding incentives: when there are many challengers and incumbents, challengers may happen to expose the same politician, leaving other incumbents without proper denouncing.\footnote{Although a system that has many incumbents is not a perfect representation of PR systems, a perfect PR representation would make the model considerably harder to understand, without changing the qualitative characteristic of its results.
-Moreover, our approach is similar to \citet{Myerson1993}, with the key difference that we do not assume the existence of a behaviorally non-corrupt politician.
-In this sense, this is a moral hazard model, while Myerson's is an adverse selection model.} This possibility makes incumbents more prone to pocket even more money than when there is only free-riding caused by a large pool of challengers.
-In sum, these collective action problems determine the incentives that challengers have to expose incumbents, therefore impacting the incentives for corruption.
+To understand how electoral systems and competition affects corruption, I investigate how changes in the number of incumbents (district magnitude) and the number of challengers (competition) affect the equilibrium level of corruption.
+I show that increase district magnitude increases the equilibrium level of political corruption.
+This because more incumbents promote coordination failures in the challengers' negative campaigning.
+For example, in an electoral system with one incumbent, this incumbent is the sole target of negative campaigning.
+In a system with two incumbents, one incumbent may be targeted with all negative campaign while the other may remain un-targeted.
+These types of coordination shortcomings make the incumbents to propose higher expenditures, increasing corruption.
 
-The results here suggest that the least corrupt system is the single-member district with restrictions for contest office and the most corrupt system is proportional representation with weak parties and personalistic voting (open-lists).
-However, as changes in electoral systems reflect more profound trade-offs, sometimes polities may decide that multi-member districts trumps single-member districts, as their primary objective is to accommodate social cleavages or improve the representation of minorities.\footnote{See \citet{carey2011electoral} for a discussion about the possibility of an optimal trade-off between representation and accountability, where PR in small districts seem to be the best for maximizing representation without lowering accountability considerably.} The historical development of each polity determines these trade-offs and the relative importance of representation, accountability, corruption, and other related components.
-My argument in this paper is that if corruption is a problem that the polity wants to fight, and if politicians want to limit corruption by reforming the electoral system, then they should raise entry barriers and decrease district size.
-Additionally, I discuss many extensions that shed light on the micro-level electoral institutions affecting the collective action problems.
-Rules such as run-offs, proportional representation thresholds, or even laws that bar convicted politicians to contest offices are sometimes proposed as a method to lower corruption.
-Again, institutions that lower competition and district size decrease political corruption.
+The effects of competition are less clear, and depend on the how voters behave in face of a successful exposure of an incumbent.
+On the one hand, if voters transfer the political support from the corrupt incumbent to the challenger that ran the negative campaign, then political corruption decreases.
+This because the reward in denouncing a corrupt incumbent makes challengers more prone to run negative campaigns.
+With more negative campaigning in equilibrium, incumbents respond by proposing an expenditure closer to the optimal spending level.
+On the other hand, if voters, upon being convinced that the incumbent is corrupt, decide to randomly elect one challenger, then political corruption increases.
+This because randomly select the challenger that substitute the corrupt incumbent creates a free-riding incentive: every challenger prefers that other challengers pay the cost of negative campaign.
+The first mechanism we denote as XXXX while the second mechanism we denote as XXXX.
 
-The last session of the paper shows that our claims hold empirically, by exploiting two quasi-experimental shocks in district size and competition in Brazil.
-First, I show that run-off and candidacy impact on corruption.
-Second, I show that exogenous thresholds for legislature size influences candidacy and district size, impact on corruption.
-This paper builds upon \citet{ferraz2011electoral}, \citet{avis2016government}, and \citet{britto2016corruption} findings, providing a theoretical explanation for their results.
-These results provide a solid empirical test for my model, showing that the electoral rules and competitiveness consistently affect corruption levels, in one of the most corrupt democracies in the world.
+This model innovates in three fronts.
+First, it provides a consistent and comparable definition of corruption.
+Despite the evidence that corruption is detrimental for XXXX and XXXX, corruption is poorly defined.
+Corruption XXXX.
+Moreover, corruption XXXX.
 
-# Corruption, politics, and institutions
-\label{sec:theorytext}
+Second, our paper builds up on the previous literature on electoral systems and corruption by adding a role for the challengers. In most of the papers, XXXX. My paper innovates by XXXX.
 
-In modern societies, elections select representatives, that carry out the interests of voters \citep{pitkin1967concept, manin1997principles}.
-Representation creates a principal-agent problem as the elected have the latitude to implement or not the voters' preferences \citep{manin1999elections}.
-As there exist many methods and rules to elect politicians, these rules affect the extent through which politicians perceive themselves as accountable to voters in several forms \citep{LizzeriPersico2001, grofman2016perspectives}.
+Third, my model abstracts away from other political concerns, focusing only on features of the electoral system, in a stylized model.
+Recent papers show that corruption correlates with ideology \citep{XXXX}, in-group behavior \citep{XXXX}, and XXXX.
+Despite the importance of these XXXX, removing these considerations is fundamental for understanding how electoral rules affect corruption.
+For example, by having ideology and district size in the same model, we would be uncertain whether which component (or even if the interaction between them) leads to corruption.
+Moreover, high polarization correlates with less punishment of corruption \citep{XXXX}, but it is unrealistic to prescribe that voters should depolarize as a way to lower corruption.
+The relation between polarization, XXXX, and XXXX are features of the political system that need to be studied in and on themselves.
+The strength of my model is to abstract away from XXXX, and considering a lean model of XXXX.
 
-For instance, consider the differences in representation generated by multi-member and single-member districts.
-In single-member districts, only one representative gets elected, and she represents the district majority.
-In homogeneous districts, single-member districts with majoritarian rule capture the social and racial composition precisely.
-However, when there is considerable heterogeneity, such as social, racial, or religious cleavages, single-member districts may under-represent those cleavages.
-In these cases, multi-member districts are preferable concerning representation, as they tend to reflect the actual proportions of these cleavages more closely.
+Finally, XXXX
 
-However, electoral institutions embed more profound trade-offs in every dimension they affect \citep{grofman1986electoral, carey2011electoral, grofman2016perspectives}.
-Multi-member districts favor representation but also translate into a more significant number of parties, increasing the governing costs \citep{duverger1959political, fujiwara2011regression}.
-Single-member districts, on the other hand, tend to produce fewer represented parties, lowering the governing costs.
-
-One dimension affected by the electoral rules is the electoral campaigns.
-Every politician divides their campaign roughly in two basic strategies: positive campaign, where they present their political platform for voters; and negative campaign, where they campaign against their opponents, aiming to affect the voter's perceptions regarding other candidates \citep{harrington1996spatial, polborn2006informative, walter2014stakes}.
-Although voters and politicians may perceive positive campaign as less controversial, negative campaigns are also essential, primarily when they aim to expose a corrupt politician \citep{polborn2006informative, FerrazFinan2008, avis2016government}.
-In this sense, to understand how electoral systems affect corruption, we need to explore the effects of electoral rules on incentives for challengers to expose corrupt incumbents.
-
-Exposing corrupt politicians consumes campaign resources, and the aim is to change the voters' perspectives about another politician.
-However, the electoral rules affect the number of politicians, either incumbent or challengers, running in the election.
-In this sense, like any other situation where there are many politicians, collective action problems affect the willingness to campaign against a corrupt incumbent \citep{olson2009logic, ostrom2015governing}.
-These collective action problems will determine the incentives that challengers face when they are willing to expose corrupt incumbent(s).
-
-For the scope of this paper, two types of collective action problems matter when studying electoral rules: free-riding and coordination failures.
-First, electoral rules influence the incentives that candidates have to free ride on others candidates' negative campaigns.
-The free-riding here entails a situation where a candidate does not pay the costs of negative campaigning but benefit from the negative campaigning undertaken by the other candidates.
-
-Second, electoral institutions may cause coordination failures, as candidates would be better-off exposing only one incumbent at a time, but as they cannot perfectly coordinate, they end up targeting the same incumbent more than one time.
-If we consider that the likelihood of exposure has decreasing returns, meaning that the more negative campaigning politicians make, the lower the effects of additional negative campaigning, inefficient targeting lowers the effectiveness of corruption exposures.
-A summary of these two effects on different electoral rules follows in Table \ref{tabcor2x2}.
-
-\begin{table}[htp!]
-\centering
-\caption{Effects of Competition and District Size on Corruption}
-\label{tabcor2x2}
-\scalebox{1}{%
-\begin{tabular}{@{}lcc@{}}
-\toprule
-& \textbf{Single-Member} & \textbf{Multi-Member} \\ 
-& \textbf{Districts} & \textbf{Districts} \\ 
-\midrule
-\textbf{One Challenger} & Low Incentives & Moderate Incentives \\
-\textbf{Per Seat} & for Corruption & for Corruption \\
- & (No Free-Riding or Coord. Probl.) & (Coordination Problems) \\[0.5em]
-\textbf{Multiple Challengers} & Moderate Incentives & High Incentives \\ 
-\textbf{Per Seat} & for Corruption & for Corruption \\
- & (Free-Riding Problems) & (Free-Riding + Coord. Probl.) \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-Regarding corruption incentives, single-member districts with one challenger running are the least corrupt systems.
-The reason here is that any negative campaign that harms the incumbent also increases the challenger's electoral perspective.
-In this sense, no free-riding or coordination failures happen, and the incentives to expose corrupt politicians are at the maximum.
-This explains why majoritarian systems with run-off are effective in lowering corruption: the run-off makes the election to polarize, eliminating the free-riding and coordination failures \citep{ferraz2011electoral}.
-
-Adding more challengers create a free-riding problem, as challengers may benefit when other fellow challengers investigate the incumbent.
-This result points to the direction that more competition increases corruption, agreeing with the majority of the empirical findings \citep{Charron2011}.\footnote{A few papers, such as \citet{Persson2003}, argue that competition is positive, as it presents lower entry barriers, and therefore, credible alternatives against corrupt politicians.
-Despite their findings, most of the literature shows a negative influence of competition.
-However, at the party level, competition seems to provide positive results \citep{schleiter2014party}.}
-
-Adding more seats and more challengers further reduce the incentives to expose corrupt politicians, and the reason is twofold.
-First, adding more seats create free-riding incentives, as it increases the absolute number of competitors, even when the ratio of competitors-per-seat is kept constant.
-Second, adding more seats increase the likelihood of coordination failure, as the same incumbent may be exposed more than once while others may be not exposed at all.
-These two effects lower the incentives for exposing corrupt politicians, and they reasonably explain why countries with open-list proportional representation systems are endemic corrupt \citep{Myerson1993, ames1995electoral}.
-
-However, the cases reported above may be considered \textit{pure forms}, that vary with the particular characteristics of each system.
-Consider, for instance, three variants of these simple electoral rules.
-First, consider that party lists may be open or closed, and this affects the strength of a party.
-Closed lists empower party leaders, and may have a positive effect on coordination, lowering corruption.
-\citet{chang2007electoral} find that there exists a threshold where closed-list proportional representation systems become less corrupt than open-list proportional representation systems.
-\citet{schleiter2016party}, along with similar lines, argue that stronger parties are better to decrease political corruption.
-
-This list can be extended, as there are many types of political rules.
-Ultimately, they will be closer to one of the forms in Table \ref{tabcor2x2}.
-The main conclusion is that larger the number of incumbents or number of challengers, the more the collective action problem in the exposure of corrupt politicians.\footnote{Moreover, the mechanism in play may not be the same as the exposed here, and the diminished incidence of corruption could be caused not because challengers investigate more, but because of some other feature.
-Here in this paper, I abstract from these other possibilities in order to explore the role of challengers in the diverse electoral systems.}
-
-# Formal Model
-\label{sec:theorymodel}
-
-Let a strategic interaction between three players: an incumbent politician ($I$), a challenger politician ($C$), and a representative voter ($V$).
-
-The incumbent $I$ has a fixed budget of $A$ units, to invest in service provision.
-The level of expenditure required to provide the public goods is a random variable $\eta \in [0, A]$, where $f(\eta)$ an increasing probability density function.
-The randomness reflects the idea that changes in real-world conditions influence the amount needed for service provision.
-The incumbent knows the optimal investment level, making it her private information.
-If incumbents were honest, they would invest the needed amount to provide the services ($\eta$), but in this model, the incumbent invests the optimal amount plus some value, that she intends to pocket.
-The utility from pocketing money is described by $u(e_i-\eta)$, which $u$ is a strictly concave utility function, and $e_i$ represents the service expenditure by an incumbent $i$.\footnote{This assumption matches a frequent empirical regularity in the political environment, especially in new democracies: corruption tend to be over-investments, meaning that politicians add kickbacks and gifts to procurement contracts, receiving benefits them.
-Usually, what happens is not that voters fail to receive the services, it is that those services cost much more than their market value.
-For instance, \citet{Bandiera2009} estimated that the waste in procurement account for around 2\% of the Italian GDP.}
-
-After the service provision period, the electoral stage starts with the incumbent and the challenger campaigning.
-The challenger and the voters do not observe the optimal service investment level, but the challenger observes the amount of money invested by the incumbent politician ($e_i$, for all $i$).
-The challenger faces no entry costs and has the opportunity to use the negative campaign to convince the voters that the incumbent has embezzled public funds.\footnote{ This assumption is strong, as many papers demonstrated the effect of quality and service provision on the decision to challenge an incumbent \citep{Gordonetal2007, ashworth2008electoral, gordon2009voter, hall2015much}.
-In this paper, I endogenously fix the number of incumbents and challengers, as the critical point here is to study how the number of politicians influences incentives.
-In the Appendix, I extend the model to have a pool of possible challengers that have their entry costs a random variable.
-In the extension, the total pool of likely entrants becomes the critical variable, holding all qualitative findings here unchanged.
-Therefore, to fix the number of entrants is easier to understand, and represents a class of models that preserve the characteristics of our results, than we adopt this approach in the main text.
-Also, for the entry decision in economics, see \citet{Milgrom1982, Nti1989}.} If she decides to use all of her campaign resources to expose the corrupt politician, she pays a cost $c>0$.
-Her chances of success depend on the strength of the corruption evidence, plus other environmental facts, such as how much control over information incumbents have \citet{ferraz2011electoral, boas2011controlling}, credibility perceived by the voter \citep{polborn2006informative, AshworthShotts2011}, access to privileged information, and the challengers' competence to spread the information among voters.
-I assume that these factors are captured by a corruption detection technology, a function $\lambda(.)$ that is increasing on the amount embezzled by the incumbents.
-It increases with the amount embezzled, as the more money the incumbent pockets, the easier to convince voters that there is hard evidence of malfeasance undertaken by the incumbents.\footnote{There are two ways to interpret the hard evidence detection technology.
-First, it can be exposure of hard corruption evidence that was brought by a law enforcement agency, such as the FBI in the US or the General Comptroller Agency in Brazil.
-Second, it can be information uncovered during the campaign process by candidates or former allies that turned to the opposition.
-Either way, we consider that the process is noisy, but more substantial sums of money embezzled makes its detection easier.}
-
-Finally, as the voters' decisions are sequentially rational, upon observing hard corruption evidence, they punish the incumbent electing the challenger.
-Otherwise, the claim that the incumbent is corrupt is interpreted as a cheap talk by the voters.\footnote{Note that it is not ex-ante rational to always dismiss (never dismiss) the politicians, even when the voters know that politicians are corrupt.
-This because always dismissing (never dismissing) would generate equilibrium where politicians always spend the total amount of resources, regardless of how much is needed to provide the services.} Thus, the voter only punishes the incumbent when the challenger presents and convinces the voters that there is hard evidence of malfeasance.
-The game then ends, and payoffs are realized.
-The timeline for this model is as follows:
-
-\begin{enumerate}
- \item Nature draws the optimal investment level to provide the public services.
- \item The incumbent observes the optimal investment level and choose the expenditure.
- \item The election starts with the challenger choosing her campaign strategy.
- \item Voters observe the campaign and choose whether to retain or dismiss the incumbent.
-\end{enumerate}
-
-The strategic decisions in this game are the expenditure level chosen by the incumbent ($\varepsilon$), the fraction of time that the challenger invests in exposing the corrupt incumbent ($\varphi$), and the voter's decision to retain or dismiss the incumbent.
-Condensing the discussion above, we have the following expected utility functions.
-For the incumbents:
-
-\[
-U_i (\varepsilon_i; \ \eta, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) \ = \ u(\varepsilon_i - \eta) + B \ \Prob (\upsilon_i = 1 \ | \ \psi, \dd) 
-\]
-
-Where $B$ is the reward for staying in office (assumed the same for every player) and $\Prob (\upsilon_i = 1 \ | \ \psi, \dd)$ is the probability of being retained, given $\psi$ and the exposure profile $\dd$.
-For a challenger $j$:
-
-\[
-U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}) \ = \ B \int_{0}^A \Prob (\upsilon_j = 1 \ | \ \eta, \bveps^{*}, \bvphi^{*})\mu(\eta|\bveps^{*}) d\mu(\eta) - c \sum_{i=1}^K \varphi_{ij}(\psi, \bveps^{*})
-\]
-
-With $c > 0$ being the cost of performing one full corruption exposure.
-Notice that the total amount spent on exposing corrupt politicians will be the sum of the amounts spent on each exposure.
-The representative voter's expected utility is equal to:
-
-\[
-U_V (\psi, \dd, \bups) \ = \ \indf \{\psi=G \}r_G
-\]
-
-Where $\indf$ is the indicator function for $\psi=G$ and $r_G$ the value of the public good for the voter.
-Notice that no $\psi=B$ is observed on the equilibrium path, as under-spending is a dominated strategy.
-
-Any retention rule selected for the voters is sequentially rational because there is no uncertainty about the results when they cast their votes.
-I impose the retention rule for the voter to be to dismiss all incumbents when $\psi=B$ or replace incumbents that were successfully exposed by challengers when $\psi=G$.
-This rule is ex-post efficient as over-dismissal would make incumbents pocket all the money regardless of $\eta$.
-
-I solve this game for a \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}, and as this is a signaling game, I also use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}.\footnote{The restriction imposed by the universal divinity requires that the challengers, facing a deviation from the equilibrium path, put probability one on the type that is more likely to deviate.
-Moreover, as we have a continuum of types, we use the approach by \citet{Malaith1987}, which consists in finding the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.}
-
-\begin{definition}
- \label{def_eqn}
- A Perfect Bayesian Equilibrium for the game described, with $|I|=K$ and $|C|=L$, $K$ and $L$ in $\mathbb{N}$, type space $T=[0,A]$, consists in optimal strategies $\bveps^{*}$, $\bvphi^{*}$, $\bups^{*}$ and beliefs $\mu^*$, that satisfy
- \begin{enumerate}
-  \item $\forall t_i \in T$, $\varepsilon^{*}_i(t_i)$ maximizes $ U_i (\varepsilon_i; \ t_i, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) $ $\forall i \in \{1, \cdots, K\}$.
-  \item $\forall \bveps \in \left[0,A \right]^K $ and $\psi \in \{B, \ G \}$, $\bvphi^{*}_j(\bveps, \psi)$ maximizes $ U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}, \ \mu^*) $, $\forall j \in \{1, \cdots, L\}$
-  \item $\forall \psi \in \{B, \ G \}$ and $\dd \in \{0,1\}^L$, $\bups^{*}(\psi, \dd)$ maximizes $ U_V (\psi, \dd, \bups^*) $.
-  \item The beliefs are derived using Bayes rule whenever possible, and for all $\varepsilon_i$ that are off-the-equilibrium path, $\mu^*(t_i| \varepsilon_i)>0$ (in fact, 1) only if $\widehat{\varepsilon}_i \in \arg \min_{t_i} p(t_i, \widehat{\varepsilon}_i)$, where $ p(t_i, \widehat{\varepsilon}_i)$ is the profit from deviating from $\varepsilon_i$ to $\tilde{\varepsilon}_i$ for a type $t_i$.
- \end{enumerate}
-\end{definition}
-
-Note four characteristics of the model proposed.
-First, the incumbent politicians always embezzle some amount in equilibrium.
-Second, conditional on the benefits from holding office, to spend less than the optimal investment is harmful to the incumbent.
-In concrete terms, this means that politicians' first aim is to be elected.
-If the voter always dismisses the politician, then the politician will always say that the good costs $A$.
-Third, the voters always receive the public goods, regardless of the amount of money embezzled.
-The voter decides to punish the corrupt incumbent to discipline the incumbent's behavior, minimizing the rents extracted.
-Finally, this model has no ideological proximity, or affinity between the voter and any of the politicians: the paper aims to explore the incentives for corruption, not the trade-offs between ideology and corruption.
-Ideology is vital to understand why voters may not want to punish a corrupt politician, but this is not the main point of this paper, and adding this to the paper only blurs the logic of the argument.
-I now solve the model for the scenarios relevant to this paper.
-
-\subsection{One incumbent and one challenger}
-
-Applying backward induction, the voters retain the incumbent if the policy result was good and no corruption was exposed.
-From the challenger's perspective, as there is no cost of entry, she decides whether to invest or not her campaign resources in exposing the incumbent.
-She does so when the expected utility of exposing is higher than or equal the expected utility of not exposing, given her beliefs about the real value of $\eta$.
-Thus:
-
-\[
-B \int_{t_i \in T} \Prob (\bups = (0,1)\ | \ \eta, \varepsilon^*, \varphi)\mu^*(t_i|\varepsilon^*) d\mu - c \varphi(\psi, \varepsilon^*) \geq 0
-\]
-
-Rearranging and applying the fact that $ \Prob(\bups = (0,1) | \varepsilon^*, \varphi ( \psi, \varepsilon^*), \eta) = \varphi(\psi, \varepsilon^*) \lambda(\varepsilon^*-\eta) $ and $\mu^*(t_i | \varepsilon^*) = \mu(\eta) = \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta}$ yields to:
-
-\[
-B \varphi(\psi, \varepsilon^*) \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta - c \varphi(\psi, \varepsilon^*)
-\]
-
-Isolating $\varphi(\psi, \varepsilon^*)$, let $\lambda_\varepsilon = \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta$ and $Q(B, c) = \dfrac{c}{B}$.
-Sequential rationality implies three distinct decisions: first, the challenger exposes the corrupt incumbent for sure whenever $\lambda_\varepsilon > Q(B, c)$; second, the challenger never exposes the corrupt incumbent when $ \lambda_\varepsilon < Q(B, c)$; and finally, the challenger is indifferent between exposing or not the corrupt incumbent when $\lambda_\varepsilon = Q(B, c)$.
-Optimality suggests that incumbent politicians will calibrate their rent extraction in order to make challengers indifferent between investigating or not.\footnote{To avoid a trivial equilibrium we assume that $Q < \dfrac{\int_0^A \lambda(A - \eta)f(\eta) d\eta}{\int_0^Af(\eta)d\eta} = Q^*$.
-If $Q \geq Q^*$, then the only equilibrium is to play $A$ regardless of $\eta$, and there will be no exposures.}
-
-In this situation, there exists $\overline{\eta}$ such that:
-
-\[
-\lambda_A = \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta)f(\eta) d\eta}{\int_{\overline{\eta}}^Af(\eta)d\eta} = Q(B, c)
-\]
-
-This equation represents the upper limit in the incumbent politician's strategy when the randomly drawn optimal expenditure is too close to the maximum expenditure.
-In these situations is more profitable for them to play $A$.
-We say that the threshold for this case is $\overline{\eta}$.
-
-Now, let $\delta(\varepsilon)$ the probability function that characterizes the amount of negative campaign chosen by the challenger when $\varepsilon \in [ 0, \ \overline{\eta}]$.
-The optimal $\varepsilon$ solves the equation $\lambda_\varepsilon = Q(B, c)$, making the challenger indifferent between exposing or not the incumbent's corruption.
-As $\lambda(.)$ has an inverse function, the optimal strategy for the incumbent is:
-
-\begin{equation*}
-\varepsilon^*(\eta) \ = \ \eta + \lambda^{-1}\left(\dfrac{c}{B}\right)
-\end{equation*}
-
-Therefore, the optimal strategy for the incumbent politician is to add a kickback $\kappa$ to the cost for providing the public good.
-The incumbent devises the optimal kickback to make the challenger indifferent between expose or not the corrupt incumbent.
-The optimal kickback is increasing in the cost of the negative campaign and decreasing in the benefit of holding office.
-
-The incumbent, on the other hand, only plays this strategy when it is incentive compatible for her.
-To be an optimal response, it should be a $\arg \max$ for $U_I$.
-Taking the derivative of $U_I$, and setting it to zero gives us the following differential equation for $\delta(\varepsilon)$:
-
-\[
-\dfrac{d \delta}{d \varepsilon} + \delta(\varepsilon)\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)} = \frac{1}{B}\frac{u^{'}(\kappa)}{\lambda(\kappa)}
-\]
-
-Under the boundary condition $\delta(\kappa)=0$.
-The equation is a well defined first order differential equation that has a straightforward unique solution determined by the boundary condition.
-Solving for $\delta(\varepsilon)$, we have:
-
-\[
-\delta(\varepsilon) = \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right)
-\]
-
-Combining all these results together gives us the following lemma:
-
-\begin{lemma}
- \label{lemma_m1}
- A Perfect Bayesian Equilibrium for the game when there is one incumbent and one challenger is a pair of strategies and beliefs such that the optimal strategies are
- \begin{enumerate}
-  \item For the incumbent 
-  \[
-   \varepsilon^{*}(\eta) \quad = \quad \twopd{\eta + \kappa}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
-  \]
-  \item For the challenger
-  \[
-   \varphi^*(\varepsilon) \quad = \quad \threepdo{0}{\varepsilon < \kappa}{\delta(\varepsilon)}{\kappa \leq \varepsilon \leq \overline{\eta}}{\delta(A)}
-  \]
- \item And the voter replaces the incumbent if there is evidence of corruption.
- \end{enumerate}
- Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
- \[
- \kappa = \lambda^{-1}\left(\dfrac{c}{B}\right)
- \]
- The upper threshold, $\overline{\eta}$, satisfies 
- \[
- \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta) f(\eta) d\eta}{\int_{\overline{\eta}}^A f(\eta)d\eta} - \dfrac{c}{B} = 0
- \]
- \[
- \delta(\varepsilon) \ = \ \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right) 
- \]
- And the beliefs are updated using Bayes rule whenever possible.
-\end{lemma}
-
-The remainder of the proof and the demonstration that this strategy is indeed an equilibrium is in the Appendix.
-Note three critical features on this equilibrium.
-First, an increase in the value of office ($B$) decreases the kickbacks extracted and the amount of negative campaign.
-Decreases kickbacks because it becomes more profitable to be reelected vis-a-vis extract rents, and lowers the amount of negative campaign because there are fewer opportunities to detect corrupt behavior.
-Second, increasing the costs of exposing corruption ($c$) increases the kickbacks and decreases the amount of exposure in equilibrium.
-Finally, increasing the gains from extracting rents (increasing $u'$) does not change the amount of extraction, but increases the amount of negative campaign, as a form to cope with the possibility of deviating from the equilibrium.
-These results are intuitive but demonstrate that the model follows a reasonable logic.
-
-\subsection{One incumbent and many challengers}
-
-Let $|I|=1$ and $|C|=L$.
-Starting with the voters, their optimal strategy is to retain the incumbent if the incumbent provides the public good and no corruption has been uncovered.
-If the voters dismiss the incumbent, they randomly select a challenger with equal probability.\footnote{One might think that an optimal scheme would be to reward the challengers that uncovered the corruption scandal.
-The problem with this consideration is twofold: first, once the corruption has been detected, all challengers could use these facts in their campaigns, making the corruption exposure a ``non-excludable good.'' Second, even if we consider that challengers inherit the votes from the exposed incumbent, the collective action remains, as every challenger will have incentives for negative campaign, but if all do, the voter will keep choosing by chance.
-The equilibrium changes slightly but qualitatively, it is still worse than just one challenger.}
-
-Challengers observe $\psi$ and $\varepsilon$ and have to simultaneously compute the time to invest in negative campaign $\varphi_i$.
-As challengers have the same utility function, we solve for a symmetric equilibrium.
-Let $\lambda(\varepsilon-\eta) = \lambda_\varepsilon$.
-If we have $k$ players investing in a negative campaign against the incumbent politician, the probability that the incumbent gets successfully exposed and lose the election is:
-
-\[
-f(\varphi, x) = \sum_{k=0}^{L-1} {L \choose k} \varphi^k (1-\varphi)^{L-1-k} \cdot (1 - (1-\lambda_\varepsilon)^{k+x})
-\]
-
-So when $i$ decides to commit all her resources in a negative campaign, we let $x=1$ in $f$. This strategy allows us to compute the expected utility for the challenger $i$ as:
-
-\[
-\frac{B}{L}\int_0^A f(\varphi, 0) \mu(\eta|\varepsilon) d\mu + \varphi_i  \left[\frac{B}{L} \int_0^A \left( f(\varphi, 1)-f(\varphi, 0) \right) \mu(\eta|\varepsilon) d\mu - c \right]
-\]
-
-Sequential rationality requires that $\varphi_i > 0$ when this quantity is greater than zero, and zero otherwise.
-After some algebra, we can rewrite the critical term in the decision process as an equation $G$:
-
-\[
-G(\lambda, \varphi; L) = (1-\varphi\lambda_\varepsilon)^{L-1}\lambda_\varepsilon - Q(B, c) L
-\]
-
-Where $Q$ is defined as in the previous section: $Q(B,c) = \dfrac{c}{B}$.
-This equation yields to the optimal $\varepsilon$.
-The problem is that we will have, for each value of $\varepsilon$, a corresponding optimal value of $\varphi$, and vice-versa.
-As the incumbent plays first, she can choose the max-min value for $\lambda$, which is the maximum value for $\varepsilon$ that still delivers the lowest $\varphi$ possible.
-For a numerical example, if we assume $Q=0.15$ and $L$ ranging from $1$ to $5$, we can have a contour for the possible values for $\lambda$ in Figure \ref{fig_m2_1}.
-
-\begin{figure}[htb!]
- \centering 
- \includegraphics{figm21.pdf}
- \caption{Contour plot for $G=0$ when $Q=0.15$ and $L$ ranges from $1$ to $5$}
- \label{fig_m2_1}
-\end{figure}
-
-Making $G=0$ yields to the following optimal incumbent expenditure strategy:
-
-\[
-\varepsilon^*(\eta) = \eta + \lambda^{-1}\left( Q(B, c)\cdot L \right) = \eta + \kappa(L)
-\]
-
-Again, the actual value required to provide the service plus a kickback comprises the incumbent strategy.
-The kickback has the same characteristics expressed in the case with one challenger, except now it is augmented linearly by the number of challengers contesting the seat.
-In order to this expenditure profile be incentive compatible it has to satisfy the following differential equation in $\delta(\varepsilon)$:
-
-\[
-\delta^{'}(\varepsilon)-\delta(\varepsilon)\dfrac{\lambda^{'}(\kappa(L))}{\lambda(\kappa(L))} \ = \ \dfrac{u^{'}(\kappa(L))}{BQ(B, c)L^2}
-\]
-
-With the boundary condition $\delta(\kappa(L))=0$, we have the following optimal exposure strategy:
-\[
-\delta(\varepsilon) \ = \ \dfrac{u^{'}(\kappa(L))}{BQ(B, c)L^2} \left( 1- e^{\frac{\lambda^{'}(\kappa(L))}{\lambda(\kappa(L))}(\kappa(L)-\varepsilon)}\right)
-\]
-
-Collecting all the results leads us to the following Lemma.
-
-\begin{lemma}
- \label{lemma_m2}
- A Perfect Bayesian Equilibrium for the game when there is one incumbent and $L$ challengers is a pair of strategies and beliefs such that
- \begin{enumerate}
-  \item For the incumbent
-  \[
-  \varepsilon^{*}(\eta) \quad = \quad \twopd{\eta + \kappa (L)}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
-  \]
-  \item For each of the challengers
-  \[
-  \varphi^*(\varepsilon) \quad = \quad \threepdo{0}{\varepsilon < \kappa(L)}{\delta(\varepsilon)}{\varepsilon \in [\underline{\eta}, \ \overline{\eta}]}{\delta(A)}
-  \]
-  \item And the voter dismiss the incumbent if there is evidence of corruption, electing one of the $L$ challengers with probability $1/L$.
- \end{enumerate}
- Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
- \[
- \kappa(L) = \lambda^{-1}\left(L\dfrac{c}{B}\right)
- \]
- And the $\delta(.)$ defined as in the Appendix.
-\end{lemma}
-
-The proof with the step-by-step derivations is in the Appendix.
-Note here that all the comparative statics with relation to the benefit from holding office, the costs of exposing corrupt politicians, and the utility of rent extractions remain unchanged.
-The fundamental differences here are the effect of the number of challengers: it increases the kickbacks while decreasing the incentives for investigating the corrupt incumbent.
-The reason is intuitive: the more challenger added, the more the collective action problem faced by the challengers.
-For every individual challenger, it is better to let someone else pay the cost of a negative campaign but if all challengers reason similarly no exposures are performed in equilibrium.
-Thus, adding challengers increase the incentives for corruption.
-
-\subsection{Many incumbents and challengers}
-
-In multi-member districts there are more than one incumbent.
-All proportional representation countries, and most non-Westminster democracies use some variety of multi-member districts to elect representatives to their parliaments.\footnote{Proportional representation systems elect many representatives within a district, but also use apportionment rules to ensure proportional distribution of votes to parties.
-With the only difference that the apportionment rules may generate a few differences in the translation between votes and seats, in general, our representation encompasses the main features in a PR systems.} The following Lemma summarizes the case when there are many incumbents and many challengers.
-
-\begin{lemma}
- \label{lemma_m3}
- A Perfect Bayesian Equilibrium for the game when there are $K$ incumbents and $L$ challengers is a pair of strategies and beliefs such that
- \begin{enumerate}
-  \item For the Incumbent
-  \[
-  \varepsilon^{*}(\eta) \ = \ \twopd{\eta + \kappa(L+K)}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
-  \]
-  \item For the Challenger
-  \[
-  \varphi^*(\varepsilon) \ = \ \threepdo{0}{\varepsilon < \kappa(L+K)}{\delta(\varepsilon)}{\varepsilon \in [\kappa(L+K), \overline{\eta}]}{\delta(A)}
-  \]
-  \item The voters dismiss the corrupt incumbents, choosing randomly the substitutes among the $L$ challengers.
- \end{enumerate}
- Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
- \[
- \kappa(L+K) = \lambda^{-1}\left((L+K)\dfrac{c}{B}\right)
- \]
- And the $\delta(.)$ defined as in the Appendix.
-\end{lemma}
-
-The full derivation resembles the case with many challengers, and we leave for the Appendix.
-Qualitatively, the addition of more incumbents aggravate the collective action problems in two aspects.
-First, we have the free-riding problem, as politicians prefer to leave others to pay the exposing costs.
-Second, the absence of coordination among rival politicians increases the chances that challengers target some incumbents more than others.
-
-\subsection{Summarizing the effects of the number of incumbents and challengers}
-
-The following corollary summarizes the effects found above:
-
-\begin{corollary}
-Let the strategic interaction as summarized in the previous Lemmas.
-Then, increasing the number of challengers increases the incentives for corruption, as it promotes free-riding in the corruption exposures by challengers.
-Increasing the number of incumbents increases even further the incentives for corruption by promoting free-riding and coordination failures in the corruption exposures.
-\end{corollary}
-
-In equilibrium, the situation that induces the major incentive to embezzle is when we add challengers and incumbents simultaneously.
-Lowering the amount of either one of them, we also decrease the incentives for corruption, as denouncing the wrongdoing by incumbents become more profitable for challengers.
-
-To summarize the discussion in the previous Lemmas, we have the following testable hypothesis:
-
-\begin{enumerate}
- \item[H. 1] Increasing the number of seats, keeping all other characteristics constant, increase corruption.
- \item[H. 2] Increasing the number of competitors, keeping all other characteristics constant, increase corruption.
-\end{enumerate}
-
-These hypothesis can be rephrased in terms of the incentives they produce for challengers to use corruption information against incumbents.
-However, phrased in terms of corruption incentives they have the advantage to lead to testable implications.
-
-# Corruption and XXXX: Evidence from Brazilian and Italian Municipalities
-\label{sec:results}
-
-Empirical evidence shows that electoral rules affect corruption.
-However, papers present often-contradictory evidence, due to the difficulty of isolating the causes of corruption using observational data.
-To remedy this gap, I study two quasi-natural experiments in the Brazilian context: the exogenous population thresholds for the legislature size and competition \citep{cepaluni2015politicians, britto2016corruption} and population threshold for run-off \citep{ferraz2011electoral, fujiwara2011regression}.\footnote{Some of these results were found originally by \citet{ferraz2011electoral} for runoff, and by \citet{britto2016corruption} for legislature size.
-I replicate their findings, mainly confirming their original assessment, and providing microfoundations for their results.} The results confirm that competitiveness and district sizes are key for corruption.
-
-\subsection{Data, Sources of Variation, and Identification Strategy}
-
-To construct the dependent variable, I use two different codings for the Brazilian Municipal Audit program.
-This program was launched in 2003 by the Brazilian Federal government, and since 2004 it consists of a federal audit of a random lottery of 60 municipalities.
-Federal auditors go to each selected town collecting evidence of inefficiencies and corruption with the use of federal transfers.
-\citet{brollo2013political} and \citet{avelino2016replication} coded these lotteries, each with a different focus.
-\citet{brollo2013political} coded the lotteries 2 to 29, looking for \textit{broad} irregularities (incompetence) and \textit{narrow} irregularities (corruption).
-\citet{avelino2016replication} coded the lotteries 8 to 33, with the focus on health care transfers, coding the \textit{frequency} of detected malfeasance events, and the \textit{amount} involved.
-
-I use two population thresholds as an exogenous variation for competition, legislature size (city council district size), and competition in single-member district elections (mayoral elections).
-First, in 2004, the Brazilian Electoral Court ruled that the 29th Federal Constitution article that assumes a range from 9 to 21 city councilors for municipalities with less than a million inhabitants be miss-interpreted by towns.
-The court suggested that each municipal council should start with nine councilors, adding one councilor for every 47,619 inhabitants, which is the ratio of a million divided by 21 councilors.
-The electoral justice enforced the population thresholds for the council during two terms: 2004 and 2008.
-In 2009, the Congress amended the constitution, changing the council sizes and other council characteristics \citep{cepaluni2015politicians, britto2016corruption}.
-We use these thresholds as a shock on district size, and also on the competition.
-This because district size varies sharply with legislature size, pushing competition to also increase with these threshold variations.
-Second, the Brazilian electoral law mandates that municipalities with more than 200 thousand inhabitants should have a run-off for their mayoral elections \citep{fujiwara2011regression}.
-This emulates a single-member district with one competitor dispute (run-off), versus a single-member district with more than one competitor (no run-off).
-Figure \ref{empstrat} illustrates the empirical strategy.
-
-\begin{figure}[htp!]
-    \centering
-    \begin{tikzpicture}
-      \node[block] (a) {Run-off\\ threshold};
-      \node[block, below =2cm of a] (b) {Council size\\ thresholds};
-      \node[block, right =2cm of a] (c) {Competition\\ mayors' offices};
-      \node[block, below =2cm of c] (d) {Competition\\ city councils};
-      \node[block, below =2cm of d] (e) {City council \\ sizes};
-      \node[block, right =2cm of d] (f) {Corruption\\ measurements};
-
-      \draw[line] (a.east) -- (c.west);
-      \draw[line] (b.east) -- (d.west);
-      \draw[line] (b.south) |- (e.west);
-
-      \draw[line] (c.east) -| (f.north);
-      \draw[line] (d.east) -- (f.west);
-      \draw[line] (e.east) -| (f.south);
-
-      \node[container, fit=(a) (b)] (es) {};
-      \node at (es.north west) [above right,node distance=0 and 0] {Exogenous Shocks};
-
-      \node[container, fit=(c) (d)] (trc) {};
-      \node at (trc.north west) [above right,node distance=0 and 0] {Competitiveness};
-
-      \node[container, fit=(e)] (trd) {};
-      \node at (trd.north west) [above right,node distance=0 and 0] {District Size};
-    \end{tikzpicture}
-    \caption{Empirical strategy}
-    \label{empstrat}
-\end{figure}
-
-The model starts with the institution design to measure the corruption impacts, but the empirical strategy abstracts away from the precise formulation in order to estimate the model.
-There are two key changed features.
-First, it assumes that competition relates to district size.
-Second, it abstracts the role of challengers, assuming that it is working on the background as postulated by the formal model.
-For the first caveat, I also run robustness checks, splitting the sample into above and below the median competition per seat, and the results remain as postulated (above the median the coefficient is more significant).
-For the second point, I show in the appendix qualitative evidence that negative campaign and corruption claims, especially aimed against mayors, are considerably larger in run-off municipalities, compared with municipalities closer to the run-off thresholds.
-
-\subsection{Results}
-
-On the top of Figure \ref{figregcoef} I apply the empirical strategy for \citet{brollo2013political} \textit{broad} and \textit{narrow} irregularities detection, and below I estimate the same models for \citet{avelino2016replication} data on incidence and amount of discovered malfeasance on health care transfers.
-To keep our approach consistent, I limit the data to the 2005-2008 mayoral term.
-The results follow below.
-
-\begin{figure}[!htb]
- \centering 
- \includegraphics[width=1\textwidth]{graphCoefs.pdf}
- \caption{Regression coefficients for interplay between electoral systems, competition, and corruption}
- \label{figregcoef}
-\end{figure}
-
-I divide the results into four quadrants, plotting the coefficients for each model I run, based on the strategy presented in Figure \ref{empstrat}.\footnote{ I run an instrumental variable regression using the legislator threshold cutoffs as an exogenous shock for candidacy, regression discontinuity design for city council size, and t-test, selecting the municipalities close to the run-off cutoff, for a run-off.
-The reason for not running an RDD for the run-off is the fact that there were too few cases in the right-hand size (municipalities with more than 200 thousand voters).
-To emulate an RDD result I restrict the sample to the municipalities with 50 thousand voters around the 200 thousand run-off threshold.} In the top-left, the broad corruption findings represent inefficiency detection.
-As the model has no prior hypothesis on inefficiency, I keep it here as a placebo check, in order to study a possible oversensitivity of the empirical model.
-As the Figure shows, no coefficient is significant for inefficiency detection.
-
-In the top-right I present the results for \citet{brollo2013political} narrow corruption charges.
-These estimates work as expected: more competition and larger district sizes increase the chance of detect corruption 24\% and 56\%, respectively.
-Run-off decreases the amount of corruption 67\%.
-
-In the bottom-left we examine the \citet{avelino2016replication} frequency of detected corruption in health care.\footnote{ Health care is a good outcome of studying corruption incidence because it consumes a considerable portion of the municipal budget (around 25\%), and most voters in Brazil reward handsomely a good public healthcare administration \citep{fujiwara2015voting}.} As we can see, one standard deviation increase in candidates running for mayor and council increase in 20\% and 12\% the frequency of detected malfeasance, respectively.\footnote{ One standard deviation for the competition variables is 1.04 and 4.6 competitors for mayor and city council, respectively.
-See the Appendix for the full list of descriptive statistics.} The other coefficients are in the predicted direction, but not significant at 10 or 5\% levels.
-
-Finally, in the bottom right we have the fraction of healthcare investments where the auditors detected incidences of corruption.
-Consistent with the model predictions, adding one standard deviation of mayoral and city council competitors increase the investments with corruption irregularities by 15\% and 9\%, respectively.
-Having run-off decreases the investments with corruption by 47\%.
-The city council size coefficient is in the predicted direction, but not significant at the conventional levels.
-
-In sum, the empirical results largely confirm the hypotheses \textbf{H1} and \textbf{H2} derived from the formal model.
-In the appendix we run a few robustness and placebo checks, to test whether the findings here are resistant to small specification changes.
-All results remain consistent and significant in the majority of the different specifications.
-
-# Discussion
-\label{sec:discussion}
-
-This paper lays out the micro-foundations for the relation between corruption and electoral rules.
-It shows that challengers and incumbents have different incentives to investigate or engage in corruption activity in equilibrium.
-It also tests the theory using quasi-experimental variation, showing that the incentives generated by the institutions key for political corruption.
-
-Electoral systems are embedded into an array of trade-offs, and also generate many other political and representational effects within the society.
-Majoritarian systems are great for accountability, as they foster clarity of responsibility \citep{tavits2007clarity, xezonakis2015can}, and as this paper shows, they also promote lower levels of corruption.
-However, they also tend to be highly polarizing and have a considerable amount of wasted votes, which grow steadily with the number of candidates credibly competing for the seat.
-On the other extreme, proportional representation systems ensure less wasted votes, but parties proliferate on it.
-It quickly becomes ungovernable without broad coalitions and inter-party agreements, which are usually rigged by corruption in developing economies.
-
-To some extent, this paper delivers a very synthetic result: the incentives for engagement and for exposing corrupt behavior are dependent on the collective action problems generated within the political system.
-The results favor single-member districts with just one competitor when it comes to corruption.
-However, in between the extremes of single-member districts and full open-list proportional representation, some institutions work positively in fighting corruption.
-
-First, the existence of run-offs, such as in the French parliament, improves corruption outcomes without artificially limit the number of competitors.
-The run-off compensates the predatory competition that happens in the first round, and politicians may work to expose corruption by incumbents, lowering the incentives to corrupt behavior.
-
-Second, threshold laws, which are harmful to the inclusion of different cleavages, may help to avoid predatory competition, decreasing corruption.
-Third, the results here tend to favor findings such as \citet{schleiter2014party} and \citet{schleiter2016party}, which claim that strengthening parties in proportional representation systems decrease political corruption, suggesting that closed lists may be better for lowering corruption.
-In my model, the rationale is because strong parties may efficiently coordinate the corruption exposures, aiming at taking down not only a single politician but also an entire corrupt rival party.
-Stronger parties improve coordination and lower free-riding, especially when there are a limited number of parties.
-
-Finally, small district sizes in proportional representation, such as in the Chilean electoral system, maybe not only positive for the interplay between representation and accountability \citep{carey2011electoral}, but also in lowering corruption, when compared with large district proportional representation.
-The Brazilian system, with weak parties, open-list proportional representation, and large district sizes (varying between 8 and 70 legislators) proves that corruption can easily become endemic, with considerable negative impact on the quality of democracy and accountability \citep{avis2016government}.
+# District Magnitude, Competition, and Corruption
 

### 2021-08-26 article/article.Rmd
main paper editing model and intro

@@
 
-Corruption is one of the most prevalent and harmful diseases of developing countries.
-Corruption lowers public goods provision \citep{banerjee201227, beekman2014corruption}, decreases foreign investments \citep{habib2002corruption}, stunt economic growth \citep{mauro1995corruption, grundler2019corruption}, and affects human capital investments \citep{ferraz2012corrupting}.
-Corruption also have detrimental effects on trust \citep{you2018trust}, attitudes toward political parties \citep{winters2015political}, and fuels the distrust in the political system \citep{mignozzetti2019brazil}.
-The International Transparency estimates that corruption is responsible for $1.23 trillion US dollars every year, a sum that could lift 1.4 billion people out of the extreme poverty for consecutive six years \citep{fleming2019corruption}.
+Corruption is one of the most prevalent and harmful XXXX of developing countries.
+Corruption lowers public goods provision \citep{banerjee201227, beekman2014corruption}, decreases foreign investments \citep{habib2002corruption}, stunts economic growth \citep{mauro1995corruption, grundler2019corruption}, and affects human capital investments \citep{ferraz2012corrupting}.
+Corruption also has detrimental effects on interpersonal trust \citep{you2018trust}, attitudes toward political parties \citep{winters2015political}, and fuels the distrust in the political system \citep{mignozzetti2019brazil}.
+The International Transparency estimates that corruption is responsible for $1.23 trillion US dollars every year, a sum that could lift 1.4 billion people out of the extreme poverty for six consecutive years \citep{fleming2019corruption}.
 
-One crucial distinction in corruption activity is the actor that is perpetrating corruption.
+One distinctive characteristic of corruption activity is the actor perpetrating corruption.
 While bureaucratic corruption may be more frequent, it is also easier to sanction and to punish.
-Political corruption, on the other hand, involves higher rents than bribes to services.
-They are usually associated with large government contracts and procurement \citep{broms2019political}, have a more disruptive effects on the trust in political institutions \citep{sole2018trust}, divert the bureaucracy toward rent seeking \citep{brierley2020unprincipled}.
+Political corruption, on the other hand, involves higher rents than bribes to access public services.
+Political corruption is associated with XXXX large government contracts and procurement \citep{broms2019political}, have a more disruptive effects on trust in political institutions \citep{rose2001trust, sole2018trust}, and divert the bureaucracy toward rent seeking \citep{brierley2020unprincipled}.
 For instance, one of the major corruption scandals in the world, the Car Wash scandal in Brazil, involved more than 50 politicians, several high level bureaucrats, and about five billion US dollars in kickbacks \citep{watts2017operation}.
-Political corruption is intricate also because the electoral sanctioning often fails \citep{klavsnja2017uninformed, canete2020voting, janezic2020eliciting}.
-However, as elections are the primary mechanism to sanction corrupt politicians, are there electoral system features that could improve the sanctioning and lower corruption?
+Given the XXXX of political corruption, it is essential to create mechanisms to sanction corrupt politicians involved in wrongdoings.
 
-In this paper, I investigate the interplay between the number of incumbents in a polity, the number of competitors challenging those incumbents, and the incentives incumbents have for engaging in corruption.
+In democracies, elections are the primary mechanism to sanction politicians \citep{XXXX}.
+In most free and fair democracies, politicians can still manipulate XXXX, XXXX, and sometimes even the XXXX.
+This lowers the effectiveness of the XXXX.
+In this context, this paper XXXX.
+
+However, many XXXX makes voters XXXX \citep{klavsnja2017uninformed, canete2020voting, janezic2020eliciting}.
+, are there electoral system features that could improve the sanctioning and lower corruption?
+This paper studies the XXXX.
+
+I investigate the interplay between the number of incumbents in a polity (electoral district sizes), the number of competitors challenging those incumbents (competitiveness), and the incentives incumbents have for engaging in corruption.
 I propose a model where incumbents know the optimal level of investment required for public goods provision, but challengers only see the amount that incumbents spend.
@@
 
-Challengers have incomplete information about the required investment in public goods provision, but they may run a negative campaigning against incumbents.
-Challengers have a prior expectation regarding the optimal investments, and naturally, they know that the higher the level of investment proposed, the more the chances that incumbents are extracting rents.
-They decide to run a negative campaign that aims to gather and expose information supporting that a given incumbent is corrupt.
-To run a negative campaign is costly, both in terms of gathering information to prove that the incumbent is dishonest, and also in terms of XXXX.
+Challengers have incomplete information about the required investment in public goods provision, but they may decide to run a negative campaign against incumbents.
+Challengers have a prior expectation regarding the optimal investments, and they know that the higher the expenditure proposed, the more the chances that incumbents are extracting rents.
+They decide to run a negative campaign that aims to gather information supporting that a given incumbent is corrupt.
+To run a negative campaign is costly, both in terms of collecting information, and also in terms of opportunity costs of decreasing the focus on positive proposals \citep{haselmayer2019negative}.
 The extent through which the negative campaign is successful depends on the rents extracted by incumbents: While voters know that challengers may accuse an honest incumbent of corruption, the amount of evidence shown to voters can tilt the perception that a given incumbent is honest, triggering his or her dismissal.
 
-To understand how electoral systems and competition affects corruption, I investigate how changes in the number of incumbents (district magnitude) and the number of challengers (competition) affect the equilibrium level of corruption.
-I show that increase district magnitude increases the equilibrium level of political corruption.
+By manipulate the parameters in the model, I show that increase district magnitude increases the equilibrium level of political corruption.
 This because more incumbents promote coordination failures in the challengers' negative campaigning.
-For example, in an electoral system with one incumbent, this incumbent is the sole target of negative campaigning.
-In a system with two incumbents, one incumbent may be targeted with all negative campaign while the other may remain un-targeted.
-These types of coordination shortcomings make the incumbents to propose higher expenditures, increasing corruption.
+For example, in an electoral system with one incumbent, this incumbent is the sole target of all negative campaign.
+In a system with two incumbents, one incumbent may be targeted with all negative campaign while the other may receive no attacks.
+These coordination shortcomings make the incumbents to propose higher expenditures, increasing corruption.
 
-The effects of competition are less clear, and depend on the how voters behave in face of a successful exposure of an incumbent.
-On the one hand, if voters transfer the political support from the corrupt incumbent to the challenger that ran the negative campaign, then political corruption decreases.
+The effects of competition are less straightforward, and depend on how voters behave in face of a successful incumbent exposure.
+I investigate two behavioral mechanisms: \textit{Excludable} versus \textit{non-excludable} negative campaigning.
+In the \textit{excludable} negative campaign, if voters transfer the political support from the corrupt incumbent to the challenger that ran the negative campaign, then the political corruption decreases.
 This because the reward in denouncing a corrupt incumbent makes challengers more prone to run negative campaigns.
-With more negative campaigning in equilibrium, incumbents respond by proposing an expenditure closer to the optimal spending level.
-On the other hand, if voters, upon being convinced that the incumbent is corrupt, decide to randomly elect one challenger, then political corruption increases.
+More challengers mean more negative campaigning in equilibrium, and incumbents respond by proposing expenditures closer to the optimal spending level.
+On the other hand, in the \textit{non-excludable} negative campaign if voters, upon being convinced that the incumbent is corrupt, decide to randomly elect one challenger, then political corruption increases.
 This because randomly select the challenger that substitute the corrupt incumbent creates a free-riding incentive: every challenger prefers that other challengers pay the cost of negative campaign.
-The first mechanism we denote as XXXX while the second mechanism we denote as XXXX.
 
-This model innovates in three fronts.
+This model innovates in four aspects.
 First, it provides a consistent and comparable definition of corruption.
-Despite the evidence that corruption is detrimental for XXXX and XXXX, corruption is poorly defined.
-Corruption XXXX.
-Moreover, corruption XXXX.
+Despite the evidence that corruption is detrimental for countries, corruption is poorly defined.
+Studies have shown that there is wide variation, even within countries, in which acts are perceived as corruption \citep{peters1978political}.
+\citet{barr2010corruption} show that the propensity engage in corruption can be predicted by education and corruption in the country of origin.
+The variation is also pronounced in the willingness to punish corrupt behavior \citep{cameron2009propensities}.
+Despite the variability, reporting a higher than necessary cost of providing a public good seem to be overwhelmingly accepted as corruption \citep{peters1978political}.
 
-Second, our paper builds up on the previous literature on electoral systems and corruption by adding a role for the challengers. In most of the papers, XXXX. My paper innovates by XXXX.
+Second, this paper builds on the literature on electoral systems and corruption by proposing a simple model of the trade-offs involved in electoral rules choices. : Number of seats and entry barriers.
 
-Third, my model abstracts away from other political concerns, focusing only on features of the electoral system, in a stylized model.
-Recent papers show that corruption correlates with ideology \citep{XXXX}, in-group behavior \citep{XXXX}, and XXXX.
+Third, my model abstracts away from other political concerns, focusing only on features of the relationship between number of challengers and number of incumbents.
+Recent papers have shown that corruption correlates with ideology \citep{XXXX}, in-group behavior \citep{XXXX}, and XXXX.
 Despite the importance of these XXXX, removing these considerations is fundamental for understanding how electoral rules affect corruption.
-For example, by having ideology and district size in the same model, we would be uncertain whether which component (or even if the interaction between them) leads to corruption.
+For example, by having ideology and district size in the same model, we would be uncertain about which component (or even if the interaction between them) leads to corruption.
 Moreover, high polarization correlates with less punishment of corruption \citep{XXXX}, but it is unrealistic to prescribe that voters should depolarize as a way to lower corruption.
-The relation between polarization, XXXX, and XXXX are features of the political system that need to be studied in and on themselves.
-The strength of my model is to abstract away from XXXX, and considering a lean model of XXXX.
+The relation between polarization, ideology, and or in-group sentiments are features of the society that need to be studied in and on themselves.
+The strength of my model is to abstract away from these concerns, and constructing a lean model of XXXX.
 
-Finally, XXXX
+Finally, differences in the behavioral mechanism that voters use to reward challengers explain the empirical variations in corruption.
+In polities with widespread corruption, successfully exposing a corrupt politician have a small signaling effect \citep{pavao2018corruption}.
+This because the electorate considers the politician exposing the corrupt incumbent as as also corrupt.
+In these systems, increasing competition also increase the equilibrium corruption.
+Conversely, in countries with low corruption, voters may reward the politician exposing the corrupt incumbent.
+This creates an incentive for politicians to run negative campaigns, making incumbents to extract less rents in equilibrium.
 
-# District Magnitude, Competition, and Corruption
+# Electoral Rules and Corruption
+
+XXXX
+
+# Formal Model
+\label{sec:theorymodel}
+
+Consider a strategic interaction between three players: an incumbent politician ($I$), a challenger politician ($C$), and a representative voter ($V$).
+
+The game starts in the \textit{governing stage}, with the incumbent deciding the governmental investment in public goods provision.
+Incumbents have a budget $R$ units, and they choose the level of investment in public goods between zero and $R$.
+To decide about the investment, they receive privileged information from governmental agencies about the optimal investment required to maximize voters' welfare.
+For example, if a politician is deciding the funding for a governmental agency, the optimal budget is the amount that makes the agency to function perfectly.
+Less resources than needed could decrease significantly the quality of services but more resources than needed would not improve the services much.
+In technical terms, the optimal amount of service provision is a random variable $\theta \in [0, R]$, that is drawn before the game starts, and it is informed to the incumbent after she wins the election.
+I assume that the optimal level of expenditure is drawn from a uniform probability distribution, with support in $[0, R]$.\footnote{In the online companion of this paper, I solve the model for a generic probability density function $f$.}
+
+When deciding the expenditure, the incumbent can choose to invest more or less money then the optimal investment level.
+If the incumbent decide to invest less money, I assume that the goods are not provided.
+This simplification matches the reality in most cases, especially in developing economies, where restricting investments can cripple the entirety of the service provision.
+On the other hand, if the incumbent proposes an expenditure higher than the required investment, I assume that she pockets the difference between the proposed and the optimal expenditure.
+This has two implications: first, the public goods are always provided, satisfying the voters' needs; second, the incumbent has an excuse and a method to extract rents.
+Although corruption that ensures public goods provision seem counter-intuitive, the whole idea of kickbacks presumes that the expenditure is materialized.
+For instance, during the 2016 Brazilian World Cup, the stadiums constructed with public money were delivered, despite the fact that they costed 1.5 to 2.5 times more than comparable stadiums in less corrupt countries \citep{XXXX}.
+
+After the governing stage, it starts the \textit{campaign stage}.
+During the campaign, the incumbent faces a challenger in an election with two characteristics.
+First, I assume that voters have a incumbent-bias, so that voters prefer to reelect incumbents for sure when the public good were successfully provided.
+This XXXX.
+Second, challengers have only one campaign instrument at their disposal: to use negative campaign against the incumbent, expose their malfeasance (if present), and XXXX.
+
+Once in office, they learn the optimal public goods provision, but they have discretion to decide   is responsible for investing in public goods provision for the voters. For instance, XXXX.
+
+XXXX, and proposes a public goods provision XXXX.
+The incumbent has a fixed budget of $A$ units, to invest in service provision.
+The level of expenditure required to provide the public goods is a random variable $\eta \in [0, A]$, where  The randomness reflects the idea that changes in real-world conditions influence the amount needed for service provision.
+The incumbent knows the optimal investment level, making it her private information.
+If incumbents were honest, they would invest the needed amount to provide the services ($\eta$), but in this model, the incumbent invests the optimal amount plus some value, that she intends to pocket.
+The utility from pocketing money is described by $u(e_i-\eta)$, which $u$ is a strictly concave utility function, and $e_i$ represents the service expenditure by an incumbent $i$.\footnote{This assumption matches a frequent empirical regularity in the political environment, especially in new democracies: corruption tend to be over-investments, meaning that politicians add kickbacks and gifts to procurement contracts, receiving benefits them.
+Usually, what happens is not that voters fail to receive the services, it is that those services cost much more than their market value.
+For instance, \citet{Bandiera2009} estimated that the waste in procurement account for around 2\% of the Italian GDP.}
+
+After the service provision period, the electoral stage starts with the incumbent and the challenger campaigning.
+The challenger and the voters do not observe the optimal service investment level, but the challenger observes the amount of money invested by the incumbent politician ($e_i$, for all $i$).
+The challenger faces no entry costs and has the opportunity to use the negative campaign to convince the voters that the incumbent has embezzled public funds.\footnote{ This assumption is strong, as many papers demonstrated the effect of quality and service provision on the decision to challenge an incumbent \citep{Gordonetal2007, ashworth2008electoral, gordon2009voter, hall2015much}.
+In this paper, I endogenously fix the number of incumbents and challengers, as the critical point here is to study how the number of politicians influences incentives.
+In the Appendix, I extend the model to have a pool of possible challengers that have their entry costs a random variable.
+In the extension, the total pool of likely entrants becomes the critical variable, holding all qualitative findings here unchanged.
+Therefore, to fix the number of entrants is easier to understand, and represents a class of models that preserve the characteristics of our results, than we adopt this approach in the main text.
+Also, for the entry decision in economics, see \citet{Milgrom1982, Nti1989}.} If she decides to use all of her campaign resources to expose the corrupt politician, she pays a cost $c>0$.
+Her chances of success depend on the strength of the corruption evidence, plus other environmental facts, such as how much control over information incumbents have \citet{ferraz2011electoral, boas2011controlling}, credibility perceived by the voter \citep{polborn2006informative, AshworthShotts2011}, access to privileged information, and the challengers' competence to spread the information among voters.
+I assume that these factors are captured by a corruption detection technology, a function $\lambda(.)$ that is increasing on the amount embezzled by the incumbents.
+It increases with the amount embezzled, as the more money the incumbent pockets, the easier to convince voters that there is hard evidence of malfeasance undertaken by the incumbents.\footnote{There are two ways to interpret the hard evidence detection technology.
+First, it can be exposure of hard corruption evidence that was brought by a law enforcement agency, such as the FBI in the US or the General Comptroller Agency in Brazil.
+Second, it can be information uncovered during the campaign process by candidates or former allies that turned to the opposition.
+Either way, we consider that the process is noisy, but more substantial sums of money embezzled makes its detection easier.}
+
+Finally, as the voters' decisions are sequentially rational, upon observing hard corruption evidence, they punish the incumbent electing the challenger.
+Otherwise, the claim that the incumbent is corrupt is interpreted as a cheap talk by the voters.\footnote{Note that it is not ex-ante rational to always dismiss (never dismiss) the politicians, even when the voters know that politicians are corrupt.
+This because always dismissing (never dismissing) would generate equilibrium where politicians always spend the total amount of resources, regardless of how much is needed to provide the services.} Thus, the voter only punishes the incumbent when the challenger presents and convinces the voters that there is hard evidence of malfeasance.
+The game then ends, and payoffs are realized.
+The timeline for this model is as follows:
+
+\begin{enumerate}
+ \item Nature draws the optimal investment level to provide the public services.
+ \item The incumbent observes the optimal investment level and choose the expenditure.
+ \item The election starts with the challenger choosing her campaign strategy.
+ \item Voters observe the campaign and choose whether to retain or dismiss the incumbent.
+\end{enumerate}
+
+The strategic decisions in this game are the expenditure level chosen by the incumbent ($\varepsilon$), the fraction of time that the challenger invests in exposing the corrupt incumbent ($\varphi$), and the voter's decision to retain or dismiss the incumbent.
+Condensing the discussion above, we have the following expected utility functions.
+For the incumbents:
+
+\[
+U_i (\varepsilon_i; \ \eta, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) \ = \ u(\varepsilon_i - \eta) + B \ \Prob (\upsilon_i = 1 \ | \ \psi, \dd) 
+\]
+
+Where $B$ is the reward for staying in office (assumed the same for every player) and $\Prob (\upsilon_i = 1 \ | \ \psi, \dd)$ is the probability of being retained, given $\psi$ and the exposure profile $\dd$.
+For a challenger $j$:
+
+\[
+U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}) \ = \ B \int_{0}^A \Prob (\upsilon_j = 1 \ | \ \eta, \bveps^{*}, \bvphi^{*})\mu(\eta|\bveps^{*}) d\mu(\eta) - c \sum_{i=1}^K \varphi_{ij}(\psi, \bveps^{*})
+\]
+
+With $c > 0$ being the cost of performing one full corruption exposure.
+Notice that the total amount spent on exposing corrupt politicians will be the sum of the amounts spent on each exposure.
+The representative voter's expected utility is equal to:
+
+\[
+U_V (\psi, \dd, \bups) \ = \ \indf \{\psi=G \}r_G
+\]
+
+Where $\indf$ is the indicator function for $\psi=G$ and $r_G$ the value of the public good for the voter.
+Notice that no $\psi=B$ is observed on the equilibrium path, as under-spending is a dominated strategy.
+
+Any retention rule selected for the voters is sequentially rational because there is no uncertainty about the results when they cast their votes.
+I impose the retention rule for the voter to be to dismiss all incumbents when $\psi=B$ or replace incumbents that were successfully exposed by challengers when $\psi=G$.
+This rule is ex-post efficient as over-dismissal would make incumbents pocket all the money regardless of $\eta$.
+
+I solve this game for a \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}, and as this is a signaling game, I also use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}.\footnote{The restriction imposed by the universal divinity requires that the challengers, facing a deviation from the equilibrium path, put probability one on the type that is more likely to deviate.
+Moreover, as we have a continuum of types, we use the approach by \citet{Malaith1987}, which consists in finding the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.}
+
+\begin{definition}
+ \label{def_eqn}
+ A Perfect Bayesian Equilibrium for the game described, with $|I|=K$ and $|C|=L$, $K$ and $L$ in $\mathbb{N}$, type space $T=[0,A]$, consists in optimal strategies $\bveps^{*}$, $\bvphi^{*}$, $\bups^{*}$ and beliefs $\mu^*$, that satisfy
+ \begin{enumerate}
+  \item $\forall t_i \in T$, $\varepsilon^{*}_i(t_i)$ maximizes $ U_i (\varepsilon_i; \ t_i, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) $ $\forall i \in \{1, \cdots, K\}$.
+  \item $\forall \bveps \in \left[0,A \right]^K $ and $\psi \in \{B, \ G \}$, $\bvphi^{*}_j(\bveps, \psi)$ maximizes $ U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}, \ \mu^*) $, $\forall j \in \{1, \cdots, L\}$
+  \item $\forall \psi \in \{B, \ G \}$ and $\dd \in \{0,1\}^L$, $\bups^{*}(\psi, \dd)$ maximizes $ U_V (\psi, \dd, \bups^*) $.
+  \item The beliefs are derived using Bayes rule whenever possible, and for all $\varepsilon_i$ that are off-the-equilibrium path, $\mu^*(t_i| \varepsilon_i)>0$ (in fact, 1) only if $\widehat{\varepsilon}_i \in \arg \min_{t_i} p(t_i, \widehat{\varepsilon}_i)$, where $ p(t_i, \widehat{\varepsilon}_i)$ is the profit from deviating from $\varepsilon_i$ to $\tilde{\varepsilon}_i$ for a type $t_i$.
+ \end{enumerate}
+\end{definition}
+
+Note four characteristics of the model proposed.
+First, the incumbent politicians always embezzle some amount in equilibrium.
+Second, conditional on the benefits from holding office, to spend less than the optimal investment is harmful to the incumbent.
+In concrete terms, this means that politicians' first aim is to be elected.
+If the voter always dismisses the politician, then the politician will always say that the good costs $A$.
+Third, the voters always receive the public goods, regardless of the amount of money embezzled.
+The voter decides to punish the corrupt incumbent to discipline the incumbent's behavior, minimizing the rents extracted.
+Finally, this model has no ideological proximity, or affinity between the voter and any of the politicians: the paper aims to explore the incentives for corruption, not the trade-offs between ideology and corruption.
+Ideology is vital to understand why voters may not want to punish a corrupt politician, but this is not the main point of this paper, and adding this to the paper only blurs the logic of the argument.
+I now solve the model for the scenarios relevant to this paper.
+
+\subsection{One incumbent and one challenger}
+
+Applying backward induction, the voters retain the incumbent if the policy result was good and no corruption was exposed.
+From the challenger's perspective, as there is no cost of entry, she decides whether to invest or not her campaign resources in exposing the incumbent.
+She does so when the expected utility of exposing is higher than or equal the expected utility of not exposing, given her beliefs about the real value of $\eta$.
+Thus:
+
+\[
+B \int_{t_i \in T} \Prob (\bups = (0,1)\ | \ \eta, \varepsilon^*, \varphi)\mu^*(t_i|\varepsilon^*) d\mu - c \varphi(\psi, \varepsilon^*) \geq 0
+\]
+
+Rearranging and applying the fact that $ \Prob(\bups = (0,1) | \varepsilon^*, \varphi ( \psi, \varepsilon^*), \eta) = \varphi(\psi, \varepsilon^*) \lambda(\varepsilon^*-\eta) $ and $\mu^*(t_i | \varepsilon^*) = \mu(\eta) = \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta}$ yields to:
+
+\[
+B \varphi(\psi, \varepsilon^*) \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta - c \varphi(\psi, \varepsilon^*)
+\]
+
+Isolating $\varphi(\psi, \varepsilon^*)$, let $\lambda_\varepsilon = \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta$ and $Q(B, c) = \dfrac{c}{B}$.
+Sequential rationality implies three distinct decisions: first, the challenger exposes the corrupt incumbent for sure whenever $\lambda_\varepsilon > Q(B, c)$; second, the challenger never exposes the corrupt incumbent when $ \lambda_\varepsilon < Q(B, c)$; and finally, the challenger is indifferent between exposing or not the corrupt incumbent when $\lambda_\varepsilon = Q(B, c)$.
+Optimality suggests that incumbent politicians will calibrate their rent extraction in order to make challengers indifferent between investigating or not.\footnote{To avoid a trivial equilibrium we assume that $Q < \dfrac{\int_0^A \lambda(A - \eta)f(\eta) d\eta}{\int_0^Af(\eta)d\eta} = Q^*$.
+If $Q \geq Q^*$, then the only equilibrium is to play $A$ regardless of $\eta$, and there will be no exposures.}
+
+In this situation, there exists $\overline{\eta}$ such that:
+
+\[
+\lambda_A = \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta)f(\eta) d\eta}{\int_{\overline{\eta}}^Af(\eta)d\eta} = Q(B, c)
+\]
+
+This equation represents the upper limit in the incumbent politician's strategy when the randomly drawn optimal expenditure is too close to the maximum expenditure.
+In these situations is more profitable for them to play $A$.
+We say that the threshold for this case is $\overline{\eta}$.
+
+Now, let $\delta(\varepsilon)$ the probability function that characterizes the amount of negative campaign chosen by the challenger when $\varepsilon \in [ 0, \ \overline{\eta}]$.
+The optimal $\varepsilon$ solves the equation $\lambda_\varepsilon = Q(B, c)$, making the challenger indifferent between exposing or not the incumbent's corruption.
+As $\lambda(.)$ has an inverse function, the optimal strategy for the incumbent is:
+
+\begin{equation*}
+\varepsilon^*(\eta) \ = \ \eta + \lambda^{-1}\left(\dfrac{c}{B}\right)
+\end{equation*}
+
+Therefore, the optimal strategy for the incumbent politician is to add a kickback $\kappa$ to the cost for providing the public good.
+The incumbent devises the optimal kickback to make the challenger indifferent between expose or not the corrupt incumbent.
+The optimal kickback is increasing in the cost of the negative campaign and decreasing in the benefit of holding office.
+
+The incumbent, on the other hand, only plays this strategy when it is incentive compatible for her.
+To be an optimal response, it should be a $\arg \max$ for $U_I$.
+Taking the derivative of $U_I$, and setting it to zero gives us the following differential equation for $\delta(\varepsilon)$:
+
+\[
+\dfrac{d \delta}{d \varepsilon} + \delta(\varepsilon)\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)} = \frac{1}{B}\frac{u^{'}(\kappa)}{\lambda(\kappa)}
+\]
+
+Under the boundary condition $\delta(\kappa)=0$.
+The equation is a well defined first order differential equation that has a straightforward unique solution determined by the boundary condition.
+Solving for $\delta(\varepsilon)$, we have:
+
+\[
+\delta(\varepsilon) = \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right)
+\]
+
+Combining all these results together gives us the following lemma:
+
+\begin{lemma}
+ \label{lemma_m1}
+ A Perfect Bayesian Equilibrium for the game when there is one incumbent and one challenger is a pair of strategies and beliefs such that the optimal strategies are
+ \begin{enumerate}
+  \item For the incumbent 
+  \[
+   \varepsilon^{*}(\eta) \quad = \quad \twopd{\eta + \kappa}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
+  \]
+  \item For the challenger
+  \[
+   \varphi^*(\varepsilon) \quad = \quad \threepdo{0}{\varepsilon < \kappa}{\delta(\varepsilon)}{\kappa \leq \varepsilon \leq \overline{\eta}}{\delta(A)}
+  \]
+ \item And the voter replaces the incumbent if there is evidence of corruption.
+ \end{enumerate}
+ Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
+ \[
+ \kappa = \lambda^{-1}\left(\dfrac{c}{B}\right)
+ \]
+ The upper threshold, $\overline{\eta}$, satisfies 
+ \[
+ \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta) f(\eta) d\eta}{\int_{\overline{\eta}}^A f(\eta)d\eta} - \dfrac{c}{B} = 0
+ \]
+ \[
+ \delta(\varepsilon) \ = \ \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right) 
+ \]
+ And the beliefs are updated using Bayes rule whenever possible.
+\end{lemma}
+
+The remainder of the proof and the demonstration that this strategy is indeed an equilibrium is in the Appendix.
+Note three critical features on this equilibrium.
+First, an increase in the value of office ($B$) decreases the kickbacks extracted and the amount of negative campaign.
+Decreases kickbacks because it becomes more profitable to be reelected vis-a-vis extract rents, and lowers the amount of negative campaign because there are fewer opportunities to detect corrupt behavior.
+Second, increasing the costs of exposing corruption ($c$) increases the kickbacks and decreases the amount of exposure in equilibrium.
+Finally, increasing the gains from extracting rents (increasing $u'$) does not change the amount of extraction, but increases the amount of negative campaign, as a form to cope with the possibility of deviating from the equilibrium.
+These results are intuitive but demonstrate that the model follows a reasonable logic.
 

### 2021-08-27 article/article.Rmd
article revising 1

@@
 
-Corruption is one of the most prevalent and harmful XXXX of developing countries.
-Corruption lowers public goods provision \citep{banerjee201227, beekman2014corruption}, decreases foreign investments \citep{habib2002corruption}, stunts economic growth \citep{mauro1995corruption, grundler2019corruption}, and affects human capital investments \citep{ferraz2012corrupting}.
-Corruption also has detrimental effects on interpersonal trust \citep{you2018trust}, attitudes toward political parties \citep{winters2015political}, and fuels the distrust in the political system \citep{mignozzetti2019brazil}.
-The International Transparency estimates that corruption is responsible for $1.23 trillion US dollars every year, a sum that could lift 1.4 billion people out of the extreme poverty for six consecutive years \citep{fleming2019corruption}.
+Corruption is one of the most prevalent and harmful XXXX of developing countries. 2B2
 
@@
 In technical terms, the optimal amount of service provision is a random variable $\theta \in [0, R]$, that is drawn before the game starts, and it is informed to the incumbent after she wins the election.
-I assume that the optimal level of expenditure is drawn from a uniform probability distribution, with support in $[0, R]$.\footnote{In the online companion of this paper, I solve the model for a generic probability density function $f$.}
+I assume that the optimal level of expenditure is drawn from a uniform probability distribution, with support in $[0, R]$.\footnote{In the online companion of this paper, I solve the model for a generic probability density function $f$, and lay down the conditions for an equilibrium.}
 
-When deciding the expenditure, the incumbent can choose to invest more or less money then the optimal investment level.
-If the incumbent decide to invest less money, I assume that the goods are not provided.
-This simplification matches the reality in most cases, especially in developing economies, where restricting investments can cripple the entirety of the service provision.
-On the other hand, if the incumbent proposes an expenditure higher than the required investment, I assume that she pockets the difference between the proposed and the optimal expenditure.
-This has two implications: first, the public goods are always provided, satisfying the voters' needs; second, the incumbent has an excuse and a method to extract rents.
-Although corruption that ensures public goods provision seem counter-intuitive, the whole idea of kickbacks presumes that the expenditure is materialized.
-For instance, during the 2016 Brazilian World Cup, the stadiums constructed with public money were delivered, despite the fact that they costed 1.5 to 2.5 times more than comparable stadiums in less corrupt countries \citep{XXXX}.
+When deciding the public goods provision, the incumbent can choose to invest more or less money then the optimal investment level.
+If the incumbent decides to invest less money, I assume that the goods are not provided.
+This simplification matches the reality in most cases where restricting investments can cripple the entirety of the service provision.
+Conversely, when the incumbent proposes an expenditure higher than the required investment, I assume she pockets the difference between the proposed and the optimal expenditure.
+This assumption has two implications: first, the public goods are always provided, satisfying the voters' needs; second, the incumbent has an excuse and a method to extract rents.
+Although corruption that ensures public goods provision seem counter-intuitive, the whole principle of kickbacks presumes that the service provision is materialized.
+For instance, during the 2016 Brazilian World Cup, the stadiums constructed with public money were delivered for the world cup, despite the fact that they costed 1.5 to 2.5 times more than comparable stadiums in less corrupt countries \citep{XXXX}.
 
@@
 During the campaign, the incumbent faces a challenger in an election with two characteristics.
-First, I assume that voters have a incumbent-bias, so that voters prefer to reelect incumbents for sure when the public good were successfully provided.
-This XXXX.
-Second, challengers have only one campaign instrument at their disposal: to use negative campaign against the incumbent, expose their malfeasance (if present), and XXXX.
+First, voters have a incumbent-bias, so that they prefer to reelect incumbents for sure when the public goods were successfully provided.
+This correlates with incumbency advantage findings \citep{XXXX} as well as formal models of public service provision \citep{XXXX}.
+Second, I assume that challengers have only one campaign instrument at their disposal: to use negative campaign against the incumbent, expose their malfeasance if present, and receive the benefits from the denouncing.
+Although this seems unrealistic, having only one campaign strategy helps us focus on to what extent this strategy will be employed.
+Moreover, when the challenger decides to run negative campaign against an incumbent, she pays a value $c>0$.
+This value captures the direct costs of collecting information about corruption, and also XXXX.
 
-Once in office, they learn the optimal public goods provision, but they have discretion to decide   is responsible for investing in public goods provision for the voters. For instance, XXXX.
+Finally, the last stage of the game features the representative voter observing the information gathered by the challengers, and deciding whether to sanction the incumbent.
+Challengers have an incentive to run negative campaign against incumbents, regardless of whether the incumbent engaged in corruption.
+The voters, knowing the challenger's incentives to falsely accuse incumbents, evaluate the presented evidence.
+The strength of the evidence correlates with the difference between the optimal expenditure and the proposed expenditure.
+Voters and challengers do not know the optimal expenditure, but the greater the distance between the optimal and the enacted expenditures, the easier for challengers to convince voters that the incumbents are corrupt.
+This assumption has empirical support is most accounting literature, as the higher the kickbacks, the harder it is to hide it from authorities \citep{XXXX}.
 
-XXXX, and proposes a public goods provision XXXX.
-The incumbent has a fixed budget of $A$ units, to invest in service provision.
-The level of expenditure required to provide the public goods is a random variable $\eta \in [0, A]$, where  The randomness reflects the idea that changes in real-world conditions influence the amount needed for service provision.
-The incumbent knows the optimal investment level, making it her private information.
-If incumbents were honest, they would invest the needed amount to provide the services ($\eta$), but in this model, the incumbent invests the optimal amount plus some value, that she intends to pocket.
-The utility from pocketing money is described by $u(e_i-\eta)$, which $u$ is a strictly concave utility function, and $e_i$ represents the service expenditure by an incumbent $i$.\footnote{This assumption matches a frequent empirical regularity in the political environment, especially in new democracies: corruption tend to be over-investments, meaning that politicians add kickbacks and gifts to procurement contracts, receiving benefits them.
-Usually, what happens is not that voters fail to receive the services, it is that those services cost much more than their market value.
-For instance, \citet{Bandiera2009} estimated that the waste in procurement account for around 2\% of the Italian GDP.}
-
-After the service provision period, the electoral stage starts with the incumbent and the challenger campaigning.
-The challenger and the voters do not observe the optimal service investment level, but the challenger observes the amount of money invested by the incumbent politician ($e_i$, for all $i$).
-The challenger faces no entry costs and has the opportunity to use the negative campaign to convince the voters that the incumbent has embezzled public funds.\footnote{ This assumption is strong, as many papers demonstrated the effect of quality and service provision on the decision to challenge an incumbent \citep{Gordonetal2007, ashworth2008electoral, gordon2009voter, hall2015much}.
-In this paper, I endogenously fix the number of incumbents and challengers, as the critical point here is to study how the number of politicians influences incentives.
-In the Appendix, I extend the model to have a pool of possible challengers that have their entry costs a random variable.
-In the extension, the total pool of likely entrants becomes the critical variable, holding all qualitative findings here unchanged.
-Therefore, to fix the number of entrants is easier to understand, and represents a class of models that preserve the characteristics of our results, than we adopt this approach in the main text.
-Also, for the entry decision in economics, see \citet{Milgrom1982, Nti1989}.} If she decides to use all of her campaign resources to expose the corrupt politician, she pays a cost $c>0$.
-Her chances of success depend on the strength of the corruption evidence, plus other environmental facts, such as how much control over information incumbents have \citet{ferraz2011electoral, boas2011controlling}, credibility perceived by the voter \citep{polborn2006informative, AshworthShotts2011}, access to privileged information, and the challengers' competence to spread the information among voters.
-I assume that these factors are captured by a corruption detection technology, a function $\lambda(.)$ that is increasing on the amount embezzled by the incumbents.
-It increases with the amount embezzled, as the more money the incumbent pockets, the easier to convince voters that there is hard evidence of malfeasance undertaken by the incumbents.\footnote{There are two ways to interpret the hard evidence detection technology.
-First, it can be exposure of hard corruption evidence that was brought by a law enforcement agency, such as the FBI in the US or the General Comptroller Agency in Brazil.
-Second, it can be information uncovered during the campaign process by candidates or former allies that turned to the opposition.
-Either way, we consider that the process is noisy, but more substantial sums of money embezzled makes its detection easier.}
-
-Finally, as the voters' decisions are sequentially rational, upon observing hard corruption evidence, they punish the incumbent electing the challenger.
-Otherwise, the claim that the incumbent is corrupt is interpreted as a cheap talk by the voters.\footnote{Note that it is not ex-ante rational to always dismiss (never dismiss) the politicians, even when the voters know that politicians are corrupt.
-This because always dismissing (never dismissing) would generate equilibrium where politicians always spend the total amount of resources, regardless of how much is needed to provide the services.} Thus, the voter only punishes the incumbent when the challenger presents and convinces the voters that there is hard evidence of malfeasance.
-The game then ends, and payoffs are realized.
 The timeline for this model is as follows:
@@
  \item Nature draws the optimal investment level to provide the public services.
- \item The incumbent observes the optimal investment level and choose the expenditure.
- \item The election starts with the challenger choosing her campaign strategy.
+ \item The incumbent observes the optimal investment level and chooses the government investment in public goods.
+ \item After the public goods provision, the election starts with the challenger choosing her campaign strategy.
  \item Voters observe the campaign and choose whether to retain or dismiss the incumbent.
@@
 
-The strategic decisions in this game are the expenditure level chosen by the incumbent ($\varepsilon$), the fraction of time that the challenger invests in exposing the corrupt incumbent ($\varphi$), and the voter's decision to retain or dismiss the incumbent.
-Condensing the discussion above, we have the following expected utility functions.
-For the incumbents:
+To differentiate between strategies and actions, I assume that the incumbent's decision for the expenditure is a function $\varepsilon: [0,R] \rightarrow [0,R]$, i.
+e., the decision-making process receives the information about the optimal level of public goods provision, and returns the expenditure decision.
+For the challenger there is a similar reasoning, and the decision to investigate the incumbent is a function $\varphi: [0,R] \rightarrow [0,1]$, that receives the expenditure decision and returns a probability of running the negative campaign.
+Condensing the discussion above, the incumbent, upon observing the optimal public goods provision level $\theta \in [0,R]$, decides the expenditure $\varepsilon \in [0,R]$.
+The benefits from pocketing resources are captured by a function $u(.)$.
+In the main paper, I assume it is equal to the identity function but that in the appendix I solve the model for a generic concave function.
+The expected utility of the incumbent also adds the benefit from winning the election $B>0$ times the probability of this event, given the optimal and enacted expenditures and the decision to investigate $\varphi$.
 
 \[
-U_i (\varepsilon_i; \ \eta, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) \ = \ u(\varepsilon_i - \eta) + B \ \Prob (\upsilon_i = 1 \ | \ \psi, \dd) 
+U_I (\varepsilon; \theta, \varphi) \ = \ u(\varepsilon - \theta) + B \mathbb{P} (\text{re-election}; \varepsilon, \theta, \varphi) 
 \]
 
-Where $B$ is the reward for staying in office (assumed the same for every player) and $\Prob (\upsilon_i = 1 \ | \ \psi, \dd)$ is the probability of being retained, given $\psi$ and the exposure profile $\dd$.
-For a challenger $j$:
+The expected utility for the challenger involves a decision in terms of the probability to win the election and the costs of running a negative campaign.
+This benefit from holding office  $B>0$ is multiplied by the probability that the challenger replaces the incumbent.\footnote{I assume the material and non-material benefits from office the same for both the challenger and the incumbent.
+This simplifies the exposition, and makes it easier to think about these benefits as salaries or other types of pecuniary benefits.} The probability that the challenger wins the election depend on the decision to run a negative campaign, the enacted expenditure, and on her beliefs about the optimal expenditure, when she observes the enacted expenditure.
+The beliefs are captured by a probability rule $\mu(\theta|\varepsilon)$.
+The challenger also decides the investigation strategy $\varphi \in [0,R]$, and if she undertakes the strategy, then she pays a cost of $c>0$.
 
 \[
-U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}) \ = \ B \int_{0}^A \Prob (\upsilon_j = 1 \ | \ \eta, \bveps^{*}, \bvphi^{*})\mu(\eta|\bveps^{*}) d\mu(\eta) - c \sum_{i=1}^K \varphi_{ij}(\psi, \bveps^{*})
+U_C (\varphi; \varepsilon) \ = \ B \int_{0}^R \mathbb{P}(election|\varphi, \varepsilon, \theta) \mu(\theta|\varepsilon) d\mu(\theta) - c \varphi
 \]
 
-With $c > 0$ being the cost of performing one full corruption exposure.
-Notice that the total amount spent on exposing corrupt politicians will be the sum of the amounts spent on each exposure.
-The representative voter's expected utility is equal to:
+Finally, the voter's decisions are sequentially rational, in the sense that they are undertaken after the expenditure and investigations are undertaken.
+They cannot change the decisions ex-post, and this facilitates the decision rules for voters.
+Ex-ante, I assume that the best is to remove from office the incumbent whenever the challenger credibly shows evidence that the incumbent is corrupt.
+The chance that the challenger convinces the voter is a function $d(\varepsilon-\theta)$, and to simplify, I consider that this function is equal to $d(\varepsilon-\theta) = \dfrac{\varepsilon-\theta}{R}$.
+In the appendix, I model the decision for a generic functional form for $d(.)$.
 
-\[
-U_V (\psi, \dd, \bups) \ = \ \indf \{\psi=G \}r_G
-\]
-
-Where $\indf$ is the indicator function for $\psi=G$ and $r_G$ the value of the public good for the voter.
-Notice that no $\psi=B$ is observed on the equilibrium path, as under-spending is a dominated strategy.
-
-Any retention rule selected for the voters is sequentially rational because there is no uncertainty about the results when they cast their votes.
-I impose the retention rule for the voter to be to dismiss all incumbents when $\psi=B$ or replace incumbents that were successfully exposed by challengers when $\psi=G$.
-This rule is ex-post efficient as over-dismissal would make incumbents pocket all the money regardless of $\eta$.
-
-I solve this game for a \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}, and as this is a signaling game, I also use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}.\footnote{The restriction imposed by the universal divinity requires that the challengers, facing a deviation from the equilibrium path, put probability one on the type that is more likely to deviate.
-Moreover, as we have a continuum of types, we use the approach by \citet{Malaith1987}, which consists in finding the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.}
+I solve this game for a \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}, and as this is a signaling game, I also use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}.
+The restriction imposed by the universal divinity requires that the challenger, facing a deviation from the equilibrium path, assign a probability one on for the type that is more likely to deviate.
+Moreover, as I have a continuum of possible investment strategies, I use the approach by \citet{Malaith1987}, which consists in finding the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.
 
@@
  \label{def_eqn}
- A Perfect Bayesian Equilibrium for the game described, with $|I|=K$ and $|C|=L$, $K$ and $L$ in $\mathbb{N}$, type space $T=[0,A]$, consists in optimal strategies $\bveps^{*}$, $\bvphi^{*}$, $\bups^{*}$ and beliefs $\mu^*$, that satisfy
+ A Perfect Bayesian Equilibrium for the strategic interaction described consists in strategic choices of the expenditure $\varepsilon$ and the negative campaign $\varphi$ such that:
  \begin{enumerate}
-  \item $\forall t_i \in T$, $\varepsilon^{*}_i(t_i)$ maximizes $ U_i (\varepsilon_i; \ t_i, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) $ $\forall i \in \{1, \cdots, K\}$.
+  \item For an optimal expenditure level, $\theta \in [0,R]$, the proposed expenditure $\varepsilon$ maximizes $U_I (\varepsilon; \varphi, \theta)$.
   \item $\forall \bveps \in \left[0,A \right]^K $ and $\psi \in \{B, \ G \}$, $\bvphi^{*}_j(\bveps, \psi)$ maximizes $ U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}, \ \mu^*) $, $\forall j \in \{1, \cdots, L\}$
-  \item $\forall \psi \in \{B, \ G \}$ and $\dd \in \{0,1\}^L$, $\bups^{*}(\psi, \dd)$ maximizes $ U_V (\psi, \dd, \bups^*) $.
-  \item The beliefs are derived using Bayes rule whenever possible, and for all $\varepsilon_i$ that are off-the-equilibrium path, $\mu^*(t_i| \varepsilon_i)>0$ (in fact, 1) only if $\widehat{\varepsilon}_i \in \arg \min_{t_i} p(t_i, \widehat{\varepsilon}_i)$, where $ p(t_i, \widehat{\varepsilon}_i)$ is the profit from deviating from $\varepsilon_i$ to $\tilde{\varepsilon}_i$ for a type $t_i$.
+  \item The beliefs are derived using Bayes Rule, whenever possible.
+The universal divinity also requires that for all expenditure levels that are off-the-equilibrium path, $\mu(\theta| \varepsilon)>0$ (in fact, 1) only if $\widehat{\varepsilon} \in \arg \min_{\theta} p(\theta, \widehat{\varepsilon})$, where $ p(\theta, \widehat{\varepsilon})$ is the profit from deviating from the optimal $\varepsilon$ to a deviation expenditure $\tilde{\varepsilon}$, when the optimal expenditure level is $\theta$.
  \end{enumerate}
@@
 
-Note four characteristics of the model proposed.
-First, the incumbent politicians always embezzle some amount in equilibrium.
-Second, conditional on the benefits from holding office, to spend less than the optimal investment is harmful to the incumbent.
-In concrete terms, this means that politicians' first aim is to be elected.
-If the voter always dismisses the politician, then the politician will always say that the good costs $A$.
-Third, the voters always receive the public goods, regardless of the amount of money embezzled.
-The voter decides to punish the corrupt incumbent to discipline the incumbent's behavior, minimizing the rents extracted.
-Finally, this model has no ideological proximity, or affinity between the voter and any of the politicians: the paper aims to explore the incentives for corruption, not the trade-offs between ideology and corruption.
-Ideology is vital to understand why voters may not want to punish a corrupt politician, but this is not the main point of this paper, and adding this to the paper only blurs the logic of the argument.
-I now solve the model for the scenarios relevant to this paper.
+Note that this model has no ideological proximity, or affinity between the voter and any of the politician.
+This because the paper's objective is to explore the incentives for corruption, not the trade-offs between ideology and corruption.
 
-\subsection{One incumbent and one challenger}
+\subsection{The Solution for the One Incumbent - One Challenger Model}
 

### 2021-09-29 article/article.Rmd
changing 1x1 situation

--- 2021-08-24 article/article.Rmd
@@
 title:  |
-        | Electoral Systems, Competition, and Incentives for Corruption
+        | Electoral Competition and Incentives for Political Corruption
 author: 
@@
 date: \today
-thanks: "I thank Livio DiLonardo, Sandy Gordon, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Adam Przeworski, Howard Rosenthal, Renard Sexton, Denis Stukal, and Scott Tyson for their comments.
+thanks: "I thank Livio DiLonardo, Sandy Gordon, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, John Patty, Elizabeth Maggie Penn, Adam Przeworski, Howard Rosenthal, Miguel Rueda, Renard Sexton, Denis Stukal, and Scott Tyson for their comments.
 I also thank participants at APSA, MPSA, and SPSA.
 All materials required to replicate this study are available at <https://github.com/umbertomig/electoral-systems-corruption>."
-abstract: "What are the effects of electoral systems and competition on political corruption?
-In this paper, I propose a formal model of political corruption where incumbents decide how much kickbacks to add in the XXXX, and challengers may run anti-corruption campaigns against the incumbents.
-To understand how institutions and competition affect the results, I study two benchmarks: in the first, called the non-excludable anti-corruption campaign, successful exposure of an incumbent opens her seats to all other competitors.
+abstract: "What are the effects of electoral competition on political corruption?
+In this paper, I propose a formal model of political corruption where an incumbent decides how much kickbacks to add to public goods expenditure, and challengers may run anti-corruption campaigns against the incumbent.
+To understand how the number of competitors affect the results, I study two benchmarks: in the first, called the non-excludable anti-corruption campaign, successful exposure of an incumbent opens her seats to all other competitors.
 In the second benchmark, the excludable anti-corruption campaign, the politician successfully exposing the corruption signals competence, and voters tend to prefer her vis-a-vis the other challengers.
-When anti-corruption campaigns are non-excludable, an increase in the number of challengers or incumbents monotonically raises corruption.
+When anti-corruption campaigns are non-excludable, an increase in the number of challengers raises corruption.
 However, when anti-corruption campaigns are excludable, the number of challengers is endogenously limited.
 The excludability makes the free-riding in corruption exposure disappear.
-When I increase the number of incumbents, corruption rises less than in the non-excludable benchmark.
 These predictions hold empirically using quasi-experimental data from Brazilian and Italian municipalities.
-This study has implications for the design of electoral institutions and entry barriers in democratic elections."
+This study has implications for the design of electoral institutions."
 abstractspacing: double
-keywords: Political Corruption; District Magnitude; Single-member districts; Multi-member districts; Welfare; Brazil
+keywords: Political Corruption; Competition; Negative Campaign; Welfare; Brazil
 #jelcodes: HXXXX
@@
 
-Corruption is one of the most prevalent and harmful diseases of developing countries.
-Corruption lowers public goods provision \citep{banerjee201227, beekman2014corruption}, decreases foreign investments \citep{habib2002corruption}, stunt economic growth \citep{mauro1995corruption, grundler2019corruption}, and affects human capital investments \citep{ferraz2012corrupting}.
-Corruption also have detrimental effects on trust \citep{you2018trust}, attitudes toward political parties \citep{winters2015political}, and fuels the distrust in the political system \citep{mignozzetti2019brazil}.
-The International Transparency estimates that corruption is responsible for $1.23 trillion US dollars every year, a sum that could lift 1.4 billion people out of the extreme poverty for consecutive six years \citep{fleming2019corruption}.
+Political accountability requires that voters, upon XXXX, sanction XXXX.
+As the electoral process creates a XXXX, voters use elections to reward beneficial XXXX and to sanction XXXX.
+Different from markets, the electoral sanctioning is XXXX and XXXX [@banksXXXXsundaranEconometrica].
 
-One crucial distinction in corruption activity is the actor that is perpetrating corruption.
-While bureaucratic corruption may be more frequent, it is also easier to sanction and to punish.
-Political corruption, on the other hand, involves higher rents than bribes to services.
-They are usually associated with large government contracts and procurement \citep{broms2019political}, have a more disruptive effects on the trust in political institutions \citep{sole2018trust}, divert the bureaucracy toward rent seeking \citep{brierley2020unprincipled}.
-For instance, one of the major corruption scandals in the world, the Car Wash scandal in Brazil, involved more than 50 politicians, several high level bureaucrats, and about five billion US dollars in kickbacks \citep{watts2017operation}.
-Political corruption is intricate also because the electoral sanctioning often fails \citep{klavsnja2017uninformed, canete2020voting, janezic2020eliciting}.
-However, as elections are the primary mechanism to sanction corrupt politicians, are there electoral system features that could improve the sanctioning and lower corruption?
+However, when sanctioning political corruption, voters seem to have a more XXXX approach to XXXX.
+For instance, two cases in Latin America well illustrate this XXXX.
+In Argentina, XXXX.
+On the other hand, Jair Bolsonaro in Brazil XXXX.
+Albeit remarkable differences between the cases, in Bolsonaro successfully exploited the major corruption scandal uncovered in Brazilian history, and made its way to XXXX against the XXXX.
+In Argentina, Macri lost his reelection bid without going to runoff, because he could not credibly XXXX the uncover of XXXX that happened a few months earlier by the Argentinian justice.
+Therefore, what is the XXXX?
 
-In this paper, I investigate the interplay between the number of incumbents in a polity, the number of competitors challenging those incumbents, and the incentives incumbents have for engaging in corruption.
-I propose a model where incumbents know the optimal level of investment required for public goods provision, but challengers only see the amount that incumbents spend.
-Incumbents have privileged information because they are inside the government, and receive information from governmental agencies.
-When they propose an investment higher than the optimal amount, the public goods is provided, and they pocket the difference between the optimal amount and their proposed expenditure.
-Thus, in this paper, the difference between the optimal and the proposed investment is the definition of political corruption.
+In this paper, I propose a simple theoretical model to understand the electoral sanctioning of political corruption.
+In the model, I investigate one main feature celebrated as a signal of a healthy democracy: the existence and abundance of electoral challengers, running against a XXXX incumbent.
 
-Challengers have incomplete information about the required investment in public goods provision, but they may run a negative campaigning against incumbents.
-Challengers have a prior expectation regarding the optimal investments, and naturally, they know that the higher the level of investment proposed, the more the chances that incumbents are extracting rents.
-They decide to run a negative campaign that aims to gather and expose information supporting that a given incumbent is corrupt.
-To run a negative campaign is costly, both in terms of gathering information to prove that the incumbent is dishonest, and also in terms of XXXX.
-The extent through which the negative campaign is successful depends on the rents extracted by incumbents: While voters know that challengers may accuse an honest incumbent of corruption, the amount of evidence shown to voters can tilt the perception that a given incumbent is honest, triggering his or her dismissal.
+My model has XXXX distinctive characteristics.
+First, I model political corruption as the XXXX of kickbacks in a public goods provision XXXX.
+The provision of the public goods usually hides the corruption involved and distract voters.
+However, a public good that costs considerably more than its market price XXXX.
+Second, challengers are the main XXXX in exposing corrupt politicians.
+XXXX.
+Finally, exposing corruption has an XXXX.
+Challengers have the incentive to always claim that XXXX.
 
-To understand how electoral systems and competition affects corruption, I investigate how changes in the number of incumbents (district magnitude) and the number of challengers (competition) affect the equilibrium level of corruption.
-I show that increase district magnitude increases the equilibrium level of political corruption.
-This because more incumbents promote coordination failures in the challengers' negative campaigning.
-For example, in an electoral system with one incumbent, this incumbent is the sole target of negative campaigning.
-In a system with two incumbents, one incumbent may be targeted with all negative campaign while the other may remain un-targeted.
-These types of coordination shortcomings make the incumbents to propose higher expenditures, increasing corruption.
+I solve the model in three stages.
+First, I solve the model for one incumbent versus one challenger.
+In this case, exposing a corrupt politician has a direct effect on XXXX, as XXXX.
+Second, I solve the case of one incumbent versus many challengers assuming the *non-excludable benchmark*, where XXXX.
 
-The effects of competition are less clear, and depend on the how voters behave in face of a successful exposure of an incumbent.
-On the one hand, if voters transfer the political support from the corrupt incumbent to the challenger that ran the negative campaign, then political corruption decreases.
-This because the reward in denouncing a corrupt incumbent makes challengers more prone to run negative campaigns.
-With more negative campaigning in equilibrium, incumbents respond by proposing an expenditure closer to the optimal spending level.
-On the other hand, if voters, upon being convinced that the incumbent is corrupt, decide to randomly elect one challenger, then political corruption increases.
-This because randomly select the challenger that substitute the corrupt incumbent creates a free-riding incentive: every challenger prefers that other challengers pay the cost of negative campaign.
-The first mechanism we denote as XXXX while the second mechanism we denote as XXXX.
+I show that, compared with the one challenger case, the *non-excludable* benchmark generates more corruption while the *excludable* benchmark generates less corruption.
+When there is one challenger, all the negative campaign benefits directly the challenger.
+In this sense, the costs of running a negative campaign are mostly paid off when taking down a corrupt politician.
+However, when there are more challengers, exposing corruption aggregates a free-riding incentive.
+Whenever the person denouncing the corruption gains directly from it, then the XXXX, On the other hand, when XXXX.
+The intensity of the free-riding is crucial to determine whether XXXX is XXXX.
 
-This model innovates in three fronts.
-First, it provides a consistent and comparable definition of corruption.
-Despite the evidence that corruption is detrimental for XXXX and XXXX, corruption is poorly defined.
-Corruption XXXX.
-Moreover, corruption XXXX.
+XXXX.
 
-Second, our paper builds up on the previous literature on electoral systems and corruption by adding a role for the challengers. In most of the papers, XXXX. My paper innovates by XXXX.
+This model contributes to four strands in the literature.
+First, it contributes with the literature on the effect of electoral systems on political corruption.
+XXXX.
+This paper shows that political competition also plays an important role to understand political corruption.
+But different from @charronXXXX, competition have a non-linear effect, depending on XXXX: competition in countries with widespread corruption generates free-riding incentives, as challengers know that a successful exposure benefit all of them.
+In countries with low corruption, XXXX.
+XXXX can have a beneficial or harmful effect, depending on how widespread the corruption in the country is.
+XXXX.
 
-Third, my model abstracts away from other political concerns, focusing only on features of the electoral system, in a stylized model.
-Recent papers show that corruption correlates with ideology \citep{XXXX}, in-group behavior \citep{XXXX}, and XXXX.
-Despite the importance of these XXXX, removing these considerations is fundamental for understanding how electoral rules affect corruption.
-For example, by having ideology and district size in the same model, we would be uncertain whether which component (or even if the interaction between them) leads to corruption.
-Moreover, high polarization correlates with less punishment of corruption \citep{XXXX}, but it is unrealistic to prescribe that voters should depolarize as a way to lower corruption.
-The relation between polarization, XXXX, and XXXX are features of the political system that need to be studied in and on themselves.
-The strength of my model is to abstract away from XXXX, and considering a lean model of XXXX.
+Second, this paper contributes to the literature on retrospective voting. XXXX.
 
-Finally, XXXX
+Third, this paper contributes to a growing literature on the effects of political competitiveness on elections.
+XXXX.
+This paper aligns with XXXX, showing that competition can be harmful, especially in cases when XXXX.
 
-# District Magnitude, Competition, and Corruption
+Finally, this paper contributes to a growing literature on the effects of negative campaign.
+XXXX.
+Despite the nefarious effects, negative campaign by challengers, aimed at exposing a corruption, is crucial to hold politicians accountable.
+When the judicial prosecution fails, the best alternative to sanction corrupt politicians is to use the electoral system, and XXXX.
+
+# Elections and Political Corruption
+
+XXXX
+
+# A Model of Elections under XXXX
+\label{sec:theorymodel}
+
+Consider a strategic interaction between three players: an incumbent politician ($I$), a challenger politician ($C$), and a representative voter ($V$).
+
+The game starts in the *governing stage*, with a recently elected incumbent politician deciding the expenditure in public goods provision.
+Upon taking office, the incumbent learns the required expenditure to provide the public goods and services that voters need.
+For instance, the incumbent may learn that a school or hospital needs investments in infrastructure, and she decides how much to allocate for this.
+The required expenditure is only learned when the incumbent takes office, and it is her private information.
+I denote the required expenditure level $\theta \in [0, R]$, and the incumbent has a budget of $R > 0$ resources to invest in public goods.
+
+But the *enacted* expenditure in public goods provision is under the incumbent's discretion.
+This means that, despite knowing the required investment levels, incumbents are under no obligation to spend optimally, and may invest more or less than this required investment level.
+For simplicity, I assume two consequences for the differences between required and enacted investments.
+If the incumbent decides to invest less than the required amount, I assume the public goods are not provided.
+This simplification matches the reality in most cases where restricting investments can cripple the entirety of the service provision.
+On the other hand, when they invest more than the optimal amount, they can pocket the difference as rents.
+These assumptions together imply that incumbents will always provide the public goods.
+In fact, if they care about rents, they will always over-provide the goods, to pocket the differences between the required and the proposed expenditure.
+
+This provides an interesting micro-foundation for corruption: Political corruption here are kickbacks, and public goods are always provided by corrupt politicians.
+This matches most cases of corruption in procurement contracts, where the government provides the goods, at a higher-than-market prices.
+For instance, during the 2016 Brazilian World Cup, the stadiums constructed with public money were delivered for the world cup, despite the fact that they costed 1.5 to 2.5 times more than comparable stadiums in less corrupt settings \citep{XXXX}.
+
+After the governing stage, it starts the \textit{campaign stage}.
+During the campaign, the challenger learns the expenditure enacted by the incumbent $e$, and she knows that $e$ most likely higher than the required expenditure $\theta$.
+However, she knows that the required expenditure is a random variable, distributed uniformly between zero and $R$, and with that information, she form a belief about the optimal expenditure using Bayes' rule.
+
+The challenger then decides whether or not to run a negative campaign against the incumbent.
+As I assume that voters have an incumbent-bias,\footnote{Meaning that they prefer to reelect incumbents when the public goods were successfully provided.
+This correlates with incumbency advantage findings \citep{XXXX} as well as formal models of public service provision \citep{XXXX}.} so that negative campaign is the only instrument that makes voters to revise their bias toward an incumbent that successfully provided the public goods.
+Additionally, when the challenger decides to run negative campaign against an incumbent, she pays a value $c>0$.
+This value captures the direct and indirect costs of collecting information about corruption.
+Moreover, it also represents the potential opportunity costs of trying to convince the voters that the incumbent is corrupt.
+
+Finally, the \textit{voting stage} of the game features the representative voter observing the information presented by the challenger, and deciding whether to sanction or not the incumbent.
+Challengers have an incentive to run negative campaign against incumbents, regardless of whether the incumbent engaged in corruption.
+The representative voter, knowing the challenger's incentives to falsely accuse incumbents, evaluates the presented evidence of corruption.
+The strength of the evidence correlates with the difference between the required expenditure and the proposed expenditure.
+Voters and challengers do not know the require expenditure, but the greater the distance between the required and the enacted expenditures, the easier for challengers to convince voters that the incumbents are corrupt.
+This assumption has empirical support is most accounting literature, as the higher the kickbacks, the harder it is to hide it from authorities \citep{XXXX}.
+
+The timeline for this strategic interaction is as follows:
+
+\begin{enumerate}
+ \item Nature draws the required expenditure level to provide the public services.
+ \item The incumbent observes the required expenditure level and chooses the government's expenditure in public goods.
+ \item After the public goods provision, the election starts with the challenger deciding her campaign strategy.
+ \item The representative voter observes the campaign and the expenditure, and chooses whether to retain or dismiss the incumbent.
+If she dismisses the incumbent, she automatically selects the challenger.
+\end{enumerate}
+
+To differentiate between strategies and actions, I assume that the incumbent's decision for the expenditure is a function $\varepsilon: [0,R] \rightarrow [0,R]$, i.
+e., the decision-making process receives the information about the required expenditure level, and returns the expenditure decision.
+For the challenger there is a similar reasoning, and the decision to investigate the incumbent is a function $\varphi: [0,R] \rightarrow [0,1]$, that receives the expenditure decision and returns a probability of running the negative campaign.
+Condensing the discussion above, the incumbent, upon observing the optimal public goods provision level $\theta \in [0,R]$, decides the expenditure $\varepsilon \in [0,R]$.
+The benefits from pocketing resources are captured by a function $u(.)$.
+In the main paper, I assume it is equal to the identity function but that in the appendix I solve the model for a generic concave function.
+The expected utility of the incumbent also adds the benefit from winning the election $B>0$ times the probability of this event, given the optimal and enacted expenditures and the decision to investigate $\varphi$.
+
+\[
+U_I (\varepsilon; \theta, \varphi) \ = \ u(\varepsilon - \theta) + B \mathbb{P} (\text{re-election}; \varepsilon, \theta, \varphi) 
+\]
+
+The expected utility for the challenger involves a decision in terms of the probability to win the election and the costs of running a negative campaign.
+This benefit from holding office  $B>0$ is multiplied by the probability that the challenger replaces the incumbent.\footnote{I assume the material and non-material benefits from office the same for both the challenger and the incumbent.
+This simplifies the exposition, and makes it easier to think about these benefits as salaries or other types of pecuniary benefits.} The probability that the challenger wins the election depend on the decision to run a negative campaign, the enacted expenditure, and on her beliefs about the required expenditure, when she observes the enacted expenditure.
+The beliefs are captured by a probability rule $\mu(\theta|\varepsilon)$.
+The challenger also decides the anti-corruption campaign strategy $\varphi \in [0,1]$ and, if she pursues the investigation, she pays a cost of $c>0$.
+
+\[
+U_C (\varphi; \varepsilon) \ = \ B \int_{0}^\varepsilon \mathbb{P}(\text{win election}|\varphi, \varepsilon, \theta) \mu(\theta|\varepsilon) d\mu - c \varphi
+\]
+
+Finally, any voter's decision is sequentially rational, as it happens after the incumbent implements her expenditure strategy and the challenger runs the anti-corruption campaign.
+They cannot change the incumbent's or the challenger's decisions ex-post, and this makes it easier for me to set the decision rule of the voter.
+The voter's decision will be to remove the incumbent from office whenever the challenger shows credible evidence that the incumbent is corrupt.\footnote{In the appendix XXXX, I discuss why this decision rule may be optimal from the perspective of the voter.
+Intuitively, when compared with reelection decisions such as @ferejohnXXXX, that has a single threshold for dismissal, this decision rule partitions the voter's information set more finely.
+The partitioning reduces the amounts of kickbacks at a range for the random variable larger than when only the voter sanctions.} The chance that the challenger convinces the voter is a function $\lambda(\varepsilon-\theta)$, with $\lambda' > 0$ to capture the idea that more kickbacks represent a higher chance of detect corruption.\footnote{For the simulations, I use $\lambda(\varepsilon-\theta) = \dfrac{\varepsilon-\theta}{R}$.
+In the online appendix, I model the decision for a generic functional form for $\lambda(.)$.}
+
+I solve this game for a \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}, and as this is a signaling game, I also use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}.
+The restriction imposed by the universal divinity requires that the challenger, facing a deviation from the equilibrium path, assign a probability one on for the type that is more likely to deviate.
+Moreover, as I have a continuum of possible expenditure strategies, I use the approach by \citet{Malaith1987}, which consists in finding the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.
+
+\begin{definition}
+\label{def_eqn}
+A Perfect Bayesian Equilibrium for the strategic interaction described consists in strategic choices of the expenditure $\varepsilon$ and the probability of running negative campaign $\varphi$ such that:
+ \begin{enumerate}
+  \item For a given required expenditure level, $\theta \in [0,R]$, the proposed expenditure $\varepsilon$ maximizes the incumbent's expected utility $U_I (\varepsilon; \varphi^*(\varepsilon), \theta)$.
+  \item The challenger observes the incumbent's equilibrium expenditure level $\varepsilon^*$, and decides her negative campaign strategy $\varphi$ to maximize the expected utility $ U_C (\varphi; \varepsilon^*, \mu(\theta|\varepsilon^*))$, given her beliefs $\mu(\theta|\varepsilon^*)$ about the required expenditure level $\theta$.
+  \item The voter observes $\varepsilon^*$ and the realization of $\varphi^*$ (which is either zero or one), plus the result of the anti-corruption campaign $\lambda(.) \in \{0,1\}$.
+She dismisses the incumbent if the anti-corruption campaign reveals corruption, and retain otherwise.
+  \item The beliefs are derived using Bayes' Rule, whenever possible.
+The *universal divinity* also requires that for all expenditure levels that are off-the-equilibrium path, the challenger beliefs $\mu(\theta| \varepsilon)>0$ (in fact, 1) only if the deviant type $\widehat{\varepsilon}$ is in $\widehat{\varepsilon} \in \arg \min_{\theta} p(\theta, \widehat{\varepsilon})$, where $ p(\theta, \widehat{\varepsilon})$ is the profit from deviating from the equilibrium expenditure $\varepsilon$ to a deviation expenditure $\widehat{\varepsilon}$, when the required expenditure level is $\theta$.
+ \end{enumerate}
+\end{definition}
+
+Note that this model has no ideological proximity, or affinity between the voter and any of the politicians.
+This because the paper's objective is to explore the incentives for corruption, not the trade-offs between ideology and corruption.\footnote{For papers exploring these trade-offs, see XXXX.} In the appendix, we model a situation where there is a positive valence shock towards one of the candidates, that is known before the election.
+My findings, qualitatively, remain the same, with the caveat that depending on the direction of the valence shock, the incumbent extracts even more rents in equilibrium.
+
+The benchmark for the model is the one incumbent x one challenger setting.
+By comparing this situation with the one incumbent x multiple challengers, I show the impact of the competitiveness on the equilibrium rents.
+Moreover, using Monotone Comparative Statics on the equilibrium, I can show the conditions under which the rent extraction decreases as the number of challenger increases.
+This threshold is characterized by an XXXX of excludability $\eta$ that determines XXXX.
+
+\subsection{One Incumbent x One Challenger}
+
+Applying backward induction, the voters retain the incumbent if the incumbent provided the public goods and no corruption was found.
+From the challenger's perspective, as she faces no entry costs, she decides whether to run an anti-corruption campaign.
+She does so when the expected utility of run a negative campaign is higher than or equal the expected utility of not running a negative campaign, given her beliefs about the required level of public goods investment $\theta$.
+The expected utility of running a negative campaign is equal to the benefit from office $B$ times the probability of the anti-corruption campaign be successful.
+This probability depends on the beliefs about the true value of the required public goods investment, derived by Bayes' rule $\varepsilon$, $\mu(\theta|\varepsilon) = \dfrac{f(\theta)}{\int_0^\varepsilon f(\theta)d\theta}$, and the chance that the anti-corruption campaign works $\lambda(\varepsilon - \theta)$.
+All this minus the cost $c>0$ of running an anti-corruption campaign.
+When the anti-corruption campaign strategy is $\varphi(\varepsilon)$, the expected benefit is equal to:
+
+\[
+\varphi(\varepsilon)\left[B \int_0^\varepsilon \lambda(\varepsilon - \theta)\dfrac{f(\theta)}{\int_0^\varepsilon f(\theta)d\theta}d\theta - c \right] \geq 0
+\]
+
+Running a negative campaign is a risky bet: it costs $c$ for sure, but the benefits are uncertain.
+The incumbent calibrates her rent extraction to make the challenger's cost-benefit equation $B \int_0^\varepsilon\left( \lambda(\varepsilon-\theta)\dfrac{f(\theta)}{\int_0^\varepsilon f(\theta)d\theta}\right)d\theta - c$ never always positive or always negative.
+If the challenger's cost-benefit equation is always positive, the incumbent is extracting too much rents.
+In this case, it is beneficial for challengers to run a negative campaign for sure ($\varphi(\varepsilon) = 1$).
+If the challenger's cost-benefit equation is always negative, on the other hand, the incumbents are extracting to little rents.
+In this case, the challenger should never run a negative campaign ($\varphi(\varepsilon) = 0$).
+In the always positive case, the incumbent can do better by extracting *fewer* rents.
+In the always negative case, the incumbent can do better by extracting *more* rents.
+If we consider that these two forces are at play simultaneously, they converge to a point where the challenger's cost-benefit to run an anti-corruption campaign is equal to zero.
+Zeroing the cost-benefit decision makes the challenger indifferent between running or not running an anti-corruption campaign.
+However, it could be the case that either the office benefits are too small, or the costs are too high, that even when incumbents extract all the rents possible, no anti-corruption campaign happens in equilibrium.
+To rule out this possibility, I assume the following:
+
+\begin{assumption}
+
+To avoid a trivial equilibrium where there is no anti-corruption campaign in equilibrium, I assume that the benefits from office $B$ and the costs to run a negative campaign $c$ are such that:
+
+\[
+\dfrac{c}{B} < \int_0^R \lambda(R - \theta)f(\theta) d\theta = Q^*
+\]
+
+I.e., the costs are low enough and the benefits from office are high enough to avoid a trivial equilibrium with no anti-corruption campaign.
+
+\end{assumption}
+
+By solving for the amount of rents that makes the challenger indifferent between run or not an anti-corruption campaign, I find the incumbents rent extraction strategy.
+
+\[
+\varepsilon^*(\theta) \ = \ \theta + \lambda^{-1}\left(\dfrac{c}{B}\right)
+\]
+
+The derivation, with all the details, is in the appendix.
+Note that strategic expenditure is equal to the required expenditure plus kickbacks.
+A simple inspection shows that the proposed expenditure is increasing in the cost to run the anti-corruption campaign $c$, decreasing in the office benefits $B$.
+Moreover, the proposed expenditure is linear on the amount of kickbacks $\lambda^{-1}\left(\dfrac{c}{B}\right)$: the proposed expenditure is equal to the required expenditure $\theta$ plus the amount of kickbacks $\lambda^{-1}\left(\dfrac{c}{B}\right)$.
+Note also that it could be the case that the required expenditure is high, making the strategic expenditure to be higher than the budget for some levels of $\theta$.
+In this case, define $\overline{\theta} = R - \lambda^{-1}\left(\dfrac{c}{B}\right)$ such that when the required expenditure surpasses this threshold, then the expenditure proposed by the incumbent equals the maximal expenditure, $\varepsilon^*(\theta) = R$.
+
+By solving for the indifference in the challenger's expected utility, I find the expenditure strategy for the incumbent.
+This is how a perfect Bayesian equilibrium works: by solving the game backwards, the decision of one player is usually derived by maximizing the utility of another player.
+To find the challenger's anti-corruption investigation strategy, I need to show that the incumbent's expenditure strategy  maximizes her expected utility.
+Proceeding backwards, the incumbent's expected utility is equal to the utility accrued from rents $u(\varepsilon-\theta)$ plus the benefits from holding office times the chance of win the election.
+The incumbent wins the election when there is no anti-corruption campaign ($1-\varphi(\varepsilon)$) or when the anti-corruption campaign fails ($\varphi(\varepsilon)(1-\lambda(\varepsilon-\theta))$).
+
+\[
+U_I(\varepsilon; \theta, \varphi(\varepsilon)) = u(\varepsilon - \theta) + B\left( 1-\varphi(\varepsilon) + \varphi(\varepsilon)(1-\lambda(\varepsilon - \theta)) \right)
+\]
+
+To maximize this equation, we take the derivative in $\varepsilon$ and equate the result to zero. This gives us the following differential equation:
+
+\[
+\dfrac{d \varphi}{d \varepsilon} + \varphi(\varepsilon)\frac{B\lambda'\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)}{c} = \frac{u'\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)}{c}
+\]
+
+The solution of the above equation characterizes the anti-corruption campaign decision by the challenger.
+Note that the equation has an unique solution when the boundary condition is well characterized.
+The boundary condition here states that when the challenger proposes $\varepsilon^* = \lambda^{-1}\left(\dfrac{c}{B}\right)$, this is the minimum amount of kickback possible, and it means that $\theta = 0$.
+In this situation, $\varphi\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)=0$.
+I solve this equation for $\varphi(\varepsilon)$ in details in the online appendix.
+The result is:
+
+\[
+\varphi(\varepsilon) = \dfrac{u^{'}\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)}{B\lambda^{'}\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)}\left(1 - e^{\frac{B}{c}\lambda^{'}\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)\left(\lambda^{-1}\left(\dfrac{c}{B}\right)-\varepsilon\right)}\right)
+\]
+
+A simple derivative check shows that when $\varepsilon$ increases, the chance of running the anti-corruption campaign increases; when the costs $c$ increase, the chance of running an anti-corruption campaign decreases; and when the benefits from office increase, the chances for running an anti-corruption campaign increases.
+
+This anti-corruption campaign strategy works well for all incumbent's expenditures between $\lambda^{-1}\left(\dfrac{c}{B}\right)$ and $\overline{\theta}$.
+However, what if the incumbent expenditure is between $0$ and $\lambda^{-1}\left(\dfrac{c}{B}\right)$ or between $\overline{\theta}$ and $R$?
+These are *out-of-path-of-play* expenditures, and under the *universal divinity* equilibrium, we should best-respond based on the types that are more likely to deviate.
+Any expenditure between $0$ and $\lambda^{-1}\left(\dfrac{c}{B}\right)$ should be met with $\varphi(\varepsilon) = 0$, as the challenger's cost-benefit to run the anti-corruption campaign is negative.
+The interesting case is when the incumbent proposes an expenditure between $\overline{\theta}$ and $R$.
+In this case, the required expenditure $\theta$ is surely between $0$ and $\overline{\theta}$.
+Otherwise, the incumbent would have selected $R$.
+This signals that the incumbent is trying to get more rents than the equilibrium prescribes, and this makes the cost-benefit for the challenger positive.
+The challenger's best response in this case is to set $\varphi(\varepsilon) = 1$.
+
+Combining all these results together gives us the following lemma, that characterizes the equilibrium for the one incumbent versus one challenger case.
+
+\begin{lemma}
+ \label{lemma_m1}
+A Perfect Bayesian Equilibrium for the game when there is one incumbent and one challenger is a group of strategies and beliefs such that:
+ \begin{enumerate}
+  \item For the incumbent, upon observing the required expenditure $\theta$, she proposes the expenditure level:
+  \[
+   \varepsilon^{*}(\theta) \quad = \quad \twopd{\theta + \lambda^{-1}\left(\dfrac{c}{B}\right)}{0 \leq \theta \leq \overline{\theta}}{A}{\theta > \overline{\theta}}
+  \]
+  \item For the challenger, upon observing the incumbent's investment strategy $\varepsilon$, she runs an anti-corruption campaign with the probability:
+  \[
+\varphi^*(\varepsilon) =
+\begin{cases}
+0 & \text{if $\varepsilon < \lambda^{-1}\left(\dfrac{c}{B}\right)$} \\
+\dfrac{u^{'}\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)}{B\lambda^{'}\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)}\left(1 - e^{\frac{B}{c}\lambda^{'}\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)\left(\lambda^{-1}\left(\dfrac{c}{B}\right)-\varepsilon\right)}\right) & \text{if $\lambda^{-1}\left(\dfrac{c}{B}\right) \leq \varepsilon \leq \overline{\theta}$} \\
+1 & \text{if $\overline{\theta} < \varepsilon < A$} \\
+\dfrac{u^{'}\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)}{B\lambda^{'}\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)}\left(1 - e^{\frac{B}{c}\lambda^{'}\left(\lambda^{-1}\left(\dfrac{c}{B}\right)\right)\left(\lambda^{-1}\left(\dfrac{c}{B}\right)-A\right)}\right) & \text{if $\varepsilon = A$}
+\end{cases}
+\]
+ \item For the voter, upon observing the anti-corruption investigation and the proposed expenditure by the incumbent, she replaces the incumbent if there is evidence of corruption.
+ \end{enumerate}
+And the beliefs are updated using Bayes' Rule, whenever possible.
+\end{lemma}
+
+The remainder of the proof and the demonstration that this strategy is indeed an equilibrium is in the online appendix.
+Note three critical features on this equilibrium: First, an increase in the value of office ($B$) decreases the kickbacks extracted and the chance that the challenger runs an anti-corruption campaign.
+Decreases kickbacks because it becomes more profitable to be reelected vis-a-vis extract rents, and lowers the chance of an anti-corruption campaign because lower rent extraction it makes it harder to detect the corrupt behavior.
+Second, increasing the costs of running an anti-corruption campaign ($c$), increases the kickbacks and decreases the chance of running an anti-corruption campaign.
+The This because amount of exposure in equilibrium.
+Finally, increasing the gains from extracting rents (increasing $u'$) does not change the amount of extraction, but increases the chance that the challenger runs an anti-corruption campaign, as rents became more valuable for the incumbents.
+These results are intuitive, but they reinforce that the model is grounded in reasonable logic.
+
+\subsection{One Incumbent x Many Challengers}
+
+Consider a change in the previous setup whereby we add multiple challengers running against the incumbent.
+Starting with the voters, suppose that she learns something about the challenger that brought the corrupt incumbent down with probability $\eta \in (0,1)$.
+This is the case that, for example, the challenger that successfully ran the anti-corruption campaign receives a large quantity of media exposure, which helps her election bid, making the voter to prefer her vis-a-vis the other challengers.
+On the other extreme, there is a chance of $1-\eta$ that the voter selects one of the challengers randomly regardless of her running or not an anti-corruption campaign.
+In this case, each challenger has a chance of $1/L$ to get elected.
+I label $\eta$ the degree of excludability in the anti-corruption campaign, i.e., the extent through which the voter uses a successful anti-corruption campaign to reward the challenger running it.
+
+The degree of excludability in the anti-corruption campaign is related to how widespread corruption is.
+In countries like Brazil, \citet{PAVAOXXXX} show that the systemic corruption makes it almost impossible for voters to use corruption cues to reward or punish politicians.
+Running a campaign on corruption would pose significant costs and other challengers would free-ride on a successful anti-corruption campaign.
+However, in countries where corruption is low, a successful exposure of a corrupt politician carries a non-trivial premium for the successful challenger.
+This premium can incentivize challengers to expose corruption even more, and this could make rents plummet.
+In the first case, $\eta$ is low, in the second case, $\eta$ is high.
+
+Challengers observe the expenditure in public goods provision proposed by the incumbent $\varepsilon$, and have to simultaneously decide on the chance to run an anti-corruption campaign.
+Let the challengers be indexed in $i \in \{1, 2, \cdots, L\}$.
+A given challenger $i$ decides to run an anti-corruption campaign that costs $c$ compute the time to invest in negative campaign $\varphi_i$.
+As challengers have the same utility function, I solve for the symmetric equilibrium, with all challengers implementing the same anti-corruption campaign strategy $\varphi_i = \varphi$.
+If the challengers use the $\varphi$ strategy to their anti-corruption campaigns, the chance of $k$ challengers run an anti-corruption campaign, among $L-1$ challengers, follows the Binomial distribution, with $p = \varphi$ and $n = L-1$:
+
+\[
+{L-1 \choose k} \varphi^k (1-\varphi)^{L-1-k}
+\]
+
+For any given number $k$ of challengers running a negative campaign, the chance that the campaign is successful is $k\lambda(\varepsilon - \theta)$.
+For any given challenger, the chance that she decides to do nothing and is still elected is equal to $\dfrac{1-\eta}{L}$.
+The chance that she does something and is elected is equal to The decision for a given XXXX is then equal to probability XXXX.
+
+\[
+f(\varphi, x) = \sum_{k=0}^{L-1} {L-1 \choose k} \varphi^k (1-\varphi)^{L-1-k} \cdot (1 - (1-\lambda_\varepsilon)^{k+x})
+\]
+
+So when $i$ decides to commit all her resources in a negative campaign, we let $x=1$ in $f$. This strategy allows us to compute the expected utility for the challenger $i$ as:
+
+\[
+\frac{B}{L}\int_0^A f(\varphi, 0) \mu(\eta|\varepsilon) d\mu + \varphi_i  \left[\frac{B}{L} \int_0^A \left( f(\varphi, 1)-f(\varphi, 0) \right) \mu(\eta|\varepsilon) d\mu - c \right]
+\]
+
+Sequential rationality requires that $\varphi_i > 0$ when this quantity is greater than zero, and zero otherwise.
+After some algebra, we can rewrite the critical term in the decision process as an equation $G$:
+
+\[
+G(\lambda, \varphi; L) = (1-\varphi\lambda (\varepsilon-\theta))^{L-1}\lambda(\varepsilon-\theta) - \dfrac{c}{B} L
+\]
+
+Where $Q$ is defined as in the previous section: $Q(B,c) = \dfrac{c}{B}$.
+This equation yields to the optimal $\varepsilon$.
+The problem is that we will have, for each value of $\varepsilon$, a corresponding optimal value of $\varphi$, and vice-versa.
+As the incumbent plays first, she can choose the max-min value for $\lambda$, which is the maximum value for $\varepsilon$ that still delivers the lowest $\varphi$ possible.
+For a numerical example, if we assume $Q=0.15$ and $L$ ranging from $1$ to $5$, we can have a contour for the possible values for $\lambda$ in Figure \ref{fig_m2_1}.
+
+<!-- \begin{figure}[htb!] -->
+<!--  \centering  -->
+<!--  \includegraphics{figm21.pdf} -->
+<!--  \caption{Contour plot for $G=0$ when $Q=0.15$ and $L$ ranges from $1$ to $5$} -->
+<!--  \label{fig_m2_1} -->
+<!-- \end{figure} -->
+
+Making $G=0$ yields to the following optimal incumbent expenditure strategy:
+
+\[
+\varepsilon^*(\eta) = \eta + \lambda^{-1}\left( Q(B, c)\cdot L \right) = \eta + \kappa(L)
+\]
+
+Again, the actual value required to provide the service plus a kickback comprises the incumbent strategy.
+The kickback has the same characteristics expressed in the case with one challenger, except now it is augmented linearly by the number of challengers contesting the seat.
+In order to this expenditure profile be incentive compatible it has to satisfy the following differential equation in $\delta(\varepsilon)$:
+
+\[
+\delta^{'}(\varepsilon)-\delta(\varepsilon)\dfrac{\lambda^{'}(\kappa(L))}{\lambda(\kappa(L))} \ = \ \dfrac{u^{'}(\kappa(L))}{BQ(B, c)L^2}
+\]
+
+With the boundary condition $\delta(\kappa(L))=0$, we have the following optimal exposure strategy:
+\[
+\delta(\varepsilon) \ = \ \dfrac{u^{'}(\kappa(L))}{BQ(B, c)L^2} \left( 1- e^{\frac{\lambda^{'}(\kappa(L))}{\lambda(\kappa(L))}(\kappa(L)-\varepsilon)}\right)
+\]
+
+Collecting all the results leads us to the following Lemma.
+
+\begin{lemma}
+ \label{lemma_m2}
+ A Perfect Bayesian Equilibrium for the game when there is one incumbent and $L$ challengers is a pair of strategies and beliefs such that
+ \begin{enumerate}
+  \item For the incumbent
+  \[
+  \varepsilon^{*}(\eta) \quad = \quad \twopd{\eta + \kappa (L)}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
+  \]
+  \item For each of the challengers
+  \[
+  \varphi^*(\varepsilon) \quad = \quad \threepdo{0}{\varepsilon < \kappa(L)}{\delta(\varepsilon)}{\varepsilon \in [\underline{\eta}, \ \overline{\eta}]}{\delta(A)}
+  \]
+  \item And the voter dismiss the incumbent if there is evidence of corruption, electing one of the $L$ challengers with probability $1/L$.
+ \end{enumerate}
+ Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
+ \[
+ \kappa(L) = \lambda^{-1}\left(L\dfrac{c}{B}\right)
+ \]
+ And the $\delta(.)$ defined as in the Appendix.
+\end{lemma}
+
+The proof with the step-by-step derivations is in the Appendix.
+Note here that all the comparative statics with relation to the benefit from holding office, the costs of exposing corrupt politicians, and the utility of rent extractions remain unchanged.
+The fundamental differences here are the effect of the number of challengers: it increases the kickbacks while decreasing the incentives for investigating the corrupt incumbent.
+The reason is intuitive: the more challenger added, the more the collective action problem faced by the challengers.
+For every individual challenger, it is better to let someone else pay the cost of a negative campaign but if all challengers reason similarly no exposures are performed in equilibrium.
+Thus, adding challengers increase the incentives for corruption.
 
